### 2019-04-03 paperdraft.tex
Add files via upload

\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
%                              according to the author-year natbib style

%
%\documentclass{aa}  
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bmi}[1]{\begin{minipage}{#1 cm}}
\newcommand{\emi}{\end{minipage}}
\renewcommand{\[}{\begin{equation}}
\renewcommand{\]}{\end{equation}}

\renewcommand{\rm}{\mathrm}
\def\inv{^{-1}}
\def\({\left(}
\def\r){\right)}
\def\b#1{\bm{#1}}
\def\Dd{D_{\text{d}}}
\def\Dds{D_{\text{ds}}}
\def\Ds{D_{\text{s}}}
\def\la{\left<}
\def\ra{\right>}
\def\gammao{\gamma^{\text{obs}}}
\def\gammaoh{\hat{\gamma}^{\text{obs}}}
\def\epsilonsij{\epsilon_{a_i}\epsilon_{b_j}^*}
\def\epsilonsii{\epsilon_{a_i}\epsilon_{b_i}^*}
\def\deltafuncij{\Delta(\b\theta_{a_i}-\b\theta_{b_j})}
\def\d{\rm{d}}

%\newcommand{\todo}{\emph}

\usepackage{bm}
\usepackage{verbatim}
%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%
\usepackage{todonotes}

\begin{document}

   \title{The Effects of Varying Depth in Cosmic Shear Surveys}

%   \subtitle{}

   \author{S. Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
          \and Peter Schneider\inst{1} 
          \and Hendrik Hildebrandt\inst{2,1}
          \and Catherine Heymans\inst{3} 
          \and Marika Asgari\inst{3}
          \todo{order of authors?, KiDS-Authors?}
          }
   \institute{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany 
\and 
Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany \and
Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de}
             }

   \date{Received XXX; accepted XXX}

  \abstract
% context (optional)
   {Cosmic shear proves to be a powerful tool to study the properties of the local Universe. The discrepancy in the parameter $S_8$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases. 
% aims
   Especially ground-based surveys are subject to a variation in depth. We want to understand and quantify the resulting effects. In particular, we check if they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
% methods
   We construct a semi-analytic model to estimate the impact on the shear correlation function and analyze the implications for cosmological parameters. Furthermore we construct COSEBIs of the correlation functions to quantify the occuring B-Modes.
% results
   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$. However, the parameter $S_8$ is robust against this modification. We also report the occurrence of B-Modes, although not to a significant degree.
% conclusions (optional)
   We conclude that the effects of varying optical depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}

   \keywords{gravitational lensing --
                weak lensing --
                cosmic shear
               }

   \maketitle

%
%-------------------------------------------------------------------

\section{Introduction}
The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the $\Lambda$CDM Model and determine its parameters. Contrary to the analysis of the Cosmic Microwave Background \citep{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology. Current Cosmic Shear surveys are especially sensitive to the paramter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, 
%\citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data,
\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2017MNRAS.465.1454H} report $S_8 = 0.745\pm 0.038$ from KiDS data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$. Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data. This discrepancy could be a statistical coincidence, a sign of new physics or the manifestation of an unknown systematic effect. \todo{Citations.. \citet{2017MNRAS.464.1676A} has a few...}

To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citet{2002ApJ...568...20C,2002A&A...389..729S}. To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics. As \citet{2017MNRAS.465.1454H} report the significant detection of B-modes, it is well motivated to check for possible systematics that are yet unaccounted for. Note that the non-existence of B-modes does not imply that the sample is free of remaining systematics.

One systematic effect is the variation of depth in a survey. While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions, that are found in ground-based surveys. To first order, this variation can be modelled by a step-like depth function that varies from pointing to pointing. In this work we assume the specifications of the Kilo-Degree Survey, namely a collection of $1\,\text{deg}^2$ square fields. Furthermore we neglect boundary effects.

In Section \ref{sec:modelling_single_lens} we will introduce a simple toy model to understand this effect and analyze the impact on the power spectrum. In Section \ref{sec:xipm} we will estimate the effect on the shear correlation functions $\xi_\pm$ using two different models. We will present our results in Section \ref{sec:results}. In Section \ref{sec:discussion} we will discuss our results and comment on the impacts of our used simplifications. We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.

\section{Modelling the Power Spectrum}
\label{sec:modelling_single_lens}
For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer. If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm ds}/D_{\rm s}$. 
% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
%\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
%\]

%Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate. Assuming that the optical depth, and thus the source redshift populations, vary between pointing, an observer will measure a shear-signal that is modified by a depth-function $W(\bm{\theta}) = 1-w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. The reconstruction of the observed convergence $\kappa^{\rm obs}$ will thus not yield the original convergence. In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part. This allows us to separate our received signal into E- and B-modes following \[
%	\kappa = \kappa^E+i\kappa^B\, ,
%\]
%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
%2002A&A...389..729S SRC

\subsection{Effects on the Power Spectrum}
Assuming that the depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a locally constant depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
In accordance to the definition of the shear power spectrum \begin{equation}
(2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) = \la \hat{\gamma}(\b\ell)\hat{\gamma}(\b\ell')\ra \, ,
\end{equation}
we define the observed power spectrum via \begin{equation}
P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \, .
\end{equation}
Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as 
\begin{equation}
w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
0 \qquad \text{else}
\end{cases},
\label{eq:defweightf}
\end{equation}
where $L$ is the length of one pointing.
Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
\begin{equation}
P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)P(\b k)\, ,
\end{equation}
where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function.
The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with the fourier transfrom of a box-function, scaling with the variance of the geometric lensing efficiency $\la \frac{D_{\rm ds}}{D_{s}}\ra$. In particular, the power spectrum is not isotropic anymore. Following \citet{2002A&A...389..729S}, it would be interesting to extract E- and B-mode information out of this power spectrum, however \citet{2010A&A...520A.116S} present a more sophisticated decomposition of E- and B-modes, that can also be applied to real data using the shear correlation function, so instead we want to focus our efforts on these parts.
\section{Modelling the shear correlation function}
\label{sec:xipm}
A convenient way to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
\xi_\pm = \la \gamma_{\rm t}\gamma_{\rm t}\ra \pm \la \gamma_\times\gamma_\times\ra \, .
\]
They are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear-measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions. Cosmologically, given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation function from the underlyting matter power spectrum $P_\delta$ via \todo{Citation!}\begin{align}
\label{eq:xipm-pkappa}
\xi_\pm[\theta,p_i,p_j] =& \int_0^\infty \frac{{\rm d}l\,l}{2\pi}J_{0,4}(l\theta)P(l,p_i,p_j)\, , \\
\label{eq:pkappa-pdelta/lenseff}
P(l,p_i,p_j) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_h} {\rm d}\chi\frac{g(\chi,p_i)g(\chi,p_j)}{a^2(\chi)}P_\delta\left(\frac{l}{f_K(\chi)},\chi\right)\, , \\
\label{eq:lenseff}
g(\chi,p_i) =& \int_\chi^{\chi_H} {\rm d}\chi'\, p_i(\chi') \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
\end{align}
Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions.
\subsection{Using an analytic Model}
For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal. Following \citet{2006APh....26...91V}, we estimate
\[
\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
\]
\todo{Maybe implement redshift-dependent index?}
Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.

%For a pair of galaxies that we use to measure the correlation function, it is crucial to determine whether those two galaxies lie within the same pointing. We want to define a function $E(\theta)$ that determines

Let $N(\b \theta)$ be the number-density per tile and $W(\b \theta)$ the weighting of average shear. The observed correlation function $\xi^{\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{\rm const}$ via 
\begin{align*}
\xi^{\text{obs}}_\pm(\theta) = & \frac{\la N(\b 0)N(\b \theta)\gammao_{\rm t}(\b 0)\gammao_{\rm t}(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \pm \frac{\la N(\b 0)N(\b \theta)\gammao_\times(\b 0)\gammao_\times(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \\
 = & \frac{\la N(\b 0)N(\b \theta)W(\b 0)W(\b \theta)\ra}{\la N(\b 0)N(\b \theta)\ra} \xi_{\pm}^{\rm const}(\theta) \, .
 \end{align*}
 Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing. We want to denote the probability that a random pair of galaxies of distance $\theta$ lie in the same pointing with $E(\theta)$. An analytical expression for this function is surprisingly hard to obtain, but it can easily be calculated to arbitrary accuracy, following the procedure explained in Appendix \ref{sec:details on etheta}. The function is depicted in Figure \ref{fig:eoftheta_lin}.

 \begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{images/eoftheta.png}
 \caption{Probability that a random pair of galaxies of distance $\theta$ lie in the same pointing.}
 \label{fig:eoftheta_lin}
 \end{figure}

We again parametrize the number density $N(\b \theta)=\la N \ra (1+n(\b \theta))$ and the weight $W(\b \theta)=1+w(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n(\b \theta)$ as a locally constant function with average $\la n \ra = 0$. We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get
 \begin{align}
\xi^{\text{obs}}_\pm(\theta) = & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta) \\
\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, . \nonumber
 \label{eq:ffunct}
\end{align}
\todo{The formula for a cross-correlation of different bins is much longer, but follows the same principle. Maybe put it into the Appendix?}
We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.

However, as a survey of constant depth is completely unrealistic, also the modelled correlation function will be subject to the same effect. If we assume the same redshift-distributions for galaxies as in the case of varying depth, and just assert that those changes are not correlated with position, we get 
\begin{equation}
\xi_\pm = (1+2\la nw\ra)\xi_\pm^{\rm const}\, .
\end{equation}
The ratio of modelled and observed correlation function thus becomes: \begin{align}
\frac{\xi_\pm}{\xi_\pm^{\rm obs}} = & \frac{\left(1+2\la nw\ra\left)\left(1+E(\theta)\la n^2\ra\right)\right.\right.}{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]} \\
\equiv & F(\theta) \, .
\end{align}
%It is interesting to note that $F(\theta)=1$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. 
We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts. 
\subsection{Using a semi-analytic Model}
The analysis of data from the Kilo-Degree Survey showed that the redshift-distribution of sources was highly correlated with the depth in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on. Now for each percentile $i$ and each tomographic redshift bin $z$ we can extract a weighted number density of galaxies $N_i(z)$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p_i(z)$. Using \eqref{eq:xipm-pkappa}, we can for each set of percentiles $i,j$ and redshift bins $z_1,z_2$ compute the shear correlation function $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.\todo{Should we cite \textsc{nicaea} here?} When we compute the measured shear correlation function of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process). If, for a single pair of galaxies, one galaxy lies in the $i$-th percentile of redshift bin $z_1$ and the second one lies in the $j$-th percentile of redshift bin $z_2$, then their contribution to the observed correlation function is, on average, $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$. This means that if we know each of those single correlation functions, we can reconstruct the total correlation function via a weighted average of the single functions. As an example, if we want to calculate the correlation function between tomographic bins $z_1$ and $z_2$ and pick a galaxy from bin $z_1$, the probability of this galaxy being in the $i$-th percentile of $z_1$ is proportional to $N_i(z_1)$. Now let the second galaxy be in bin $z_2$ and of distance $\theta$ to the first. If we imagine a thin annulus of radius $\theta$ around the first galaxy, then the number of galaxies in this annulus, that lie within the same pointing as the first galaxy, is proportional to $E(\theta)N_i(z_2)$, whereas the number of galaxies that lie in a different pointing is $[1-E(\theta)]\la N(z_2)\ra$, where $\la N(z_2)\ra$ is the average number density in redshift bin $z_2$. If the galaxy lies within a different pointing, the chances of it being in the $j$-th percentile are again just proportional to $N_j(z_2)$. We conclude that if we sum the single correlation functions $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$ according to these weightings, we can simulate the observed correlation function that accounts for the variation in optical depth via 
\begin{align}
\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \la N(z_2)\ra\sum_{j=1}^{10}\frac{  N_j(z_2)}{\sum_k N_k(z_2)} \big[1-E(\theta)\big]\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\} \nonumber \\
 = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \sum_{j=1}^{10}\frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\}\, ,
\label{eq:correctionfunction1}
\end{align}
with the normalization
\[
C = \sum_{i=1}^{10} N_i(z_1) \bigg[ E(\theta)  N_i(z_2) + \sum_{j=1}^{10} \frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\bigg]\,.
\]
A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
If we want to compute this for all 5 redshift bins of the KiDSV-survey, this forces us to calculate 1265 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive). However, if we examine Equation \eqref{eq:lenseff}, we see that it is linear in its second argument, which in turn makes Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} bilinear in their second and third arguments. This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation function of that. As an example, the following equation holds: \[
N_j\xi_\pm[\theta,p_i,p_j]+N_k\xi_\pm[\theta,p_i,p_k] = (N_j+N_k)\,\xi_\pm\left[\theta,p_i,\frac{N_jp_j+N_kp_k}{N_j+N_k}\right]\, .
\]
Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
\begin{equation}
\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{C}\bigg\{ E(\theta)\sum_{i=1}^{10} N_i(z_1)N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] +\frac{1}{10}\big[1-E(\theta)\big]\xi_\pm\left[\theta,p(z_1),p(z_2)\right]N(z_1)N(z_2)\bigg\}\, .
\label{eq:correctionfunction2}
\end{equation}
Here, we defined the \textit{average redshift distribution} $p(z)$ and \textit{combined number density} $N(z)$ of tomographic bin $z$ as \[
p(z):= \frac{\sum_i N_i(z)p_i(z)}{\sum_i N_i(z)}\, , \qquad N(z):=\sum_i N_i(z)\, .
\]
\todo{Maybe label the $N(z)$ differently to avoid confusion with $\la N(z)\ra$?}
For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165. We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N(z_1)N(z_2)$ and thus \[
\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{N(z_1)N(z_2)}\xi_\pm\left(\theta,n(z_1),n(z_2)\right)N(z_1)N(z_2) = \xi_{\pm,z_1,z_2}(\theta)\, ,
\]
so on large scales our observed correlation function agrees with the one that we would usually calculate.
\section{Results}
\label{sec:results}
We applied both our methods to data from the KiDSV-450 survey and computed the ratio of observed and modeled correlation functions. Furthermore, we have conducted a simulation using ray-tracing through the millenium simulations (?)\todo{I should ask catherine about what exactly she did for the simulations or maybe even ask her to write this part of the paper?}. As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins. The result can be seen in Figure \ref{fig:all_xis}.
	\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{images/xis_111.png}
	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.}
	\label{fig:all_xis}
	\end{figure}
We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge. We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk? Maybe in the appendix to avoid too many Figures?} The simulations seem to be in rough agreement with the models, but there are some features that can not be explained. Especially we observe that the ratios of the correlation functions for large values of $\theta$ seem to consistently surpass unity, which can not be explained by our models.

As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model. Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}. As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.\todo{Maybe expand this to more parameters?}  As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties. However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area. As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.

To estimate the B-Modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare \citet{2010A&A...520A.116S}), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth. We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}. Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KiDSV-450 survey for the same range in $\theta$. The real B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant. Given these facts, we conclude that the creation of B-Modes due to varying depth in the KiDS survey is not significant. However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, that show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).

\begin{figure}
\centering
\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/bmodes.pdf}
\caption{The $B$-modes created by a variation in survey-depth. We used the logarithmic COSEBIs described in \citet{2010A&A...520A.116S} with a range from $\theta_{\rm min} = 0.5\arcmin$ to $\theta_{\rm max} = 100\arcmin$.}
\label{fig:bmodes_cosebi}
\end{figure}

\section{Discussion}
\label{sec:discussion}
With our semi-analytic model we try to describe the impacts of varying depth in ground-based surveys. During our analysis we have assumed a few simplifications, which we will discuss.
\begin{enumerate}
\item We implemented a variation in depth that only depends on the pointing. However, in reality galactic extinction, CCD imperfections, dithering strategies and other factors also influence the depth on different scales. Although the variation between pointings is the dominating factor, a complete analysis implementing those factors could yield a slightly different result.
\item In our main analysis we assumed an infinite number of fields. This ignores boundary effects that would arise in the vincinity of the edge of a footprint (there finding a galaxy outside of the same pointing would be less likely). Also, another effect is ignored: If one has a number of $N$ fields in each percentile, and one galaxy is in a pointing of a certain percentile, then the probability that a different pointing is of the \emph{same} percentile is reduced by the factor $(N-1)/N$. However, we modeled the second effect, and already at 100 pointings it barely makes any difference. We did not model the boundary effects, but we assume that they are likewise neglible. \todo{This needs to be rewritten to account for the new insights.}
\item We have assumed that the depth of neighbouring pointings is uncorrelated. While there is no reason not to assume that, we have not yet verified that this is indeed the case.
\item In our Monte Carlo simulations we have only had $\Omega_{\rm m}$ and $\sigma_8$ as free parameters. While we do not expect most other parameters to make a difference, baryonic feedback and/or intrinsic alignments also change the correlation functions on small scales, so it is definitely possible that in a Monte Carlo chain including free parameters for these effects, those would change to mitigate the varying depth, and the impact on the actual cosmological parameters would be much smaller.
\end{enumerate}
We have determined that the effects of varying depth are not significant for the KiDSV-450 survey. For a Euclid-like survey they will play an important role, but before a model is implemented in such a precise survey, one should revise the used simplifications, especially the first one. We suspect that it should be possible to account for different aspects of varying optical depth by just modifying the function $E(\theta)$.

However, for the parameter $S_8$ this effect is insignificant, which in particular means that a variation in depth can not explain the discrepancies between the analyses of the CMB and those of the local universe. It can also be responsible for the occurence of $B$-Modes, although only to an insignificant amount.

%--------------------------------------------------------------------

\begin{acknowledgements}
Something should probably be put in here...
\end{acknowledgements}

\bibliographystyle{aa}
\bibliography{cite}
\begin{appendix}
\section{Detailed Calculations}
\subsection{Calculation of the Power Spectrum}
In this Section we will perform the calculation for the observed power spectrum \todo{I need to add cdots for scalar products in this section...} $P^{\text{obs}}(\b \ell)$. For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$. In reality, finite field effects would play a role here. We begin with the calculation of the correlation for the Fourier transformed shear:
\begin{align}
\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta')\ra\nonumber\\
 = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta') \int \frac{\text{d}^2\b k}{(2\pi)^2}\int \frac{\text{d}^2\b k'}{(2\pi)^2}\, \hat{\gamma}(\b k)\hat{\gamma}^*(\b k')\exp(-i\b k\b \theta+i\b k'\b \theta')\ra \nonumber\\
= & \la \int \text{d}^2\b \theta \int \text{d}^2\b \theta' \int \frac{\text{d}^2\b k}{(2\pi)^2} \int \frac{\text{d}^2\b k'}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b k') \exp[i(\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b k'\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
  = & \la \int \frac{\text{d}^2\b k}{(2\pi)^2} \, P(\b k) \int \text{d}^2\b \theta\, W(\b \theta)\exp[i\b \theta(\b \ell-\b k)]\int \text{d}^2\b \theta'\, W(\b \theta') \exp[-i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
  = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k)\widehat{W}(\b \ell-\b k)\widehat{W}^* (\b \ell'-\b k)\ra
\end{align}
It is important to keep in mind that the ensemble averages of the weight function are independent of the ensemble averages of the shear values, meaning $\la W(\b \theta)\gamma(\b \theta)\ra = \la W(\b \theta)\ra \la \gamma(\b \theta)\ra$. We can define $W(\b \theta)=1+w(\b\theta)$ with $\la w(\b \theta)\ra = 0$, which leads to the expession
\begin{align}
\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big( \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big)\right.\right. \nonumber\\
 & \qquad \left.\left. + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
 = & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \big[ \la \hat{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \hat{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\big] + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
\overset{(*)}{=} & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
\label{eq:pobs1}
\end{align}
where in $(*)$ we have used that the average $\la \hat{w}(\b \ell)\ra$ vanishes.
Up until now, we have not specified our weight-function $w$. So we now parametrize it as \begin{equation}
w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
0 \qquad \text{else}
\end{cases}.
\end{equation}
Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier-Transform we compute: \begin{equation}
\hat{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-i \b \ell L\b \alpha) \widehat{\Xi}(\b \ell)\, ,
\end{equation}
where
\begin{equation}
\widehat{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
\end{equation}
is a 2-dimensional sinc function.
Assuming an uncorrelated weight-distribution $\left(\la w_{\b \alpha} w_{\b \beta}\ra = 0\text{ for }\b \alpha\neq\b \beta\right)$ and setting $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ for each $\b \alpha$, we get
\begin{align}
\la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra = & \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-i(\b \ell - \b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k) \exp[i(\b \ell' - \b k)L\b \beta]\, \widehat{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
 = & \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)\widehat{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
\end{align}
Using this result, we can obtain the observed power spectrum \begin{equation}
P^{\rm{obs}}(\b\ell) = \frac{1}{(2\pi)^2}\int\d^2\ell' \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\, ,
\end{equation}
by performing the $\b \ell'$-integration in \eqref{eq:pobs1}:
\begin{align}
P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha+i(\b \ell'-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell-\b k)\widehat{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widehat{\Xi}^*(\b \ell'-\b k)\exp[i(\b \ell'- \b k)L\b \alpha] \nonumber\\
 = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widehat{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
 = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widehat{\Xi}(\b \ell-\b k)P(\b k)\, ,
\end{align}
which is a 2-dimensional convolution of the power spectrum and the 2-dimensional sinc function.
\label{sec:calc of PS}
\subsection{Details on the function $E(\theta)$}
\label{sec:details on etheta}
The function $E(\theta)$ is of central importance in this model, so we want to explain how to obtain it. It describes, given a pair of galaxies with distance $\theta$, the probability that they are in the same pointing. We obtain the function in the following way:

Given one square field of length 1 and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$. As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing. The volume of this square equals \begin{equation}
\tilde{V}(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, ,
\end{equation} where $\phi$ represents the angle of the vector $\b\theta$. To exclude negative Volumes (which would occur when $|\b\theta|>1$ holds), we nead to add the Heaviside theta function $H$:
\begin{equation}
V(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big] H\big[1-|\b\theta|\cos(\phi)\big]\,H\big[1-|\b\theta|\sin(\phi)\big]\, .
\label{eq:eoftheta1}
\end{equation} 
To obtain the function $E(\theta)$, we need to average Equation \eqref{eq:eoftheta1} over all angles $\phi$. While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
\begin{align}
E(\theta) = & \frac{4}{2\pi}\int_0^{\frac{\pi}{2}}\d\phi\, V(|\b\theta|,\phi) = \frac{2}{\pi}\begin{cases}
\int_0^{\frac{\pi}{2}} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , & |\b\theta|\leq 1 \\
\int_{\arccos(|\b\theta|^{-1})}^{\arcsin(|\b\theta|^{-1})} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , \quad & 1\leq |\b\theta| \leq \sqrt{2} \\
0\, , & \sqrt{2}\leq\theta
\end{cases} \nonumber\\
 = & \begin{cases}
\frac{\pi + (\theta-4)*\theta}{\pi}\, , & \theta \leq 1 \\
\frac{2[-1+2\sqrt{1-\theta^{-2}}*2\theta - \theta^2/2 - \arccos(\theta^{-1}) + \arcsin(\theta^{-1})]}{\pi}\, , & 1\leq \theta \leq \sqrt{2} \\
0\, , & \sqrt{2}\leq \theta
\end{cases}\, .
\end{align}
\begin{figure}
    \centering
    \def\svgwidth{200pt}    
    \input{images/eoftheta_new.pdf_tex}  
    \caption{Graphic representation on how to obtain the function $E(\theta)$. For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
    \label{fig:explain_etheta}
\end{figure}
\subsection{Calculation of the shear correlation functions}
\label{sec:calc of xipm}
Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation function via \begin{equation}
\xi_+(\theta) = \frac{\sum_{a,b}w_aw_b\epsilon_a\epsilon_b^*\Delta(\b\theta_a-\b\theta_b)}{\sum_{a,b}w_aw_b\Delta(\b\theta_a-\b\theta_b)}\, .
\label{eq:xip_from_observations}
\end{equation}
Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky. We have defined the function $\Delta$ as \[
\Delta(\b\theta_a-\b\theta_b) = \begin{cases}
1, \,\, & |\b\theta_a-\b\theta_b| \in [\theta,\theta+{\rm d}\theta] \\
0, & \text{ else}
\end{cases}\, ,
\]
where we assume ${\rm d}\theta \ll \theta$. When we now separate our galaxy samples into the ten percentiles $I$ defined above, and denote the galaxies from sample $a$ that are in pointing $i$ with $a_i$, the numerator in Equation \eqref{eq:xip_from_observations} transforms to:
\begin{align*}
 & \sum_{i,j=1}^{10} \sum_{a_i,b_j} w_{a_i}w_{b_j}\epsilon_{a_i}\epsilon_{b_j}^*\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
 = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \sum_{j=1}^{10} \sum_{b_j} w_{b_j}\epsilon_{a_i}\epsilon_{b_j}\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
 = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ \sum_{j=1}^{10} \sum_{b_j\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij \right]
\end{align*}
We take the ensemble average of that equation in the sense that we assume that the product of the ellipticities of the galaxies are equal to their respective shear correlation functions, namely $\xi_+^{ij}\equiv \epsilon_{a_i}\epsilon_{b_j}^*$ for all $a_i$ and $b_j$.

Let $b_j\in P_{a_i}$ denote all $b_j$ that lie in the same pointing as the $a_i$. We observe that the left term is zero for $i\neq j$, as only galaxies of the same percentile can lie in the same pointing. The term $\sum_{b_i\in P_{a_i}}\deltafuncij$ now is the number of galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a_i$, which is equal to the number of galaxies in the whole pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$. The prefactor $w_{b_i}$ transforms the number of galaxies to the \emph{weighted number density} of galaxy sample $b$ in percentile $i$, or $N_i(b)$, so the numerator now reads:
\begin{align*}
\sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\xi_+^{ij} \right]
\end{align*}

 A similar argument can be made for the right term: Assuming for a second that all pointings outside of the one where galaxy $a_i$ is in are of percentile $j^*$, the right hand side would read \[
\sum_{b_{j^*}\not\in P_{a_i}} w_{b_{j^*}} \Delta(\b\theta_{a_i}-\b\theta_{b_{j^*}})\xi_+^{i{j^*}} = 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j^*}(b)\xi_+^{i{j^*}}\, .
 \]  
 Taking the ensemble average of all realisations of depth-distributions, we can just denote the probability that a pointing neighbouring one of percentile $i$ is of percentile $j$ as $P(j | i,\theta)$. The numerator then reads \[
 \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta)\, 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
 \]
 In our case we assume an infinite number of randomly distributed fields, so $P(j | i,\theta)=1/10$ holds. However, for a finite survey the footprint of depth-distributions seems to be of importance, as due to a limited number of fields the $P(j | i,\theta)$ does not equate its expectation value. For smaller surveys (or surveys with correlated depth-distributions) it seems appropriate to adjust this parameter. \todo{Wait for catherines 450deg${}^2$ simulations, maybe they are big enough?}

 If we define $A$ as the (arbitrarily big) survey area, we can set \[
 \sum_{a_i} w_{a_i} = A\, N_i(a)
 \]
 and see that the numerator becomes \[
 2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
 \]
 The exact line of argumentation can be applied to the denominator, which then reads: \[
  2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b) + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b) \right]\, .
 \]
Taking the ratio of the two quantities, and setting $P(j | i,\theta)=1/10$, we receive Equation \eqref{eq:correctionfunction1}.
\section{Additional Figures}
\subsection{Results of the MCMC}
\begin{figure}[h]
\centering
	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
	\caption{Bias in the parameters for a KiDS-like Survey.}
	\label{fig:mcmc_kids}
\end{figure}  
\begin{figure}[h]
\centering
	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
	\caption{Bias in the parameters for a Euclid-like Survey.}
	\label{fig:mcmc_euclid}
\end{figure}  
\todo{Put both in one plot? Maybe put reference MC simulation where $\xi_\pm$ was not changed?}
\end{appendix}
\end{document}
%

### 2019-04-03 introduction.tex
Create introduction.tex

--- 2019-04-03 paperdraft.tex
@@
-\documentclass[referee]{aa} % for a referee version
-%\documentclass[onecolumn]{aa} % for a paper on 1 column  
-%\documentclass[longauth]{aa} % for the long lists of affiliations 
-%\documentclass[letter]{aa} % for the letters 
-%\documentclass[bibyear]{aa} % if the references are not structured 
-%                              according to the author-year natbib style
-
-%
-%\documentclass{aa}  
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\ben}{\begin{enumerate}}
-\newcommand{\een}{\end{enumerate}}
-\newcommand{\bi}{\begin{itemize}}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\bmi}[1]{\begin{minipage}{#1 cm}}
-\newcommand{\emi}{\end{minipage}}
-\renewcommand{\[}{\begin{equation}}
-\renewcommand{\]}{\end{equation}}
-
-\renewcommand{\rm}{\mathrm}
-\def\inv{^{-1}}
-\def\({\left(}
-\def\r){\right)}
-\def\b#1{\bm{#1}}
-\def\Dd{D_{\text{d}}}
-\def\Dds{D_{\text{ds}}}
-\def\Ds{D_{\text{s}}}
-\def\la{\left<}
-\def\ra{\right>}
-\def\gammao{\gamma^{\text{obs}}}
-\def\gammaoh{\hat{\gamma}^{\text{obs}}}
-\def\epsilonsij{\epsilon_{a_i}\epsilon_{b_j}^*}
-\def\epsilonsii{\epsilon_{a_i}\epsilon_{b_i}^*}
-\def\deltafuncij{\Delta(\b\theta_{a_i}-\b\theta_{b_j})}
-\def\d{\rm{d}}
-
-%\newcommand{\todo}{\emph}
-
-\usepackage{bm}
-\usepackage{verbatim}
-%
-\usepackage{graphicx}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{txfonts}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage[options]{hyperref}
-% To add links in your PDF file, use the package "hyperref"
-% with options according to your LaTeX or PDFLaTeX drivers.
-%
-\usepackage{todonotes}
-
-\begin{document}
-
-   \title{The Effects of Varying Depth in Cosmic Shear Surveys}
-
-%   \subtitle{}
-
-   \author{S. Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
-          \and Peter Schneider\inst{1} 
-          \and Hendrik Hildebrandt\inst{2,1}
-          \and Catherine Heymans\inst{3} 
-          \and Marika Asgari\inst{3}
-          \todo{order of authors?, KiDS-Authors?}
-          }
-   \institute{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany 
-\and 
-Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany \and
-Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de}
-             }
-
-   \date{Received XXX; accepted XXX}
-
-  \abstract
-% context (optional)
-   {Cosmic shear proves to be a powerful tool to study the properties of the local Universe.
-The discrepancy in the parameter $S_8$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases.
-% aims
-   Especially ground-based surveys are subject to a variation in depth.
-We want to understand and quantify the resulting effects.
-In particular, we check if they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
-% methods
-   We construct a semi-analytic model to estimate the impact on the shear correlation function and analyze the implications for cosmological parameters.
-Furthermore we construct COSEBIs of the correlation functions to quantify the occuring B-Modes.
-% results
-   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$.
-However, the parameter $S_8$ is robust against this modification.
-We also report the occurrence of B-Modes, although not to a significant degree.
-% conclusions (optional)
-   We conclude that the effects of varying optical depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}
-
-   \keywords{gravitational lensing --
-                weak lensing --
-                cosmic shear
-               }
-
-   \maketitle
-
-%
-%-------------------------------------------------------------------
-
 \section{Introduction}
@@
 We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
-
-\section{Modelling the Power Spectrum}
-\label{sec:modelling_single_lens}
-For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
-If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm ds}/D_{\rm s}$.
-% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
-%\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
-%\]
-
-%Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate.
-Assuming that the optical depth, and thus the source redshift populations, vary between pointing, an observer will measure a shear-signal that is modified by a depth-function $W(\bm{\theta}) = 1-w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-The reconstruction of the observed convergence $\kappa^{\rm obs}$ will thus not yield the original convergence.
-In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part.
-This allows us to separate our received signal into E- and B-modes following \[
-%	\kappa = \kappa^E+i\kappa^B\, ,
-%\]
-%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
-%2002A&A...389..729S SRC
-
-\subsection{Effects on the Power Spectrum}
-Assuming that the depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a locally constant depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-In accordance to the definition of the shear power spectrum \begin{equation}
-(2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) = \la \hat{\gamma}(\b\ell)\hat{\gamma}(\b\ell')\ra \, ,
-\end{equation}
-we define the observed power spectrum via \begin{equation}
-P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \, .
-\end{equation}
-Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
-To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as
-\begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
-1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
-0 \qquad \text{else}
-\end{cases},
-\label{eq:defweightf}
-\end{equation}
-where $L$ is the length of one pointing.
-Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
-\begin{equation}
-P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)P(\b k)\, ,
-\end{equation}
-where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function.
-The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with the fourier transfrom of a box-function, scaling with the variance of the geometric lensing efficiency $\la \frac{D_{\rm ds}}{D_{s}}\ra$.
-In particular, the power spectrum is not isotropic anymore.
-Following \citet{2002A&A...389..729S}, it would be interesting to extract E- and B-mode information out of this power spectrum, however \citet{2010A&A...520A.116S} present a more sophisticated decomposition of E- and B-modes, that can also be applied to real data using the shear correlation function, so instead we want to focus our efforts on these parts.
-\section{Modelling the shear correlation function}
-\label{sec:xipm}
-A convenient way to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
-\xi_\pm = \la \gamma_{\rm t}\gamma_{\rm t}\ra \pm \la \gamma_\times\gamma_\times\ra \, .
-\]
-They are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear-measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions.
-Cosmologically, given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation function from the underlyting matter power spectrum $P_\delta$ via \todo{Citation!}\begin{align}
-\label{eq:xipm-pkappa}
-\xi_\pm[\theta,p_i,p_j] =& \int_0^\infty \frac{{\rm d}l\,l}{2\pi}J_{0,4}(l\theta)P(l,p_i,p_j)\, , \\
-\label{eq:pkappa-pdelta/lenseff}
-P(l,p_i,p_j) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_h} {\rm d}\chi\frac{g(\chi,p_i)g(\chi,p_j)}{a^2(\chi)}P_\delta\left(\frac{l}{f_K(\chi)},\chi\right)\, , \\
-\label{eq:lenseff}
-g(\chi,p_i) =& \int_\chi^{\chi_H} {\rm d}\chi'\, p_i(\chi') \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
-\end{align}
-Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions.
-\subsection{Using an analytic Model}
-For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal. Following \citet{2006APh....26...91V}, we estimate
-\[
-\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
-\]
-\todo{Maybe implement redshift-dependent index?}
-Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
-
-%For a pair of galaxies that we use to measure the correlation function, it is crucial to determine whether those two galaxies lie within the same pointing.
-We want to define a function $E(\theta)$ that determines
-
-Let $N(\b \theta)$ be the number-density per tile and $W(\b \theta)$ the weighting of average shear.
-The observed correlation function $\xi^{\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{\rm const}$ via
-\begin{align*}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{\la N(\b 0)N(\b \theta)\gammao_{\rm t}(\b 0)\gammao_{\rm t}(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \pm \frac{\la N(\b 0)N(\b \theta)\gammao_\times(\b 0)\gammao_\times(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \\
- = & \frac{\la N(\b 0)N(\b \theta)W(\b 0)W(\b \theta)\ra}{\la N(\b 0)N(\b \theta)\ra} \xi_{\pm}^{\rm const}(\theta) \, .
- \end{align*}
- Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
-We want to denote the probability that a random pair of galaxies of distance $\theta$ lie in the same pointing with $E(\theta)$.
-An analytical expression for this function is surprisingly hard to obtain, but it can easily be calculated to arbitrary accuracy, following the procedure explained in Appendix \ref{sec:details on etheta}.
-The function is depicted in Figure \ref{fig:eoftheta_lin}.
-
- \begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{images/eoftheta.png}
- \caption{Probability that a random pair of galaxies of distance $\theta$ lie in the same pointing.}
- \label{fig:eoftheta_lin}
- \end{figure}
-
-We again parametrize the number density $N(\b \theta)=\la N \ra (1+n(\b \theta))$ and the weight $W(\b \theta)=1+w(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n(\b \theta)$ as a locally constant function with average $\la n \ra = 0$.
-We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get
- \begin{align}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta) \\
-\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, . \nonumber
- \label{eq:ffunct}
-\end{align}
-\todo{The formula for a cross-correlation of different bins is much longer, but follows the same principle. Maybe put it into the Appendix?}
-We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.
-
-However, as a survey of constant depth is completely unrealistic, also the modelled correlation function will be subject to the same effect.
-If we assume the same redshift-distributions for galaxies as in the case of varying depth, and just assert that those changes are not correlated with position, we get
-\begin{equation}
-\xi_\pm = (1+2\la nw\ra)\xi_\pm^{\rm const}\, .
-\end{equation}
-The ratio of modelled and observed correlation function thus becomes: \begin{align}
-\frac{\xi_\pm}{\xi_\pm^{\rm obs}} = & \frac{\left(1+2\la nw\ra\left)\left(1+E(\theta)\la n^2\ra\right)\right.\right.}{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]} \\
-\equiv & F(\theta) \, .
-\end{align}
-%It is interesting to note that $F(\theta)=1$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. 
-We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts. 
-\subsection{Using a semi-analytic Model}
-The analysis of data from the Kilo-Degree Survey showed that the redshift-distribution of sources was highly correlated with the depth in the $r$-band.
-We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-Now for each percentile $i$ and each tomographic redshift bin $z$ we can extract a weighted number density of galaxies $N_i(z)$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p_i(z)$.
-Using \eqref{eq:xipm-pkappa}, we can for each set of percentiles $i,j$ and redshift bins $z_1,z_2$ compute the shear correlation function $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.\todo{Should we cite \textsc{nicaea} here?} When we compute the measured shear correlation function of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process).
-If, for a single pair of galaxies, one galaxy lies in the $i$-th percentile of redshift bin $z_1$ and the second one lies in the $j$-th percentile of redshift bin $z_2$, then their contribution to the observed correlation function is, on average, $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.
-This means that if we know each of those single correlation functions, we can reconstruct the total correlation function via a weighted average of the single functions.
-As an example, if we want to calculate the correlation function between tomographic bins $z_1$ and $z_2$ and pick a galaxy from bin $z_1$, the probability of this galaxy being in the $i$-th percentile of $z_1$ is proportional to $N_i(z_1)$.
-Now let the second galaxy be in bin $z_2$ and of distance $\theta$ to the first.
-If we imagine a thin annulus of radius $\theta$ around the first galaxy, then the number of galaxies in this annulus, that lie within the same pointing as the first galaxy, is proportional to $E(\theta)N_i(z_2)$, whereas the number of galaxies that lie in a different pointing is $[1-E(\theta)]\la N(z_2)\ra$, where $\la N(z_2)\ra$ is the average number density in redshift bin $z_2$.
-If the galaxy lies within a different pointing, the chances of it being in the $j$-th percentile are again just proportional to $N_j(z_2)$.
-We conclude that if we sum the single correlation functions $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$ according to these weightings, we can simulate the observed correlation function that accounts for the variation in optical depth via
-\begin{align}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \la N(z_2)\ra\sum_{j=1}^{10}\frac{  N_j(z_2)}{\sum_k N_k(z_2)} \big[1-E(\theta)\big]\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\} \nonumber \\
- = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \sum_{j=1}^{10}\frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\}\, ,
-\label{eq:correctionfunction1}
-\end{align}
-with the normalization
-\[
-C = \sum_{i=1}^{10} N_i(z_1) \bigg[ E(\theta)  N_i(z_2) + \sum_{j=1}^{10} \frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\bigg]\,.
-\]
-A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
-If we want to compute this for all 5 redshift bins of the KiDSV-survey, this forces us to calculate 1265 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive).
-However, if we examine Equation \eqref{eq:lenseff}, we see that it is linear in its second argument, which in turn makes Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} bilinear in their second and third arguments.
-This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation function of that.
-As an example, the following equation holds: \[
-N_j\xi_\pm[\theta,p_i,p_j]+N_k\xi_\pm[\theta,p_i,p_k] = (N_j+N_k)\,\xi_\pm\left[\theta,p_i,\frac{N_jp_j+N_kp_k}{N_j+N_k}\right]\, .
-\]
-Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
-\begin{equation}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{C}\bigg\{ E(\theta)\sum_{i=1}^{10} N_i(z_1)N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] +\frac{1}{10}\big[1-E(\theta)\big]\xi_\pm\left[\theta,p(z_1),p(z_2)\right]N(z_1)N(z_2)\bigg\}\, .
-\label{eq:correctionfunction2}
-\end{equation}
-Here, we defined the \textit{average redshift distribution} $p(z)$ and \textit{combined number density} $N(z)$ of tomographic bin $z$ as \[
-p(z):= \frac{\sum_i N_i(z)p_i(z)}{\sum_i N_i(z)}\, , \qquad N(z):=\sum_i N_i(z)\, .
-\]
-\todo{Maybe label the $N(z)$ differently to avoid confusion with $\la N(z)\ra$?}
-For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
-We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N(z_1)N(z_2)$ and thus \[
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{N(z_1)N(z_2)}\xi_\pm\left(\theta,n(z_1),n(z_2)\right)N(z_1)N(z_2) = \xi_{\pm,z_1,z_2}(\theta)\, ,
-\]
-so on large scales our observed correlation function agrees with the one that we would usually calculate.
-\section{Results}
-\label{sec:results}
-We applied both our methods to data from the KiDSV-450 survey and computed the ratio of observed and modeled correlation functions.
-Furthermore, we have conducted a simulation using ray-tracing through the millenium simulations (?)\todo{I should ask catherine about what exactly she did for the simulations or maybe even ask her to write this part of the paper?}.
-As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
-The result can be seen in Figure \ref{fig:all_xis}.
-	\begin{figure}
-	\centering
-	\includegraphics[width=1\textwidth]{images/xis_111.png}
-	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.}
-	\label{fig:all_xis}
-	\end{figure}
-We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
-We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk?
-Maybe in the appendix to avoid too many Figures?} The simulations seem to be in rough agreement with the models, but there are some features that can not be explained.
-Especially we observe that the ratios of the correlation functions for large values of $\theta$ seem to consistently surpass unity, which can not be explained by our models.
-
-As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model.
-Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
-As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.\todo{Maybe expand this to more parameters?}  As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties.
-However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area.
-As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.
-
-To estimate the B-Modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare \citet{2010A&A...520A.116S}), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
-We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KiDSV-450 survey for the same range in $\theta$.
-The real B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant.
-Given these facts, we conclude that the creation of B-Modes due to varying depth in the KiDS survey is not significant.
-However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, that show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).
-
-\begin{figure}
-\centering
-\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/bmodes.pdf}
-\caption{The $B$-modes created by a variation in survey-depth.
-We used the logarithmic COSEBIs described in \citet{2010A&A...520A.116S} with a range from $\theta_{\rm min} = 0.5\arcmin$ to $\theta_{\rm max} = 100\arcmin$.}
-\label{fig:bmodes_cosebi}
-\end{figure}
-
-\section{Discussion}
-\label{sec:discussion}
-With our semi-analytic model we try to describe the impacts of varying depth in ground-based surveys. During our analysis we have assumed a few simplifications, which we will discuss.
-\begin{enumerate}
-\item We implemented a variation in depth that only depends on the pointing.
-However, in reality galactic extinction, CCD imperfections, dithering strategies and other factors also influence the depth on different scales.
-Although the variation between pointings is the dominating factor, a complete analysis implementing those factors could yield a slightly different result.
-\item In our main analysis we assumed an infinite number of fields.
-This ignores boundary effects that would arise in the vincinity of the edge of a footprint (there finding a galaxy outside of the same pointing would be less likely).
-Also, another effect is ignored: If one has a number of $N$ fields in each percentile, and one galaxy is in a pointing of a certain percentile, then the probability that a different pointing is of the \emph{same} percentile is reduced by the factor $(N-1)/N$.
-However, we modeled the second effect, and already at 100 pointings it barely makes any difference.
-We did not model the boundary effects, but we assume that they are likewise neglible.
-\todo{This needs to be rewritten to account for the new insights.}
-\item We have assumed that the depth of neighbouring pointings is uncorrelated. While there is no reason not to assume that, we have not yet verified that this is indeed the case.
-\item In our Monte Carlo simulations we have only had $\Omega_{\rm m}$ and $\sigma_8$ as free parameters.
-While we do not expect most other parameters to make a difference, baryonic feedback and/or intrinsic alignments also change the correlation functions on small scales, so it is definitely possible that in a Monte Carlo chain including free parameters for these effects, those would change to mitigate the varying depth, and the impact on the actual cosmological parameters would be much smaller.
-\end{enumerate}
-We have determined that the effects of varying depth are not significant for the KiDSV-450 survey.
-For a Euclid-like survey they will play an important role, but before a model is implemented in such a precise survey, one should revise the used simplifications, especially the first one.
-We suspect that it should be possible to account for different aspects of varying optical depth by just modifying the function $E(\theta)$.
-
-However, for the parameter $S_8$ this effect is insignificant, which in particular means that a variation in depth can not explain the discrepancies between the analyses of the CMB and those of the local universe.
-It can also be responsible for the occurence of $B$-Modes, although only to an insignificant amount.
-
-%--------------------------------------------------------------------
-
-\begin{acknowledgements}
-Something should probably be put in here...
-\end{acknowledgements}
-
-\bibliographystyle{aa}
-\bibliography{cite}
-\begin{appendix}
-\section{Detailed Calculations}
-\subsection{Calculation of the Power Spectrum}
-In this Section we will perform the calculation for the observed power spectrum \todo{I need to add cdots for scalar products in this section...} $P^{\text{obs}}(\b \ell)$.
-For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$.
-In reality, finite field effects would play a role here.
-We begin with the calculation of the correlation for the Fourier transformed shear:
-\begin{align}
-\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta')\ra\nonumber\\
- = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta') \int \frac{\text{d}^2\b k}{(2\pi)^2}\int \frac{\text{d}^2\b k'}{(2\pi)^2}\, \hat{\gamma}(\b k)\hat{\gamma}^*(\b k')\exp(-i\b k\b \theta+i\b k'\b \theta')\ra \nonumber\\
-= & \la \int \text{d}^2\b \theta \int \text{d}^2\b \theta' \int \frac{\text{d}^2\b k}{(2\pi)^2} \int \frac{\text{d}^2\b k'}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b k') \exp[i(\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b k'\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
-  = & \la \int \frac{\text{d}^2\b k}{(2\pi)^2} \, P(\b k) \int \text{d}^2\b \theta\, W(\b \theta)\exp[i\b \theta(\b \ell-\b k)]\int \text{d}^2\b \theta'\, W(\b \theta') \exp[-i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
-  = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k)\widehat{W}(\b \ell-\b k)\widehat{W}^* (\b \ell'-\b k)\ra
-\end{align}
-It is important to keep in mind that the ensemble averages of the weight function are independent of the ensemble averages of the shear values, meaning $\la W(\b \theta)\gamma(\b \theta)\ra = \la W(\b \theta)\ra \la \gamma(\b \theta)\ra$.
-We can define $W(\b \theta)=1+w(\b\theta)$ with $\la w(\b \theta)\ra = 0$, which leads to the expession
-\begin{align}
-\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big( \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big)\right.\right.
-\nonumber\\
- & \qquad \left.\left. + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
- = & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \big[ \la \hat{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \hat{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\big] + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
-\overset{(*)}{=} & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
-\label{eq:pobs1}
-\end{align}
-where in $(*)$ we have used that the average $\la \hat{w}(\b \ell)\ra$ vanishes.
-Up until now, we have not specified our weight-function $w$. So we now parametrize it as \begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
-1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
-0 \qquad \text{else}
-\end{cases}.
-\end{equation}
-Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier-Transform we compute: \begin{equation}
-\hat{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-i \b \ell L\b \alpha) \widehat{\Xi}(\b \ell)\, ,
-\end{equation}
-where
-\begin{equation}
-\widehat{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
-\end{equation}
-is a 2-dimensional sinc function.
-Assuming an uncorrelated weight-distribution $\left(\la w_{\b \alpha} w_{\b \beta}\ra = 0\text{ for }\b \alpha\neq\b \beta\right)$ and setting $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ for each $\b \alpha$, we get
-\begin{align}
-\la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra = & \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-i(\b \ell - \b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k) \exp[i(\b \ell' - \b k)L\b \beta]\, \widehat{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
- = & \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)\widehat{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
-\end{align}
-Using this result, we can obtain the observed power spectrum \begin{equation}
-P^{\rm{obs}}(\b\ell) = \frac{1}{(2\pi)^2}\int\d^2\ell' \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\, ,
-\end{equation}
-by performing the $\b \ell'$-integration in \eqref{eq:pobs1}:
-\begin{align}
-P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha+i(\b \ell'-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell-\b k)\widehat{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
-= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widehat{\Xi}^*(\b \ell'-\b k)\exp[i(\b \ell'- \b k)L\b \alpha] \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widehat{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widehat{\Xi}(\b \ell-\b k)P(\b k)\, ,
-\end{align}
-which is a 2-dimensional convolution of the power spectrum and the 2-dimensional sinc function.
-\label{sec:calc of PS}
-\subsection{Details on the function $E(\theta)$}
-\label{sec:details on etheta}
-The function $E(\theta)$ is of central importance in this model, so we want to explain how to obtain it.
-It describes, given a pair of galaxies with distance $\theta$, the probability that they are in the same pointing.
-We obtain the function in the following way:
-
-Given one square field of length 1 and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
-As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
-The volume of this square equals \begin{equation}
-\tilde{V}(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, ,
-\end{equation} where $\phi$ represents the angle of the vector $\b\theta$. To exclude negative Volumes (which would occur when $|\b\theta|>1$ holds), we nead to add the Heaviside theta function $H$:
-\begin{equation}
-V(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big] H\big[1-|\b\theta|\cos(\phi)\big]\,H\big[1-|\b\theta|\sin(\phi)\big]\, .
-\label{eq:eoftheta1}
-\end{equation} 
-To obtain the function $E(\theta)$, we need to average Equation \eqref{eq:eoftheta1} over all angles $\phi$.
-While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
-\begin{align}
-E(\theta) = & \frac{4}{2\pi}\int_0^{\frac{\pi}{2}}\d\phi\, V(|\b\theta|,\phi) = \frac{2}{\pi}\begin{cases}
-\int_0^{\frac{\pi}{2}} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , & |\b\theta|\leq 1 \\
-\int_{\arccos(|\b\theta|^{-1})}^{\arcsin(|\b\theta|^{-1})} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , \quad & 1\leq |\b\theta| \leq \sqrt{2} \\
-0\, , & \sqrt{2}\leq\theta
-\end{cases} \nonumber\\
- = & \begin{cases}
-\frac{\pi + (\theta-4)*\theta}{\pi}\, , & \theta \leq 1 \\
-\frac{2[-1+2\sqrt{1-\theta^{-2}}*2\theta - \theta^2/2 - \arccos(\theta^{-1}) + \arcsin(\theta^{-1})]}{\pi}\, , & 1\leq \theta \leq \sqrt{2} \\
-0\, , & \sqrt{2}\leq \theta
-\end{cases}\, .
-\end{align}
-\begin{figure}
-    \centering
-    \def\svgwidth{200pt}    
-    \input{images/eoftheta_new.pdf_tex}  
-    \caption{Graphic representation on how to obtain the function $E(\theta)$.
-For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
-    \label{fig:explain_etheta}
-\end{figure}
-\subsection{Calculation of the shear correlation functions}
-\label{sec:calc of xipm}
-Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation function via \begin{equation}
-\xi_+(\theta) = \frac{\sum_{a,b}w_aw_b\epsilon_a\epsilon_b^*\Delta(\b\theta_a-\b\theta_b)}{\sum_{a,b}w_aw_b\Delta(\b\theta_a-\b\theta_b)}\, .
-\label{eq:xip_from_observations}
-\end{equation}
-Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky. We have defined the function $\Delta$ as \[
-\Delta(\b\theta_a-\b\theta_b) = \begin{cases}
-1, \,\, & |\b\theta_a-\b\theta_b| \in [\theta,\theta+{\rm d}\theta] \\
-0, & \text{ else}
-\end{cases}\, ,
-\]
-where we assume ${\rm d}\theta \ll \theta$.
-When we now separate our galaxy samples into the ten percentiles $I$ defined above, and denote the galaxies from sample $a$ that are in pointing $i$ with $a_i$, the numerator in Equation \eqref{eq:xip_from_observations} transforms to:
-\begin{align*}
- & \sum_{i,j=1}^{10} \sum_{a_i,b_j} w_{a_i}w_{b_j}\epsilon_{a_i}\epsilon_{b_j}^*\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
- = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \sum_{j=1}^{10} \sum_{b_j} w_{b_j}\epsilon_{a_i}\epsilon_{b_j}\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
- = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ \sum_{j=1}^{10} \sum_{b_j\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij \right]
-\end{align*}
-We take the ensemble average of that equation in the sense that we assume that the product of the ellipticities of the galaxies are equal to their respective shear correlation functions, namely $\xi_+^{ij}\equiv \epsilon_{a_i}\epsilon_{b_j}^*$ for all $a_i$ and $b_j$.
-
-Let $b_j\in P_{a_i}$ denote all $b_j$ that lie in the same pointing as the $a_i$.
-We observe that the left term is zero for $i\neq j$, as only galaxies of the same percentile can lie in the same pointing.
-The term $\sum_{b_i\in P_{a_i}}\deltafuncij$ now is the number of galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a_i$, which is equal to the number of galaxies in the whole pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$.
-The prefactor $w_{b_i}$ transforms the number of galaxies to the \emph{weighted number density} of galaxy sample $b$ in percentile $i$, or $N_i(b)$, so the numerator now reads:
-\begin{align*}
-\sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\xi_+^{ij} \right]
-\end{align*}
-
- A similar argument can be made for the right term: Assuming for a second that all pointings outside of the one where galaxy $a_i$ is in are of percentile $j^*$, the right hand side would read \[
-\sum_{b_{j^*}\not\in P_{a_i}} w_{b_{j^*}} \Delta(\b\theta_{a_i}-\b\theta_{b_{j^*}})\xi_+^{i{j^*}} = 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j^*}(b)\xi_+^{i{j^*}}\, .
- \]  
- Taking the ensemble average of all realisations of depth-distributions, we can just denote the probability that a pointing neighbouring one of percentile $i$ is of percentile $j$ as $P(j | i,\theta)$.
-The numerator then reads \[
- \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta)\, 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
- \]
- In our case we assume an infinite number of randomly distributed fields, so $P(j | i,\theta)=1/10$ holds.
-However, for a finite survey the footprint of depth-distributions seems to be of importance, as due to a limited number of fields the $P(j | i,\theta)$ does not equate its expectation value.
-For smaller surveys (or surveys with correlated depth-distributions) it seems appropriate to adjust this parameter.
-\todo{Wait for catherines 450deg${}^2$ simulations, maybe they are big enough?}
-
- If we define $A$ as the (arbitrarily big) survey area, we can set \[
- \sum_{a_i} w_{a_i} = A\, N_i(a)
- \]
- and see that the numerator becomes \[
- 2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
- \]
- The exact line of argumentation can be applied to the denominator, which then reads: \[
-  2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b) + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b) \right]\, .
- \]
-Taking the ratio of the two quantities, and setting $P(j | i,\theta)=1/10$, we receive Equation \eqref{eq:correctionfunction1}.
-\section{Additional Figures}
-\subsection{Results of the MCMC}
-\begin{figure}[h]
-\centering
-	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
-	\caption{Bias in the parameters for a KiDS-like Survey.}
-	\label{fig:mcmc_kids}
-\end{figure}  
-\begin{figure}[h]
-\centering
-	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
-	\caption{Bias in the parameters for a Euclid-like Survey.}
-	\label{fig:mcmc_euclid}
-\end{figure}  
-\todo{Put both in one plot? Maybe put reference MC simulation where $\xi_\pm$ was not changed?}
-\end{appendix}
-\end{document}
-%

### 2019-04-03 discussion.tex
Create discussion.tex

--- 2019-04-03 paperdraft.tex
@@
-\documentclass[referee]{aa} % for a referee version
-%\documentclass[onecolumn]{aa} % for a paper on 1 column  
-%\documentclass[longauth]{aa} % for the long lists of affiliations 
-%\documentclass[letter]{aa} % for the letters 
-%\documentclass[bibyear]{aa} % if the references are not structured 
-%                              according to the author-year natbib style
-
-%
-%\documentclass{aa}  
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\ben}{\begin{enumerate}}
-\newcommand{\een}{\end{enumerate}}
-\newcommand{\bi}{\begin{itemize}}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\bmi}[1]{\begin{minipage}{#1 cm}}
-\newcommand{\emi}{\end{minipage}}
-\renewcommand{\[}{\begin{equation}}
-\renewcommand{\]}{\end{equation}}
-
-\renewcommand{\rm}{\mathrm}
-\def\inv{^{-1}}
-\def\({\left(}
-\def\r){\right)}
-\def\b#1{\bm{#1}}
-\def\Dd{D_{\text{d}}}
-\def\Dds{D_{\text{ds}}}
-\def\Ds{D_{\text{s}}}
-\def\la{\left<}
-\def\ra{\right>}
-\def\gammao{\gamma^{\text{obs}}}
-\def\gammaoh{\hat{\gamma}^{\text{obs}}}
-\def\epsilonsij{\epsilon_{a_i}\epsilon_{b_j}^*}
-\def\epsilonsii{\epsilon_{a_i}\epsilon_{b_i}^*}
-\def\deltafuncij{\Delta(\b\theta_{a_i}-\b\theta_{b_j})}
-\def\d{\rm{d}}
-
-%\newcommand{\todo}{\emph}
-
-\usepackage{bm}
-\usepackage{verbatim}
-%
-\usepackage{graphicx}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{txfonts}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage[options]{hyperref}
-% To add links in your PDF file, use the package "hyperref"
-% with options according to your LaTeX or PDFLaTeX drivers.
-%
-\usepackage{todonotes}
-
-\begin{document}
-
-   \title{The Effects of Varying Depth in Cosmic Shear Surveys}
-
-%   \subtitle{}
-
-   \author{S. Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
-          \and Peter Schneider\inst{1} 
-          \and Hendrik Hildebrandt\inst{2,1}
-          \and Catherine Heymans\inst{3} 
-          \and Marika Asgari\inst{3}
-          \todo{order of authors?, KiDS-Authors?}
-          }
-   \institute{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany 
-\and 
-Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany \and
-Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de}
-             }
-
-   \date{Received XXX; accepted XXX}
-
-  \abstract
-% context (optional)
-   {Cosmic shear proves to be a powerful tool to study the properties of the local Universe.
-The discrepancy in the parameter $S_8$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases.
-% aims
-   Especially ground-based surveys are subject to a variation in depth.
-We want to understand and quantify the resulting effects.
-In particular, we check if they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
-% methods
-   We construct a semi-analytic model to estimate the impact on the shear correlation function and analyze the implications for cosmological parameters.
-Furthermore we construct COSEBIs of the correlation functions to quantify the occuring B-Modes.
-% results
-   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$.
-However, the parameter $S_8$ is robust against this modification.
-We also report the occurrence of B-Modes, although not to a significant degree.
-% conclusions (optional)
-   We conclude that the effects of varying optical depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}
-
-   \keywords{gravitational lensing --
-                weak lensing --
-                cosmic shear
-               }
-
-   \maketitle
-
-%
-%-------------------------------------------------------------------
-
-\section{Introduction}
-The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the $\Lambda$CDM Model and determine its parameters.
-Contrary to the analysis of the Cosmic Microwave Background \citep{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
-Current Cosmic Shear surveys are especially sensitive to the paramter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
-It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$,
-%\citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data,
-\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2017MNRAS.465.1454H} report $S_8 = 0.745\pm 0.038$ from KiDS data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$.
-Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data.
-This discrepancy could be a statistical coincidence, a sign of new physics or the manifestation of an unknown systematic effect.
-\todo{Citations..
-\citet{2017MNRAS.464.1676A} has a few...}
-
-To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citet{2002ApJ...568...20C,2002A&A...389..729S}.
-To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
-As \citet{2017MNRAS.465.1454H} report the significant detection of B-modes, it is well motivated to check for possible systematics that are yet unaccounted for.
-Note that the non-existence of B-modes does not imply that the sample is free of remaining systematics.
-
-One systematic effect is the variation of depth in a survey.
-While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions, that are found in ground-based surveys.
-To first order, this variation can be modelled by a step-like depth function that varies from pointing to pointing.
-In this work we assume the specifications of the Kilo-Degree Survey, namely a collection of $1\,\text{deg}^2$ square fields.
-Furthermore we neglect boundary effects.
-
-In Section \ref{sec:modelling_single_lens} we will introduce a simple toy model to understand this effect and analyze the impact on the power spectrum.
-In Section \ref{sec:xipm} we will estimate the effect on the shear correlation functions $\xi_\pm$ using two different models.
-We will present our results in Section \ref{sec:results}.
-In Section \ref{sec:discussion} we will discuss our results and comment on the impacts of our used simplifications.
-We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
-
-\section{Modelling the Power Spectrum}
-\label{sec:modelling_single_lens}
-For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
-If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm ds}/D_{\rm s}$.
-% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
-%\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
-%\]
-
-%Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate.
-Assuming that the optical depth, and thus the source redshift populations, vary between pointing, an observer will measure a shear-signal that is modified by a depth-function $W(\bm{\theta}) = 1-w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-The reconstruction of the observed convergence $\kappa^{\rm obs}$ will thus not yield the original convergence.
-In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part.
-This allows us to separate our received signal into E- and B-modes following \[
-%	\kappa = \kappa^E+i\kappa^B\, ,
-%\]
-%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
-%2002A&A...389..729S SRC
-
-\subsection{Effects on the Power Spectrum}
-Assuming that the depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a locally constant depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-In accordance to the definition of the shear power spectrum \begin{equation}
-(2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) = \la \hat{\gamma}(\b\ell)\hat{\gamma}(\b\ell')\ra \, ,
-\end{equation}
-we define the observed power spectrum via \begin{equation}
-P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \, .
-\end{equation}
-Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
-To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as
-\begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
-1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
-0 \qquad \text{else}
-\end{cases},
-\label{eq:defweightf}
-\end{equation}
-where $L$ is the length of one pointing.
-Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
-\begin{equation}
-P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)P(\b k)\, ,
-\end{equation}
-where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function.
-The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with the fourier transfrom of a box-function, scaling with the variance of the geometric lensing efficiency $\la \frac{D_{\rm ds}}{D_{s}}\ra$.
-In particular, the power spectrum is not isotropic anymore.
-Following \citet{2002A&A...389..729S}, it would be interesting to extract E- and B-mode information out of this power spectrum, however \citet{2010A&A...520A.116S} present a more sophisticated decomposition of E- and B-modes, that can also be applied to real data using the shear correlation function, so instead we want to focus our efforts on these parts.
-\section{Modelling the shear correlation function}
-\label{sec:xipm}
-A convenient way to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
-\xi_\pm = \la \gamma_{\rm t}\gamma_{\rm t}\ra \pm \la \gamma_\times\gamma_\times\ra \, .
-\]
-They are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear-measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions.
-Cosmologically, given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation function from the underlyting matter power spectrum $P_\delta$ via \todo{Citation!}\begin{align}
-\label{eq:xipm-pkappa}
-\xi_\pm[\theta,p_i,p_j] =& \int_0^\infty \frac{{\rm d}l\,l}{2\pi}J_{0,4}(l\theta)P(l,p_i,p_j)\, , \\
-\label{eq:pkappa-pdelta/lenseff}
-P(l,p_i,p_j) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_h} {\rm d}\chi\frac{g(\chi,p_i)g(\chi,p_j)}{a^2(\chi)}P_\delta\left(\frac{l}{f_K(\chi)},\chi\right)\, , \\
-\label{eq:lenseff}
-g(\chi,p_i) =& \int_\chi^{\chi_H} {\rm d}\chi'\, p_i(\chi') \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
-\end{align}
-Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions.
-\subsection{Using an analytic Model}
-For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal. Following \citet{2006APh....26...91V}, we estimate
-\[
-\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
-\]
-\todo{Maybe implement redshift-dependent index?}
-Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
-
-%For a pair of galaxies that we use to measure the correlation function, it is crucial to determine whether those two galaxies lie within the same pointing.
-We want to define a function $E(\theta)$ that determines
-
-Let $N(\b \theta)$ be the number-density per tile and $W(\b \theta)$ the weighting of average shear.
-The observed correlation function $\xi^{\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{\rm const}$ via
-\begin{align*}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{\la N(\b 0)N(\b \theta)\gammao_{\rm t}(\b 0)\gammao_{\rm t}(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \pm \frac{\la N(\b 0)N(\b \theta)\gammao_\times(\b 0)\gammao_\times(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \\
- = & \frac{\la N(\b 0)N(\b \theta)W(\b 0)W(\b \theta)\ra}{\la N(\b 0)N(\b \theta)\ra} \xi_{\pm}^{\rm const}(\theta) \, .
- \end{align*}
- Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
-We want to denote the probability that a random pair of galaxies of distance $\theta$ lie in the same pointing with $E(\theta)$.
-An analytical expression for this function is surprisingly hard to obtain, but it can easily be calculated to arbitrary accuracy, following the procedure explained in Appendix \ref{sec:details on etheta}.
-The function is depicted in Figure \ref{fig:eoftheta_lin}.
-
- \begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{images/eoftheta.png}
- \caption{Probability that a random pair of galaxies of distance $\theta$ lie in the same pointing.}
- \label{fig:eoftheta_lin}
- \end{figure}
-
-We again parametrize the number density $N(\b \theta)=\la N \ra (1+n(\b \theta))$ and the weight $W(\b \theta)=1+w(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n(\b \theta)$ as a locally constant function with average $\la n \ra = 0$.
-We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get
- \begin{align}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta) \\
-\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, . \nonumber
- \label{eq:ffunct}
-\end{align}
-\todo{The formula for a cross-correlation of different bins is much longer, but follows the same principle. Maybe put it into the Appendix?}
-We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.
-
-However, as a survey of constant depth is completely unrealistic, also the modelled correlation function will be subject to the same effect.
-If we assume the same redshift-distributions for galaxies as in the case of varying depth, and just assert that those changes are not correlated with position, we get
-\begin{equation}
-\xi_\pm = (1+2\la nw\ra)\xi_\pm^{\rm const}\, .
-\end{equation}
-The ratio of modelled and observed correlation function thus becomes: \begin{align}
-\frac{\xi_\pm}{\xi_\pm^{\rm obs}} = & \frac{\left(1+2\la nw\ra\left)\left(1+E(\theta)\la n^2\ra\right)\right.\right.}{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]} \\
-\equiv & F(\theta) \, .
-\end{align}
-%It is interesting to note that $F(\theta)=1$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. 
-We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts. 
-\subsection{Using a semi-analytic Model}
-The analysis of data from the Kilo-Degree Survey showed that the redshift-distribution of sources was highly correlated with the depth in the $r$-band.
-We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-Now for each percentile $i$ and each tomographic redshift bin $z$ we can extract a weighted number density of galaxies $N_i(z)$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p_i(z)$.
-Using \eqref{eq:xipm-pkappa}, we can for each set of percentiles $i,j$ and redshift bins $z_1,z_2$ compute the shear correlation function $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.\todo{Should we cite \textsc{nicaea} here?} When we compute the measured shear correlation function of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process).
-If, for a single pair of galaxies, one galaxy lies in the $i$-th percentile of redshift bin $z_1$ and the second one lies in the $j$-th percentile of redshift bin $z_2$, then their contribution to the observed correlation function is, on average, $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.
-This means that if we know each of those single correlation functions, we can reconstruct the total correlation function via a weighted average of the single functions.
-As an example, if we want to calculate the correlation function between tomographic bins $z_1$ and $z_2$ and pick a galaxy from bin $z_1$, the probability of this galaxy being in the $i$-th percentile of $z_1$ is proportional to $N_i(z_1)$.
-Now let the second galaxy be in bin $z_2$ and of distance $\theta$ to the first.
-If we imagine a thin annulus of radius $\theta$ around the first galaxy, then the number of galaxies in this annulus, that lie within the same pointing as the first galaxy, is proportional to $E(\theta)N_i(z_2)$, whereas the number of galaxies that lie in a different pointing is $[1-E(\theta)]\la N(z_2)\ra$, where $\la N(z_2)\ra$ is the average number density in redshift bin $z_2$.
-If the galaxy lies within a different pointing, the chances of it being in the $j$-th percentile are again just proportional to $N_j(z_2)$.
-We conclude that if we sum the single correlation functions $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$ according to these weightings, we can simulate the observed correlation function that accounts for the variation in optical depth via
-\begin{align}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \la N(z_2)\ra\sum_{j=1}^{10}\frac{  N_j(z_2)}{\sum_k N_k(z_2)} \big[1-E(\theta)\big]\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\} \nonumber \\
- = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \sum_{j=1}^{10}\frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\}\, ,
-\label{eq:correctionfunction1}
-\end{align}
-with the normalization
-\[
-C = \sum_{i=1}^{10} N_i(z_1) \bigg[ E(\theta)  N_i(z_2) + \sum_{j=1}^{10} \frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\bigg]\,.
-\]
-A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
-If we want to compute this for all 5 redshift bins of the KiDSV-survey, this forces us to calculate 1265 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive).
-However, if we examine Equation \eqref{eq:lenseff}, we see that it is linear in its second argument, which in turn makes Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} bilinear in their second and third arguments.
-This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation function of that.
-As an example, the following equation holds: \[
-N_j\xi_\pm[\theta,p_i,p_j]+N_k\xi_\pm[\theta,p_i,p_k] = (N_j+N_k)\,\xi_\pm\left[\theta,p_i,\frac{N_jp_j+N_kp_k}{N_j+N_k}\right]\, .
-\]
-Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
-\begin{equation}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{C}\bigg\{ E(\theta)\sum_{i=1}^{10} N_i(z_1)N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] +\frac{1}{10}\big[1-E(\theta)\big]\xi_\pm\left[\theta,p(z_1),p(z_2)\right]N(z_1)N(z_2)\bigg\}\, .
-\label{eq:correctionfunction2}
-\end{equation}
-Here, we defined the \textit{average redshift distribution} $p(z)$ and \textit{combined number density} $N(z)$ of tomographic bin $z$ as \[
-p(z):= \frac{\sum_i N_i(z)p_i(z)}{\sum_i N_i(z)}\, , \qquad N(z):=\sum_i N_i(z)\, .
-\]
-\todo{Maybe label the $N(z)$ differently to avoid confusion with $\la N(z)\ra$?}
-For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
-We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N(z_1)N(z_2)$ and thus \[
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{N(z_1)N(z_2)}\xi_\pm\left(\theta,n(z_1),n(z_2)\right)N(z_1)N(z_2) = \xi_{\pm,z_1,z_2}(\theta)\, ,
-\]
-so on large scales our observed correlation function agrees with the one that we would usually calculate.
-\section{Results}
-\label{sec:results}
-We applied both our methods to data from the KiDSV-450 survey and computed the ratio of observed and modeled correlation functions.
-Furthermore, we have conducted a simulation using ray-tracing through the millenium simulations (?)\todo{I should ask catherine about what exactly she did for the simulations or maybe even ask her to write this part of the paper?}.
-As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
-The result can be seen in Figure \ref{fig:all_xis}.
-	\begin{figure}
-	\centering
-	\includegraphics[width=1\textwidth]{images/xis_111.png}
-	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.}
-	\label{fig:all_xis}
-	\end{figure}
-We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
-We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk?
-Maybe in the appendix to avoid too many Figures?} The simulations seem to be in rough agreement with the models, but there are some features that can not be explained.
-Especially we observe that the ratios of the correlation functions for large values of $\theta$ seem to consistently surpass unity, which can not be explained by our models.
-
-As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model.
-Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
-As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.\todo{Maybe expand this to more parameters?}  As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties.
-However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area.
-As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.
-
-To estimate the B-Modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare \citet{2010A&A...520A.116S}), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
-We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KiDSV-450 survey for the same range in $\theta$.
-The real B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant.
-Given these facts, we conclude that the creation of B-Modes due to varying depth in the KiDS survey is not significant.
-However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, that show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).
-
-\begin{figure}
-\centering
-\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/bmodes.pdf}
-\caption{The $B$-modes created by a variation in survey-depth.
-We used the logarithmic COSEBIs described in \citet{2010A&A...520A.116S} with a range from $\theta_{\rm min} = 0.5\arcmin$ to $\theta_{\rm max} = 100\arcmin$.}
-\label{fig:bmodes_cosebi}
-\end{figure}
-
 \section{Discussion}
@@
 It can also be responsible for the occurence of $B$-Modes, although only to an insignificant amount.
-
-%--------------------------------------------------------------------
-
-\begin{acknowledgements}
-Something should probably be put in here...
-\end{acknowledgements}
-
-\bibliographystyle{aa}
-\bibliography{cite}
-\begin{appendix}
-\section{Detailed Calculations}
-\subsection{Calculation of the Power Spectrum}
-In this Section we will perform the calculation for the observed power spectrum \todo{I need to add cdots for scalar products in this section...} $P^{\text{obs}}(\b \ell)$.
-For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$.
-In reality, finite field effects would play a role here.
-We begin with the calculation of the correlation for the Fourier transformed shear:
-\begin{align}
-\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta')\ra\nonumber\\
- = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta') \int \frac{\text{d}^2\b k}{(2\pi)^2}\int \frac{\text{d}^2\b k'}{(2\pi)^2}\, \hat{\gamma}(\b k)\hat{\gamma}^*(\b k')\exp(-i\b k\b \theta+i\b k'\b \theta')\ra \nonumber\\
-= & \la \int \text{d}^2\b \theta \int \text{d}^2\b \theta' \int \frac{\text{d}^2\b k}{(2\pi)^2} \int \frac{\text{d}^2\b k'}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b k') \exp[i(\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b k'\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
-  = & \la \int \frac{\text{d}^2\b k}{(2\pi)^2} \, P(\b k) \int \text{d}^2\b \theta\, W(\b \theta)\exp[i\b \theta(\b \ell-\b k)]\int \text{d}^2\b \theta'\, W(\b \theta') \exp[-i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
-  = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k)\widehat{W}(\b \ell-\b k)\widehat{W}^* (\b \ell'-\b k)\ra
-\end{align}
-It is important to keep in mind that the ensemble averages of the weight function are independent of the ensemble averages of the shear values, meaning $\la W(\b \theta)\gamma(\b \theta)\ra = \la W(\b \theta)\ra \la \gamma(\b \theta)\ra$.
-We can define $W(\b \theta)=1+w(\b\theta)$ with $\la w(\b \theta)\ra = 0$, which leads to the expession
-\begin{align}
-\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big( \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big)\right.\right.
-\nonumber\\
- & \qquad \left.\left. + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
- = & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \big[ \la \hat{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \hat{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\big] + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
-\overset{(*)}{=} & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
-\label{eq:pobs1}
-\end{align}
-where in $(*)$ we have used that the average $\la \hat{w}(\b \ell)\ra$ vanishes.
-Up until now, we have not specified our weight-function $w$. So we now parametrize it as \begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
-1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
-0 \qquad \text{else}
-\end{cases}.
-\end{equation}
-Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier-Transform we compute: \begin{equation}
-\hat{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-i \b \ell L\b \alpha) \widehat{\Xi}(\b \ell)\, ,
-\end{equation}
-where
-\begin{equation}
-\widehat{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
-\end{equation}
-is a 2-dimensional sinc function.
-Assuming an uncorrelated weight-distribution $\left(\la w_{\b \alpha} w_{\b \beta}\ra = 0\text{ for }\b \alpha\neq\b \beta\right)$ and setting $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ for each $\b \alpha$, we get
-\begin{align}
-\la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra = & \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-i(\b \ell - \b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k) \exp[i(\b \ell' - \b k)L\b \beta]\, \widehat{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
- = & \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)\widehat{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
-\end{align}
-Using this result, we can obtain the observed power spectrum \begin{equation}
-P^{\rm{obs}}(\b\ell) = \frac{1}{(2\pi)^2}\int\d^2\ell' \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\, ,
-\end{equation}
-by performing the $\b \ell'$-integration in \eqref{eq:pobs1}:
-\begin{align}
-P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha+i(\b \ell'-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell-\b k)\widehat{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
-= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widehat{\Xi}^*(\b \ell'-\b k)\exp[i(\b \ell'- \b k)L\b \alpha] \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widehat{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widehat{\Xi}(\b \ell-\b k)P(\b k)\, ,
-\end{align}
-which is a 2-dimensional convolution of the power spectrum and the 2-dimensional sinc function.
-\label{sec:calc of PS}
-\subsection{Details on the function $E(\theta)$}
-\label{sec:details on etheta}
-The function $E(\theta)$ is of central importance in this model, so we want to explain how to obtain it.
-It describes, given a pair of galaxies with distance $\theta$, the probability that they are in the same pointing.
-We obtain the function in the following way:
-
-Given one square field of length 1 and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
-As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
-The volume of this square equals \begin{equation}
-\tilde{V}(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, ,
-\end{equation} where $\phi$ represents the angle of the vector $\b\theta$. To exclude negative Volumes (which would occur when $|\b\theta|>1$ holds), we nead to add the Heaviside theta function $H$:
-\begin{equation}
-V(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big] H\big[1-|\b\theta|\cos(\phi)\big]\,H\big[1-|\b\theta|\sin(\phi)\big]\, .
-\label{eq:eoftheta1}
-\end{equation} 
-To obtain the function $E(\theta)$, we need to average Equation \eqref{eq:eoftheta1} over all angles $\phi$.
-While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
-\begin{align}
-E(\theta) = & \frac{4}{2\pi}\int_0^{\frac{\pi}{2}}\d\phi\, V(|\b\theta|,\phi) = \frac{2}{\pi}\begin{cases}
-\int_0^{\frac{\pi}{2}} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , & |\b\theta|\leq 1 \\
-\int_{\arccos(|\b\theta|^{-1})}^{\arcsin(|\b\theta|^{-1})} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , \quad & 1\leq |\b\theta| \leq \sqrt{2} \\
-0\, , & \sqrt{2}\leq\theta
-\end{cases} \nonumber\\
- = & \begin{cases}
-\frac{\pi + (\theta-4)*\theta}{\pi}\, , & \theta \leq 1 \\
-\frac{2[-1+2\sqrt{1-\theta^{-2}}*2\theta - \theta^2/2 - \arccos(\theta^{-1}) + \arcsin(\theta^{-1})]}{\pi}\, , & 1\leq \theta \leq \sqrt{2} \\
-0\, , & \sqrt{2}\leq \theta
-\end{cases}\, .
-\end{align}
-\begin{figure}
-    \centering
-    \def\svgwidth{200pt}    
-    \input{images/eoftheta_new.pdf_tex}  
-    \caption{Graphic representation on how to obtain the function $E(\theta)$.
-For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
-    \label{fig:explain_etheta}
-\end{figure}
-\subsection{Calculation of the shear correlation functions}
-\label{sec:calc of xipm}
-Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation function via \begin{equation}
-\xi_+(\theta) = \frac{\sum_{a,b}w_aw_b\epsilon_a\epsilon_b^*\Delta(\b\theta_a-\b\theta_b)}{\sum_{a,b}w_aw_b\Delta(\b\theta_a-\b\theta_b)}\, .
-\label{eq:xip_from_observations}
-\end{equation}
-Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky. We have defined the function $\Delta$ as \[
-\Delta(\b\theta_a-\b\theta_b) = \begin{cases}
-1, \,\, & |\b\theta_a-\b\theta_b| \in [\theta,\theta+{\rm d}\theta] \\
-0, & \text{ else}
-\end{cases}\, ,
-\]
-where we assume ${\rm d}\theta \ll \theta$.
-When we now separate our galaxy samples into the ten percentiles $I$ defined above, and denote the galaxies from sample $a$ that are in pointing $i$ with $a_i$, the numerator in Equation \eqref{eq:xip_from_observations} transforms to:
-\begin{align*}
- & \sum_{i,j=1}^{10} \sum_{a_i,b_j} w_{a_i}w_{b_j}\epsilon_{a_i}\epsilon_{b_j}^*\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
- = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \sum_{j=1}^{10} \sum_{b_j} w_{b_j}\epsilon_{a_i}\epsilon_{b_j}\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
- = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ \sum_{j=1}^{10} \sum_{b_j\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij \right]
-\end{align*}
-We take the ensemble average of that equation in the sense that we assume that the product of the ellipticities of the galaxies are equal to their respective shear correlation functions, namely $\xi_+^{ij}\equiv \epsilon_{a_i}\epsilon_{b_j}^*$ for all $a_i$ and $b_j$.
-
-Let $b_j\in P_{a_i}$ denote all $b_j$ that lie in the same pointing as the $a_i$.
-We observe that the left term is zero for $i\neq j$, as only galaxies of the same percentile can lie in the same pointing.
-The term $\sum_{b_i\in P_{a_i}}\deltafuncij$ now is the number of galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a_i$, which is equal to the number of galaxies in the whole pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$.
-The prefactor $w_{b_i}$ transforms the number of galaxies to the \emph{weighted number density} of galaxy sample $b$ in percentile $i$, or $N_i(b)$, so the numerator now reads:
-\begin{align*}
-\sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\xi_+^{ij} \right]
-\end{align*}
-
- A similar argument can be made for the right term: Assuming for a second that all pointings outside of the one where galaxy $a_i$ is in are of percentile $j^*$, the right hand side would read \[
-\sum_{b_{j^*}\not\in P_{a_i}} w_{b_{j^*}} \Delta(\b\theta_{a_i}-\b\theta_{b_{j^*}})\xi_+^{i{j^*}} = 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j^*}(b)\xi_+^{i{j^*}}\, .
- \]  
- Taking the ensemble average of all realisations of depth-distributions, we can just denote the probability that a pointing neighbouring one of percentile $i$ is of percentile $j$ as $P(j | i,\theta)$.
-The numerator then reads \[
- \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta)\, 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
- \]
- In our case we assume an infinite number of randomly distributed fields, so $P(j | i,\theta)=1/10$ holds.
-However, for a finite survey the footprint of depth-distributions seems to be of importance, as due to a limited number of fields the $P(j | i,\theta)$ does not equate its expectation value.
-For smaller surveys (or surveys with correlated depth-distributions) it seems appropriate to adjust this parameter.
-\todo{Wait for catherines 450deg${}^2$ simulations, maybe they are big enough?}
-
- If we define $A$ as the (arbitrarily big) survey area, we can set \[
- \sum_{a_i} w_{a_i} = A\, N_i(a)
- \]
- and see that the numerator becomes \[
- 2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
- \]
- The exact line of argumentation can be applied to the denominator, which then reads: \[
-  2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b) + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b) \right]\, .
- \]
-Taking the ratio of the two quantities, and setting $P(j | i,\theta)=1/10$, we receive Equation \eqref{eq:correctionfunction1}.
-\section{Additional Figures}
-\subsection{Results of the MCMC}
-\begin{figure}[h]
-\centering
-	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
-	\caption{Bias in the parameters for a KiDS-like Survey.}
-	\label{fig:mcmc_kids}
-\end{figure}  
-\begin{figure}[h]
-\centering
-	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
-	\caption{Bias in the parameters for a Euclid-like Survey.}
-	\label{fig:mcmc_euclid}
-\end{figure}  
-\todo{Put both in one plot? Maybe put reference MC simulation where $\xi_\pm$ was not changed?}
-\end{appendix}
-\end{document}
-%

### 2019-04-03 appendix.tex
Create appendix.tex

--- 2019-04-03 paperdraft.tex
@@
-\documentclass[referee]{aa} % for a referee version
-%\documentclass[onecolumn]{aa} % for a paper on 1 column  
-%\documentclass[longauth]{aa} % for the long lists of affiliations 
-%\documentclass[letter]{aa} % for the letters 
-%\documentclass[bibyear]{aa} % if the references are not structured 
-%                              according to the author-year natbib style
-
-%
-%\documentclass{aa}  
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\ben}{\begin{enumerate}}
-\newcommand{\een}{\end{enumerate}}
-\newcommand{\bi}{\begin{itemize}}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\bmi}[1]{\begin{minipage}{#1 cm}}
-\newcommand{\emi}{\end{minipage}}
-\renewcommand{\[}{\begin{equation}}
-\renewcommand{\]}{\end{equation}}
-
-\renewcommand{\rm}{\mathrm}
-\def\inv{^{-1}}
-\def\({\left(}
-\def\r){\right)}
-\def\b#1{\bm{#1}}
-\def\Dd{D_{\text{d}}}
-\def\Dds{D_{\text{ds}}}
-\def\Ds{D_{\text{s}}}
-\def\la{\left<}
-\def\ra{\right>}
-\def\gammao{\gamma^{\text{obs}}}
-\def\gammaoh{\hat{\gamma}^{\text{obs}}}
-\def\epsilonsij{\epsilon_{a_i}\epsilon_{b_j}^*}
-\def\epsilonsii{\epsilon_{a_i}\epsilon_{b_i}^*}
-\def\deltafuncij{\Delta(\b\theta_{a_i}-\b\theta_{b_j})}
-\def\d{\rm{d}}
-
-%\newcommand{\todo}{\emph}
-
-\usepackage{bm}
-\usepackage{verbatim}
-%
-\usepackage{graphicx}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{txfonts}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage[options]{hyperref}
-% To add links in your PDF file, use the package "hyperref"
-% with options according to your LaTeX or PDFLaTeX drivers.
-%
-\usepackage{todonotes}
-
-\begin{document}
-
-   \title{The Effects of Varying Depth in Cosmic Shear Surveys}
-
-%   \subtitle{}
-
-   \author{S. Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
-          \and Peter Schneider\inst{1} 
-          \and Hendrik Hildebrandt\inst{2,1}
-          \and Catherine Heymans\inst{3} 
-          \and Marika Asgari\inst{3}
-          \todo{order of authors?, KiDS-Authors?}
-          }
-   \institute{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany 
-\and 
-Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany \and
-Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de}
-             }
-
-   \date{Received XXX; accepted XXX}
-
-  \abstract
-% context (optional)
-   {Cosmic shear proves to be a powerful tool to study the properties of the local Universe.
-The discrepancy in the parameter $S_8$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases.
-% aims
-   Especially ground-based surveys are subject to a variation in depth.
-We want to understand and quantify the resulting effects.
-In particular, we check if they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
-% methods
-   We construct a semi-analytic model to estimate the impact on the shear correlation function and analyze the implications for cosmological parameters.
-Furthermore we construct COSEBIs of the correlation functions to quantify the occuring B-Modes.
-% results
-   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$.
-However, the parameter $S_8$ is robust against this modification.
-We also report the occurrence of B-Modes, although not to a significant degree.
-% conclusions (optional)
-   We conclude that the effects of varying optical depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}
-
-   \keywords{gravitational lensing --
-                weak lensing --
-                cosmic shear
-               }
-
-   \maketitle
-
-%
-%-------------------------------------------------------------------
-
-\section{Introduction}
-The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the $\Lambda$CDM Model and determine its parameters.
-Contrary to the analysis of the Cosmic Microwave Background \citep{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
-Current Cosmic Shear surveys are especially sensitive to the paramter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
-It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$,
-%\citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data,
-\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2017MNRAS.465.1454H} report $S_8 = 0.745\pm 0.038$ from KiDS data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$.
-Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data.
-This discrepancy could be a statistical coincidence, a sign of new physics or the manifestation of an unknown systematic effect.
-\todo{Citations..
-\citet{2017MNRAS.464.1676A} has a few...}
-
-To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citet{2002ApJ...568...20C,2002A&A...389..729S}.
-To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
-As \citet{2017MNRAS.465.1454H} report the significant detection of B-modes, it is well motivated to check for possible systematics that are yet unaccounted for.
-Note that the non-existence of B-modes does not imply that the sample is free of remaining systematics.
-
-One systematic effect is the variation of depth in a survey.
-While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions, that are found in ground-based surveys.
-To first order, this variation can be modelled by a step-like depth function that varies from pointing to pointing.
-In this work we assume the specifications of the Kilo-Degree Survey, namely a collection of $1\,\text{deg}^2$ square fields.
-Furthermore we neglect boundary effects.
-
-In Section \ref{sec:modelling_single_lens} we will introduce a simple toy model to understand this effect and analyze the impact on the power spectrum.
-In Section \ref{sec:xipm} we will estimate the effect on the shear correlation functions $\xi_\pm$ using two different models.
-We will present our results in Section \ref{sec:results}.
-In Section \ref{sec:discussion} we will discuss our results and comment on the impacts of our used simplifications.
-We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
-
-\section{Modelling the Power Spectrum}
-\label{sec:modelling_single_lens}
-For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
-If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm ds}/D_{\rm s}$.
-% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
-%\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
-%\]
-
-%Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate.
-Assuming that the optical depth, and thus the source redshift populations, vary between pointing, an observer will measure a shear-signal that is modified by a depth-function $W(\bm{\theta}) = 1-w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-The reconstruction of the observed convergence $\kappa^{\rm obs}$ will thus not yield the original convergence.
-In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part.
-This allows us to separate our received signal into E- and B-modes following \[
-%	\kappa = \kappa^E+i\kappa^B\, ,
-%\]
-%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
-%2002A&A...389..729S SRC
-
-\subsection{Effects on the Power Spectrum}
-Assuming that the depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a locally constant depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-In accordance to the definition of the shear power spectrum \begin{equation}
-(2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) = \la \hat{\gamma}(\b\ell)\hat{\gamma}(\b\ell')\ra \, ,
-\end{equation}
-we define the observed power spectrum via \begin{equation}
-P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \, .
-\end{equation}
-Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
-To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as
-\begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
-1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
-0 \qquad \text{else}
-\end{cases},
-\label{eq:defweightf}
-\end{equation}
-where $L$ is the length of one pointing.
-Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
-\begin{equation}
-P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)P(\b k)\, ,
-\end{equation}
-where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function.
-The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with the fourier transfrom of a box-function, scaling with the variance of the geometric lensing efficiency $\la \frac{D_{\rm ds}}{D_{s}}\ra$.
-In particular, the power spectrum is not isotropic anymore.
-Following \citet{2002A&A...389..729S}, it would be interesting to extract E- and B-mode information out of this power spectrum, however \citet{2010A&A...520A.116S} present a more sophisticated decomposition of E- and B-modes, that can also be applied to real data using the shear correlation function, so instead we want to focus our efforts on these parts.
-\section{Modelling the shear correlation function}
-\label{sec:xipm}
-A convenient way to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
-\xi_\pm = \la \gamma_{\rm t}\gamma_{\rm t}\ra \pm \la \gamma_\times\gamma_\times\ra \, .
-\]
-They are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear-measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions.
-Cosmologically, given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation function from the underlyting matter power spectrum $P_\delta$ via \todo{Citation!}\begin{align}
-\label{eq:xipm-pkappa}
-\xi_\pm[\theta,p_i,p_j] =& \int_0^\infty \frac{{\rm d}l\,l}{2\pi}J_{0,4}(l\theta)P(l,p_i,p_j)\, , \\
-\label{eq:pkappa-pdelta/lenseff}
-P(l,p_i,p_j) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_h} {\rm d}\chi\frac{g(\chi,p_i)g(\chi,p_j)}{a^2(\chi)}P_\delta\left(\frac{l}{f_K(\chi)},\chi\right)\, , \\
-\label{eq:lenseff}
-g(\chi,p_i) =& \int_\chi^{\chi_H} {\rm d}\chi'\, p_i(\chi') \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
-\end{align}
-Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions.
-\subsection{Using an analytic Model}
-For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal. Following \citet{2006APh....26...91V}, we estimate
-\[
-\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
-\]
-\todo{Maybe implement redshift-dependent index?}
-Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
-
-%For a pair of galaxies that we use to measure the correlation function, it is crucial to determine whether those two galaxies lie within the same pointing.
-We want to define a function $E(\theta)$ that determines
-
-Let $N(\b \theta)$ be the number-density per tile and $W(\b \theta)$ the weighting of average shear.
-The observed correlation function $\xi^{\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{\rm const}$ via
-\begin{align*}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{\la N(\b 0)N(\b \theta)\gammao_{\rm t}(\b 0)\gammao_{\rm t}(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \pm \frac{\la N(\b 0)N(\b \theta)\gammao_\times(\b 0)\gammao_\times(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \\
- = & \frac{\la N(\b 0)N(\b \theta)W(\b 0)W(\b \theta)\ra}{\la N(\b 0)N(\b \theta)\ra} \xi_{\pm}^{\rm const}(\theta) \, .
- \end{align*}
- Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
-We want to denote the probability that a random pair of galaxies of distance $\theta$ lie in the same pointing with $E(\theta)$.
-An analytical expression for this function is surprisingly hard to obtain, but it can easily be calculated to arbitrary accuracy, following the procedure explained in Appendix \ref{sec:details on etheta}.
-The function is depicted in Figure \ref{fig:eoftheta_lin}.
-
- \begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{images/eoftheta.png}
- \caption{Probability that a random pair of galaxies of distance $\theta$ lie in the same pointing.}
- \label{fig:eoftheta_lin}
- \end{figure}
-
-We again parametrize the number density $N(\b \theta)=\la N \ra (1+n(\b \theta))$ and the weight $W(\b \theta)=1+w(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n(\b \theta)$ as a locally constant function with average $\la n \ra = 0$.
-We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get
- \begin{align}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta) \\
-\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, . \nonumber
- \label{eq:ffunct}
-\end{align}
-\todo{The formula for a cross-correlation of different bins is much longer, but follows the same principle. Maybe put it into the Appendix?}
-We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.
-
-However, as a survey of constant depth is completely unrealistic, also the modelled correlation function will be subject to the same effect.
-If we assume the same redshift-distributions for galaxies as in the case of varying depth, and just assert that those changes are not correlated with position, we get
-\begin{equation}
-\xi_\pm = (1+2\la nw\ra)\xi_\pm^{\rm const}\, .
-\end{equation}
-The ratio of modelled and observed correlation function thus becomes: \begin{align}
-\frac{\xi_\pm}{\xi_\pm^{\rm obs}} = & \frac{\left(1+2\la nw\ra\left)\left(1+E(\theta)\la n^2\ra\right)\right.\right.}{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]} \\
-\equiv & F(\theta) \, .
-\end{align}
-%It is interesting to note that $F(\theta)=1$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. 
-We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts. 
-\subsection{Using a semi-analytic Model}
-The analysis of data from the Kilo-Degree Survey showed that the redshift-distribution of sources was highly correlated with the depth in the $r$-band.
-We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-Now for each percentile $i$ and each tomographic redshift bin $z$ we can extract a weighted number density of galaxies $N_i(z)$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p_i(z)$.
-Using \eqref{eq:xipm-pkappa}, we can for each set of percentiles $i,j$ and redshift bins $z_1,z_2$ compute the shear correlation function $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.\todo{Should we cite \textsc{nicaea} here?} When we compute the measured shear correlation function of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process).
-If, for a single pair of galaxies, one galaxy lies in the $i$-th percentile of redshift bin $z_1$ and the second one lies in the $j$-th percentile of redshift bin $z_2$, then their contribution to the observed correlation function is, on average, $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.
-This means that if we know each of those single correlation functions, we can reconstruct the total correlation function via a weighted average of the single functions.
-As an example, if we want to calculate the correlation function between tomographic bins $z_1$ and $z_2$ and pick a galaxy from bin $z_1$, the probability of this galaxy being in the $i$-th percentile of $z_1$ is proportional to $N_i(z_1)$.
-Now let the second galaxy be in bin $z_2$ and of distance $\theta$ to the first.
-If we imagine a thin annulus of radius $\theta$ around the first galaxy, then the number of galaxies in this annulus, that lie within the same pointing as the first galaxy, is proportional to $E(\theta)N_i(z_2)$, whereas the number of galaxies that lie in a different pointing is $[1-E(\theta)]\la N(z_2)\ra$, where $\la N(z_2)\ra$ is the average number density in redshift bin $z_2$.
-If the galaxy lies within a different pointing, the chances of it being in the $j$-th percentile are again just proportional to $N_j(z_2)$.
-We conclude that if we sum the single correlation functions $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$ according to these weightings, we can simulate the observed correlation function that accounts for the variation in optical depth via
-\begin{align}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \la N(z_2)\ra\sum_{j=1}^{10}\frac{  N_j(z_2)}{\sum_k N_k(z_2)} \big[1-E(\theta)\big]\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\} \nonumber \\
- = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \sum_{j=1}^{10}\frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\}\, ,
-\label{eq:correctionfunction1}
-\end{align}
-with the normalization
-\[
-C = \sum_{i=1}^{10} N_i(z_1) \bigg[ E(\theta)  N_i(z_2) + \sum_{j=1}^{10} \frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\bigg]\,.
-\]
-A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
-If we want to compute this for all 5 redshift bins of the KiDSV-survey, this forces us to calculate 1265 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive).
-However, if we examine Equation \eqref{eq:lenseff}, we see that it is linear in its second argument, which in turn makes Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} bilinear in their second and third arguments.
-This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation function of that.
-As an example, the following equation holds: \[
-N_j\xi_\pm[\theta,p_i,p_j]+N_k\xi_\pm[\theta,p_i,p_k] = (N_j+N_k)\,\xi_\pm\left[\theta,p_i,\frac{N_jp_j+N_kp_k}{N_j+N_k}\right]\, .
-\]
-Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
-\begin{equation}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{C}\bigg\{ E(\theta)\sum_{i=1}^{10} N_i(z_1)N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] +\frac{1}{10}\big[1-E(\theta)\big]\xi_\pm\left[\theta,p(z_1),p(z_2)\right]N(z_1)N(z_2)\bigg\}\, .
-\label{eq:correctionfunction2}
-\end{equation}
-Here, we defined the \textit{average redshift distribution} $p(z)$ and \textit{combined number density} $N(z)$ of tomographic bin $z$ as \[
-p(z):= \frac{\sum_i N_i(z)p_i(z)}{\sum_i N_i(z)}\, , \qquad N(z):=\sum_i N_i(z)\, .
-\]
-\todo{Maybe label the $N(z)$ differently to avoid confusion with $\la N(z)\ra$?}
-For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
-We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N(z_1)N(z_2)$ and thus \[
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{N(z_1)N(z_2)}\xi_\pm\left(\theta,n(z_1),n(z_2)\right)N(z_1)N(z_2) = \xi_{\pm,z_1,z_2}(\theta)\, ,
-\]
-so on large scales our observed correlation function agrees with the one that we would usually calculate.
-\section{Results}
-\label{sec:results}
-We applied both our methods to data from the KiDSV-450 survey and computed the ratio of observed and modeled correlation functions.
-Furthermore, we have conducted a simulation using ray-tracing through the millenium simulations (?)\todo{I should ask catherine about what exactly she did for the simulations or maybe even ask her to write this part of the paper?}.
-As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
-The result can be seen in Figure \ref{fig:all_xis}.
-	\begin{figure}
-	\centering
-	\includegraphics[width=1\textwidth]{images/xis_111.png}
-	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.}
-	\label{fig:all_xis}
-	\end{figure}
-We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
-We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk?
-Maybe in the appendix to avoid too many Figures?} The simulations seem to be in rough agreement with the models, but there are some features that can not be explained.
-Especially we observe that the ratios of the correlation functions for large values of $\theta$ seem to consistently surpass unity, which can not be explained by our models.
-
-As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model.
-Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
-As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.\todo{Maybe expand this to more parameters?}  As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties.
-However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area.
-As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.
-
-To estimate the B-Modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare \citet{2010A&A...520A.116S}), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
-We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KiDSV-450 survey for the same range in $\theta$.
-The real B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant.
-Given these facts, we conclude that the creation of B-Modes due to varying depth in the KiDS survey is not significant.
-However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, that show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).
-
-\begin{figure}
-\centering
-\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/bmodes.pdf}
-\caption{The $B$-modes created by a variation in survey-depth.
-We used the logarithmic COSEBIs described in \citet{2010A&A...520A.116S} with a range from $\theta_{\rm min} = 0.5\arcmin$ to $\theta_{\rm max} = 100\arcmin$.}
-\label{fig:bmodes_cosebi}
-\end{figure}
-
-\section{Discussion}
-\label{sec:discussion}
-With our semi-analytic model we try to describe the impacts of varying depth in ground-based surveys. During our analysis we have assumed a few simplifications, which we will discuss.
-\begin{enumerate}
-\item We implemented a variation in depth that only depends on the pointing.
-However, in reality galactic extinction, CCD imperfections, dithering strategies and other factors also influence the depth on different scales.
-Although the variation between pointings is the dominating factor, a complete analysis implementing those factors could yield a slightly different result.
-\item In our main analysis we assumed an infinite number of fields.
-This ignores boundary effects that would arise in the vincinity of the edge of a footprint (there finding a galaxy outside of the same pointing would be less likely).
-Also, another effect is ignored: If one has a number of $N$ fields in each percentile, and one galaxy is in a pointing of a certain percentile, then the probability that a different pointing is of the \emph{same} percentile is reduced by the factor $(N-1)/N$.
-However, we modeled the second effect, and already at 100 pointings it barely makes any difference.
-We did not model the boundary effects, but we assume that they are likewise neglible.
-\todo{This needs to be rewritten to account for the new insights.}
-\item We have assumed that the depth of neighbouring pointings is uncorrelated. While there is no reason not to assume that, we have not yet verified that this is indeed the case.
-\item In our Monte Carlo simulations we have only had $\Omega_{\rm m}$ and $\sigma_8$ as free parameters.
-While we do not expect most other parameters to make a difference, baryonic feedback and/or intrinsic alignments also change the correlation functions on small scales, so it is definitely possible that in a Monte Carlo chain including free parameters for these effects, those would change to mitigate the varying depth, and the impact on the actual cosmological parameters would be much smaller.
-\end{enumerate}
-We have determined that the effects of varying depth are not significant for the KiDSV-450 survey.
-For a Euclid-like survey they will play an important role, but before a model is implemented in such a precise survey, one should revise the used simplifications, especially the first one.
-We suspect that it should be possible to account for different aspects of varying optical depth by just modifying the function $E(\theta)$.
-
-However, for the parameter $S_8$ this effect is insignificant, which in particular means that a variation in depth can not explain the discrepancies between the analyses of the CMB and those of the local universe.
-It can also be responsible for the occurence of $B$-Modes, although only to an insignificant amount.
-
-%--------------------------------------------------------------------
-
-\begin{acknowledgements}
-Something should probably be put in here...
-\end{acknowledgements}
-
-\bibliographystyle{aa}
-\bibliography{cite}
-\begin{appendix}
 \section{Detailed Calculations}
@@
 \todo{Put both in one plot? Maybe put reference MC simulation where $\xi_\pm$ was not changed?}
-\end{appendix}
-\end{document}
-%

### 2019-04-03 paperdraft.tex
Update paperdraft.tex

@@
 %-------------------------------------------------------------------
-
-\section{Introduction}
-The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the $\Lambda$CDM Model and determine its parameters.
-Contrary to the analysis of the Cosmic Microwave Background \citep{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
-Current Cosmic Shear surveys are especially sensitive to the paramter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
-It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$,
-%\citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data,
-\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2017MNRAS.465.1454H} report $S_8 = 0.745\pm 0.038$ from KiDS data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$.
-Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data.
-This discrepancy could be a statistical coincidence, a sign of new physics or the manifestation of an unknown systematic effect.
-\todo{Citations..
-\citet{2017MNRAS.464.1676A} has a few...}
-
-To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citet{2002ApJ...568...20C,2002A&A...389..729S}.
-To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
-As \citet{2017MNRAS.465.1454H} report the significant detection of B-modes, it is well motivated to check for possible systematics that are yet unaccounted for.
-Note that the non-existence of B-modes does not imply that the sample is free of remaining systematics.
-
-One systematic effect is the variation of depth in a survey.
-While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions, that are found in ground-based surveys.
-To first order, this variation can be modelled by a step-like depth function that varies from pointing to pointing.
-In this work we assume the specifications of the Kilo-Degree Survey, namely a collection of $1\,\text{deg}^2$ square fields.
-Furthermore we neglect boundary effects.
-
-In Section \ref{sec:modelling_single_lens} we will introduce a simple toy model to understand this effect and analyze the impact on the power spectrum.
-In Section \ref{sec:xipm} we will estimate the effect on the shear correlation functions $\xi_\pm$ using two different models.
-We will present our results in Section \ref{sec:results}.
-In Section \ref{sec:discussion} we will discuss our results and comment on the impacts of our used simplifications.
-We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
-
-\section{Modelling the Power Spectrum}
-\label{sec:modelling_single_lens}
-For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
-If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm ds}/D_{\rm s}$.
-% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
-%\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
-%\]
-
-%Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate.
-Assuming that the optical depth, and thus the source redshift populations, vary between pointing, an observer will measure a shear-signal that is modified by a depth-function $W(\bm{\theta}) = 1-w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-The reconstruction of the observed convergence $\kappa^{\rm obs}$ will thus not yield the original convergence.
-In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part.
-This allows us to separate our received signal into E- and B-modes following \[
-%	\kappa = \kappa^E+i\kappa^B\, ,
-%\]
-%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
-%2002A&A...389..729S SRC
-
-\subsection{Effects on the Power Spectrum}
-Assuming that the depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a locally constant depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-In accordance to the definition of the shear power spectrum \begin{equation}
-(2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) = \la \hat{\gamma}(\b\ell)\hat{\gamma}(\b\ell')\ra \, ,
-\end{equation}
-we define the observed power spectrum via \begin{equation}
-P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \, .
-\end{equation}
-Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
-To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as
-\begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
-1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
-0 \qquad \text{else}
-\end{cases},
-\label{eq:defweightf}
-\end{equation}
-where $L$ is the length of one pointing.
-Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
-\begin{equation}
-P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)P(\b k)\, ,
-\end{equation}
-where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function.
-The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with the fourier transfrom of a box-function, scaling with the variance of the geometric lensing efficiency $\la \frac{D_{\rm ds}}{D_{s}}\ra$.
-In particular, the power spectrum is not isotropic anymore.
-Following \citet{2002A&A...389..729S}, it would be interesting to extract E- and B-mode information out of this power spectrum, however \citet{2010A&A...520A.116S} present a more sophisticated decomposition of E- and B-modes, that can also be applied to real data using the shear correlation function, so instead we want to focus our efforts on these parts.
-\section{Modelling the shear correlation function}
-\label{sec:xipm}
-A convenient way to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
-\xi_\pm = \la \gamma_{\rm t}\gamma_{\rm t}\ra \pm \la \gamma_\times\gamma_\times\ra \, .
-\]
-They are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear-measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions.
-Cosmologically, given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation function from the underlyting matter power spectrum $P_\delta$ via \todo{Citation!}\begin{align}
-\label{eq:xipm-pkappa}
-\xi_\pm[\theta,p_i,p_j] =& \int_0^\infty \frac{{\rm d}l\,l}{2\pi}J_{0,4}(l\theta)P(l,p_i,p_j)\, , \\
-\label{eq:pkappa-pdelta/lenseff}
-P(l,p_i,p_j) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_h} {\rm d}\chi\frac{g(\chi,p_i)g(\chi,p_j)}{a^2(\chi)}P_\delta\left(\frac{l}{f_K(\chi)},\chi\right)\, , \\
-\label{eq:lenseff}
-g(\chi,p_i) =& \int_\chi^{\chi_H} {\rm d}\chi'\, p_i(\chi') \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
-\end{align}
-Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions.
-\subsection{Using an analytic Model}
-For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal. Following \citet{2006APh....26...91V}, we estimate
-\[
-\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
-\]
-\todo{Maybe implement redshift-dependent index?}
-Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
-
-%For a pair of galaxies that we use to measure the correlation function, it is crucial to determine whether those two galaxies lie within the same pointing.
-We want to define a function $E(\theta)$ that determines
-
-Let $N(\b \theta)$ be the number-density per tile and $W(\b \theta)$ the weighting of average shear.
-The observed correlation function $\xi^{\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{\rm const}$ via
-\begin{align*}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{\la N(\b 0)N(\b \theta)\gammao_{\rm t}(\b 0)\gammao_{\rm t}(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \pm \frac{\la N(\b 0)N(\b \theta)\gammao_\times(\b 0)\gammao_\times(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \\
- = & \frac{\la N(\b 0)N(\b \theta)W(\b 0)W(\b \theta)\ra}{\la N(\b 0)N(\b \theta)\ra} \xi_{\pm}^{\rm const}(\theta) \, .
- \end{align*}
- Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
-We want to denote the probability that a random pair of galaxies of distance $\theta$ lie in the same pointing with $E(\theta)$.
-An analytical expression for this function is surprisingly hard to obtain, but it can easily be calculated to arbitrary accuracy, following the procedure explained in Appendix \ref{sec:details on etheta}.
-The function is depicted in Figure \ref{fig:eoftheta_lin}.
-
- \begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{images/eoftheta.png}
- \caption{Probability that a random pair of galaxies of distance $\theta$ lie in the same pointing.}
- \label{fig:eoftheta_lin}
- \end{figure}
-
-We again parametrize the number density $N(\b \theta)=\la N \ra (1+n(\b \theta))$ and the weight $W(\b \theta)=1+w(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n(\b \theta)$ as a locally constant function with average $\la n \ra = 0$.
-We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get
- \begin{align}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta) \\
-\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, . \nonumber
- \label{eq:ffunct}
-\end{align}
-\todo{The formula for a cross-correlation of different bins is much longer, but follows the same principle. Maybe put it into the Appendix?}
-We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.
-
-However, as a survey of constant depth is completely unrealistic, also the modelled correlation function will be subject to the same effect.
-If we assume the same redshift-distributions for galaxies as in the case of varying depth, and just assert that those changes are not correlated with position, we get
-\begin{equation}
-\xi_\pm = (1+2\la nw\ra)\xi_\pm^{\rm const}\, .
-\end{equation}
-The ratio of modelled and observed correlation function thus becomes: \begin{align}
-\frac{\xi_\pm}{\xi_\pm^{\rm obs}} = & \frac{\left(1+2\la nw\ra\left)\left(1+E(\theta)\la n^2\ra\right)\right.\right.}{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]} \\
-\equiv & F(\theta) \, .
-\end{align}
-%It is interesting to note that $F(\theta)=1$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. 
-We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts. 
-\subsection{Using a semi-analytic Model}
-The analysis of data from the Kilo-Degree Survey showed that the redshift-distribution of sources was highly correlated with the depth in the $r$-band.
-We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-Now for each percentile $i$ and each tomographic redshift bin $z$ we can extract a weighted number density of galaxies $N_i(z)$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p_i(z)$.
-Using \eqref{eq:xipm-pkappa}, we can for each set of percentiles $i,j$ and redshift bins $z_1,z_2$ compute the shear correlation function $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.\todo{Should we cite \textsc{nicaea} here?} When we compute the measured shear correlation function of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process).
-If, for a single pair of galaxies, one galaxy lies in the $i$-th percentile of redshift bin $z_1$ and the second one lies in the $j$-th percentile of redshift bin $z_2$, then their contribution to the observed correlation function is, on average, $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.
-This means that if we know each of those single correlation functions, we can reconstruct the total correlation function via a weighted average of the single functions.
-As an example, if we want to calculate the correlation function between tomographic bins $z_1$ and $z_2$ and pick a galaxy from bin $z_1$, the probability of this galaxy being in the $i$-th percentile of $z_1$ is proportional to $N_i(z_1)$.
-Now let the second galaxy be in bin $z_2$ and of distance $\theta$ to the first.
-If we imagine a thin annulus of radius $\theta$ around the first galaxy, then the number of galaxies in this annulus, that lie within the same pointing as the first galaxy, is proportional to $E(\theta)N_i(z_2)$, whereas the number of galaxies that lie in a different pointing is $[1-E(\theta)]\la N(z_2)\ra$, where $\la N(z_2)\ra$ is the average number density in redshift bin $z_2$.
-If the galaxy lies within a different pointing, the chances of it being in the $j$-th percentile are again just proportional to $N_j(z_2)$.
-We conclude that if we sum the single correlation functions $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$ according to these weightings, we can simulate the observed correlation function that accounts for the variation in optical depth via
-\begin{align}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \la N(z_2)\ra\sum_{j=1}^{10}\frac{  N_j(z_2)}{\sum_k N_k(z_2)} \big[1-E(\theta)\big]\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\} \nonumber \\
- = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \sum_{j=1}^{10}\frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\}\, ,
-\label{eq:correctionfunction1}
-\end{align}
-with the normalization
-\[
-C = \sum_{i=1}^{10} N_i(z_1) \bigg[ E(\theta)  N_i(z_2) + \sum_{j=1}^{10} \frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\bigg]\,.
-\]
-A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
-If we want to compute this for all 5 redshift bins of the KiDSV-survey, this forces us to calculate 1265 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive).
-However, if we examine Equation \eqref{eq:lenseff}, we see that it is linear in its second argument, which in turn makes Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} bilinear in their second and third arguments.
-This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation function of that.
-As an example, the following equation holds: \[
-N_j\xi_\pm[\theta,p_i,p_j]+N_k\xi_\pm[\theta,p_i,p_k] = (N_j+N_k)\,\xi_\pm\left[\theta,p_i,\frac{N_jp_j+N_kp_k}{N_j+N_k}\right]\, .
-\]
-Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
-\begin{equation}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{C}\bigg\{ E(\theta)\sum_{i=1}^{10} N_i(z_1)N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] +\frac{1}{10}\big[1-E(\theta)\big]\xi_\pm\left[\theta,p(z_1),p(z_2)\right]N(z_1)N(z_2)\bigg\}\, .
-\label{eq:correctionfunction2}
-\end{equation}
-Here, we defined the \textit{average redshift distribution} $p(z)$ and \textit{combined number density} $N(z)$ of tomographic bin $z$ as \[
-p(z):= \frac{\sum_i N_i(z)p_i(z)}{\sum_i N_i(z)}\, , \qquad N(z):=\sum_i N_i(z)\, .
-\]
-\todo{Maybe label the $N(z)$ differently to avoid confusion with $\la N(z)\ra$?}
-For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
-We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N(z_1)N(z_2)$ and thus \[
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{N(z_1)N(z_2)}\xi_\pm\left(\theta,n(z_1),n(z_2)\right)N(z_1)N(z_2) = \xi_{\pm,z_1,z_2}(\theta)\, ,
-\]
-so on large scales our observed correlation function agrees with the one that we would usually calculate.
-\section{Results}
-\label{sec:results}
-We applied both our methods to data from the KiDSV-450 survey and computed the ratio of observed and modeled correlation functions.
-Furthermore, we have conducted a simulation using ray-tracing through the millenium simulations (?)\todo{I should ask catherine about what exactly she did for the simulations or maybe even ask her to write this part of the paper?}.
-As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
-The result can be seen in Figure \ref{fig:all_xis}.
-	\begin{figure}
-	\centering
-	\includegraphics[width=1\textwidth]{images/xis_111.png}
-	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.}
-	\label{fig:all_xis}
-	\end{figure}
-We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
-We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk?
-Maybe in the appendix to avoid too many Figures?} The simulations seem to be in rough agreement with the models, but there are some features that can not be explained.
-Especially we observe that the ratios of the correlation functions for large values of $\theta$ seem to consistently surpass unity, which can not be explained by our models.
-
-As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model.
-Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
-As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.\todo{Maybe expand this to more parameters?}  As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties.
-However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area.
-As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.
-
-To estimate the B-Modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare \citet{2010A&A...520A.116S}), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
-We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KiDSV-450 survey for the same range in $\theta$.
-The real B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant.
-Given these facts, we conclude that the creation of B-Modes due to varying depth in the KiDS survey is not significant.
-However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, that show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).
-
-\begin{figure}
-\centering
-\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/bmodes.pdf}
-\caption{The $B$-modes created by a variation in survey-depth.
-We used the logarithmic COSEBIs described in \citet{2010A&A...520A.116S} with a range from $\theta_{\rm min} = 0.5\arcmin$ to $\theta_{\rm max} = 100\arcmin$.}
-\label{fig:bmodes_cosebi}
-\end{figure}
-
-\section{Discussion}
-\label{sec:discussion}
-With our semi-analytic model we try to describe the impacts of varying depth in ground-based surveys. During our analysis we have assumed a few simplifications, which we will discuss.
-\begin{enumerate}
-\item We implemented a variation in depth that only depends on the pointing.
-However, in reality galactic extinction, CCD imperfections, dithering strategies and other factors also influence the depth on different scales.
-Although the variation between pointings is the dominating factor, a complete analysis implementing those factors could yield a slightly different result.
-\item In our main analysis we assumed an infinite number of fields.
-This ignores boundary effects that would arise in the vincinity of the edge of a footprint (there finding a galaxy outside of the same pointing would be less likely).
-Also, another effect is ignored: If one has a number of $N$ fields in each percentile, and one galaxy is in a pointing of a certain percentile, then the probability that a different pointing is of the \emph{same} percentile is reduced by the factor $(N-1)/N$.
-However, we modeled the second effect, and already at 100 pointings it barely makes any difference.
-We did not model the boundary effects, but we assume that they are likewise neglible.
-\todo{This needs to be rewritten to account for the new insights.}
-\item We have assumed that the depth of neighbouring pointings is uncorrelated. While there is no reason not to assume that, we have not yet verified that this is indeed the case.
-\item In our Monte Carlo simulations we have only had $\Omega_{\rm m}$ and $\sigma_8$ as free parameters.
-While we do not expect most other parameters to make a difference, baryonic feedback and/or intrinsic alignments also change the correlation functions on small scales, so it is definitely possible that in a Monte Carlo chain including free parameters for these effects, those would change to mitigate the varying depth, and the impact on the actual cosmological parameters would be much smaller.
-\end{enumerate}
-We have determined that the effects of varying depth are not significant for the KiDSV-450 survey.
-For a Euclid-like survey they will play an important role, but before a model is implemented in such a precise survey, one should revise the used simplifications, especially the first one.
-We suspect that it should be possible to account for different aspects of varying optical depth by just modifying the function $E(\theta)$.
-
-However, for the parameter $S_8$ this effect is insignificant, which in particular means that a variation in depth can not explain the discrepancies between the analyses of the CMB and those of the local universe.
-It can also be responsible for the occurence of $B$-Modes, although only to an insignificant amount.
-
+\include{introduction}
+\include{model_ps}
+\include{model_xipm}
+\include{results}
+\include{discussion}
 %--------------------------------------------------------------------
@@
 \begin{appendix}
-\section{Detailed Calculations}
-\subsection{Calculation of the Power Spectrum}
-In this Section we will perform the calculation for the observed power spectrum \todo{I need to add cdots for scalar products in this section...} $P^{\text{obs}}(\b \ell)$.
-For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$.
-In reality, finite field effects would play a role here.
-We begin with the calculation of the correlation for the Fourier transformed shear:
-\begin{align}
-\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta')\ra\nonumber\\
- = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta') \int \frac{\text{d}^2\b k}{(2\pi)^2}\int \frac{\text{d}^2\b k'}{(2\pi)^2}\, \hat{\gamma}(\b k)\hat{\gamma}^*(\b k')\exp(-i\b k\b \theta+i\b k'\b \theta')\ra \nonumber\\
-= & \la \int \text{d}^2\b \theta \int \text{d}^2\b \theta' \int \frac{\text{d}^2\b k}{(2\pi)^2} \int \frac{\text{d}^2\b k'}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b k') \exp[i(\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b k'\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
-  = & \la \int \frac{\text{d}^2\b k}{(2\pi)^2} \, P(\b k) \int \text{d}^2\b \theta\, W(\b \theta)\exp[i\b \theta(\b \ell-\b k)]\int \text{d}^2\b \theta'\, W(\b \theta') \exp[-i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
-  = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k)\widehat{W}(\b \ell-\b k)\widehat{W}^* (\b \ell'-\b k)\ra
-\end{align}
-It is important to keep in mind that the ensemble averages of the weight function are independent of the ensemble averages of the shear values, meaning $\la W(\b \theta)\gamma(\b \theta)\ra = \la W(\b \theta)\ra \la \gamma(\b \theta)\ra$.
-We can define $W(\b \theta)=1+w(\b\theta)$ with $\la w(\b \theta)\ra = 0$, which leads to the expession
-\begin{align}
-\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big( \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big)\right.\right.
-\nonumber\\
- & \qquad \left.\left. + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
- = & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \big[ \la \hat{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \hat{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\big] + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
-\overset{(*)}{=} & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
-\label{eq:pobs1}
-\end{align}
-where in $(*)$ we have used that the average $\la \hat{w}(\b \ell)\ra$ vanishes.
-Up until now, we have not specified our weight-function $w$. So we now parametrize it as \begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
-1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
-0 \qquad \text{else}
-\end{cases}.
-\end{equation}
-Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier-Transform we compute: \begin{equation}
-\hat{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-i \b \ell L\b \alpha) \widehat{\Xi}(\b \ell)\, ,
-\end{equation}
-where
-\begin{equation}
-\widehat{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
-\end{equation}
-is a 2-dimensional sinc function.
-Assuming an uncorrelated weight-distribution $\left(\la w_{\b \alpha} w_{\b \beta}\ra = 0\text{ for }\b \alpha\neq\b \beta\right)$ and setting $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ for each $\b \alpha$, we get
-\begin{align}
-\la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra = & \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-i(\b \ell - \b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k) \exp[i(\b \ell' - \b k)L\b \beta]\, \widehat{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
- = & \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)\widehat{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
-\end{align}
-Using this result, we can obtain the observed power spectrum \begin{equation}
-P^{\rm{obs}}(\b\ell) = \frac{1}{(2\pi)^2}\int\d^2\ell' \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\, ,
-\end{equation}
-by performing the $\b \ell'$-integration in \eqref{eq:pobs1}:
-\begin{align}
-P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha+i(\b \ell'-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell-\b k)\widehat{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
-= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widehat{\Xi}^*(\b \ell'-\b k)\exp[i(\b \ell'- \b k)L\b \alpha] \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widehat{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widehat{\Xi}(\b \ell-\b k)P(\b k)\, ,
-\end{align}
-which is a 2-dimensional convolution of the power spectrum and the 2-dimensional sinc function.
-\label{sec:calc of PS}
-\subsection{Details on the function $E(\theta)$}
-\label{sec:details on etheta}
-The function $E(\theta)$ is of central importance in this model, so we want to explain how to obtain it.
-It describes, given a pair of galaxies with distance $\theta$, the probability that they are in the same pointing.
-We obtain the function in the following way:
 
-Given one square field of length 1 and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
-As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
-The volume of this square equals \begin{equation}
-\tilde{V}(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, ,
-\end{equation} where $\phi$ represents the angle of the vector $\b\theta$. To exclude negative Volumes (which would occur when $|\b\theta|>1$ holds), we nead to add the Heaviside theta function $H$:
-\begin{equation}
-V(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big] H\big[1-|\b\theta|\cos(\phi)\big]\,H\big[1-|\b\theta|\sin(\phi)\big]\, .
-\label{eq:eoftheta1}
-\end{equation} 
-To obtain the function $E(\theta)$, we need to average Equation \eqref{eq:eoftheta1} over all angles $\phi$.
-While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
-\begin{align}
-E(\theta) = & \frac{4}{2\pi}\int_0^{\frac{\pi}{2}}\d\phi\, V(|\b\theta|,\phi) = \frac{2}{\pi}\begin{cases}
-\int_0^{\frac{\pi}{2}} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , & |\b\theta|\leq 1 \\
-\int_{\arccos(|\b\theta|^{-1})}^{\arcsin(|\b\theta|^{-1})} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , \quad & 1\leq |\b\theta| \leq \sqrt{2} \\
-0\, , & \sqrt{2}\leq\theta
-\end{cases} \nonumber\\
- = & \begin{cases}
-\frac{\pi + (\theta-4)*\theta}{\pi}\, , & \theta \leq 1 \\
-\frac{2[-1+2\sqrt{1-\theta^{-2}}*2\theta - \theta^2/2 - \arccos(\theta^{-1}) + \arcsin(\theta^{-1})]}{\pi}\, , & 1\leq \theta \leq \sqrt{2} \\
-0\, , & \sqrt{2}\leq \theta
-\end{cases}\, .
-\end{align}
-\begin{figure}
-    \centering
-    \def\svgwidth{200pt}    
-    \input{images/eoftheta_new.pdf_tex}  
-    \caption{Graphic representation on how to obtain the function $E(\theta)$.
-For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
-    \label{fig:explain_etheta}
-\end{figure}
-\subsection{Calculation of the shear correlation functions}
-\label{sec:calc of xipm}
-Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation function via \begin{equation}
-\xi_+(\theta) = \frac{\sum_{a,b}w_aw_b\epsilon_a\epsilon_b^*\Delta(\b\theta_a-\b\theta_b)}{\sum_{a,b}w_aw_b\Delta(\b\theta_a-\b\theta_b)}\, .
-\label{eq:xip_from_observations}
-\end{equation}
-Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky. We have defined the function $\Delta$ as \[
-\Delta(\b\theta_a-\b\theta_b) = \begin{cases}
-1, \,\, & |\b\theta_a-\b\theta_b| \in [\theta,\theta+{\rm d}\theta] \\
-0, & \text{ else}
-\end{cases}\, ,
-\]
-where we assume ${\rm d}\theta \ll \theta$.
-When we now separate our galaxy samples into the ten percentiles $I$ defined above, and denote the galaxies from sample $a$ that are in pointing $i$ with $a_i$, the numerator in Equation \eqref{eq:xip_from_observations} transforms to:
-\begin{align*}
- & \sum_{i,j=1}^{10} \sum_{a_i,b_j} w_{a_i}w_{b_j}\epsilon_{a_i}\epsilon_{b_j}^*\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
- = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \sum_{j=1}^{10} \sum_{b_j} w_{b_j}\epsilon_{a_i}\epsilon_{b_j}\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
- = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ \sum_{j=1}^{10} \sum_{b_j\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij \right]
-\end{align*}
-We take the ensemble average of that equation in the sense that we assume that the product of the ellipticities of the galaxies are equal to their respective shear correlation functions, namely $\xi_+^{ij}\equiv \epsilon_{a_i}\epsilon_{b_j}^*$ for all $a_i$ and $b_j$.
+\include{appendix}
 
-Let $b_j\in P_{a_i}$ denote all $b_j$ that lie in the same pointing as the $a_i$.
-We observe that the left term is zero for $i\neq j$, as only galaxies of the same percentile can lie in the same pointing.
-The term $\sum_{b_i\in P_{a_i}}\deltafuncij$ now is the number of galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a_i$, which is equal to the number of galaxies in the whole pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$.
-The prefactor $w_{b_i}$ transforms the number of galaxies to the \emph{weighted number density} of galaxy sample $b$ in percentile $i$, or $N_i(b)$, so the numerator now reads:
-\begin{align*}
-\sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\xi_+^{ij} \right]
-\end{align*}
-
- A similar argument can be made for the right term: Assuming for a second that all pointings outside of the one where galaxy $a_i$ is in are of percentile $j^*$, the right hand side would read \[
-\sum_{b_{j^*}\not\in P_{a_i}} w_{b_{j^*}} \Delta(\b\theta_{a_i}-\b\theta_{b_{j^*}})\xi_+^{i{j^*}} = 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j^*}(b)\xi_+^{i{j^*}}\, .
- \]  
- Taking the ensemble average of all realisations of depth-distributions, we can just denote the probability that a pointing neighbouring one of percentile $i$ is of percentile $j$ as $P(j | i,\theta)$.
-The numerator then reads \[
- \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta)\, 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
- \]
- In our case we assume an infinite number of randomly distributed fields, so $P(j | i,\theta)=1/10$ holds.
-However, for a finite survey the footprint of depth-distributions seems to be of importance, as due to a limited number of fields the $P(j | i,\theta)$ does not equate its expectation value.
-For smaller surveys (or surveys with correlated depth-distributions) it seems appropriate to adjust this parameter.
-\todo{Wait for catherines 450deg${}^2$ simulations, maybe they are big enough?}
-
- If we define $A$ as the (arbitrarily big) survey area, we can set \[
- \sum_{a_i} w_{a_i} = A\, N_i(a)
- \]
- and see that the numerator becomes \[
- 2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
- \]
- The exact line of argumentation can be applied to the denominator, which then reads: \[
-  2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b) + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b) \right]\, .
- \]
-Taking the ratio of the two quantities, and setting $P(j | i,\theta)=1/10$, we receive Equation \eqref{eq:correctionfunction1}.
-\section{Additional Figures}
-\subsection{Results of the MCMC}
-\begin{figure}[h]
-\centering
-	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
-	\caption{Bias in the parameters for a KiDS-like Survey.}
-	\label{fig:mcmc_kids}
-\end{figure}  
-\begin{figure}[h]
-\centering
-	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
-	\caption{Bias in the parameters for a Euclid-like Survey.}
-	\label{fig:mcmc_euclid}
-\end{figure}  
-\todo{Put both in one plot? Maybe put reference MC simulation where $\xi_\pm$ was not changed?}
 \end{appendix}

### 2019-04-04 thesis_effectsofvardepth.tex
added tex files from thesis

\chapter{The effects of varying depth}
\label{sec:eff_of_var_depth}
In this chapter we will explore the effects of varying depth on different shear statistics. In abstract terms, this is a position-based selection effect: In some places fainter galaxies can not be detected due to higher noise levels, whereas in other places the same galaxies would be detected. This leads to a modification of number density, as in deeper pointings more galaxies can be detected, as well as a modification in the shear statistics themselves, as fainter galaxies are on average located at a higher redshift.

We will be working with data from the KiDS+Viking-450 (KV450) Survey \citep{2018arXiv181206077W}. The KV450 survey combines data in the $ugri$-band from the Kilo Degree Survey (KiDS) with the $ZYJHK_{\rm s}$-band imaging from the VISTA Kilo Degree Infrared Galaxy Survey (VIKING) over 458 square degrees. The unprecedented coverage in 9 photometric bins allows a relatively narrow photometric-to-spectroscopic redshift comparison and thus significanlty reduces systematic biases arising from incorrect redshift determination.

For the cosmic shear analysis, the galaxies were separated into five tomographic bins of photometric redshift $z_{\rm b}$. In the areas where the survey overlaps with spectroscopic surveys, a true redshift distribution was extracted for each of the tomographic bins. A summary of the bin boundaries, the (weighted) number of galaxies\footnote{Throughout this thesis, when we speak of the (weighted) number of galaxies in a sample, we refer to the sum of all lensing weights of the galaxies belonging to the respective sample. As all quantities like the average redshift distribution, the shear correlation functions etc.\! are calculated using this number, it carries way more information than the unweighted number of galaxies. For that reason, whenever we speak of a number of galaxies, unless otherwise specified, we refer to the sum of their respective lensing weights.} in each bin and the average spectroscopic redshifts can be found in Table \ref{tab:tomograpic_bins}. A detailed explanation of the determination of the redshift distributions, the measured correlation functions and the inferred cosmological parameters can be found in \citet{2017MNRAS.465.1454H,2018arXiv181206076H}.
\begin{SCtable}
\centering
\begin{tabular}{ccccc}
\toprule
Bin & $z_{\rm b}^{\rm{min}}$ & $z_{\rm b}^{\rm{max}}$ & $N$ & $\la z_{\rm{spec}} \ra$ \\
\midrule
1 & 0.1 & 0.3 &   386208 & 0.49 \\
2 & 0.3 & 0.5 &   563719 & 0.53 \\
3 & 0.5 & 0.7 &   799492 & 0.69 \\
4 & 0.7 & 0.9 &   532226 & 0.84 \\
5 & 0.9 & 1.2 &   415980 & 1.00 \\
\bottomrule
\end{tabular}
\caption[Properties of the tomographic redshift bins in the KV450 Survey.]{Minimum photometric redshift $z_{\rm b}^{\rm{min}}$, maximum photometric redshift $z_{\rm b}^{\rm{max}}$, weighted number of galaxies $N$ and average spectroscopic redshift  $\la z_{\rm{spec}} \ra$ of the five tomographic redshift bins in the KV450 Survey.}
\label{tab:tomograpic_bins}
\end{SCtable}
\begin{figure}
\centering
\includegraphics[trim={0.5cm 0 1cm 0},clip,width=\textwidth]{dist_z_all.pdf}
\caption[Redshift distribution for the worst, a medium and the best percentile]{Redshift distribution for the worst, a medium and the best percentile for each tomograpic bin. The grey area highlights photometric redshift bin.}
\label{fig:redshifts_per_percentile}
\end{figure}

While there are many position-based selection effects having similar impacts, like depth in the different colour bands, seeing, airmass, Galactic extinction, dithering strategies and CCD imperfections, we chose to focus on the $r$-band depth of a pointing. As the $r$-band served as the detection band, its depth appears to be the most relevant factor. As of now, we ignore the other effects as we expect them to play a subdominant role, but the investigation of those is definitely necessary in further studies.

To estimate the extent of the varying depth between pointings, we received some data by H.~Hildebrandt: All pointings were sorted by $r$-band depth and split into ten percentiles, ordered from shallow to deep. For each of the percentiles of every tomographic bin, the redshift distribution and the weighted number of galaxies were extracted. Inspecting Figure \ref{fig:redshifts_per_percentile}, one can clearly see that the redshift distribution strongly varies between the percentiles -- especially the lower-redshift bins show a significant tail of high-redshift galaxies for deep pointings. It is also noticeable that the spectroscopic redshift distribution of galaxies only roughly traces their photometric redshift bins. While this might seem like a problem, as long as we have a precise knowledge the spectroscopic redshift distribution for Eq.\,\eqref{eq:pkappa}, this does not affect the results.

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{cov_nz_meanz.pdf}
\caption[Weighted number of galaxies as a function of redshift]{Weighted number of galaxies $N$ as a function of average (spectroscopic) redshift $\la z \ra$ for each percentile of the five tomographic bins. Values for this can be found in Table \ref{tab:nvsz} in the Appendix.}
\label{fig:number_density_vs_redshift}
\end{figure}

Additionally, when we look at Figure \ref{fig:number_density_vs_redshift}, we notice some interesting features: First and foremost, there is an obvious strong correlation between average redshift and the number of galaxies for all bins. Furthermore, the low redshift bins seem to vary extremely strongly in redshift and only subdominantly in the number of galaxies, whereas the trend is vice versa for the high-redshift bins. This behaviour is easily explained: Almost all galaxies in the low-redshift bins are close (and thus bright) enough for us to detect them, even with suboptimal depth in the pointing. A significant fraction of the galaxies included in the high percentiles are ones with extremely high ($z \gtrsim 2$) spectroscopic redshift, which leads to a strong increase in average redshift. The galaxies in the high-redshift bins, however, are relatively dim and thus harder to detect. For shallow pointings the number of detected galaxies thus significantly decreases. Still, the additional galaxies detected in deeper pointings do not influence the average redshift that much, as the average redshift is already pretty high.

We see that the $r$-band depth has a strong effect on the number of detected galaxies as well as on their average redshift. These two effects will definitely influence the measured shear statistics if one does not account for them. In the next two sections we will develop a few models to help us answer the question whether this influence is significant for the results of the KV450 survey, and if it can be detected by analysis of the B-modes.
\section{Toy model -- a single lens plane}
\label{sec:toy_model}
For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer. If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto \Dds/D_{\rm s}$.

Assuming that the survey depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a depth function $W(\bm{\theta}) = 1+w(\bm{\theta})\propto \Dds/D_{\rm s}$, where $\langle w(\bm{\theta})\rangle=0$ holds. We will model the effects of such a depth function in three different ways - by modelling a convergence field directly, by computing the effects on the power spectrum and by investigating the change of the shear correlation functions.

\subsection{Modelling a shear field}
\label{sec:model_kappa}
As a first test, we simulated the convergence $\kappa$ as a Gaussian random field\footnote{A Gaussian random field is fully characterized by its power spectrum $P(|\b k|)$. A particular realization is obtained by drawing Gaussian deviates with dispersion $\sigma(\b k)=\sqrt{P(|\b k|)}$ for each $\b k$, multiplying them with a random phase $\phi_{\b k}$, and then Fourier transforming the obtained field.} and converted it to a shear-field $\gamma$ via Eq.\,\eqref{eq:KS_gamma_from_kappa}. This field was then multiplied by a pointing-based depth function $W(\b\theta)$. For simplicity we modelled the weighting by random variables from a normal distribution with mean $\mu = 1$ and variance $\sigma = 0.1$. After that, we transformed the shear field back into a convergence field $\kappa^{\rm{obs}}$. The transformations between the fields were done using the convolution theorem. For the Fourier transformations, periodic boundary conditions were asserted. As the observed shear field is modified, the reconstruction of the observed convergence $\kappa^{\rm{obs}}$ will not yield the original convergence. In particular, there is no reason why the convolution with a complex kernel should have a nonzero imaginary part. This allows us to separate our received signal into E- and B-modes via Eq.\,\eqref{eq:ebmodes1}. As an example, Figure \ref{fig:way_for_kappa} shows the procedure for one $4\times 4\,\rm{deg}^2$-field.
\begin{figure}
\centering
\begin{subfigure}[c]{0.49\textwidth}
\includegraphics[trim={1.2cm 0cm 1.2cm 0cm},clip,width=\textwidth]{kappa.pdf}
\subcaption{Initial convergence $\kappa$.}
\end{subfigure}
\begin{subfigure}[c]{0.49\textwidth}
\includegraphics[trim={1.2cm 0cm 1.2cm 0cm},clip,width=\textwidth]{weightf.pdf}
\subcaption{Used weight-function $W$.}
\end{subfigure}\\
\begin{subfigure}[c]{0.49\textwidth}
\includegraphics[trim={1.2cm 0cm 1.2cm 0cm},clip,width=\textwidth]{kappae.pdf}
\subcaption{Difference in E-modes between the initial convergence field $\kappa$ and the reconstructed convergence field $\kappa^{\rm{obs}}$.}
\end{subfigure}
\begin{subfigure}[c]{0.49\textwidth}
\includegraphics[trim={1.2cm 0cm 1.2cm 0cm},clip,width=\textwidth]{kappab.pdf}
\subcaption{B-modes of the reconstructed convergence field $\kappa^{\rm{obs}}$.}
\end{subfigure}
\caption{Estimating E- and B-modes of a reconstructed convergence field.}
\label{fig:way_for_kappa}
\end{figure}

It is interesting to note that the difference in E-modes is predominantly within the $1\,\rm{deg}^2$-fields, whereas the majority of B-modes arise close to the boundaries of each field. However, the reconstructed convergence field is not a good statistic for cosmic shear. Additionally, while the initial density fluctuations might be a Gaussian random field, cosmic shear is measured in the nonlinear regime of structure growth, which no longer takes the form of a Gaussian random field. While this visual inspection serves as a good first start, it is not suitable to make any reliable predictions. For this reason, I chose to investigate two-point shear statistics, namely the power spectrum and the shear correlation functions.
%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
%2002A&A...389..729S SRC
\subsection{Effects on the power spectrum}
\label{sec:model_ps}
For the analysis of the power spectrum we adopt the same pointing-based depth function \linebreak$\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
In accordance to the definition of the shear power spectrum \begin{equation}
(2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) = \la \tilde{\gamma}(\b\ell)\tilde{\gamma}(\b\ell')\ra \, ,
\end{equation}
we define the observed power spectrum via \begin{equation}
P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \, .
\end{equation}
Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$. In this section we will outline the computation of the observed power spectrum. A more detailed version can be found in Appendix \ref{sec:calc of PS}. We compute the correlation of the Fourier transformed observed shear as \begin{align*}
\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(\i\b \ell\cdot\b \theta-\i\b \ell'\cdot\b \theta')\ra \nonumber \\
  = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k)\widetilde{W}(\b \ell-\b k)\widetilde{W}^* (\b \ell'-\b k)\ra \, .
\end{align*}
Inserting $W(\b\theta) = 1+w(\b\theta)$ we derive \begin{align*}
\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \tilde{w}(\b \ell-\b k)\delta(\b \ell'-\b k)\right.\right. \nonumber\\
 & \qquad \left.\left.  + \tilde{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]+ \tilde{w}(\b \ell-\b k)\tilde{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
= & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \, .
\end{align*}
To model an arbitrary depth function that is constant on each individual pointing $\b \alpha$, we can choose weights $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as 
\begin{equation}
w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
0 \qquad \text{else}
\end{cases},
\label{eq:defweightf}
\end{equation}
where $L$ is the length of one pointing.  Assuming an uncorrelated distribution for the weight function $\left(\la w_{\b\alpha}w_{\b\beta}\ra =0\text{ for }\b\alpha\neq\b\beta\right)$, we define $\la w^2\ra\equiv\la w_{\b\alpha}^2\ra$. We can then calculate the observed power spectrum via
\begin{align}
P^{\text{obs}}(\b \ell)  = & \frac{1}{(2\pi)^2}\int\d^2\ell' \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\nonumber\\
  = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2 k}{(2\pi)^2}\,\widetilde{\Xi}(\b \ell-\b k)P(\b k)\, ,
\end{align}
where $\widetilde{\Xi}$ is the Fourier transform of a box-function, namely a sinc-function.

The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with a two-dimensional sinc-function, scaling with the variance of the geometric lensing efficiency $\la \frac{D_{\rm ds}}{D_{s}}\ra$. In particular, the power spectrum is not isotropic anymore. Following \citet{2002A&A...389..729S}, it would be interesting to extract E- and B-mode information out of this power spectrum. The B-mode power spectrum for the simulations described in Section \ref{sec:model_kappa}, this time for a $20\times 20\,\rm{deg}^2$-field, can be seen in Figure \ref{fig:powerspectra}. As the B-mode power spectrum is solely created by this effect, the imprint of the sinc-function is clearly visible.

\begin{figure}
\begin{subfigure}[c]{0.49\textwidth}
\includegraphics[trim={1.2cm 0cm 1.2cm 0cm},clip,width=\textwidth]{pp3_2.pdf}
\subcaption{Two-dimensional B-mode power spectrum.}
\end{subfigure}
\begin{subfigure}[c]{0.49\textwidth}
\includegraphics[trim={0.2cm 0cm 1.2cm 0cm},clip,width=\textwidth]{pkappa2i.pdf}
\subcaption{Azimuthally averaged B-mode power spectrum.}
\end{subfigure}
\caption[B-mode power spectra in Gaussian random fields]{One- and two-dimensional B-mode power spectra for simulations of Gaussian random fields.}
\label{fig:powerspectra}
\end{figure}

Unfortunately, it is quite difficult to include any form of weighting in the analysis of the power spectrum, both in the form of number density and in the form of lensing weights. We will therefore analyse the change in the shear correlation functions, as these functions allow for a straightforward implementation of weightings. For the E- and B-mode decomposition we will rely on the COSEBIs \citep{2010A&A...520A.116S}.
\subsection{The function $E(\theta)$}
\label{sec:model_e}
When computing the shear correlation between a pair of galaxies, it is of central importance whether those two galaxies lie in the same pointing or not. We want to model the probability that a pair of galaxies with separation $\b\theta$ lie in the same pointing by the function $E(\b\theta)$, which we will derive here:

{
\def\vec{\b}
\begin{SCfigure}
    \centering
    \def\svgwidth{200pt}    
    \hspace*{1cm}
    \input{../figs/eoftheta_new.pdf_tex}  
    \hspace*{-2cm}
    \caption[Graphic how to obtain $E(\b\theta)$]{Graphic representation on how to obtain the function $E(\b\theta)$. For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
    \label{fig:explain_etheta}
\end{SCfigure}
}
Given one square field of length $L$ (in our case $L=60\arcmin$) and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$. As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing. The volume of this square equals \begin{equation}
V(|\b\theta|,\phi)  = \big[L-|\b\theta|\cos(\phi)\big]\,\big[L-|\b\theta|\sin(\phi)\big]\, ,
\end{equation} where $\phi$ represents the angle of the vector $\b\theta$. The function $E(\b\theta)$ then simply equals $V(|\b\theta|,\phi)/L^2$. To exclude negative Volumes (which could occur when $|\b\theta|>1$ holds), we need to add the Heaviside theta function $\mathcal{H}$:
\begin{equation}
E(\b\theta)  = \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, \mathcal{H}\left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\mathcal{H}\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, .
\label{eq:eoftheta1}
\end{equation} 
As $E(\b\theta)$ is not isotropic, in order to obtain the function $E(\theta) = E(|\b\theta|)$, we need to azimuthally average Equation \eqref{eq:eoftheta1} over all angles $\phi$. While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
\begin{align}
E(\theta) = & \frac{4}{2\pi}\int_0^{\frac{\pi}{2}}\d\phi\, E(\b\theta) = \frac{2}{\pi}\begin{cases}
\int_0^{\frac{\pi}{2}} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, ,  & |\b\theta|  \leq L \\[10pt]
\int_{\cos\inv(L/|\b\theta|)}^{\sin\inv(L/|\b\theta|)} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right] \, , \quad   & L \leq |\b\theta| \leq \sqrt{2}L \\[10pt]
0\, , &\sqrt{2}L \leq\theta
\end{cases} \nonumber\\[10pt]
 = & \begin{cases}
\frac{1}{L^2 \pi}\left[L^2\pi - (4L-\theta) \theta\right]\, ,  & \theta \leq L \\[10pt]
\frac{2}{\pi}\,\left[4\sqrt{\frac{\theta^2}{L^2}-1} -1 - \frac{\theta^2}{2L^2} - \cos\inv\left(\frac{L}{\theta}\right) + \sin\inv\left(\frac{L}{\theta}\right)\right]\, ,  & L  \leq \theta \leq \sqrt{2}L \\[10pt]
0\, ,  & \sqrt{2}L \leq \theta
\end{cases}\, .
\end{align}

The function is depicted in Figure \ref{fig:eoftheta_lin}.

 \begin{figure}
 \centering
 \includegraphics[width=0.7\textwidth]{eoftheta.pdf}
 \caption{Probability that a random pair of galaxies of separation $\theta$ lie in the same pointing.}
 \label{fig:eoftheta_lin}
 \end{figure}
\subsection{Modelling the shear correlation functions}
\label{sec:xipm_analytic}
For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal, in the sense that the shear field for a deeper redshift distribution gets multiplied by a weight $W$. While this is not true for a 3-dimensional matter distribution, it should be valid for small variations in redshift. Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.

Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear. The observed correlation function $\xi^{ij,\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{ij,\rm{const}}(\theta)$ via (compare Eq. \ref{eq:xipm_from_data})
\begin{align}
\xi^{ij,\text{obs}}_\pm(\theta) = & \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_{\rm t}(\bth)\gamma^{j,\rm{obs}}_{\rm t}(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \pm \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_\times(\bth)\gamma^{j,\rm{obs}}_\times(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \nonumber\\
 = & \frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i(\bth)N^j(\bthp)\ra}\left( \la \gamma^i_{\rm t}(\bth)\gamma^j_{\rm t}(\bthp)\ra \pm \la \gamma^i_\times(\bth)\gamma^j_\times(\bthp)\ra \right) \nonumber\\
 = & \frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i(\bth)N^j(\bthp)\ra} \xi_{\pm}^{ij,\rm{const}}(\theta) \, ,
 \label{eq:xipmblub1}
 \end{align}
 where the average $\la\ldots\ra$ represents both an ensemble average as well as an average over the position $\bth$.
 Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing, which is described by the function $E(\theta)$.

To compute the modified shear correlation functions, we parametrize the number densities \linebreak$N^{i}(\b \theta)=\la N^{i} \ra [1+n^{i}(\b \theta)]$ and the weight $W^{i}(\b \theta)=1+w^{i}(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n^{i}(\b \theta)$ as a function with average $\la n^{i} \ra = 0$, that is constant on each pointing. Inspecting Eq.\,\eqref{eq:xipmblub1}, without loss of generality we can set $\la N^i\ra = 1$, as this term appears both in numerator and denominator. We can see that $\la n^i(\bth)n^j(\bthp)\ra = E(\theta)\la n^i(\bth)n^j(\bth)\ra \equiv E(\theta)\la n^i n^j \ra$ holds and compute:
\begin{align}
&\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra \nonumber\\
&\qquad =  \la [1+n^i(\bth)]\,[1+n^j(\bthp)]\,[1+w^i(\bth)]\,[1+w^j(\bthp)]\ra \nonumber\\
&\qquad =  1 + \la n^i(\bth)n^j(\bthp)\ra + \la n^i(\bth)w^i(\bth)\ra + \la n^i(\bth)w^j(\bthp)\ra + \la n^j(\bthp) w^i(\bth)\ra \nonumber\\
&\qquad\quad + \la n^j(\bthp) w^j(\bthp) \ra + \la w^i(\bth)w^j(\bthp)\ra + \la n^i(\bth)n^j(\bthp)w^i(\bth)\ra \nonumber\\
&\qquad\quad + \la n^i(\bth)n^j(\bthp)w^j(\bthp)\ra  + \la n^i(\bth)w^i(\bth)w^j(\bthp)\ra + \la n^j(\bthp) w^i(\bth)w^j(\bthp)\ra \nonumber\\
&\qquad\quad + \la  n^i(\bth)n^j(\bthp)w^i(\bth)w^j(\bthp)\ra \nonumber\\
&\qquad =  1 + \la n^iw^i\ra + \la n^j w^j\ra + E(\theta)\left[ \la n^in^j\ra + \la n^i w^j \ra  + \la n^jw^i\ra + \la w^iw^j\ra + \la n^in^jw^i\ra + \la n^in^jw^j\ra + \la n^iw^iw^j\ra \right. \nonumber\\
&\qquad\quad \left. + \la n^jw^iw^j\ra + \la n^in^jw^iw^j\ra  \right] 
 \end{align}
Ignoring correlations higher than second order\footnote{Assuming $n$ and $w$ are small, this is a valid approximation. However, inspecting Figure \ref{fig:number_density_vs_redshift}, we see that this assumption is not necessarily valid. However, we performed both calculations for the KV450-survey and found no significant difference.}, and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
 \begin{align}
 \xi^{ij,\rm{obs}}_\pm(\theta) = \frac{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}{1+E(\theta)\la n^i n^j\ra }\xi^{ij,\rm{const}}_\pm (\theta) \, .
 \end{align}
We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.

For the calculation of the reference correlation functions $\xi_\pm^{ij}(\theta)$ we distribute the \textit{same} galaxies into our survey, only this time we will not order their weightings $W$ or their number densities $N$ by pointing. We can imagine this by cutting the footprint into infinitesimal elements $\d^2\b\theta$, and redistributing those at random. When we calculate the correlation function of this survey, we note that $\la n^i(\bth)\ra \la n^j(\bthp)\ra = 0$ holds for $\b\theta\neq \b 0$, as the two corresponding infinitesimal elements have uncorrelated weighting and number density. We again calculate \begin{align}
\xi^{ij}_\pm(\theta) = \frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i(\bth)N^j(\bthp)\ra} \xi_{\pm}^{ij,\rm{const}}(\theta) \, ,
 \label{eq:referencecorr1}
\end{align}
only this time, as weight and number density between different positions are uncorrelated, the denominator of Eq.\,\eqref{eq:referencecorr1} is unity and the numerator is \[
\la [1+n^i(\bth)]\,[1+n^j(\bthp)]\,[1+w^i(\bth)]\,[1+w^j(\bthp)]\ra = 1 + \la n^iw^i\ra + \la n^j w^j\ra\, .
\]
This yields a relation between the correlation function of constant optical depth $\xi_\pm^{ij,\rm{const}}$ and the modelled one $\xi_\pm^{ij}$:
\begin{equation}
\xi_\pm^{ij}(\theta) = \left(1+\la n^iw^i\ra + \la n^jw^j\ra \right)\xi_\pm^{ij,\rm{const}}(\theta)\, .
\end{equation}
The ratio of modelled and observed correlation function thus becomes: \begin{align}
\frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} = & \frac{\left(1+\la n^iw^i\ra+\la n^jw^j\ra \left)\left(1+E(\theta)\la n^in^j\ra\right)\right.\right.}{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]} \nonumber\\[10pt]
\approx & \frac{1+\la n^iw^i\ra+\la n^jw^j\ra + E(\theta)\la n^in^j\ra}{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}
\, .
\end{align}
It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. Given a set of average redshifts, following \citet{2006APh....26...91V}, we can estimate 
\[
\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
\]
We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts. We thus want to construct a model that is valid for an arbitrary distribution of redshifts and does not rely on the assumption of a single lens plane.

\section{Semi-analytical model for the shear correlation functions}
\label{sec:xipm_semianalytic}
The analysis of data from the Kilo-Degree Survey showed that the redshift-distribution of sources was highly correlated with the depth in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on. Now for each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p^i_m(z)$. Using \eqref{eq:xipm_from_pkappa}, we can compute the shear correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each set of percentiles $m,n$ and redshift bins $i,j$\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program. Among other things, it calculates the shear correlation functions for a given cosmology and source redshift distribution. To estimate the power spectrum on nonlinear scales we use the methods developed by \citet{2012ApJ...761..152T}.}. When we compute the measured shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process). If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$. This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions. Formally, we define \[
\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} P_{mn}^{ij}(\theta)\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} P_{mn}^{ij}(\theta)}\, ,
\label{eq:def_xiobs}
\]
where $P_{mn}^{ij}$ is the new weighting of the correlation functions. This weighting has to be proportional to the probability that a galaxy pair of distance $\theta$ is of percentiles $m$ and $n$, as well as to the original weighting of these galaxies.

For $m\neq n$ we know that the pair of galaxies has to lie in different pointings, which is accounted for by including the factor $[1-E(\theta)]$. Furthermore, the first galaxy has to lie in percentile $m$, the probability of which we will denote with $P(m)$. As we have 10 different percentiles, and average over the whole footprint of the survey, $P(m)=1/10$ holds. When the first pointing is of percentile $m$, we want to denote the probability that a galaxy in a different pointing with distance $\theta$ is of percentile $n$ by $P(n|m,\theta)$. The impact of such a galaxy pair on the correlation functions scales with the product of the weighted number of galaxies $N_m^i,N_n^j$. We get for $n\neq m$: \[
P_{mn}^{ij}(\theta) = [1-E(\theta)]\frac{1}{10}P(n|m,\theta) N_m^i N_n^j\, .
\label{eq:pmnij_corr1}
\]
For the calculation of $P_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxy lies in the same pointing [accounted for by the factor $E(\theta)$], it automatically is of the same percentile. We therefore set \[
P_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{10}P(m|m,\theta) N_m^i N_m^j \, .
\label{eq:pmnij_corr2}
\]
In our case, we assume an uncorrelated distribution of percentiles, such that we can set $P(n|m,\theta)=1/10$. We can then write $P_{mn}^{ij}(\theta)$ as: \[
P_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, ,
\label{eq:pmnij_uncorr}
\]
where $\delta_{mn}$ denotes the Kronecker delta.
Inserting this into Eq.\,\eqref{eq:def_xiobs}, we compute
\begin{align}
\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\sum_{m=1}^{10} N_m^i \bigg\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\bigg\}\, ,
\label{eq:correctionfunction1}
\end{align}
with the normalization
\[
C = \sum_{m=1}^{10} N_m^i \bigg[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\bigg]\, .
\]
A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.

If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive). However, if we examine Eq.\,\eqref{eq:lens_efficiency}, we see that the comoving distance distribution of sources factors in linearly. This in turn implies that in Equations \eqref{eq:pkappa} and \eqref{eq:xipm_from_pkappa} both source distance distributions factor in linearly. This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that. In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average redshift distribution} $p^i(z)$ of tomographic bin $i$ as \[
N^i\equiv\sum_m N_m^i\, , \qquad p^i(z) = \frac{\sum_m N_m^i p_m^i(z)}{\sum_m N_m^i} \, .
\]
If we define $\xi^{ij}_\pm$ as the correlation functions between the average redshift distributions $p^i(z)$ and $p^j(z)$, then we observe: \[
\sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = N^iN^j\xi^{ij}_\pm\, .
\]
Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
\begin{equation}
\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{C}\bigg\{ E(\theta)\left[\sum_{m=1}^{10} N_m^iN_m^j \xi_{\pm,mm}^{ij}(\theta)\right] +\frac{\big[1-E(\theta)\big]}{10}\xi_\pm^{ij}(\theta)N^iN^j\bigg\}\, .
\label{eq:correctionfunction2}
\end{equation}
For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165. We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N^iN^j$ and thus \[
\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{N^iN^j}\xi_\pm^{ij}(\theta)N^iN^j = \xi_\pm^{ij}(\theta)\, ,
\]
so on large scales our observed correlation functions agree with the ones that we would usually calculate.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End:

### 2019-04-11 model_ps.tex

\section{Modelling the Power Spectrum}
\label{sec:modelling_single_lens}
For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer. If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm ds}/D_{\rm s}$. 
% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
%\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
%\]

%Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate. Assuming that the optical depth, and thus the source redshift populations, vary between pointing, an observer will measure a shear-signal that is modified by a depth-function $W(\bm{\theta}) = 1-w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. The reconstruction of the observed convergence $\kappa^{\rm obs}$ will thus not yield the original convergence. In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part. This allows us to separate our received signal into E- and B-modes following \[
%	\kappa = \kappa^E+i\kappa^B\, ,
%\]
%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
%2002A&A...389..729S SRC

\subsection{Effects on the Power Spectrum}
Assuming that the depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a locally constant depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
In accordance to the definition of the shear power spectrum \begin{equation}
(2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) = \la \hat{\gamma}(\b\ell)\hat{\gamma}(\b\ell')\ra \, ,
\end{equation}
we define the observed power spectrum via \begin{equation}
P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \, .
\end{equation}
Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as 
\begin{equation}
w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
0 \qquad \text{else}
\end{cases},
\label{eq:defweightf}
\end{equation}
where $L$ is the length of one pointing.
Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
\begin{equation}
P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)P(\b k)\, ,
\end{equation}
where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function.
The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with the fourier transfrom of a box-function, scaling with the variance of the geometric lensing efficiency $\la \frac{D_{\rm ds}}{D_{s}}\ra$. In particular, the power spectrum is not isotropic anymore. Following \citet{2002A&A...389..729S}, it would be interesting to extract E- and B-mode information out of this power spectrum, however \citet{2010A&A...520A.116S} present a more sophisticated decomposition of E- and B-modes, that can also be applied to real data using the shear correlation function, so instead we want to focus our efforts on these parts.

### 2019-04-11 model_xipm.tex

\section{Modelling the shear correlation functions}
\label{sec:xipm}
A convenient way to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
\xi_\pm = \la \gamma_{\rm t}\gamma_{\rm t}\ra \pm \la \gamma_\times\gamma_\times\ra \, .
\]
They are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear-measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions. Cosmologically, given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation function from the underlyting matter power spectrum $P_\delta$ via \todo{Citation!}\begin{align}
\label{eq:xipm-pkappa}
\xi_\pm[\theta,p_i,p_j] =& \int_0^\infty \frac{{\rm d}l\,l}{2\pi}J_{0,4}(l\theta)P(l,p_i,p_j)\, , \\
\label{eq:pkappa-pdelta/lenseff}
P(l,p_i,p_j) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_h} {\rm d}\chi\frac{g(\chi,p_i)g(\chi,p_j)}{a^2(\chi)}P_\delta\left(\frac{l}{f_K(\chi)},\chi\right)\, , \\
\label{eq:lenseff}
g(\chi,p_i) =& \int_\chi^{\chi_H} {\rm d}\chi'\, p_i(\chi') \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
\end{align}
Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions.
\subsection{Using an analytic Model}
For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal. Following \citet{2006APh....26...91V}, we estimate
\[
\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
\]
\todo{Maybe implement redshift-dependent index?}
Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.

%For a pair of galaxies that we use to measure the correlation function, it is crucial to determine whether those two galaxies lie within the same pointing. We want to define a function $E(\theta)$ that determines

Let $N(\b \theta)$ be the number-density per tile and $W(\b \theta)$ the weighting of average shear. The observed correlation function $\xi^{\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{\rm const}$ via 
\begin{align*}
\xi^{\text{obs}}_\pm(\theta) = & \frac{\la N(\b 0)N(\b \theta)\gammao_{\rm t}(\b 0)\gammao_{\rm t}(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \pm \frac{\la N(\b 0)N(\b \theta)\gammao_\times(\b 0)\gammao_\times(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \\
 = & \frac{\la N(\b 0)N(\b \theta)W(\b 0)W(\b \theta)\ra}{\la N(\b 0)N(\b \theta)\ra} \xi_{\pm}^{\rm const}(\theta) \, .
 \end{align*}
 Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing. We want to denote the probability that a random pair of galaxies of distance $\theta$ lie in the same pointing with $E(\theta)$. An analytical expression for this function is surprisingly hard to obtain, but it can easily be calculated to arbitrary accuracy, following the procedure explained in Appendix \ref{sec:details on etheta}. The function is depicted in Figure \ref{fig:eoftheta_lin}.

 \begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{images/eoftheta.png}
 \caption{Probability that a random pair of galaxies of distance $\theta$ lie in the same pointing.}
 \label{fig:eoftheta_lin}
 \end{figure}

We again parametrize the number density $N(\b \theta)=\la N \ra (1+n(\b \theta))$ and the weight $W(\b \theta)=1+w(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n(\b \theta)$ as a locally constant function with average $\la n \ra = 0$. We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get
 \begin{align}
\xi^{\text{obs}}_\pm(\theta) = & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta) \\
\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, . \nonumber
 \label{eq:ffunct}
\end{align}
\todo{The formula for a cross-correlation of different bins is much longer, but follows the same principle. Maybe put it into the Appendix?}
We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.

However, as a survey of constant depth is completely unrealistic, also the modelled correlation function will be subject to the same effect. If we assume the same redshift-distributions for galaxies as in the case of varying depth, and just assert that those changes are not correlated with position, we get 
\begin{equation}
\xi_\pm = (1+2\la nw\ra)\xi_\pm^{\rm const}\, .
\end{equation}
The ratio of modelled and observed correlation function thus becomes: \begin{align}
\frac{\xi_\pm}{\xi_\pm^{\rm obs}} = & \frac{\left(1+2\la nw\ra\left)\left(1+E(\theta)\la n^2\ra\right)\right.\right.}{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]} \\
\equiv & F(\theta) \, .
\end{align}
%It is interesting to note that $F(\theta)=1$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. 
We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts. 
\subsection{Using a semi-analytic Model}
The analysis of data from the Kilo-Degree Survey showed that the redshift-distribution of sources was highly correlated with the depth in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on. Now for each percentile $i$ and each tomographic redshift bin $z$ we can extract a weighted number density of galaxies $N_i(z)$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p_i(z)$. Using \eqref{eq:xipm-pkappa}, we can for each set of percentiles $i,j$ and redshift bins $z_1,z_2$ compute the shear correlation function $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.\todo{Should we cite \textsc{nicaea} here?} When we compute the measured shear correlation function of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process). If, for a single pair of galaxies, one galaxy lies in the $i$-th percentile of redshift bin $z_1$ and the second one lies in the $j$-th percentile of redshift bin $z_2$, then their contribution to the observed correlation function is, on average, $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$. This means that if we know each of those single correlation functions, we can reconstruct the total correlation function via a weighted average of the single functions. As an example, if we want to calculate the correlation function between tomographic bins $z_1$ and $z_2$ and pick a galaxy from bin $z_1$, the probability of this galaxy being in the $i$-th percentile of $z_1$ is proportional to $N_i(z_1)$. Now let the second galaxy be in bin $z_2$ and of distance $\theta$ to the first. If we imagine a thin annulus of radius $\theta$ around the first galaxy, then the number of galaxies in this annulus, that lie within the same pointing as the first galaxy, is proportional to $E(\theta)N_i(z_2)$, whereas the number of galaxies that lie in a different pointing is $[1-E(\theta)]\la N(z_2)\ra$, where $\la N(z_2)\ra$ is the average number density in redshift bin $z_2$. If the galaxy lies within a different pointing, the chances of it being in the $j$-th percentile are again just proportional to $N_j(z_2)$. We conclude that if we sum the single correlation functions $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$ according to these weightings, we can simulate the observed correlation function that accounts for the variation in optical depth via 
\begin{align}
\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \la N(z_2)\ra\sum_{j=1}^{10}\frac{  N_j(z_2)}{\sum_k N_k(z_2)} \big[1-E(\theta)\big]\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\} \nonumber \\
 = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \sum_{j=1}^{10}\frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\}\, ,
\label{eq:correctionfunction1}
\end{align}
with the normalization
\[
C = \sum_{i=1}^{10} N_i(z_1) \bigg[ E(\theta)  N_i(z_2) + \sum_{j=1}^{10} \frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\bigg]\,.
\]
A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
If we want to compute this for all 5 redshift bins of the KiDSV-survey, this forces us to calculate 1265 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive). However, if we examine Equation \eqref{eq:lenseff}, we see that it is linear in its second argument, which in turn makes Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} bilinear in their second and third arguments. This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation function of that. As an example, the following equation holds: \[
N_j\xi_\pm[\theta,p_i,p_j]+N_k\xi_\pm[\theta,p_i,p_k] = (N_j+N_k)\,\xi_\pm\left[\theta,p_i,\frac{N_jp_j+N_kp_k}{N_j+N_k}\right]\, .
\]
Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
\begin{equation}
\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{C}\bigg\{ E(\theta)\sum_{i=1}^{10} N_i(z_1)N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] +\frac{1}{10}\big[1-E(\theta)\big]\xi_\pm\left[\theta,p(z_1),p(z_2)\right]N(z_1)N(z_2)\bigg\}\, .
\label{eq:correctionfunction2}
\end{equation}
Here, we defined the \textit{average redshift distribution} $p(z)$ and \textit{combined number density} $N(z)$ of tomographic bin $z$ as \[
p(z):= \frac{\sum_i N_i(z)p_i(z)}{\sum_i N_i(z)}\, , \qquad N(z):=\sum_i N_i(z)\, .
\]
\todo{Maybe label the $N(z)$ differently to avoid confusion with $\la N(z)\ra$?}
For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165. We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N(z_1)N(z_2)$ and thus \[
\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{N(z_1)N(z_2)}\xi_\pm\left(\theta,n(z_1),n(z_2)\right)N(z_1)N(z_2) = \xi_{\pm,z_1,z_2}(\theta)\, ,
\]
so on large scales our observed correlation function agrees with the one that we would usually calculate.

### 2019-04-11 results.tex

\section{Results}
\label{sec:results}
We applied both our methods to data from the KiDSV-450 survey and computed the ratio of observed and modeled correlation functions. Furthermore, we have conducted a simulation using ray-tracing through the millenium simulations (?)\todo{I should ask catherine about what exactly she did for the simulations or maybe even ask her to write this part of the paper?}. As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins. The result can be seen in Figure \ref{fig:all_xis}.
	\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{images/xis_111.png}
	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.}
	\label{fig:all_xis}
	\end{figure}
We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge. We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk? Maybe in the appendix to avoid too many Figures?} The simulations seem to be in rough agreement with the models, but there are some features that can not be explained. Especially we observe that the ratios of the correlation functions for large values of $\theta$ seem to consistently surpass unity, which can not be explained by our models.

As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model. Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}. As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.\todo{Maybe expand this to more parameters?}  As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties. However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area. As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.

To estimate the B-Modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare \citet{2010A&A...520A.116S}), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth. We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}. Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KiDSV-450 survey for the same range in $\theta$. The real B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant. Given these facts, we conclude that the creation of B-Modes due to varying depth in the KiDS survey is not significant. However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, that show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).

\begin{figure}
\centering
\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/bmodes.pdf}
\caption{The $B$-modes created by a variation in survey-depth. We used the logarithmic COSEBIs described in \citet{2010A&A...520A.116S} with a range from $\theta_{\rm min} = 0.5\arcmin$ to $\theta_{\rm max} = 100\arcmin$.}
\label{fig:bmodes_cosebi}
\end{figure}

### 2019-04-11 thesis_appendix.tex

%------------------------------------------------------------------------------
\chapter{Detailed calculations}
\section{Calculation of the power spectrum}
In this Section we will perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$. For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$. In reality, finite field effects would play a role here. We begin with the calculation of the correlation for the Fourier transformed shear:
\begin{align}
& \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\nonumber\\
 &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta')\ra\nonumber\\
 &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta') \int \frac{\text{d}^2 k}{(2\pi)^2}\int \frac{\text{d}^2 \ell}{(2\pi)^2}\, \tilde{\gamma}(\b k)\tilde{\gamma}^*(\b \ell)\exp(-\i \b k\b \theta+\i \b \ell\b \theta')\ra \nonumber\\
&\qquad = \la \int \text{d}^2 \theta \int \text{d}^2 \theta' \int \frac{\text{d}^2 k}{(2\pi)^2} \int \frac{\text{d}^2 \ell}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b \ell) \exp[\i (\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b \ell\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
  &\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \int \text{d}^2 \theta\, W(\b \theta)\exp[\i\b \theta(\b \ell-\b k)]\int \text{d}^2 \theta'\, W(\b \theta') \exp[-\i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
  &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k)\widetilde{W}(\b \ell-\b k)\widetilde{W}^* (\b \ell'-\b k)\ra
\end{align}
It is important to keep in mind that the ensemble averages of the weight function are independent of the ensemble averages of the shear values, meaning $\la W(\b \theta)\gamma(\b \theta)\ra = \la W(\b \theta)\ra \la \gamma(\b \theta)\ra$. We can define $W(\b \theta)=1+w(\b\theta)$ with $\la w(\b \theta)\ra = 0$, which leads to the expession
\begin{align}
& \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \nonumber\\
 &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \tilde{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \tilde{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]\right.\right. \nonumber\\
 & \quad\qquad \left.\left. + \tilde{w}(\b \ell-\b k)\tilde{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
 &\qquad =  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \left[ \la \tilde{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \tilde{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\right] + \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
& \qquad \overset{(*)}{=}  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
\label{eq:pobs1}
\end{align}
where in $(*)$ we have used that the average $\la \tilde{w}(\b \ell)\ra$ vanishes.
Up until now, we have not specified our weight-function $w$. We parametrize it as \begin{equation}
w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
0 \qquad \text{else}
\end{cases}.
\end{equation}
Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier-Transform we compute: \begin{equation}
\tilde{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-\i \b \ell L\b \alpha) \widetilde{\Xi}(\b \ell)\, ,
\end{equation}
where
\begin{equation}
\widetilde{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
\end{equation}
is a 2-dimensional sinc function.
Assuming an uncorrelated weight-distribution $\left(\la w_{\b \alpha} w_{\b \beta}\ra = 0\text{ for }\b \alpha\neq\b \beta\right)$ and setting $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ for each $\b \alpha$, we get
\begin{align}
&\la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
&\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-\i(\b \ell - \b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k) \exp[\i(\b \ell' - \b k)L\b \beta]\, \widetilde{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
&\qquad = \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-\i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k)\widetilde{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
\end{align}
Using this result, we can obtain the observed power spectrum \begin{equation}
P^{\rm{obs}}(\b\ell) = \frac{1}{(2\pi)^2}\int\d^2\ell' \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\, ,
\end{equation}
by performing the $\b \ell'$-integration in \eqref{eq:pobs1}:
\begin{align}
P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha+\i(\b \ell'-\b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell-\b k)\widetilde{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widetilde{\Xi}^*(\b \ell'-\b k)\exp[\i(\b \ell'- \b k)L\b \alpha] \nonumber\\
 = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widetilde{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-\i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
 = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widetilde{\Xi}(\b \ell-\b k)P(\b k)\, ,
\end{align}
which is a convolution of the power spectrum and the 2-dimensional sinc function.
\label{sec:calc of PS}

\section{Calculation of the shear correlation functions}
\label{sec:calc of xipm}
Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation functions via \begin{equation}
\xi^{ij}_+(\theta) = \frac{\sum_{a,b}w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*}\Delta(|\b\theta_a^i-\b\theta_b^i|)}{\sum_{a,b}w_a^iw_b^j\Delta(|\b\theta_a^i-\b\theta_b^i|)}\, .
\label{eq:xip_from_observations}
\end{equation}
Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky. We have defined the function $\Delta$ as \[
\Delta(|\b\theta_a^i-\b\theta_b^i|) = \begin{cases}
1, \,\, & |\b\theta_a^i-\b\theta_b^j| \in [\theta,\theta+{\rm d}\theta] \\
0, & \text{ else}
\end{cases}\, ,
\]
where we assume ${\rm d}\theta \ll \theta$. We define $N$ as the number of pointings in the survey and $F_k^i$ as the set of galaxies in pointing $k$ and tomographic bin $i$. The numerator in Equation \eqref{eq:xip_from_observations} then transforms to: \begin{align}
& \sum_{k,\ell=1}^N \sum_{a\in F_k^i}\sum_{b\in F_{\ell}^j} w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*} \Delta(|\b\theta_a^i-\b\theta_b^i|) \nonumber\\
 = & \sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \sum_{\ell=1}^N \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} \nonumber\\
  = & \sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \left[\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} + \sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*}\right] \, .
\end{align}
When we denote the probability that pointing $k$ is of percentile $m$ by $P_m^k$ and assume that the product $\epsilon_a^i\epsilon_b^{j*}$ always equals its expectation value, we can set the numerator as \[
\sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \sum_m P_m^k \left[\overbrace{\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.a)}}\,  \xi_{+,mm}^{ij}(\theta) + \overbrace{\sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.b)}} \sum_n P_n^{\ell} \xi_{+,mn}^{ij}(\theta)\right] \, .
\label{eq:numerator1}
\]
The term (\ref{eq:numerator1}.a) denotes all galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a$, and are in the same pointing as galaxy $a$. This term is equal to the (weighted) number density of galaxies in the pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$.

The term (\ref{eq:numerator1}.b) denotes all galaxies within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a$, that are \textit{not} in the same pointing as galaxy $a$. This is equal to the number density of galaxies in the respective pointings multiplied by $2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]$.

If we assume that said number density in a pointing is equal to the number density in the percentile it belongs to, $N_n^j$, and set $P_n^\ell=1/10$, the numerator becomes \begin{align}
\sum_{k=1}^N \sum_{a\in F_k^i} w_a^i \sum_m P^k_m \left[2\pi\theta\,\d\theta\,E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + 2\pi\theta\,\d\theta\,\frac{1-E(\theta)}{10}\, \sum_n N_n^j \xi_{+,mn}^{ij}(\theta) \right] \, .
\end{align}
Now the term $\sum_{a\in F_k^i} w_a^i$ denotes the (weighted) number of galaxies in pointing $k$, which we set as the number density of galaxies in the respective percentile multiplied with the area $A$ of the pointing. Applying this and setting $P_m^k=1/10$, the numerator reads 
\begin{align}
\frac{2\pi\theta\,\d\theta}{10} \sum_{k=1}^N \sum_m N_m^i A &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \nonumber\\
 =  \, \frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \, .
\end{align}
%
 The same line of argumentation can be applied to the denominator, which then reads: \[
\frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i \left[ E(\theta) N_m^j + \frac{1-E(\theta)}{10}\sum_n N_n^j\right]\, .
 \]
Taking the ratio of the two quantities, we see that Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} are the same\footnote{Note that while here $N_m^i$ denotes a number density, in Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} it denotes the total (weighted) number of galaxies. However, the difference is just a multiplication with the area $A$ of the pointings, which appears both in the numerator and the denominator and is thus cancelled out.}.
\chapter{Outlook: Finite field effects}
\label{sec:expand_eoftheta}
\begin{SCfigure}
    \centering
    \def\svgwidth{200pt}    
%    \hspace*{1cm}
    \input{../figs/expand_eoftheta.pdf_tex}  
%    \hspace*{-2cm}
    \caption[Graphic how to obtain $E_{ab}(\theta)$]{Graphic representation of the definitions of $E_{ab}(\theta)$. When the first galaxy is in the bottom left pointing, the probability to find the second galaxy in a pointing of distance $(a,b)$ is $E_{mn}(\theta)$.}
    \label{fig:expand_etheta}
\end{SCfigure}
In this chapter we will outline how to calculate the correction of the correlation functions for a finite survey with a potentially correlated distribution of depth between pointings. Essentially, this boils down to the calculation of $P_{mn}^{ij}(\theta)$ from Equation \eqref{eq:def_xiobs}. We calculate this weighting by the geometrical probability that a pair of galaxies of separation $\theta$ is of percentiles $m$ and $n$, $P(m,n|\theta)$, weighted by the respective number of galaxies in the percentiles $N_m^i,N_n^j$: \[
P_{mn}^{ij}(\theta) = N_m^iN_n^jP(m,n|\theta)\, .
\label{eq:pmnij1}
\]
 At first we define Functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$. This situation is depicted in Figure \ref{fig:expand_etheta}. Due to symmetry, for the azimuthal average of the functions, $E_{ab}(\theta) = E_{-ab}(\theta) = E_{ba}(\theta)$ holds for all combinations of $a$ and $b$. Note that $E_{00}(\theta)=E(\theta)$ and $\sum_{a,b}E_{ab}(\theta)\equiv 1$.

Let $P^*(m,n|a,b)$ denote the probability that two pointings of distance $(a,b)$ are of percentile $m$ and $n$ (which is directly calculable from a given survey footprint). 
Then the following equation holds: \[
P(m,n|\theta) = \sum_{a,b} E_{ab}(\theta)P^*(m,n|a,b)\, .
\label{eq:pmntheta}
\]
Note that the expectation value of $P^*(m,n|a,b)$ for uncorrelated distributions is \[
\la P^*(m,n|a,b)\ra = \begin{cases}
0.1\,\delta_{mn},\qquad & \text{for }(a,b)=(0,0) \\
0.01, & \text{else}
\end{cases}\, ,
\label{eq:pmnabstar}
\]
where $\delta_{mn}$ denotes the Kronecker delta. Keeping in mind that \[
\sum_{(a,b)\neq (0,0)} E_{ab}(\theta) = 1-E(\theta)\, ,
\]
we can use the expectation value \eqref{eq:pmnabstar} to calculate \eqref{eq:pmntheta} as a consistency check. In that case, we receive the same value for the coefficients in \eqref{eq:pmnij1} as we have in Equation \eqref{eq:pmnij_uncorr} in Chapter \ref{sec:xipm_semianalytic} for the case of an infinite footprint and uncorrelated distribution of depth.

\begin{figure}
\centering
\begin{subfigure}[c]{0.49\textwidth}
\def\svgwidth{100pt}
\hspace*{2cm}
\input{../figs/graphics/e_1.pdf_tex}
\subcaption{For $\theta\sin(\phi)<L$ the volume of the dashed rectangle is $V(\theta,\phi)=\theta\sin(\phi)[L-\theta\cos(\phi)]$.}
\label{fig:e01thetaa}
\end{subfigure}
\begin{subfigure}[c]{0.49\textwidth}
\def\svgwidth{100pt}
\hspace*{2cm}
\input{../figs/graphics/e_2.pdf_tex}
\subcaption{For $\theta\sin(\phi)>L$ the volume of the dashed rectangle is $V(\theta,\phi)=[2L-\theta\sin(\phi)]\, [L-\theta\cos(\phi)]$.}
\label{fig:e01thetab}
\end{subfigure}
\caption[How to calculate $E_{01}(\theta)$]{How to calculate $E_{01}(\theta)$ for different values of $\theta$.}
\label{fig:e01theta}
\end{figure}

The $E_{ab}$ can all be calculated analytically, similar to our method in Chapter \ref{sec:model_e}. We again assume a selection of square fields with side length $L$, and later set $L=60\arcmin$ to adapt to the KV450 survey. As an example, for $E_{01}$ we have several possible situations, depicted in Figure \ref{fig:e01theta}. For a separation vector $\b\theta$ with modulus $\theta<L$ and inclination angle $\phi$, the dashed rectangle in Figure \ref{fig:e01theta}\subref{fig:e01thetaa} depicts the galaxies that have a partner in the upper pointing. For $L<\theta<\sqrt{2}L$, the dashed rectangle in Figure \ref{fig:e01theta}\subref{fig:e01thetaa} represents the area of galaxies with a partner in the upper square under the condition that $\theta\sin(\phi)<L$. For $\theta\sin(\phi)>L$, the situation is depicted by Figure \ref{fig:e01theta}\subref{fig:e01thetab}. As soon as $\theta>\sqrt{2}L$ holds, the situation of Figure \ref{fig:e01theta}\subref{fig:e01thetaa} is impossible. When $\theta<2L$ holds, the vector is only constrained by $\theta\cos(\phi)<L$, but as soon as $\theta >2L$ holds, we additionally need to impose $\theta\sin(\phi)<2L$. Again setting $E_{ab}(\b\theta) = V(\theta,\phi)/L^2$, we define \begin{align}
E_{01}^{(a)}(\b\theta) & \equiv \frac{\theta}{L}\sin(\phi)[1-\frac{\theta}{L}\cos(\phi)] \nonumber\\
E_{01}^{(b)}(\b\theta) & \equiv [2-\frac{\theta}{L}\sin(\phi)]\, [1-\frac{\theta}{L}\cos(\phi)]
\end{align}
Taking the azimuthal average, we compute:
{
\begingroup
\addtolength{\jot}{1em}
\begin{align}
E_{01}(\theta) = & \begin{cases}
\frac{1}{\pi}\int_0^{\frac{\pi}{2}} \d\phi\, E_{01}^{(a)}(\b\theta) & \frac{\theta}{L} < 1 \\[10pt]
 \frac{1}{\pi}  \left[\int_{\cos\inv(L/\theta)}^{\sin\inv(L/\theta)}\d\phi\,E_{01}^{(a)}(\b\theta) + \int_{\sin\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) \right]  & 1 < \frac{\theta}{L} < \sqrt{2} \\[10pt]
 \frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) & \sqrt{2}<\frac{\theta}{L}<2 \\[10pt]
\frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\sin\inv(2L/\theta)}\d\phi\, E_{01}^{(b)}(\b\theta) & 2<\frac{\theta}{L}<\sqrt{5} \\[10pt]
 0 & \sqrt{5}<\frac{\theta}{L}
\end{cases}\nonumber\\
 = & \begin{cases}
 \frac{(2L-\theta)\theta}{2\pi L^2} & \frac{\theta}{L} < 1 \\[10pt]
 \frac{1}{\pi}\left[\frac{3}{2}- 2\frac{\theta}{L}+\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-1}+2\rm{sec\inv}\left(\frac{\theta}{L}\right)\right] & 1<\frac{\theta}{L}<\sqrt{2} \\[10pt]
 \frac{1}{2\pi}\left[-1-4\frac{\theta}{L}+4\sqrt{\frac{\theta^2}{L^2}-1}+4\rm{csc\inv}\left(\frac{\theta}{L}\right)\right] & \sqrt{2} < \frac{\theta}{L} < 2 \\[10pt]
 \frac{1}{2\pi}\left[-5-\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-4}+4\sqrt{\frac{\theta^2}{L^2}-1}-4\rm{sec\inv}\left(\frac{\theta}{L}\right)+4\sin\inv\left(\frac{2L}{\theta}\right)\right] & 2 < \frac{\theta}{L} < \sqrt{5} \\[10pt]
 0 & \sqrt{5}<\frac{\theta}{L}
 \end{cases}\, .
\end{align}
\endgroup
}

\begin{SCfigure}
\centering
\def\svgwidth{120pt}
\input{../figs/graphics/drawing.pdf_tex}
\caption[Visualisation of the numerical computation for $E_{01}(\theta)$.]{Visualisation of the numerical computation for $E_{01}(\theta)$. For a circle of radius $\theta$, the length of the red arc divided by $2\pi$ represents the fraction of galaxies within the respective pointing. This value needs to be integrated for all possible centers of the circle in the pointing. That procedure is straightforward to expand for other $E_{ab}(\theta)$.}
\label{fig:eoftheta_sim}
\end{SCfigure}

\begin{figure}
\centering
\includegraphics[width = 0.8\textwidth]{eab.pdf}
\caption{The functions $E_{ab}(\theta)$ for the first few possible combinations.}
\label{fig:eab}
\end{figure}
Naturally, to calculate those functions for all possible combinations would be rather tedious, however they are simple to determine numerically (compare Figure \ref{fig:eoftheta_sim}). A plot of these functions can be found in Figure \ref{fig:eab}.

When we now simulate random distributions of the depth-function for a $100\,\rm{deg}^2$-field, a $450\,\rm{deg}^2$-field and a $1000\,\rm{deg}^2$-field, we can compare how they differ from each other and estimate how important finite-field effects are. As can be seen from Figures \ref{fig:100degsqr}, \ref{fig:450degsqr} and \ref{fig:1000degsqr}, the effect is quite significant for a $100\,\rm{deg}^2$-field, but almost negligible for a $1000\,\rm{deg}^2$-field. This leads to the assumption that both for the KiDS- as for the Euclid-survey, finite field effects do not need to be accounted for. However, if the distribution of depth is correlated in the surveys, that might have a noticeable impact on the results.

\chapter{Additional figures and fables}
\section{Additional tables}
\begin{table}[h]
\centering
\caption{Weighted number of galaxies $N$ and average redshift $\la z \ra$ for each percentile of each bin.}
\hspace*{0.5cm}
\begin{tabular}{c|cc|cc|cc|cc|cc}
Percentile & \multicolumn{2}{c|}{Bin 1} & \multicolumn{2}{c|}{Bin 2} & \multicolumn{2}{c|}{Bin 3}& \multicolumn{2}{c|}{Bin 4}& \multicolumn{2}{c}{Bin 5} \\
 & $\la z \ra$ & $N$ & $\la z \ra$ & $N$& $\la z \ra$ & $N$& $\la z \ra$ & $N$& $\la z \ra$ & $N$ \\
\toprule
 1 & 0.36 &  33230 & 0.45 &  45630 & 0.59 &  57873 & 0.78 &  33053 & 0.94 &  23633 \\
 2 & 0.40 &  37848 & 0.48 &  52642 & 0.62 &  69929 & 0.80 &  44464 & 0.97 &  31352 \\
 3 & 0.42 &  38410 & 0.49 &  56986 & 0.64 &  74411 & 0.81 &  47164 & 0.97 &  34352 \\
 4 & 0.44 &  37445 & 0.50 &  54066 & 0.66 &  75132 & 0.82 &  46911 & 0.98 &  34788 \\
 5 & 0.46 &  38698 & 0.52 &  57357 & 0.67 &  75679 & 0.83 &  49620 & 0.99 &  39126 \\
 6 & 0.49 &  40742 & 0.54 &  55456 & 0.69 &  82209 & 0.84 &  53458 & 0.99 &  42326 \\
 7 & 0.51 &  38417 & 0.55 &  56883 & 0.70 &  80228 & 0.85 &  54378 & 1.01 &  44319 \\
 8 & 0.51 &  40110 & 0.56 &  60966 & 0.72 &  91835 & 0.86 &  63515 & 1.01 &  49094 \\
 9 & 0.59 &  39655 & 0.59 &  59207 & 0.75 &  87330 & 0.86 &  59674 & 1.02 &  53566 \\
10 & 0.63 &  41653 & 0.62 &  64526 & 0.80 & 104866 & 0.89 &  79990 & 1.04 &  63426 \\
\bottomrule
\end{tabular}
\label{tab:nvsz}
\end{table}

\clearpage
\section{Results of the MCMC}
\begin{figure}[h]
\centering
	\includegraphics[width=0.7\textwidth]{obscorr.pdf}
	\caption{Bias in the parameters for a KiDS-like Survey.}
	\label{fig:mcmc_kids}
\end{figure}  
\begin{figure}[h]
\centering
	\includegraphics[width=0.7\textwidth]{euclid.pdf}
	\caption{Bias in the parameters for a Euclid-like Survey.}
	\label{fig:mcmc_euclid}
\end{figure}  
\clearpage
\section{Finite field effects}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{100degtwofoot_final.pdf}
\caption[Correction of the correlation functions for a $100\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $100\,\rm{deg}^2$-field.}
\label{fig:100degsqr}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{450degtwofoot_final.pdf}
\caption[Correction of the correlation functions for a $450\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $450\,\rm{deg}^2$-field.}
\label{fig:450degsqr}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{1000degtwofoot_final.pdf}
\caption[Correction of the correlation functions for a $1000\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $1000\,\rm{deg}^2$-field.}
\label{fig:1000degsqr}
\end{figure}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End:

### 2019-04-11 thesis_discussion.tex

\chapter{Discussion and conclusion}
\label{sec:discussion}
In this thesis, we have analysed the effects of varying depth on different shear statistics. We started with the simplest case of Gaussian random fields being modified by a weight function with weights following a normal distribution, and then gradually moved on to more realistic cases. There are, however, a few simplifications that we could not get rid of. In this chapter, we will discuss the remaining assumptions and their impact on the results.
\begin{enumerate}
\item In the most general terms, we are analysing the effects of a position-based selection function on cosmic shear surveys. In our analysis, this selection function was governed by the $r$-band depth of a pointing. This neglects a number of other effects: The depth in different bands and the seeing of a pointing will also modify the number densities and redshift distributions on the scale of a pointing, whereas dithering strategies as well as imperfections in the telescope and CCD cause modifications on sub-pointing scales. However, we believe that these effects are subdominant compared to the variations caused by the $r$-band depth.

\item We have assumed an infinitely large survey area with an uncorrelated distribution of the depth-function. While the boundary effects arising from a finite survey footprint would have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has less neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the shot noise of the depth-distribution. We have assumed that the probability that a neighbouring pointing is of percentile $n$ is exactly the expectation value, namely $1/10$. While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, Figure \ref{fig:all_xis} clearly shows that it is not valid for a $100\,\rm{deg}^2$ field. Whether our assumption holds true for the $450\,\rm{deg}^2$ footprint of the KV450 survey, or even the $1350\,\rm{deg}^2$ footprint of the final survey is an important question. Also, we have assumed an uncorrelated distribution of the depth-function, both in the simulations as well as in the models. While this is likely true as a rough approximation (very few pointings of the survey were taken on the same night and thus under the same weather conditions), effects like airmass, lunar phase, Galactic extinction and seasonal weather are likely to influence the depth on scales larger than one pointing.

These effects, however, can be mitigated: When investigating Equations \eqref{eq:pmnij_corr1} and \eqref{eq:pmnij_corr2}, we see that $P(m|n,\theta)$ denotes the probability that when one galaxy of a pair is in percentile $n$, then the second galaxy, in a different pointing, is of percentile $m$. We set this to $1/10$, but a more sophisticated approach is possible here: One can construct functions, similar to $E(\theta)$, representing the probability that the galaxy is in a neighbouring pointing in a certain direction. Then one can construct the probability distribution that this exact neighbouring pointing is of percentile $m$, given the actual survey footprint. This mitigates boundary effects, finite field effects and a correlated distribution of depth-functions and should thus be done in future analysis. An outlook to this and a few examples are given in Appendix \ref{sec:expand_eoftheta}. As a preliminary result we find that finite field effects are not significant for a $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$-field, if the distribution of depth is uncorrelated.

\item In our MCMC simulations we did not account for degeneracies with other cosmological parameters
% (apart from $\Omega_{\rm m}, \sigma_8, w_0$ and $w_a$)
 or observational effects. Especially intrinsic alignments and baryonic feedback also modify the correlation functions especially on small scales, so they are probably degenerate with the effect of varying depth. In an actual MCMC simulation that accounts for these effects, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, and the impact on cosmological parameters is actually smaller than in our results. Also, possible degeneracies between $S_8$ and other cosmological parameters might bias the resulting values. %Furthermore, when including the effects of dark energy we notice that our observation of $S_8$ being constant is no longer valid: For a `Euclid-like' survey we notice a bias of $\sim 0.8\sigma$. This gives rise to the assumption that the results of an MCMC with the full parameter space, including observational effects, will differ from our results. 
\end{enumerate}

Despite these repercussions, we are confident to say that the effects of varying depth are not significant for the KV450 survey. The cosmological parameters did not change significantly and the main parameter, $S_8$, is especially robust against this effect. In particular this means that a varying depth can not explain the discrepancy between observations of the local Universe and results from analysis of the CMB.

We have shown that this effect can create B-modes. However, \citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range. Those B-modes are at least one order of magnitude larger and still consistent with zero, so it is safe to say that the modes created by varying depth are negligible. An interesting observation is that the change in E-modes is as big as the created B-modes (compare Figure \ref{fig:cosebis_eandb}). This means that as soon as this effect causes significant biases in the cosmological parameters, it will also create significant B-modes\footnote{While this is no big surprise, it is not trivial. It could be possible that a systematic effect only creates E-modes and no B-modes, which would be extremely unfortunate as it could bias cosmological parameters without ever being detected by a B-mode analysis.}. Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey.

For next-generation surveys like Euclid, this effect will be significant. Although Euclid is a space-based telescope, the photometric redshift determination will still be done by ground-based telescopes and therefore suffer from the same effects. While this thesis in no way serves as a quantitative study of this effect for Euclid, it does indicate that a such a study should be conducted.

As an outlook it would be interesting to perform a full MCMC simulation, including both cosmological and nuisance parameters. One might also check the most popular extensions to the standard model of cosmology, and see whether varying depth could cause a bias towards one of these models. Furthermore, the method developed in Appendix \ref{sec:expand_eoftheta} could be applied to the actual footprint of the KV450 survey to see whether finite field effects or a correlated distribution of $r$-band depth are significant.
Additionally is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$, which is not isotropic. Therefore, it would be possible to observe a direction-dependent correlation function $\xi_\pm^{ij,\rm{obs}}(\b\theta)$ in future surveys. An anisotropy in the observed correlation function could be a sign for the influence of varying depth.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End:

### 2019-04-11 thesis_intro.tex

%==============================================================================
\chapter{Introduction}
\label{sec:intro}
%==============================================================================

For the last two decades, the $\Lambda$CDM model has been the standard model of cosmology. With only a few free parameters, it is able to explain a huge variety of observations; the existence and fluctuations of the Cosmic Microwave Background (CMB), the large scale structure in the Universe, the luminosity of supernovae of type Ia and the abundances of light elements all yield roughly consistent results for the standard model. Apart from the nature of Dark Matter and Dark Energy, the challenges for modern cosmology are the precise determination of the free parameters as well as the search for possible extensions to the standard model.

One tool to probe the $\Lambda$CDM Model and determine its parameters was provided by the discovery of cosmic shear: The distortion of light bundles travelling from distant galaxies through the matter distribution of the Universe to Earth provides useful insights on the large scale structure. Contrary to the analysis of the CMB by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology. Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, 
%\citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data,
\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2018arXiv181206076H} report $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$. Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data. This discrepancy has received a lot of attention \citep{2013PDU.....2..166V}. It could be interpreted as a statistical coincidence, a sign of new physics like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P}; or as the manifestation of a systematic effect, either in the cosmic shear surveys or in the Planck mission \citep{2016ApJ...818..132A}, that is not yet accounted for.

As weak gravitational lensing measures a tiny signal over a large sample, it is extremely sensitive to anything that systematically biases the measurements, such that the error bars in current surveys arise to equal parts from statistical and systematic uncertainties \citep[compare][]{2017MNRAS.465.1454H}. With next-generation surveys like the Large Synoptic Survey Telescope and Euclid right at the doorstep, systematic effects in gravitational lensing have received an unprecedented amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}. %\todo{Citations.. \citet{2017MNRAS.464.1676A} has a few...}

To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}. To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics. As \citet{2017MNRAS.465.1454H} reported the significant detection of B-modes, it was well motivated to check for possible systematics that are not yet accounted for. Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.

One systematic effect is the variation of depth in a survey. While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions, that are found in ground-based surveys. To first order, this variation can be modelled by a step-like depth function which varies from pointing to pointing. In this work we assume the specifications of the Kilo-Degree Survey, namely a collection of $1\,\text{deg}^2$ square fields.

We will give a brief overview over the necessary knowledge in cosmology and gravitational lensing in Chapter \ref{sec:theory}. We will then review the extent of the variation of depth in the KiDS+VIKING-450 survey in Chapter \ref{sec:eff_of_var_depth} and develop several models to describe its effect in Sections \ref{sec:toy_model} and \ref{sec:xipm_semianalytic}. Afterwards we will present our results in Chapter \ref{sec:results} and discuss them in Chapter \ref{sec:discussion}, focussing on the used simplifications and possible mitigation strategies.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End:

### 2019-04-11 thesis_results.tex

\chapter{Results}
\label{sec:results}
In the previous chapter we discussed two methods to model the shear correlation functions -- an analytic model, that simply relies on the correlations between number density and average redshift, as well as their respective variances, was introduced in Section \ref{sec:xipm_analytic}, whereas a more sophisticated model, that relies on the computation of the correlation functions from different redshift distributions, was discussed in Section \ref{sec:xipm_semianalytic}. Both of these methods can be applied to data extracted from the KV450 survey, as outlined in the beginning of Chapter \ref{sec:eff_of_var_depth}.

Furthermore, we appreciate to have received some data from Catherine Heymans, who conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles. For each tomographic redshift bin of each percentile, galaxies were placed to trace the respective redshift distribution. Afterwards, their expected shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included). This was compared to a set of simulations where the galaxies were simply distributed according to the combined redshift distribution of each respective tomographic bin.

	\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{allxis_0111.pdf}
	\caption[The ratio of modelled to observed correlation functions]{The ratio of modelled to observed correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins. The upper left triangle shows the ratios for $\xi_+$, the lower right triangle the ones for $\xi_-$. The numbers in the plots denote the respective bins.}
	\label{fig:all_xis}
	\end{figure}

In Figure \ref{fig:all_xis} we can see a plot of the ratios between the modelled and observed correlation functions for each of the three methods. It is interesting to note that for the higher redshift bins, the analytic and semi-analytic methods seem to agree on the whole range of $\theta$. However, especially for $\xi_-$, the lower redshift bins show a significant discrepancy between those two methods, which is expected: The power-law $
\la |\gamma|\ra \propto z^{0.85}
$
inspired by \citet{2006APh....26...91V} is redshift-dependent and thus not valid for all tomographic bins. Furthermore, especially the lower tomographic bins experience a strong variation in average redshift, whereas the simple model is only valid for small variations in redshift.

We also observe that in the semi-analytic model, $\xi_-$ seems to be much stronger affected by this effect. We can explain this by investigating Figure \ref{fig:bessel}: Following Equation \eqref{eq:xipm_from_pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function. This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$. However, $\xi_-$ is obtained by filtering with the 4-th order Bessel function, which peaks at approximately $\ell\theta\approx 5$, so for different $\theta$ this function is sensitive to varying parts of the convergence power spectrum. A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.

The simulations seem to be in rough agreement with the models, but there are some significant differences. After a thorough analysis we explain these discrepancies the following way: The simulations were performed on a $100\,\rm{deg}^2$ field, which means that shot-noise of the fields plays a significant role. After performing the same simulations for a different distribution of depth between the pointings and obtaining completely different results, we are quite certain that this is the dominating effect. The implications of this and possible mitigation strategies will be discussed in Chapter \ref{sec:discussion}.

To estimate the effects on the cosmological parameters, we performed a Markov-Chain-Monte-Carlo (MCMC) simulation. Given a fiducial cosmology, we calculated a reference set of correlation functions and divided them by the ratios plotted in Figure \ref{fig:all_xis}, to simulate an observed correlation function. We then calculated sets of correlation functions for different cosmologies and computed the difference to the reference functions, weighted by the respective elements in the inverse covariance matrix $C\inv$ of the correlation functions, which was determined by \citet{2018arXiv181206076H}. The code for this method is a modified version of work by Jan Luca van den Busch.

As our main interest is the investigation of the parameter $S_8$, we chose to limit our analysis to the $\Omega_{\rm m} - \sigma_8$ plane. For the KV450 survey we saw a slight change in the results for $\Omega_{\rm m}$ and $\sigma_8$, but it was far from being relevant. To estimate the impact for the upcoming Euclid-survey we divided the covariance matrix $C$ by 30, to account for the increased survey area\footnote{We want to stress that this is in no way a valid forecast for the Euclid survey. However, we are positive that the qualitative question whether this effect will be relevant, can be answered using this method.}. In these simulations we saw a bias of about $1\sigma$ both for $\Omega_{\rm m}$ and $\sigma_8$. Curiously, both parameters changed in a way such that the parameter $S_8$ stayed unbiased. The exact values determined by the MCMC simulations can be found in Table \ref{tab:parameter_constraints}, the likelihood functions can be found in Figures \ref{fig:mcmc_kids} and \ref{fig:mcmc_euclid} in the Appendix.
{
\renewcommand{\arraystretch}{1.3}
\begin{table}
\centering
\caption[Parameter constraints from the MCMC simulations]{Parameter constraints from the MCMC simulations for a KiDS-like and a `Euclid-like' survey subject to varying depth.}
\begin{tabular}{c | S S S }
\centering
 & {$\Omega_{\rm m}$} & {$\sigma_8$} & {$S_8$} \\
 \toprule
 Fiducial & 0.250 & 0.849 & 0.775 \\
 KiDS-like & 0.290$_{-0.091}^{+0.045}$ & 0.80\phantom{0}$_{-0.14}^{+0.14}$ & 0.763\phantom{9}$_{-0.027}^{+0.044}$ \\
 `Euclid-like' & 0.264$_{-0.013}^{+0.011}$ & 0.828$_{-0.025}^{+0.025}$ & 0.7759$_{-0.0059}^{+0.0067}$
\end{tabular}
\label{tab:parameter_constraints}
\end{table}
}

As the next step we wanted to investigate the B-modes created by this effect. For this we decided to use the COSEBIs discussed in Section \ref{sec:e_and_bmode_separation}. As the COSEBIs separate E- and B-modes based on a finite interval $[\theta_{\rm{min}},\theta_{\rm{max}}]$, they are convenient to use for real data. As varying depth modifies the correlation functions on scales from $0\arcmin$ to roughly $85\arcmin$, we chose our interval as $\theta_{\rm{min}}=0.\!^\prime 5$ and $\theta_{\rm{max}}=100\arcmin$ to be especially sensitive to this effect. We calculated the logarithmic COSEBIs \citep[compare][]{2010A&A...520A.116S} for a reference set of correlation functions $\xi_\pm$ and a set of correlation functions simulating the observed ones, $\xi_\pm\obs$. To minimize numerical errors, we determined both correlation functions in $10^6$ angular bins. The E- and B-modes determined by this analysis can be seen in Figure \ref{fig:cosebis_all}. As the reference correlation functions should not show any B-modes, they serve as an estimate for the numerical errors. As one can see, those errors are several orders of magnitude lower than the determined E- and B-modes for low $n$, but they rise with increasing $n$. This is not surprising, as for higher $n$ the filter functions $T_{\pm,n}$ from Equation \eqref{eq:ebmodes1} oscillate faster and are thus more prone to numerical errors. As \citet{2018arXiv181002353A} pointed out, $\xi_\pm$ are relatively smooth functions and are thus already pretty well constrained by the first few E-modes. This is the reason why the E-modes start to rapidly drop for higher $n$. The B-modes, however, can have more complicated origins, so that they do not necessarily drop as quickly for higher modes. Due to that, for high $n$ the B-modes actually surpass the E-modes.
\begin{figure}
\centering
\includegraphics[trim={0cm 1cm 2.5cm 0.5cm},clip,width = 0.9\textwidth]{cosebis_all.pdf}
\caption[E- and B-modes of the reference and the observed correlation functions]{Logarithmic E- and B-modes of the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=100\arcmin$.}
\label{fig:cosebis_all}
\end{figure}

When we focus on the difference between reference and observed modes (depicted in Figure \ref{fig:cosebis_eandb}), we notice that the difference in E-modes is roughly as high as the one in the B-modes (where the B-modes of the reference function are zero). We also notice that both the E-modes and the B-modes show a characteristic pattern that is consistent throughout all redshift bins.

\begin{figure}
\centering
\includegraphics[trim={0cm 1cm 2.5cm 0.5cm},clip,width = 0.9\textwidth]{eandbmodes0p5t100.pdf}
\caption[Difference in E- and B-modes between the reference and the observed correlation functions]{Difference in the logarithmic E- and B-modes between the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=100\arcmin$.}
\label{fig:cosebis_eandb}
\end{figure}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End:

### 2019-05-03 model_xipm.tex
Modified derivation of correlation function

@@
 We want to denote the probability that a random pair of galaxies of distance $\theta$ lie in the same pointing with $E(\theta)$.
-An analytical expression for this function is surprisingly hard to obtain, but it can easily be calculated to arbitrary accuracy, following the procedure explained in Appendix \ref{sec:details on etheta}.
-The function is depicted in Figure \ref{fig:eoftheta_lin}.
+This function can be calculated as in Appendix \ref{sec:details on etheta} and equates to
+\begin{equation}
+E(\theta) =  \begin{cases}
+\frac{1}{L^2 \pi}\left[L^2\pi - (4L-\theta) \theta\right]\, ,  & \theta \leq L \\[10pt]
+\frac{2}{\pi}\,\left[4\sqrt{\frac{\theta^2}{L^2}-1} -1 - \frac{\theta^2}{2L^2} - \cos\inv\left(\frac{L}{\theta}\right) + \sin\inv\left(\frac{L}{\theta}\right)\right]\, ,  & L  \leq \theta \leq \sqrt{2}L \\[10pt]
+0\, ,  & \sqrt{2}L \leq \theta
+\end{cases}\, .
+\end{equation} 
+ This function is depicted in Figure \ref{fig:eoftheta_lin}.
 
@@
 We again parametrize the number density $N(\b \theta)=\la N \ra (1+n(\b \theta))$ and the weight $W(\b \theta)=1+w(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n(\b \theta)$ as a locally constant function with average $\la n \ra = 0$.
-We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get
+We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get for the autocorrelation of a single bin,
  \begin{align}
 \xi^{\text{obs}}_\pm(\theta) = & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta) \\
-\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, . \nonumber
+\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, , \nonumber
  \label{eq:ffunct}
 \end{align}
-\todo{The formula for a cross-correlation of different bins is much longer, but follows the same principle. Maybe put it into the Appendix?}
+holds.
 We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.
@@
 \end{align}
+A similar, but longer, equation governs the cross-correlation between different bins. This equation and its derivation can be found in Appendix \todo{create this and cite it.}.
 %It is interesting to note that $F(\theta)=1$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. 
@@
 We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-Now for each percentile $i$ and each tomographic redshift bin $z$ we can extract a weighted number density of galaxies $N_i(z)$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p_i(z)$.
-Using \eqref{eq:xipm-pkappa}, we can for each set of percentiles $i,j$ and redshift bins $z_1,z_2$ compute the shear correlation function $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.\todo{Should we cite \textsc{nicaea} here?} When we compute the measured shear correlation function of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process).
-If, for a single pair of galaxies, one galaxy lies in the $i$-th percentile of redshift bin $z_1$ and the second one lies in the $j$-th percentile of redshift bin $z_2$, then their contribution to the observed correlation function is, on average, $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$.
-This means that if we know each of those single correlation functions, we can reconstruct the total correlation function via a weighted average of the single functions.
-As an example, if we want to calculate the correlation function between tomographic bins $z_1$ and $z_2$ and pick a galaxy from bin $z_1$, the probability of this galaxy being in the $i$-th percentile of $z_1$ is proportional to $N_i(z_1)$.
-Now let the second galaxy be in bin $z_2$ and of distance $\theta$ to the first.
-If we imagine a thin annulus of radius $\theta$ around the first galaxy, then the number of galaxies in this annulus, that lie within the same pointing as the first galaxy, is proportional to $E(\theta)N_i(z_2)$, whereas the number of galaxies that lie in a different pointing is $[1-E(\theta)]\la N(z_2)\ra$, where $\la N(z_2)\ra$ is the average number density in redshift bin $z_2$.
-If the galaxy lies within a different pointing, the chances of it being in the $j$-th percentile are again just proportional to $N_j(z_2)$.
-We conclude that if we sum the single correlation functions $\xi_\pm[\theta,p_i(z_1),p_j(z_2)]$ according to these weightings, we can simulate the observed correlation function that accounts for the variation in optical depth via
+Now for each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p^i_m(z)$.
+Using \eqref{eq:xipm_from_pkappa}, we can compute the shear correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each set of percentiles $m,n$ and redshift bins $i,j$\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program.
+Among other things, it calculates the shear correlation functions for a given cosmology and source redshift distribution.
+To estimate the power spectrum on nonlinear scales we use the methods developed by \citet{2012ApJ...761..152T}.}.
+When we compute the measured shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process).
+If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$.
+This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions.
+Formally, we define \[
+\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} P_{mn}^{ij}(\theta)\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} P_{mn}^{ij}(\theta)}\, ,
+\label{eq:def_xiobs}
+\]
+where $P_{mn}^{ij}$ is the new weighting of the correlation functions.
+This weighting has to be proportional to the probability that a galaxy pair of distance $\theta$ is of percentiles $m$ and $n$, as well as to the original weighting of these galaxies.\todo{We could completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.}
+
+In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
+We will later discuss the validity of these assumptions as well as possible mitigation strategies.
+For $m\neq n$ we know that the pair of galaxies has to lie in different pointings, which is accounted for by including the factor $[1-E(\theta)]$.
+Furthermore, the first galaxy has to lie in percentile $m$, the probability of which is $1/10$.
+When the first pointing is of percentile $m$, the probability that a galaxy in a different pointing is of percentile $n$ is also equal to $1/10$.
+The impact of such a galaxy pair on the correlation functions scales with the product of the weighted number of galaxies $N_m^i,N_n^j$.
+We get for $n\neq m$: \[
+P_{mn}^{ij}(\theta) = [1-E(\theta)]\frac{1}{100} N_m^i N_n^j\, .
+\label{eq:pmnij_corr1}
+\]
+For the calculation of $P_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxy lies in the same pointing [accounted for by the factor $E(\theta)$], it automatically is of the same percentile.
+We therefore set \[
+P_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
+\label{eq:pmnij_corr2}
+\]
+We can then write $P_{mn}^{ij}(\theta)$ as: \[
+P_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, ,
+\label{eq:pmnij_uncorr}
+\]
+where $\delta_{mn}$ denotes the Kronecker delta.
+Inserting this into Eq.\,\eqref{eq:def_xiobs}, we compute
 \begin{align}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \la N(z_2)\ra\sum_{j=1}^{10}\frac{  N_j(z_2)}{\sum_k N_k(z_2)} \big[1-E(\theta)\big]\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\} \nonumber \\
- = & \frac{1}{C}\sum_{i=1}^{10} N_i(z_1) \bigg\{ E(\theta) N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] + \sum_{j=1}^{10}\frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\xi_\pm\big[\theta,p_i(z_1),p_j(z_2)\big]\bigg\}\, ,
+\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\sum_{m=1}^{10} N_m^i \left\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
 \label{eq:correctionfunction1}
@@
 \[
-C = \sum_{i=1}^{10} N_i(z_1) \bigg[ E(\theta)  N_i(z_2) + \sum_{j=1}^{10} \frac{1}{10} \big[1-E(\theta)\big] N_j(z_2)\bigg]\,.
+C = \sum_{m=1}^{10} N_m^i \bigg[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\bigg]\, .
 \]
 A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
-If we want to compute this for all 5 redshift bins of the KiDSV-survey, this forces us to calculate 1265 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive).
-However, if we examine Equation \eqref{eq:lenseff}, we see that it is linear in its second argument, which in turn makes Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} bilinear in their second and third arguments.
-This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation function of that.
-As an example, the following equation holds: \[
-N_j\xi_\pm[\theta,p_i,p_j]+N_k\xi_\pm[\theta,p_i,p_k] = (N_j+N_k)\,\xi_\pm\left[\theta,p_i,\frac{N_jp_j+N_kp_k}{N_j+N_k}\right]\, .
+
+If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive).
+However, if we examine Eq.\,\eqref{eq:lenseff}, we see that the comoving distance distribution of sources factors in linearly.
+This in turn implies that in Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions factor in linearly.
+This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
+In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average redshift distribution} $p^i(z)$ of tomographic bin $i$ as \[
+N^i\equiv\sum_m N_m^i\, , \qquad p^i(z) = \frac{\sum_m N_m^i p_m^i(z)}{\sum_m N_m^i} \, .
+\]
+If we define $\xi^{ij}_\pm$ as the correlation functions between the average redshift distributions $p^i(z)$ and $p^j(z)$, then we observe: \[
+\sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = N^iN^j\xi^{ij}_\pm\, .
 \]
@@
 \begin{equation}
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{C}\bigg\{ E(\theta)\sum_{i=1}^{10} N_i(z_1)N_i(z_2) \xi_\pm\big[\theta,p_i(z_1),p_i(z_2)\big] +\frac{1}{10}\big[1-E(\theta)\big]\xi_\pm\left[\theta,p(z_1),p(z_2)\right]N(z_1)N(z_2)\bigg\}\, .
+\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{C}\left\{ E(\theta)\left[\sum_{m=1}^{10} N_m^iN_m^j \xi_{\pm,mm}^{ij}(\theta)\right] +\frac{\big[1-E(\theta)\big]}{10}\xi_\pm^{ij}(\theta)N^iN^j\right\}\, .
 \label{eq:correctionfunction2}
 \end{equation}
-Here, we defined the \textit{average redshift distribution} $p(z)$ and \textit{combined number density} $N(z)$ of tomographic bin $z$ as \[
-p(z):= \frac{\sum_i N_i(z)p_i(z)}{\sum_i N_i(z)}\, , \qquad N(z):=\sum_i N_i(z)\, .
+For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
+We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N^iN^j$ and thus \[
+\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{N^iN^j}\xi_\pm^{ij}(\theta)N^iN^j = \xi_\pm^{ij}(\theta)\, ,
 \]
-\todo{Maybe label the $N(z)$ differently to avoid confusion with $\la N(z)\ra$?}
-For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
-We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N(z_1)N(z_2)$ and thus \[
-\xi_{\pm,z_1,z_2}^{\rm obs}(\theta) = \frac{1}{N(z_1)N(z_2)}\xi_\pm\left(\theta,n(z_1),n(z_2)\right)N(z_1)N(z_2) = \xi_{\pm,z_1,z_2}(\theta)\, ,
-\]
-so on large scales our observed correlation function agrees with the one that we would usually calculate.
+so on large scales our observed correlation functions agree with the ones that we would usually calculate.

### 2019-05-03 appendix.tex
Added Appendix

@@
 \section{Detailed Calculations}
-\subsection{Calculation of the Power Spectrum}
-In this Section we will perform the calculation for the observed power spectrum \todo{I need to add cdots for scalar products in this section...} $P^{\text{obs}}(\b \ell)$.
+\subsection{Calculation of the power spectrum}
+In this Section we will perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$.
 For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$.
@@
 \begin{align}
-\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta')\ra\nonumber\\
- = & \la\int\text{d}^2\b \theta\int\text{d}^2\b \theta'\,W(\b \theta)W(\b \theta')\exp(i\b \ell\b \theta-i\b \ell'\b \theta') \int \frac{\text{d}^2\b k}{(2\pi)^2}\int \frac{\text{d}^2\b k'}{(2\pi)^2}\, \hat{\gamma}(\b k)\hat{\gamma}^*(\b k')\exp(-i\b k\b \theta+i\b k'\b \theta')\ra \nonumber\\
-= & \la \int \text{d}^2\b \theta \int \text{d}^2\b \theta' \int \frac{\text{d}^2\b k}{(2\pi)^2} \int \frac{\text{d}^2\b k'}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b k') \exp[i(\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b k'\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
-  = & \la \int \frac{\text{d}^2\b k}{(2\pi)^2} \, P(\b k) \int \text{d}^2\b \theta\, W(\b \theta)\exp[i\b \theta(\b \ell-\b k)]\int \text{d}^2\b \theta'\, W(\b \theta') \exp[-i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
-  = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k)\widehat{W}(\b \ell-\b k)\widehat{W}^* (\b \ell'-\b k)\ra
+& \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\nonumber\\
+ &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta')\ra\nonumber\\
+ &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta') \int \frac{\text{d}^2 k}{(2\pi)^2}\int \frac{\text{d}^2 \ell}{(2\pi)^2}\, \tilde{\gamma}(\b k)\tilde{\gamma}^*(\b \ell)\exp(-\i \b k\b \theta+\i \b \ell\b \theta')\ra \nonumber\\
+&\qquad = \la \int \text{d}^2 \theta \int \text{d}^2 \theta' \int \frac{\text{d}^2 k}{(2\pi)^2} \int \frac{\text{d}^2 \ell}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b \ell) \exp[\i (\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b \ell\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
+  &\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \int \text{d}^2 \theta\, W(\b \theta)\exp[\i\b \theta(\b \ell-\b k)]\int \text{d}^2 \theta'\, W(\b \theta') \exp[-\i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
+  &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k)\widetilde{W}(\b \ell-\b k)\widetilde{W}^* (\b \ell'-\b k)\ra
 \end{align}
@@
 \begin{align}
-\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra = & \la \int\frac{\text{d}^2 \b k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big( \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big)\right.\right.
+& \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \nonumber\\
+ &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \tilde{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \tilde{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]\right.\right.
 \nonumber\\
- & \qquad \left.\left. + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
- = & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \big[ \la \hat{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \hat{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\big] + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
-\overset{(*)}{=} & (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
+ & \quad\qquad \left.\left. + \tilde{w}(\b \ell-\b k)\tilde{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
+ &\qquad =  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \left[ \la \tilde{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \tilde{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\right] + \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
+& \qquad \overset{(*)}{=}  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
 \label{eq:pobs1}
 \end{align}
-where in $(*)$ we have used that the average $\la \hat{w}(\b \ell)\ra$ vanishes.
-Up until now, we have not specified our weight-function $w$. So we now parametrize it as \begin{equation}
+where in $(*)$ we have used that the average $\la \tilde{w}(\b \ell)\ra$ vanishes.
+Up until now, we have not specified our weight-function $w$. We parametrize it as \begin{equation}
 w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
@@
 Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier-Transform we compute: \begin{equation}
-\hat{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-i \b \ell L\b \alpha) \widehat{\Xi}(\b \ell)\, ,
+\tilde{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-\i \b \ell L\b \alpha) \widetilde{\Xi}(\b \ell)\, ,
 \end{equation}
@@
 \begin{equation}
-\widehat{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
+\widetilde{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
 \end{equation}
@@
 \begin{align}
-\la \int \frac{\text{d}^2 \b k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra = & \la \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-i(\b \ell - \b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k) \exp[i(\b \ell' - \b k)L\b \beta]\, \widehat{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
- = & \int \frac{\text{d}^2 \b k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)\widehat{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
+&\la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
+&\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-\i(\b \ell - \b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k) \exp[\i(\b \ell' - \b k)L\b \beta]\, \widetilde{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
+&\qquad = \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-\i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k)\widetilde{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
 \end{align}
@@
 \begin{align}
-P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha+i(\b \ell'-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell-\b k)\widehat{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
-= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-i(\b \ell-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widehat{\Xi}^*(\b \ell'-\b k)\exp[i(\b \ell'- \b k)L\b \alpha] \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widehat{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widehat{\Xi}(\b \ell-\b k)P(\b k)\, ,
+P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha+\i(\b \ell'-\b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell-\b k)\widetilde{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
+= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widetilde{\Xi}^*(\b \ell'-\b k)\exp[\i(\b \ell'- \b k)L\b \alpha] \nonumber\\
+ = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widetilde{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-\i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
+ = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widetilde{\Xi}(\b \ell-\b k)P(\b k)\, ,
 \end{align}
-which is a 2-dimensional convolution of the power spectrum and the 2-dimensional sinc function.
+which is a convolution of the power spectrum and the 2-dimensional sinc function.
 \label{sec:calc of PS}
-\subsection{Details on the function $E(\theta)$}
-\label{sec:details on etheta}
-The function $E(\theta)$ is of central importance in this model, so we want to explain how to obtain it.
-It describes, given a pair of galaxies with distance $\theta$, the probability that they are in the same pointing.
-We obtain the function in the following way:
 
-Given one square field of length 1 and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
-As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
-The volume of this square equals \begin{equation}
-\tilde{V}(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, ,
-\end{equation} where $\phi$ represents the angle of the vector $\b\theta$. To exclude negative Volumes (which would occur when $|\b\theta|>1$ holds), we nead to add the Heaviside theta function $H$:
-\begin{equation}
-V(|\b\theta|,\phi)  = \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big] H\big[1-|\b\theta|\cos(\phi)\big]\,H\big[1-|\b\theta|\sin(\phi)\big]\, .
-\label{eq:eoftheta1}
-\end{equation} 
-To obtain the function $E(\theta)$, we need to average Equation \eqref{eq:eoftheta1} over all angles $\phi$.
-While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
-\begin{align}
-E(\theta) = & \frac{4}{2\pi}\int_0^{\frac{\pi}{2}}\d\phi\, V(|\b\theta|,\phi) = \frac{2}{\pi}\begin{cases}
-\int_0^{\frac{\pi}{2}} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , & |\b\theta|\leq 1 \\
-\int_{\arccos(|\b\theta|^{-1})}^{\arcsin(|\b\theta|^{-1})} \d\phi\, \big[1-|\b\theta|\cos(\phi)\big]\,\big[1-|\b\theta|\sin(\phi)\big]\, , \quad & 1\leq |\b\theta| \leq \sqrt{2} \\
-0\, , & \sqrt{2}\leq\theta
-\end{cases} \nonumber\\
- = & \begin{cases}
-\frac{\pi + (\theta-4)*\theta}{\pi}\, , & \theta \leq 1 \\
-\frac{2[-1+2\sqrt{1-\theta^{-2}}*2\theta - \theta^2/2 - \arccos(\theta^{-1}) + \arcsin(\theta^{-1})]}{\pi}\, , & 1\leq \theta \leq \sqrt{2} \\
-0\, , & \sqrt{2}\leq \theta
-\end{cases}\, .
-\end{align}
-\begin{figure}
-    \centering
-    \def\svgwidth{200pt}    
-    \input{images/eoftheta_new.pdf_tex}  
-    \caption{Graphic representation on how to obtain the function $E(\theta)$.
-For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
-    \label{fig:explain_etheta}
-\end{figure}
 \subsection{Calculation of the shear correlation functions}
 \label{sec:calc of xipm}
-Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation function via \begin{equation}
-\xi_+(\theta) = \frac{\sum_{a,b}w_aw_b\epsilon_a\epsilon_b^*\Delta(\b\theta_a-\b\theta_b)}{\sum_{a,b}w_aw_b\Delta(\b\theta_a-\b\theta_b)}\, .
+Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation functions via \begin{equation}
+\xi^{ij}_+(\theta) = \frac{\sum_{a,b}w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*}\Delta(|\b\theta_a^i-\b\theta_b^i|)}{\sum_{a,b}w_a^iw_b^j\Delta(|\b\theta_a^i-\b\theta_b^i|)}\, .
 \label{eq:xip_from_observations}
@@
 Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky. We have defined the function $\Delta$ as \[
-\Delta(\b\theta_a-\b\theta_b) = \begin{cases}
-1, \,\, & |\b\theta_a-\b\theta_b| \in [\theta,\theta+{\rm d}\theta] \\
+\Delta(|\b\theta_a^i-\b\theta_b^i|) = \begin{cases}
+1, \,\, & |\b\theta_a^i-\b\theta_b^j| \in [\theta,\theta+{\rm d}\theta] \\
 0, & \text{ else}
@@
 where we assume ${\rm d}\theta \ll \theta$.
-When we now separate our galaxy samples into the ten percentiles $I$ defined above, and denote the galaxies from sample $a$ that are in pointing $i$ with $a_i$, the numerator in Equation \eqref{eq:xip_from_observations} transforms to:
-\begin{align*}
- & \sum_{i,j=1}^{10} \sum_{a_i,b_j} w_{a_i}w_{b_j}\epsilon_{a_i}\epsilon_{b_j}^*\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
- = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \sum_{j=1}^{10} \sum_{b_j} w_{b_j}\epsilon_{a_i}\epsilon_{b_j}\Delta(\b\theta_{a_i}-\b\theta_{b_j}) \\
- = & \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ \sum_{j=1}^{10} \sum_{b_j\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\epsilonsij \right]
-\end{align*}
-We take the ensemble average of that equation in the sense that we assume that the product of the ellipticities of the galaxies are equal to their respective shear correlation functions, namely $\xi_+^{ij}\equiv \epsilon_{a_i}\epsilon_{b_j}^*$ for all $a_i$ and $b_j$.
+We define $N$ as the number of pointings in the survey and $F_k^i$ as the set of galaxies in pointing $k$ and tomographic bin $i$.
+The numerator in Equation \eqref{eq:xip_from_observations} then transforms to: \begin{align}
+& \sum_{k,\ell=1}^N \sum_{a\in F_k^i}\sum_{b\in F_{\ell}^j} w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*} \Delta(|\b\theta_a^i-\b\theta_b^i|) \nonumber\\
+ = & \sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \sum_{\ell=1}^N \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} \nonumber\\
+  = & \sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \left[\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} + \sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*}\right] \, .
+\end{align}
+When we denote the probability that pointing $k$ is of percentile $m$ by $P_m^k$ and assume that the product $\epsilon_a^i\epsilon_b^{j*}$ always equals its expectation value, we can set the numerator as \[
+\sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \sum_m P_m^k \left[\overbrace{\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.a)}}\,  \xi_{+,mm}^{ij}(\theta) + \overbrace{\sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.b)}} \sum_n P_n^{\ell} \xi_{+,mn}^{ij}(\theta)\right] \, .
+\label{eq:numerator1}
+\]
+The term (\ref{eq:numerator1}.a) denotes all galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a$, and are in the same pointing as galaxy $a$.
+This term is equal to the (weighted) number density of galaxies in the pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$.
 
-Let $b_j\in P_{a_i}$ denote all $b_j$ that lie in the same pointing as the $a_i$.
-We observe that the left term is zero for $i\neq j$, as only galaxies of the same percentile can lie in the same pointing.
-The term $\sum_{b_i\in P_{a_i}}\deltafuncij$ now is the number of galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a_i$, which is equal to the number of galaxies in the whole pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$.
-The prefactor $w_{b_i}$ transforms the number of galaxies to the \emph{weighted number density} of galaxy sample $b$ in percentile $i$, or $N_i(b)$, so the numerator now reads:
-\begin{align*}
-\sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10}\sum_{b_j\not\in P_{a_i}} w_{b_j} \Delta(\b\theta_{a_i}-\b\theta_{b_j})\xi_+^{ij} \right]
-\end{align*}
+The term (\ref{eq:numerator1}.b) denotes all galaxies within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a$, that are \textit{not} in the same pointing as galaxy $a$.
+This is equal to the number density of galaxies in the respective pointings multiplied by $2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]$.
 
- A similar argument can be made for the right term: Assuming for a second that all pointings outside of the one where galaxy $a_i$ is in are of percentile $j^*$, the right hand side would read \[
-\sum_{b_{j^*}\not\in P_{a_i}} w_{b_{j^*}} \Delta(\b\theta_{a_i}-\b\theta_{b_{j^*}})\xi_+^{i{j^*}} = 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j^*}(b)\xi_+^{i{j^*}}\, .
+If we assume that said number density in a pointing is equal to the number density in the percentile it belongs to, $N_n^j$, and set $P_n^\ell=1/10$, the numerator becomes \begin{align}
+\sum_{k=1}^N \sum_{a\in F_k^i} w_a^i \sum_m P^k_m \left[2\pi\theta\,\d\theta\,E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + 2\pi\theta\,\d\theta\,\frac{1-E(\theta)}{10}\, \sum_n N_n^j \xi_{+,mn}^{ij}(\theta) \right] \, .
+\end{align}
+Now the term $\sum_{a\in F_k^i} w_a^i$ denotes the (weighted) number of galaxies in pointing $k$, which we set as the number density of galaxies in the respective percentile multiplied with the area $A$ of the pointing.
+Applying this and setting $P_m^k=1/10$, the numerator reads
+\begin{align}
+\frac{2\pi\theta\,\d\theta}{10} \sum_{k=1}^N \sum_m N_m^i A &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \nonumber\\
+ =  \, \frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \, .
+\end{align}
+%
+ The same line of argumentation can be applied to the denominator, which then reads: \[
+\frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i \left[ E(\theta) N_m^j + \frac{1-E(\theta)}{10}\sum_n N_n^j\right]\, .
  \]
- Taking the ensemble average of all realisations of depth-distributions, we can just denote the probability that a pointing neighbouring one of percentile $i$ is of percentile $j$ as $P(j | i,\theta)$.
-The numerator then reads \[
- \sum_{i=1}^{10}\sum_{a_i}w_{a_i} \left[ 2\pi\theta\, {\rm d}\theta\, E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta)\, 2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
+Taking the ratio of the two quantities, we see that Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} are the same\footnote{Note that while here $N_m^i$ denotes a number density, in Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} it denotes the total (weighted) number of galaxies.
+However, the difference is just a multiplication with the area $A$ of the pointings, which appears both in the numerator and the denominator and is thus cancelled out.}.
+\section{Outlook: Finite field effects}
+\label{sec:expand_eoftheta}
+\begin{figure}
+    \centering
+    \def\svgwidth{200pt}    
+%    \hspace*{1cm}
+    \input{images/expand_eoftheta.pdf_tex}  
+%    \hspace*{-2cm}
+    \caption[Graphic how to obtain $E_{ab}(\theta)$]{Graphic representation of the definitions of $E_{ab}(\theta)$.
+When the first galaxy is in the bottom left pointing, the probability to find the second galaxy in a pointing of distance $(a,b)$ is $E_{mn}(\theta)$.}
+    \label{fig:expand_etheta}
+\end{figure}
+In this chapter we will outline how to calculate the correction of the correlation functions for a finite survey with a potentially correlated distribution of depth between pointings.
+Essentially, this boils down to the calculation of $P_{mn}^{ij}(\theta)$ from Equation \eqref{eq:def_xiobs}.
+We calculate this weighting by the geometrical probability that a pair of galaxies of separation $\theta$ is of percentiles $m$ and $n$, $P(m,n|\theta)$, weighted by the respective number of galaxies in the percentiles $N_m^i,N_n^j$: \[
+P_{mn}^{ij}(\theta) = N_m^iN_n^jP(m,n|\theta)\, .
+\label{eq:pmnij1}
 \]
- In our case we assume an infinite number of randomly distributed fields, so $P(j | i,\theta)=1/10$ holds.
-However, for a finite survey the footprint of depth-distributions seems to be of importance, as due to a limited number of fields the $P(j | i,\theta)$ does not equate its expectation value.
-For smaller surveys (or surveys with correlated depth-distributions) it seems appropriate to adjust this parameter.
-\todo{Wait for catherines 450deg${}^2$ simulations, maybe they are big enough?}
+ At first we define Functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$.
+This situation is depicted in Figure \ref{fig:expand_etheta}.
+Due to symmetry, for the azimuthal average of the functions, $E_{ab}(\theta) = E_{-ab}(\theta) = E_{ba}(\theta)$ holds for all combinations of $a$ and $b$.
+Note that $E_{00}(\theta)=E(\theta)$ and $\sum_{a,b}E_{ab}(\theta)\equiv 1$.
 
- If we define $A$ as the (arbitrarily big) survey area, we can set \[
- \sum_{a_i} w_{a_i} = A\, N_i(a)
+Let $P^*(m,n|a,b)$ denote the probability that two pointings of distance $(a,b)$ are of percentile $m$ and $n$ (which is directly calculable from a given survey footprint). 
+Then the following equation holds: \[
+P(m,n|\theta) = \sum_{a,b} E_{ab}(\theta)P^*(m,n|a,b)\, .
+\label{eq:pmntheta}
 \]
- and see that the numerator becomes \[
- 2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b)\xi_+^{ii} + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b)\xi_+^{i{j}} \right]\, .
+Note that the expectation value of $P^*(m,n|a,b)$ for uncorrelated distributions is \[
+\la P^*(m,n|a,b)\ra = \begin{cases}
+0.1\,\delta_{mn},\qquad & \text{for }(a,b)=(0,0) \\
+0.01, & \text{else}
+\end{cases}\, ,
+\label{eq:pmnabstar}
 \]
- The exact line of argumentation can be applied to the denominator, which then reads: \[
-  2\pi\theta\, {\rm d}\theta\, A \sum_{i=1}^{10}N_i(a) \left[E(\theta) N_i(b) + \sum_{j=1}^{10} P(j|i,\theta) [1-E(\theta)]N_{j}(b) \right]\, .
+where $\delta_{mn}$ denotes the Kronecker delta. Keeping in mind that \[
+\sum_{(a,b)\neq (0,0)} E_{ab}(\theta) = 1-E(\theta)\, ,
 \]
-Taking the ratio of the two quantities, and setting $P(j | i,\theta)=1/10$, we receive Equation \eqref{eq:correctionfunction1}.
-\section{Additional Figures}
-\subsection{Results of the MCMC}
-\begin{figure}[h]
+we can use the expectation value \eqref{eq:pmnabstar} to calculate \eqref{eq:pmntheta} as a consistency check.
+In that case, we receive the same value for the coefficients in \eqref{eq:pmnij1} as we have in Equation \eqref{eq:pmnij_uncorr} in Chapter \ref{sec:xipm_semianalytic} for the case of an infinite footprint and uncorrelated distribution of depth.
+
+\begin{figure}
 \centering
-	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
-	\caption{Bias in the parameters for a KiDS-like Survey.}
-	\label{fig:mcmc_kids}
+\begin{subfigure}[c]{0.49\textwidth}
+\def\svgwidth{100pt}
+\hspace*{2cm}
+\input{images/e_1.pdf_tex}
+\subcaption{For $\theta\sin(\phi)<L$ the volume of the dashed rectangle is $V(\theta,\phi)=\theta\sin(\phi)[L-\theta\cos(\phi)]$.}
+\label{fig:e01thetaa}
+\end{subfigure}
+\begin{subfigure}[c]{0.49\textwidth}
+\def\svgwidth{100pt}
+\hspace*{2cm}
+\input{images/e_2.pdf_tex}
+\subcaption{For $\theta\sin(\phi)>L$ the volume of the dashed rectangle is $V(\theta,\phi)=[2L-\theta\sin(\phi)]\, [L-\theta\cos(\phi)]$.}
+\label{fig:e01thetab}
+\end{subfigure}
+\caption[How to calculate $E_{01}(\theta)$]{How to calculate $E_{01}(\theta)$ for different values of $\theta$.}
+\label{fig:e01theta}
 \end{figure}
-\begin{figure}[h]
+
+The $E_{ab}$ can all be calculated analytically, similar to our method in Chapter \ref{sec:model_e}.
+We again assume a selection of square fields with side length $L$, and later set $L=60\arcmin$ to adapt to the KV450 survey.
+As an example, for $E_{01}$ we have several possible situations, depicted in Figure \ref{fig:e01theta}.
+For a separation vector $\b\theta$ with modulus $\theta<L$ and inclination angle $\phi$, the dashed rectangle in Figure \ref{fig:e01theta}\subref{fig:e01thetaa} depicts the galaxies that have a partner in the upper pointing.
+For $L<\theta<\sqrt{2}L$, the dashed rectangle in Figure \ref{fig:e01theta}\subref{fig:e01thetaa} represents the area of galaxies with a partner in the upper square under the condition that $\theta\sin(\phi)<L$.
+For $\theta\sin(\phi)>L$, the situation is depicted by Figure \ref{fig:e01theta}\subref{fig:e01thetab}.
+As soon as $\theta>\sqrt{2}L$ holds, the situation of Figure \ref{fig:e01theta}\subref{fig:e01thetaa} is impossible.
+When $\theta<2L$ holds, the vector is only constrained by $\theta\cos(\phi)<L$, but as soon as $\theta >2L$ holds, we additionally need to impose $\theta\sin(\phi)<2L$.
+Again setting $E_{ab}(\b\theta) = V(\theta,\phi)/L^2$, we define \begin{align}
+E_{01}^{(a)}(\b\theta) & \equiv \frac{\theta}{L}\sin(\phi)[1-\frac{\theta}{L}\cos(\phi)] \nonumber\\
+E_{01}^{(b)}(\b\theta) & \equiv [2-\frac{\theta}{L}\sin(\phi)]\, [1-\frac{\theta}{L}\cos(\phi)]
+\end{align}
+Taking the azimuthal average, we compute:
+{
+\begingroup
+\addtolength{\jot}{1em}
+\begin{align}
+E_{01}(\theta) = & \begin{cases}
+\frac{1}{\pi}\int_0^{\frac{\pi}{2}} \d\phi\, E_{01}^{(a)}(\b\theta) & \frac{\theta}{L} < 1 \\[10pt]
+ \frac{1}{\pi}  \left[\int_{\cos\inv(L/\theta)}^{\sin\inv(L/\theta)}\d\phi\,E_{01}^{(a)}(\b\theta) + \int_{\sin\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) \right]  & 1 < \frac{\theta}{L} < \sqrt{2} \\[10pt]
+ \frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) & \sqrt{2}<\frac{\theta}{L}<2 \\[10pt]
+\frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\sin\inv(2L/\theta)}\d\phi\, E_{01}^{(b)}(\b\theta) & 2<\frac{\theta}{L}<\sqrt{5} \\[10pt]
+ 0 & \sqrt{5}<\frac{\theta}{L}
+\end{cases}\nonumber\\
+ = & \begin{cases}
+ \frac{(2L-\theta)\theta}{2\pi L^2} & \frac{\theta}{L} < 1 \\[10pt]
+ \frac{1}{\pi}\left[\frac{3}{2}- 2\frac{\theta}{L}+\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-1}+2\rm{sec\inv}\left(\frac{\theta}{L}\right)\right] & 1<\frac{\theta}{L}<\sqrt{2} \\[10pt]
+ \frac{1}{2\pi}\left[-1-4\frac{\theta}{L}+4\sqrt{\frac{\theta^2}{L^2}-1}+4\rm{csc\inv}\left(\frac{\theta}{L}\right)\right] & \sqrt{2} < \frac{\theta}{L} < 2 \\[10pt]
+ \frac{1}{2\pi}\left[-5-\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-4}+4\sqrt{\frac{\theta^2}{L^2}-1}-4\rm{sec\inv}\left(\frac{\theta}{L}\right)+4\sin\inv\left(\frac{2L}{\theta}\right)\right] & 2 < \frac{\theta}{L} < \sqrt{5} \\[10pt]
+ 0 & \sqrt{5}<\frac{\theta}{L}
+ \end{cases}\, .
+\end{align}
+\endgroup
+}
+
+\begin{figure}
 \centering
-	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
-	\caption{Bias in the parameters for a Euclid-like Survey.}
-	\label{fig:mcmc_euclid}
+\def\svgwidth{120pt}
+\input{images/drawing.pdf_tex}
+\caption[Visualisation of the numerical computation for $E_{01}(\theta)$.]{Visualisation of the numerical computation for $E_{01}(\theta)$.
+For a circle of radius $\theta$, the length of the red arc divided by $2\pi$ represents the fraction of galaxies within the respective pointing.
+This value needs to be integrated for all possible centers of the circle in the pointing.
+That procedure is straightforward to expand for other $E_{ab}(\theta)$.}
+\label{fig:eoftheta_sim}
 \end{figure}
-\todo{Put both in one plot? Maybe put reference MC simulation where $\xi_\pm$ was not changed?}
+
+\begin{figure}
+\centering
+\includegraphics[width = 0.8\textwidth]{images/eab.pdf}
+\caption{The functions $E_{ab}(\theta)$ for the first few possible combinations.}
+\label{fig:eab}
+\end{figure}
+Naturally, to calculate those functions for all possible combinations would be rather tedious, however they are simple to determine numerically (compare Figure \ref{fig:eoftheta_sim}).
+A plot of these functions can be found in Figure \ref{fig:eab}.
+
+When we now simulate random distributions of the depth-function for a $100\,\rm{deg}^2$-field, a $450\,\rm{deg}^2$-field and a $1000\,\rm{deg}^2$-field, we can compare how they differ from each other and estimate how important finite-field effects are.
+As can be seen from Figures \ref{fig:100degsqr}, \ref{fig:450degsqr} and \ref{fig:1000degsqr}, the effect is quite significant for a $100\,\rm{deg}^2$-field, but almost negligible for a $1000\,\rm{deg}^2$-field.
+This leads to the assumption that both for the KiDS- as for the Euclid-survey, finite field effects do not need to be accounted for.
+However, if the distribution of depth is correlated in the surveys, that might have a noticeable impact on the results.

### 2019-05-06 appendix.tex
First semi-complete version after recent changes. Will still be subject to many modifications.

@@
 \label{sec:calc of PS}
+
+\subsection{The function $E(\theta)$}
+\label{sec:model_e}
+When computing the shear correlation between a pair of galaxies, it is of central importance whether those two galaxies lie in the same pointing or not.
+We want to model the probability that a pair of galaxies with separation $\b\theta$ lie in the same pointing by the function $E(\b\theta)$, which we will derive here:
+
+{
+\def\vec{\b}
+\begin{figure}
+    \centering
+    \def\svgwidth{200pt}    
+    \hspace*{1cm}
+    \input{images/eoftheta_new.pdf_tex}  
+    \hspace*{-2cm}
+    \caption[Graphic how to obtain $E(\b\theta)$]{Graphic representation on how to obtain the function $E(\b\theta)$.
+For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
+    \label{fig:explain_etheta}
+\end{figure}
+}
+Given one square field of length $L$ (in our case $L=60\arcmin$) and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
+As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
+The volume of this square equals \begin{equation}
+V(|\b\theta|,\phi)  = \big[L-|\b\theta|\cos(\phi)\big]\,\big[L-|\b\theta|\sin(\phi)\big]\, ,
+\end{equation} where $\phi$ represents the angle of the vector $\b\theta$.
+The function $E(\b\theta)$ then simply equals $V(|\b\theta|,\phi)/L^2$.
+To exclude negative Volumes (which could occur when $|\b\theta|>1$ holds), we need to add the Heaviside theta function $\mathcal{H}$:
+\begin{equation}
+E(\b\theta)  = \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, \mathcal{H}\left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\mathcal{H}\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, .
+\label{eq:eoftheta1}
+\end{equation} 
+As $E(\b\theta)$ is not isotropic, in order to obtain the function $E(\theta) = E(|\b\theta|)$, we need to azimuthally average Equation \eqref{eq:eoftheta1} over all angles $\phi$.
+While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
+\begin{align}
+E(\theta) = & \frac{4}{2\pi}\int_0^{\frac{\pi}{2}}\d\phi\, E(\b\theta) = \frac{2}{\pi}\begin{cases}
+\int_0^{\frac{\pi}{2}} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, ,  & |\b\theta|  \leq L \\[10pt]
+\int_{\cos\inv(L/|\b\theta|)}^{\sin\inv(L/|\b\theta|)} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right] \, , \quad   & L \leq |\b\theta| \leq \sqrt{2}L \\[10pt]
+0\, , &\sqrt{2}L \leq\theta
+\end{cases} \nonumber\\[10pt]
+ = & \begin{cases}
+\frac{1}{L^2 \pi}\left[L^2\pi - (4L-\theta) \theta\right]\, ,  & \theta \leq L \\[10pt]
+\frac{2}{\pi}\,\left[4\sqrt{\frac{\theta^2}{L^2}-1} -1 - \frac{\theta^2}{2L^2} - \cos\inv\left(\frac{L}{\theta}\right) + \sin\inv\left(\frac{L}{\theta}\right)\right]\, ,  & L  \leq \theta \leq \sqrt{2}L \\[10pt]
+0\, ,  & \sqrt{2}L \leq \theta
+\end{cases}\, .
+\end{align}
 

### 2019-05-06 discussion.tex
First semi-complete version after recent changes. Will still be subject to many modifications.

@@
 \begin{enumerate}
-\item We implemented a variation in depth that only depends on the pointing.
-However, in reality galactic extinction, CCD imperfections, dithering strategies and other factors also influence the depth on different scales.
-Although the variation between pointings is the dominating factor, a complete analysis implementing those factors could yield a slightly different result.
-\item In our main analysis we assumed an infinite number of fields.
-This ignores boundary effects that would arise in the vincinity of the edge of a footprint (there finding a galaxy outside of the same pointing would be less likely).
-Also, another effect is ignored: If one has a number of $N$ fields in each percentile, and one galaxy is in a pointing of a certain percentile, then the probability that a different pointing is of the \emph{same} percentile is reduced by the factor $(N-1)/N$.
-However, we modeled the second effect, and already at 100 pointings it barely makes any difference.
-We did not model the boundary effects, but we assume that they are likewise neglible.
-\todo{This needs to be rewritten to account for the new insights.}
-\item We have assumed that the depth of neighbouring pointings is uncorrelated. While there is no reason not to assume that, we have not yet verified that this is indeed the case.
-\item In our Monte Carlo simulations we have only had $\Omega_{\rm m}$ and $\sigma_8$ as free parameters.
-While we do not expect most other parameters to make a difference, baryonic feedback and/or intrinsic alignments also change the correlation functions on small scales, so it is definitely possible that in a Monte Carlo chain including free parameters for these effects, those would change to mitigate the varying depth, and the impact on the actual cosmological parameters would be much smaller.
+\item In the most general terms, we are analysing the effects of a position-based selection function on cosmic shear surveys.
+In our analysis, this selection function was governed by the $r$-band depth of a pointing.
+This neglects a number of other effects: The depth in different bands and the seeing of a pointing will also modify the number densities and redshift distributions on the scale of a pointing, whereas dithering strategies as well as imperfections in the telescope and CCD cause modifications on sub-pointing scales.
+However, we believe that these effects are subdominant compared to the variations caused by the $r$-band depth.
+
+\item We have assumed an infinitely large survey area with an uncorrelated distribution of the depth-function.
+While the boundary effects arising from a finite survey footprint would have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has less neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the shot noise of the depth-distribution.
+We have assumed that the probability that a neighbouring pointing is of percentile $n$ is exactly the expectation value, namely $1/10$.
+While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, Figure \ref{fig:all_xis} clearly shows that it is not valid for a $100\,\rm{deg}^2$ field.
+Whether our assumption holds true for the $450\,\rm{deg}^2$ footprint of the KV450 survey, or even the $1350\,\rm{deg}^2$ footprint of the final survey is an important question.
+Also, we have assumed an uncorrelated distribution of the depth-function, both in the simulations as well as in the models.
+While this is likely true as a rough approximation (very few pointings of the survey were taken on the same night and thus under the same weather conditions), effects like airmass, lunar phase, Galactic extinction and seasonal weather are likely to influence the depth on scales larger than one pointing.
+
+An outlook for the mitigation of finite field effects, boundaries and a correlated distribution of depth is given in Appendix \ref{sec:expand_eoftheta}.
+As a preliminary result we find that finite field effects are not significant for a $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$-field, if the distribution of depth is uncorrelated.
+
+\item In our MCMC simulations we did not account for degeneracies with other cosmological parameters
+% (apart from $\Omega_{\rm m}, \sigma_8, w_0$ and $w_a$)
+ or observational effects.
+Especially intrinsic alignments and baryonic feedback also modify the correlation functions especially on small scales, so they are probably degenerate with the effect of varying depth.
+In an actual MCMC simulation that accounts for these effects, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, and the impact on cosmological parameters is actually smaller than in our results.
+Also, possible degeneracies between $S_8$ and other cosmological parameters might bias the resulting values.
+%Furthermore, when including the effects of dark energy we notice that our observation of $S_8$ being constant is no longer valid: For a `Euclid-like' survey we notice a bias of $\sim 0.8\sigma$.
+This gives rise to the assumption that the results of an MCMC with the full parameter space, including observational effects, will differ from our results.
 \end{enumerate}
-We have determined that the effects of varying depth are not significant for the KiDSV-450 survey.
-For a Euclid-like survey they will play an important role, but before a model is implemented in such a precise survey, one should revise the used simplifications, especially the first one.
-We suspect that it should be possible to account for different aspects of varying optical depth by just modifying the function $E(\theta)$.
 
-However, for the parameter $S_8$ this effect is insignificant, which in particular means that a variation in depth can not explain the discrepancies between the analyses of the CMB and those of the local universe.
-It can also be responsible for the occurence of $B$-Modes, although only to an insignificant amount.
+Despite these repercussions, we are confident to say that the effects of varying depth are not significant for the KV450 survey.
+The cosmological parameters did not change significantly and the main parameter, $S_8$, is especially robust against this effect.
+In particular this means that a varying depth can not explain the discrepancy between observations of the local Universe and results from analysis of the CMB.
+
+We have shown that this effect can create B-modes.
+However, \citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
+Those B-modes are at least one order of magnitude larger and still consistent with zero, so it is safe to say that the modes created by varying depth are negligible.
+An interesting observation is that the change in E-modes is as big as the created B-modes (compare Figure \ref{fig:cosebis_eandb}).
+This means that as soon as this effect causes significant biases in the cosmological parameters, it will also create significant B-modes\footnote{While this is no big surprise, it is not trivial.
+It could be possible that a systematic effect only creates E-modes and no B-modes, which would be extremely unfortunate as it could bias cosmological parameters without ever being detected by a B-mode analysis.}.
+Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey.
+
+For next-generation surveys like Euclid, this effect will be significant.
+Although Euclid is a space-based telescope, the photometric redshift determination will still be done by ground-based telescopes and therefore suffer from the same effects.
+While we did not yet perform a quantitative study of this effect for Euclid, we are certain that a such a study should be conducted.
+
+As an outlook it would be interesting to perform a full MCMC simulation, including both cosmological and nuisance parameters.
+One might also check the most popular extensions to the standard model of cosmology, and see whether varying depth could cause a bias towards one of these models.
+Furthermore, the method developed in Appendix \ref{sec:expand_eoftheta} could be applied to the actual footprint of the KV450 survey to see whether finite field effects or a correlated distribution of $r$-band depth are significant.
+Additionally is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$, which is not isotropic.
+Therefore, it would be possible to observe a direction-dependent correlation function $\xi_\pm^{ij,\rm{obs}}(\b\theta)$ in future surveys.
+An anisotropy in the observed correlation function could be a sign for the influence of varying depth.

### 2019-05-06 introduction.tex
First semi-complete version after recent changes. Will still be subject to many modifications.

@@
 The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the $\Lambda$CDM Model and determine its parameters.
-Contrary to the analysis of the Cosmic Microwave Background \citep{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
-Current Cosmic Shear surveys are especially sensitive to the paramter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
+Contrary to the analysis of the CMB by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
+Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
 It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$,
 %\citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data,
-\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2017MNRAS.465.1454H} report $S_8 = 0.745\pm 0.038$ from KiDS data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$.
+\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2018arXiv181206076H} report $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$.
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data.
-This discrepancy could be a statistical coincidence, a sign of new physics or the manifestation of an unknown systematic effect.
-\todo{Citations..
+This discrepancy has received a lot of attention \citep{2013PDU.....2..166V}.
+It could be interpreted as a statistical coincidence, a sign of new physics like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P}; or as the manifestation of a systematic effect, either in the cosmic shear surveys or in the Planck mission \citep{2016ApJ...818..132A}, that is not yet accounted for.
+
+As weak gravitational lensing measures a tiny signal over a large sample, it is extremely sensitive to anything that systematically biases the measurements, such that the error bars in current surveys arise to equal parts from statistical and systematic uncertainties \citep[compare][]{2017MNRAS.465.1454H}.
+With next-generation surveys like the Large Synoptic Survey Telescope and Euclid right at the doorstep, systematic effects in gravitational lensing have received an unprecedented amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
+%\todo{Citations..
 \citet{2017MNRAS.464.1676A} has a few...}
 
-To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citet{2002ApJ...568...20C,2002A&A...389..729S}.
+To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}.
 To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
-As \citet{2017MNRAS.465.1454H} report the significant detection of B-modes, it is well motivated to check for possible systematics that are yet unaccounted for.
-Note that the non-existence of B-modes does not imply that the sample is free of remaining systematics.
+As \citet{2017MNRAS.465.1454H} reported the significant detection of B-modes, it was well motivated to check for possible systematics that are not yet accounted for.
+Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
 
@@
 While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions, that are found in ground-based surveys.
-To first order, this variation can be modelled by a step-like depth function that varies from pointing to pointing.
+To first order, this variation can be modelled by a step-like depth function which varies from pointing to pointing.
 In this work we assume the specifications of the Kilo-Degree Survey, namely a collection of $1\,\text{deg}^2$ square fields.
-Furthermore we neglect boundary effects.
 

### 2019-05-06 model_xipm.tex
First semi-complete version after recent changes. Will still be subject to many modifications.

@@
 \subsection{Using an analytic Model}
-For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal. Following \citet{2006APh....26...91V}, we estimate
+\label{sec:xipm_analytic}
+For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal, in the sense that the shear field for a deeper redshift distribution gets multiplied by a weight $W$.
+While this is not true for a 3-dimensional matter distribution, it should be valid for small variations in redshift.
+Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
+
+Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
+The observed correlation function $\xi^{ij,\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{ij,\rm{const}}(\theta)$ via (compare Eq.
+\todo{Take eq.
+from Hildebrandt et al.
+(2017)?})
+\begin{align}
+\xi^{ij,\text{obs}}_\pm(\theta) = & \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_{\rm t}(\bth)\gamma^{j,\rm{obs}}_{\rm t}(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \pm \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_\times(\bth)\gamma^{j,\rm{obs}}_\times(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \nonumber\\
+ = & \frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i(\bth)N^j(\bthp)\ra} \xi_{\pm}^{ij,\rm{const}}(\theta) \, ,
+ \label{eq:xipmblub1}
+ \end{align}
+ where the average $\la\ldots\ra$ represents both an ensemble average as well as an average over the position $\bth$.
+ Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing, which is described by the function $E(\theta)$.
+
+To compute the modified shear correlation functions, we parametrize the number densities \linebreak$N^{i}(\b \theta)=\la N^{i} \ra [1+n^{i}(\b \theta)]$ and the weight $W^{i}(\b \theta)=1+w^{i}(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n^{i}(\b \theta)$ as a function with average $\la n^{i} \ra = 0$, that is constant on each pointing.
+Without loss of generality we set $\la N^i\ra = 1$.
+We can see that $\la n^i(\bth)n^j(\bthp)\ra = E(\theta)\la n^i(\bth)n^j(\bth)\ra \equiv E(\theta)\la n^i n^j \ra$ holds and compute:
+\begin{align}
+&\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra \nonumber\\
+&\qquad =  1 + \la n^iw^i\ra + \la n^j w^j\ra + E(\theta)\left[ \la n^in^j\ra + \la n^i w^j \ra  + \la n^jw^i\ra + \la w^iw^j\ra + \la n^in^jw^i\ra + \la n^in^jw^j\ra + \la n^iw^iw^j\ra \right.
+\nonumber\\
+&\qquad\quad \left. + \la n^jw^iw^j\ra + \la n^in^jw^iw^j\ra  \right] 
+ \end{align}
+Ignoring correlations higher than second order\footnote{It is not inherently obvious that this is a valid assumption.
+However, after performing both calculations we noticed no difference between the outcomes of both equations}, and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
+ \begin{align}
+ \xi^{ij,\rm{obs}}_\pm(\theta) = \frac{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}{1+E(\theta)\la n^i n^j\ra }\xi^{ij,\rm{const}}_\pm (\theta) \, .
+ \end{align}
+For the calculation of the reference correlation functions $\xi_\pm^{ij}(\theta)$ we distribute the \textit{same} galaxies into our survey, only this time we will not order their weightings $W$ or their number densities $N$ by pointing.
+We can imagine this by cutting the footprint into infinitesimal elements $\d^2\b\theta$, and redistributing those at random.
+When we calculate the correlation function of this survey, we note that $\la n^i(\bth)\ra \la n^j(\bthp)\ra = 0$ holds for $\b\theta\neq \b 0$, as the two corresponding infinitesimal elements have uncorrelated weighting and number density.
+Performing the same calculations as above, this yields a relation between the correlation function of constant optical depth $\xi_\pm^{ij,\rm{const}}$ and the modelled one $\xi_\pm^{ij}$:
+\begin{equation}
+\xi_\pm^{ij}(\theta) = \left(1+\la n^iw^i\ra + \la n^jw^j\ra \right)\xi_\pm^{ij,\rm{const}}(\theta)\, .
+\end{equation}
+The ratio of modelled and observed correlation function thus becomes: \begin{equation}
+\frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} \approx \frac{1+\la n^iw^i\ra+\la n^jw^j\ra + E(\theta)\la n^in^j\ra}{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}
+\, .
+\end{equation}
+It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales.
+Given a set of average redshifts, following \citet{2006APh....26...91V}, we can estimate
 \[
@@
 \]
-\todo{Maybe implement redshift-dependent index?}
-Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
-
-%For a pair of galaxies that we use to measure the correlation function, it is crucial to determine whether those two galaxies lie within the same pointing.
-We want to define a function $E(\theta)$ that determines
-
-Let $N(\b \theta)$ be the number-density per tile and $W(\b \theta)$ the weighting of average shear.
-The observed correlation function $\xi^{\text{obs}}_\pm(\theta)$ now changes from one of constant depth $\xi_\pm^{\rm const}$ via
-\begin{align*}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{\la N(\b 0)N(\b \theta)\gammao_{\rm t}(\b 0)\gammao_{\rm t}(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \pm \frac{\la N(\b 0)N(\b \theta)\gammao_\times(\b 0)\gammao_\times(\b \theta)\ra }{\la N(\b 0)N(\b \theta)\ra} \\
- = & \frac{\la N(\b 0)N(\b \theta)W(\b 0)W(\b \theta)\ra}{\la N(\b 0)N(\b \theta)\ra} \xi_{\pm}^{\rm const}(\theta) \, .
- \end{align*}
- Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
-We want to denote the probability that a random pair of galaxies of distance $\theta$ lie in the same pointing with $E(\theta)$.
-This function can be calculated as in Appendix \ref{sec:details on etheta} and equates to
-\begin{equation}
-E(\theta) =  \begin{cases}
-\frac{1}{L^2 \pi}\left[L^2\pi - (4L-\theta) \theta\right]\, ,  & \theta \leq L \\[10pt]
-\frac{2}{\pi}\,\left[4\sqrt{\frac{\theta^2}{L^2}-1} -1 - \frac{\theta^2}{2L^2} - \cos\inv\left(\frac{L}{\theta}\right) + \sin\inv\left(\frac{L}{\theta}\right)\right]\, ,  & L  \leq \theta \leq \sqrt{2}L \\[10pt]
-0\, ,  & \sqrt{2}L \leq \theta
-\end{cases}\, .
-\end{equation} 
- This function is depicted in Figure \ref{fig:eoftheta_lin}.
-
- \begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{images/eoftheta.png}
- \caption{Probability that a random pair of galaxies of distance $\theta$ lie in the same pointing.}
- \label{fig:eoftheta_lin}
- \end{figure}
-
-We again parametrize the number density $N(\b \theta)=\la N \ra (1+n(\b \theta))$ and the weight $W(\b \theta)=1+w(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n(\b \theta)$ as a locally constant function with average $\la n \ra = 0$.
-We can see that $\la n(\b 0)n(\b \theta)\ra = E(\theta)\la n(\b 0)n(\b 0)\ra \equiv E(\theta)\la n n \ra$ holds and get for the autocorrelation of a single bin,
- \begin{align}
-\xi^{\text{obs}}_\pm(\theta) = & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta) \\
-\approx & \frac{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra \right]}{1+E(\theta)\la n^2\ra }\xi_\pm^{\rm const}(\theta)\, , \nonumber
- \label{eq:ffunct}
-\end{align}
-holds.
-We see that in addition to a modification of the correlation function due to the stronger shear signal in deeper pointings, we also get a scale-independent modification due to the correlation between depth and number density.
-
-However, as a survey of constant depth is completely unrealistic, also the modelled correlation function will be subject to the same effect.
-If we assume the same redshift-distributions for galaxies as in the case of varying depth, and just assert that those changes are not correlated with position, we get
-\begin{equation}
-\xi_\pm = (1+2\la nw\ra)\xi_\pm^{\rm const}\, .
-\end{equation}
-The ratio of modelled and observed correlation function thus becomes: \begin{align}
-\frac{\xi_\pm}{\xi_\pm^{\rm obs}} = & \frac{\left(1+2\la nw\ra\left)\left(1+E(\theta)\la n^2\ra\right)\right.\right.}{1 + 2\la nw \ra + E(\theta)\left[\la (n+w)^2\ra + 2 \la n^2 w\ra + 2\la nw^2\ra + \la n^2 w^2\ra \right]} \\
-\equiv & F(\theta) \, .
-\end{align}
-A similar, but longer, equation governs the cross-correlation between different bins. This equation and its derivation can be found in Appendix \todo{create this and cite it.}.
-%It is interesting to note that $F(\theta)=1$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales. 
 We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts.
+We thus want to construct a model that is valid for an arbitrary distribution of redshifts and does not rely on the assumption of a single lens plane.
 \subsection{Using a semi-analytic Model}
@@
 Now for each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p^i_m(z)$.
-Using \eqref{eq:xipm_from_pkappa}, we can compute the shear correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each set of percentiles $m,n$ and redshift bins $i,j$\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program.
+Using \eqref{eq:xipm-pkappa}, we can compute the shear correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each set of percentiles $m,n$ and redshift bins $i,j$\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program.
 Among other things, it calculates the shear correlation functions for a given cosmology and source redshift distribution.
 To estimate the power spectrum on nonlinear scales we use the methods developed by \citet{2012ApJ...761..152T}.}.
-When we compute the measured shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process).
+When we compute the measured shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (\citet{2017MNRAS.465.1454H} give a good overview for the process\todo{Cite the same eq.
+as above from Hildebrandt et al.
+(2017)}).
 If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$.
@@
 For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
-We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, we have $C=N^iN^j$ and thus \[
-\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{N^iN^j}\xi_\pm^{ij}(\theta)N^iN^j = \xi_\pm^{ij}(\theta)\, ,
-\]
-so on large scales our observed correlation functions agree with the ones that we would usually calculate.
+We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, the observed correlation functions agree with the ones that we would usually calculate.

### 2019-05-06 results.tex
First semi-complete version after recent changes. Will still be subject to many modifications.

@@
 \label{sec:results}
-We applied both our methods to data from the KiDSV-450 survey and computed the ratio of observed and modeled correlation functions.
-Furthermore, we have conducted a simulation using ray-tracing through the millenium simulations (?)\todo{I should ask catherine about what exactly she did for the simulations or maybe even ask her to write this part of the paper?}.
+We applied both our methods to data from the KV450 survey and computed the ratio of observed and modeled correlation functions.
+Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
+For each tomographic redshift bin of each percentile, galaxies were placed to trace the respective redshift distribution.
+Afterwards, their expected shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included).
+This was compared to a set of simulations where the galaxies were simply distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, is this what you did?
+If you are unhappy with any of these explanations, or feel like I missed something, please feel free to add it :)}.
 As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{images/xis_111.png}
+	\includegraphics[width=1\textwidth]{images/allxis_0111.pdf}
 	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.}
@@
 We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk?
-Maybe in the appendix to avoid too many Figures?} The simulations seem to be in rough agreement with the models, but there are some features that can not be explained.
+Maybe in the appendix to avoid too many Figures?}\footnote{We also observe that in the semi-analytic model, $\xi_-$ seems to be much stronger affected by this effect: Following Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
+This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$.
+However, $\xi_-$ is obtained by filtering with the 4-th order Bessel function, which peaks at approximately $\ell\theta\approx 5$, so for different $\theta$ this function is sensitive to varying parts of the convergence power spectrum.
+A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}
+
+The simulations seem to be in rough agreement with the models, but there are some features that can not be explained.
 Especially we observe that the ratios of the correlation functions for large values of $\theta$ seem to consistently surpass unity, which can not be explained by our models.
+The simulations seem to be in rough agreement with the models, but there are some significant differences.
+After a thorough analysis we explain these discrepancies the following way: The simulations were performed on a $100\,\rm{deg}^2$ field, which means that shot-noise of the fields plays a significant role.
+After performing the same simulations for a different distribution of depth between the pointings and obtaining completely different results, we are quite certain that this is the dominating effect.
+The implications of this and possible mitigation strategies will be discussed in Section \ref{sec:discussion}.
 
@@
 Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
-As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.\todo{Maybe expand this to more parameters?}  As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties.
+As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.
+As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties.
 However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area.
@@
 We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KiDSV-450 survey for the same range in $\theta$.
-The real B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant.
-Given these facts, we conclude that the creation of B-Modes due to varying depth in the KiDS survey is not significant.
-However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, that show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).
+Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KV450 survey for the same range in $\theta$.
+The measured B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant.
+Given these facts, we conclude that the creation of B-Modes due to varying depth in the KV450 survey is not significant.
+However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, which show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).
+We also note that the difference in E-Modes is as large as the B-Modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-Modes.
 
@@
 \centering
-\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/bmodes.pdf}
-\caption{The $B$-modes created by a variation in survey-depth.
-We used the logarithmic COSEBIs described in \citet{2010A&A...520A.116S} with a range from $\theta_{\rm min} = 0.5\arcmin$ to $\theta_{\rm max} = 100\arcmin$.}
+\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/eandbmodes0p5t100.pdf}
+\caption{Difference in the logarithmic E- and B-modes between the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=100\arcmin$.}
 \label{fig:bmodes_cosebi}

### 2019-05-07 appendix.tex
First rework, now including the new insights. Probably too long.

@@
 However, the difference is just a multiplication with the area $A$ of the pointings, which appears both in the numerator and the denominator and is thus cancelled out.}.
-\section{Outlook: Finite field effects}
+\section{Finite field effects}
 \label{sec:expand_eoftheta}
@@
 %    \hspace*{-2cm}
-    \caption[Graphic how to obtain $E_{ab}(\theta)$]{Graphic representation of the definitions of $E_{ab}(\theta)$.
-When the first galaxy is in the bottom left pointing, the probability to find the second galaxy in a pointing of distance $(a,b)$ is $E_{mn}(\theta)$.}
+    \caption{Graphic representation of the definitions of $E_{ab}(\theta)$.
+When the first galaxy is in the bottom left pointing, the probability to find the second galaxy in a pointing of distance $(a,b)$ is $E_{ab}(\theta)$.}
     \label{fig:expand_etheta}
@@
 As an example, for $E_{01}$ we have several possible situations, depicted in Figure \ref{fig:e01theta}.
-For a separation vector $\b\theta$ with modulus $\theta<L$ and inclination angle $\phi$, the dashed rectangle in Figure \ref{fig:e01theta}\subref{fig:e01thetaa} depicts the galaxies that have a partner in the upper pointing.
-For $L<\theta<\sqrt{2}L$, the dashed rectangle in Figure \ref{fig:e01theta}\subref{fig:e01thetaa} represents the area of galaxies with a partner in the upper square under the condition that $\theta\sin(\phi)<L$.
-For $\theta\sin(\phi)>L$, the situation is depicted by Figure \ref{fig:e01theta}\subref{fig:e01thetab}.
-As soon as $\theta>\sqrt{2}L$ holds, the situation of Figure \ref{fig:e01theta}\subref{fig:e01thetaa} is impossible.
-When $\theta<2L$ holds, the vector is only constrained by $\theta\cos(\phi)<L$, but as soon as $\theta >2L$ holds, we additionally need to impose $\theta\sin(\phi)<2L$.
 Again setting $E_{ab}(\b\theta) = V(\theta,\phi)/L^2$, we define \begin{align}
@@
 \end{align}
-Taking the azimuthal average, we compute:
+With some geometric considerations, we compute:
 {
@@
 E_{01}(\theta) = & \begin{cases}
-\frac{1}{\pi}\int_0^{\frac{\pi}{2}} \d\phi\, E_{01}^{(a)}(\b\theta) & \frac{\theta}{L} < 1 \\[10pt]
- \frac{1}{\pi}  \left[\int_{\cos\inv(L/\theta)}^{\sin\inv(L/\theta)}\d\phi\,E_{01}^{(a)}(\b\theta) + \int_{\sin\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) \right]  & 1 < \frac{\theta}{L} < \sqrt{2} \\[10pt]
- \frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) & \sqrt{2}<\frac{\theta}{L}<2 \\[10pt]
-\frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\sin\inv(2L/\theta)}\d\phi\, E_{01}^{(b)}(\b\theta) & 2<\frac{\theta}{L}<\sqrt{5} \\[10pt]
- 0 & \sqrt{5}<\frac{\theta}{L}
+\frac{1}{\pi}\int_0^{\frac{\pi}{2}} \d\phi\, E_{01}^{(a)}(\b\theta), & \frac{\theta}{L} < 1 \\[10pt]
+ \frac{1}{\pi}  \left[\int_{\cos\inv(L/\theta)}^{\sin\inv(L/\theta)}\d\phi\,E_{01}^{(a)}(\b\theta) + \int_{\sin\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) \right],  & 1 < \frac{\theta}{L} < \sqrt{2} \\[10pt]
+ \frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta), & \sqrt{2}<\frac{\theta}{L}<2 \\[10pt]
+\frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\sin\inv(2L/\theta)}\d\phi\, E_{01}^{(b)}(\b\theta), & 2<\frac{\theta}{L}<\sqrt{5} \\[10pt]
+ 0, & \sqrt{5}<\frac{\theta}{L}
 \end{cases}\nonumber\\
  = & \begin{cases}
- \frac{(2L-\theta)\theta}{2\pi L^2} & \frac{\theta}{L} < 1 \\[10pt]
- \frac{1}{\pi}\left[\frac{3}{2}- 2\frac{\theta}{L}+\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-1}+2\rm{sec\inv}\left(\frac{\theta}{L}\right)\right] & 1<\frac{\theta}{L}<\sqrt{2} \\[10pt]
- \frac{1}{2\pi}\left[-1-4\frac{\theta}{L}+4\sqrt{\frac{\theta^2}{L^2}-1}+4\rm{csc\inv}\left(\frac{\theta}{L}\right)\right] & \sqrt{2} < \frac{\theta}{L} < 2 \\[10pt]
- \frac{1}{2\pi}\left[-5-\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-4}+4\sqrt{\frac{\theta^2}{L^2}-1}-4\rm{sec\inv}\left(\frac{\theta}{L}\right)+4\sin\inv\left(\frac{2L}{\theta}\right)\right] & 2 < \frac{\theta}{L} < \sqrt{5} \\[10pt]
- 0 & \sqrt{5}<\frac{\theta}{L}
+ \frac{(2L-\theta)\theta}{2\pi L^2}, & \frac{\theta}{L} < 1 \\[10pt]
+ \frac{1}{\pi}\left[\frac{3}{2}- 2\frac{\theta}{L}+\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-1}+2\rm{sec\inv}\left(\frac{\theta}{L}\right)\right], & 1<\frac{\theta}{L}<\sqrt{2} \\[10pt]
+ \frac{1}{2\pi}\left[-1-4\frac{\theta}{L}+4\sqrt{\frac{\theta^2}{L^2}-1}+4\rm{csc\inv}\left(\frac{\theta}{L}\right)\right], & \sqrt{2} < \frac{\theta}{L} < 2 \\[10pt]
+ \frac{1}{2\pi}\left[-5-\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-4}+4\sqrt{\frac{\theta^2}{L^2}-1}-4\rm{sec\inv}\left(\frac{\theta}{L}\right)+4\sin\inv\left(\frac{2L}{\theta}\right)\right], & 2 < \frac{\theta}{L} < \sqrt{5} \\[10pt]
+ 0, & \sqrt{5}<\frac{\theta}{L}
  \end{cases}\, .
@@
 However, if the distribution of depth is correlated in the surveys, that might have a noticeable impact on the results.
+
+\section{Additional Figures}
+\subsection{Results of the MCMC}
+\begin{figure}[h]
+\centering
+	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
+	\caption{Bias in the parameters for a KiDS-like Survey.}
+	\label{fig:mcmc_kids}
+\end{figure}  
+\begin{figure}[h]
+\centering
+	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
+	\caption{Bias in the parameters for a Euclid-like Survey.}
+	\label{fig:mcmc_euclid}
+\end{figure}  
+\clearpage
+\subsection{Finite field effects}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/100degtwofoot_final.pdf}
+\caption[Correction of the correlation functions for a $100\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $100\,\rm{deg}^2$-field.}
+\label{fig:100degsqr}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/450degtwofoot_final.pdf}
+\caption[Correction of the correlation functions for a $450\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $450\,\rm{deg}^2$-field.}
+\label{fig:450degsqr}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/1000degtwofoot_final.pdf}
+\caption[Correction of the correlation functions for a $1000\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $1000\,\rm{deg}^2$-field.}
+\label{fig:1000degsqr}
+\end{figure}

### 2019-05-07 discussion.tex
First rework, now including the new insights. Probably too long.

@@
 
-An outlook for the mitigation of finite field effects, boundaries and a correlated distribution of depth is given in Appendix \ref{sec:expand_eoftheta}.
-As a preliminary result we find that finite field effects are not significant for a $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$-field, if the distribution of depth is uncorrelated.
+A strategy for the mitigation of finite field effects, boundaries and a correlated distribution of depth is given in Appendix \ref{sec:expand_eoftheta}.
+We find that finite field effects are not significant for a $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$-field, if the distribution of depth is uncorrelated.
 
@@
 
-As an outlook it would be interesting to perform a full MCMC simulation, including both cosmological and nuisance parameters.
+%As an outlook it would be interesting to perform a full MCMC simulation, including both cosmological and nuisance parameters.
 One might also check the most popular extensions to the standard model of cosmology, and see whether varying depth could cause a bias towards one of these models.
@@
 An anisotropy in the observed correlation function could be a sign for the influence of varying depth.
+\todo{Should we give an outlook?}

### 2019-05-07 model_ps.tex
First rework, now including the new insights. Probably too long.

@@
 For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
-If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm ds}/D_{\rm s}$.
+If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm{ds}}/D_{\rm s}$.
 % Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
@@
 \subsection{Effects on the Power Spectrum}
-Assuming that the depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a locally constant depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
+Assuming that the depth, and thus the source redshift populations, vary between pointings, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$ with $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
 In accordance to the definition of the shear power spectrum \begin{equation}

### 2019-05-07 model_xipm.tex
First rework, now including the new insights. Probably too long.

@@
 \label{eq:xipm-pkappa}
-\xi_\pm[\theta,p_i,p_j] =& \int_0^\infty \frac{{\rm d}l\,l}{2\pi}J_{0,4}(l\theta)P(l,p_i,p_j)\, , \\
+\xi_\pm^{ij}(\theta) =& \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}J_{0,4}(\ell\theta)P^{ij}(\ell)\, , \\
 \label{eq:pkappa-pdelta/lenseff}
-P(l,p_i,p_j) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_h} {\rm d}\chi\frac{g(\chi,p_i)g(\chi,p_j)}{a^2(\chi)}P_\delta\left(\frac{l}{f_K(\chi)},\chi\right)\, , \\
+P^{ij}(\ell) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_h} {\rm d}\chi\frac{g^i(\chi)g^j(\chi)}{a^2(\chi)}P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)\, , \\
 \label{eq:lenseff}
-g(\chi,p_i) =& \int_\chi^{\chi_H} {\rm d}\chi'\, p_i(\chi') \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
+g^i(\chi) =& \int_\chi^{\chi_H} {\rm d}\chi'\, p_i(\chi') \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
 \end{align}
@@
  where the average $\la\ldots\ra$ represents both an ensemble average as well as an average over the position $\bth$.
- Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing, which is described by the function $E(\theta)$.
+ Assuming that depth and galaxy number density of neighbouring pointings are uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
+We want to denote the probability, that a random galaxy pair of separation $\theta$ lies in the same pointing with $E(\theta)$.
+This function is depicted in Figure \ref{fig:eoftheta_lin}; an exact equation and derivation are given in \ref{sec:model_e}.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{images/eoftheta.pdf}
+ \caption{Probability that a random pair of galaxies of distance $\theta$ lie in the same pointing.}
+ \label{fig:eoftheta_lin}
+\end{figure}
 
@@
 Ignoring correlations higher than second order\footnote{It is not inherently obvious that this is a valid assumption.
-However, after performing both calculations we noticed no difference between the outcomes of both equations}, and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
+However, after performing both calculations we noticed no difference between the outcomes of both equations.}, and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
  \begin{align}
@@
 We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, meaning that if a pointing had a worse depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-Now for each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p^i_m(z)$.
+For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, in case the pointing overlaps with a spectroscopic survey, a source redshift distribution $p^i_m(z)$.
 Using \eqref{eq:xipm-pkappa}, we can compute the shear correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each set of percentiles $m,n$ and redshift bins $i,j$\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program.
@@
 Formally, we define \[
-\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} P_{mn}^{ij}(\theta)\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} P_{mn}^{ij}(\theta)}\, ,
+\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} P_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} P_{mn}^{ij}(\theta)}\, ,
 \label{eq:def_xiobs}
@@
 Furthermore, the first galaxy has to lie in percentile $m$, the probability of which is $1/10$.
-When the first pointing is of percentile $m$, the probability that a galaxy in a different pointing is of percentile $n$ is also equal to $1/10$.
+The pointing of the second galaxy has to be of percentile $n$; the probability of that is also equal to $1/10$.
 The impact of such a galaxy pair on the correlation functions scales with the product of the weighted number of galaxies $N_m^i,N_n^j$.
@@
 We can then write $P_{mn}^{ij}(\theta)$ as: \[
-P_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, ,
+P_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
 \label{eq:pmnij_uncorr}
@@
 For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
-We can see that for large distances $\theta$, such that $E(\theta)=0$ holds, the observed correlation functions agree with the ones that we would usually calculate.

### 2019-05-07 paperdraft.tex
Modified derivation of correlation function
Added Appendix
First semi-complete version after recent changes. Will still be subject to many modifications.
First rework, now including the new insights. Probably too long.

@@
 \def\d{\rm{d}}
+\def\bthp{\b \theta' + \b \theta}
+\def\bth{\b \theta'}
 
@@
 \usepackage{txfonts}
+\usepackage{subcaption}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \usepackage{todonotes}
-
+%\renewcommand{\todo}{\emph}
 \begin{document}
@@
 We want to understand and quantify the resulting effects.
-In particular, we check if they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
+In particular, we check whether they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
 % methods
@@
 % conclusions (optional)
-   We conclude that the effects of varying optical depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}
+   We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}
 
@@
 \begin{appendix}
-
 \include{appendix}
-
 \end{appendix}

### 2019-05-07 results.tex
First rework, now including the new insights. Probably too long.

@@
 \label{sec:results}
-We applied both our methods to data from the KV450 survey and computed the ratio of observed and modeled correlation functions.
-Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
+We applied both our methods to data from the KV450 survey and computed the ratio of observed and modeled correlation functions.\todo{Probably I should include some specifications of the KV450 survey here, like introduce the tomographic bins, etc.
+Or could I just link to Hendrik's paper?} Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
 For each tomographic redshift bin of each percentile, galaxies were placed to trace the respective redshift distribution.
@@
 	\includegraphics[width=1\textwidth]{images/allxis_0111.pdf}
-	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.}
+	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
+The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.}
 	\label{fig:all_xis}
@@
 
-The simulations seem to be in rough agreement with the models, but there are some features that can not be explained.
-Especially we observe that the ratios of the correlation functions for large values of $\theta$ seem to consistently surpass unity, which can not be explained by our models.
 The simulations seem to be in rough agreement with the models, but there are some significant differences.
@@
 We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-Although we did not determine the error bars, that a KiDS-like survey would imply on those functions, \citet{2018arXiv181110596A} calculated the COSEBIs of the KV450 survey for the same range in $\theta$.
-The measured B-Modes were about one order of magnitude higher than the ones created by the varying depth, and still found to be not significant.
-Given these facts, we conclude that the creation of B-Modes due to varying depth in the KV450 survey is not significant.
-However, the pattern seems to be very characteristic, so when one encounters B-Modes in next generation surveys, which show a similar pattern, this would suggest that they are created by a similar effect (although we can not exclude other effects that just create the same B-Mode pattern).
 We also note that the difference in E-Modes is as large as the B-Modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-Modes.

### 2019-05-08 discussion.tex
Added cosmology dependency

@@
 
+While the cosmology dependency (compare Fig.
+\ref{fig:comparecosmo}) is not significant for the KV450 survey, it will be relevant for the Euclid survey.
+In that case, a calculation of the correction for this effect is necessary for every cosmology in the MCMC simulation, underlining the necessity for a fast, analytic model.
+
 %As an outlook it would be interesting to perform a full MCMC simulation, including both cosmological and nuisance parameters.

### 2019-05-08 paperdraft.tex
Added cosmology dependency

@@
 However, the parameter $S_8$ is robust against this modification.
+We find that the dependency of this effect on the underlying cosmology is not neglible.
 We also report the occurrence of B-Modes, although not to a significant degree.
 % conclusions (optional)
-   We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}
+   We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.
+Due to the cosmology dependency, further analyses require a fast, analytic model for this effect.}
 

### 2019-06-03 introduction.tex
First rework, now including the new insights. Probably too long.
first changes after talking to peter

@@
 \section{Introduction}
-The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the $\Lambda$CDM Model and determine its parameters.
-Contrary to the analysis of the CMB by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
+The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the Standard Model of Cosmology and to determine its parameters.
+Contrary to the analysis of the Cosmic Microwave Background (CMB) by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
 Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
-It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$,
-%\citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data,
-\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2018arXiv181206076H} report $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$.
-Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data.
+It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
+Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
 This discrepancy has received a lot of attention \citep{2013PDU.....2..166V}.
@@
 To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
-As \citet{2017MNRAS.465.1454H} reported the significant detection of B-modes, it was well motivated to check for possible systematics that are not yet accounted for.
 Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.

### 2019-06-03 paperdraft.tex
first changes after talking to peter

@@
 %                              according to the author-year natbib style
-
 %
@@
 % context (optional)
-   {Cosmic shear proves to be a powerful tool to study the properties of the local Universe.
-The discrepancy in the parameter $S_8$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases.
+   {Cosmic shear proves to be a powerful tool to study the properties of the Universe.
+The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases.
 % aims
-   Especially ground-based surveys are subject to a variation in depth.
-We want to understand and quantify the resulting effects.
-In particular, we check whether they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
+   Since ground-based surveys are subject to a variation in depth, we investigate and quantify the resulting effects.
+In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
 % methods
-   We construct a semi-analytic model to estimate the impact on the shear correlation function and analyze the implications for cosmological parameters.
-Furthermore we construct COSEBIs of the correlation functions to quantify the occuring B-Modes.
+   We construct a semi-analytic model to estimate the impact on the shear correlation functions and analyse the implications for cosmological parameters.
+Furthermore, we construct COSEBIs of the correlation functions to quantify the occurring B-modes.
 % results
@@
 However, the parameter $S_8$ is robust against this modification.
-We find that the dependency of this effect on the underlying cosmology is not neglible.
-We also report the occurrence of B-Modes, although not to a significant degree.
+We find that the dependency of this effect on the underlying cosmology is not negligible.
+We also report the occurrence of B-modes, although not at a significant level.
 % conclusions (optional)

### 2019-06-06 paperdraft.tex
test?

@@
 \def\b#1{\bm{#1}}
-\def\Dd{D_{\text{d}}}
-\def\Dds{D_{\text{ds}}}
-\def\Ds{D_{\text{s}}}
+\def\Dd{D_{\rm{d}}}
+\def\Dds{D_{\rm{ds}}}
+\def\Ds{D_{\rm{s}}}
 \def\la{\left<}
@@
 %-------------------------------------------------------------------
-\include{introduction}
-\include{model_ps}
-\include{model_xipm}
-\include{results}
-\include{discussion}
+\section{Introduction}
+The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the Standard Model of Cosmology and to determine its parameters.
+Contrary to the analysis of the Cosmic Microwave Background (CMB) by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
+Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
+It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
+Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
+This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2016MNRAS.459..971K}.
+It could be interpreted as a statistical coincidence, a sign of new physics like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P}; or as the manifestation of a systematic effect, either in the cosmic shear surveys or in the Planck mission \citep{2016ApJ...818..132A}, that is not yet accounted for.
+
+For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[compare][hereafter H17]{2017MNRAS.465.1454H}.
+With next-generation surveys like the Large Synoptic Survey Telescope and Euclid \todo{Could someone please point me to papers to cite for these surveys?} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
+%\todo{Citations..
+\citet{2017MNRAS.464.1676A} has a few...}
+
+To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}.
+To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
+Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
+
+One systematic effect is the variation of depth in a survey.
+While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions that are found in ground-based surveys.
+To first order, this variation can be modelled by a piece-wise constant depth function which varies from pointing to pointing.
+In this work we assume the specifications of the Kilo-Degree Survey, namely an assembly of $1\,\text{deg}^2$ square fields.
+
+In Sect.
+\ref{sec:modelling_single_lens} we will introduce a simple toy model to understand this effect and analyze the impact on the cosmic shear power spectrum.
+In Sect.
+\ref{sec:xipm} we will estimate the effect on the shear correlation functions $\xi_\pm$ using two different models.
+We will present our results in Sect.
+\ref{sec:results}.
+In Sect.
+\ref{sec:discussion} we will discuss our results and comment on the impacts of our used simplifications.
+We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
+
+%-------------------------------------------------------------------
+
+\section{Modelling the power spectrum}
+\label{sec:modelling_single_lens}
+For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
+If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm{ds}}/D_{\rm s}$.
+% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
+%\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
+%\]
+
+%Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate.
+Assuming that the optical depth, and thus the source redshift populations, vary between pointing, an observer will measure a shear-signal that is modified by a depth-function $W(\bm{\theta}) = 1-w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
+The reconstruction of the observed convergence $\kappa^{\rm obs}$ will thus not yield the original convergence.
+In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part.
+This allows us to separate our received signal into E- and B-modes following \[
+%	\kappa = \kappa^E+i\kappa^B\, ,
+%\]
+%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
+%2002A&A...389..729S SRC
+
+Assuming that the depth, and thus the source redshift populations, varies between pointings, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of average depth.
+We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
+In accordance to the definition of the shear power spectrum \begin{equation}
+\la \hat{\gamma}(\b\ell)\,\hat{\gamma}^*(\b\ell')\ra = (2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) \, ,
+\end{equation}
+we define the observed power spectrum via \begin{equation}
+P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell)\, \gammaoh {}^*(\b \ell')\ra \, .
+\end{equation}
+Here, and throughout the rest of this paper, $\hat{\gamma}$ denotes the Fourier transform of $\gamma$.
+Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
+To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as
+\begin{equation}
+w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
+1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
+0 \qquad \text{else}
+\end{cases},
+\label{eq:defweightf}
+\end{equation}
+where $L$ is the length of one pointing.
+Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
+\begin{equation}
+P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)\, P(\b k)\, ,
+\end{equation}
+where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function and $\hat{\Xi}$ is the Fourier transform of a box-function, which is a 2-dimensional sinc-function (compare \ref{sec:calc of PS}).
+The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with a sinc-function, scaling with the variance of the function $w(\b\theta)$.
+In particular, the power spectrum is not isotropic anymore.
+
+%-------------------------------------------------------------------
+
+\section{Modelling the shear correlation functions}
+\label{sec:xipm}
+Convenient measures to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
+\xi_\pm(\theta) = \la \gamma_{\rm t}\gamma_{\rm t}\ra(\theta) \pm \la \gamma_\times\gamma_\times\ra(\theta) \, .
+\]
+Here, $\gamma_t$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[compare][]{2002A&A...396....1S}.
+The shear correlation functions are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions.
+Given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation functions from the underlying matter power spectrum $P_\delta(\ell,\chi)$ via \citep[compare][]{1992ApJ...388..272K} \begin{align}
+\label{eq:xipm-pkappa}
+\xi_\pm^{ij}(\theta) =& \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta)\, P^{ij}(\ell)\, , \\
+\label{eq:pkappa-pdelta/lenseff}
+P^{ij}(\ell) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_{\rm{H}}} {\rm d}\chi\, \frac{g^i(\chi)g^j(\chi)}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)\, , \\
+\label{eq:lenseff}
+g^i(\chi) =& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, p_i(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
+\end{align}
+Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is chosen such that $p_i(\chi)=0$ holds for all $\chi>\chi_{\rm{H}}$.
+\subsection{Using an analytic model}
+\label{sec:xipm_analytic}
+For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal, in the sense that the shear field for a deeper redshift distribution gets multiplied by a weight $W>1$.
+While this is not true for a 3-dimensional lensing matter distribution, it should be a reasonable first approximation for small variations in mean source redshift.
+Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
+
+Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
+The observed correlation functions $\xi^{ij,\text{obs}}_\pm(\theta)$ now change from one of uniform depth $\xi_\pm^{ij,\rm{uni}}(\theta)$ via (compare H17)
+\begin{align}
+\xi^{ij,\text{obs}}_\pm(\theta) = & \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_{\rm t}(\bth)\gamma^{j,\rm{obs}}_{\rm t}(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \pm \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_\times(\bth)\gamma^{j,\rm{obs}}_\times(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \nonumber\\
+ = & \frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i(\bth)N^j(\bthp)\ra} \xi_{\pm}^{ij,\rm{const}}(\theta) \, ,
+ \label{eq:xipmblub1}
+ \end{align}
+ where the average $\la\ldots\ra$ represents both an ensemble average as well as an average over the position $\bth$.
+ Assuming that depth of different pointings is uncorrelated implies that the same holds for the functions $W$ and $N$.
+This means that the only important property of a galaxy pair is whether or not they lie in the same pointing.
+We want to denote the probability that a random galaxy pair of separation $\theta$ lies in the same pointing, by $E(\theta)$.
+This function is depicted in Figure \ref{fig:eoftheta_lin}, and an analytical expression is derived in \ref{sec:model_e}.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{images/eoftheta.pdf}
+ \caption{Probability $E(\theta)$ that a random pair of galaxies of distance $\theta$ lie in the same $1\deg ^2$ pointing.}
+ \label{fig:eoftheta_lin}
+\end{figure}
+
+To compute the modified shear correlation functions, we parametrize the number densities \linebreak$N^{i}(\b \theta)=\la N^{i} \ra [1+n^{i}(\b \theta)]$ and the weight $W^{i}(\b \theta)=1+w^{i}(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n^{i}(\b \theta)$ as a function with average $\la n^{i} \ra = 0$ that is constant on each pointing.
+We can see that $\la n^i(\bth)n^j(\bthp)\ra = E(\theta)\la n^i(\bth)n^j(\bth)\ra \equiv E(\theta)\la n^i n^j \ra$ holds and compute:
+\begin{align}
+&\frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i\ra \la N^j\ra } \nonumber\\
+&\qquad =  1 + \la n^iw^i\ra + \la n^j w^j\ra + E(\theta)\left[ \la n^in^j\ra + \la n^i w^j \ra  + \la n^jw^i\ra + \la w^iw^j\ra + \la n^in^jw^i\ra + \la n^in^jw^j\ra + \la n^iw^iw^j\ra \right.
+\nonumber\\
+&\qquad\quad \left. + \la n^jw^iw^j\ra + \la n^in^jw^iw^j\ra  \right] \, .
+ \end{align}
+Ignoring correlations higher than second order in $n^i$ and $w^i$,\footnote{It is not inherently obvious that this is a valid assumption.
+However, after performing calculations with and without higher order correlations, we noticed no difference between the outcomes of both equations.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
+ \begin{align}
+ \xi^{ij,\rm{obs}}_\pm(\theta) = \frac{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}{1+E(\theta)\la n^i n^j\ra }\xi^{ij,\rm{const}}_\pm (\theta) \, .
+ \end{align}
+ A model correlation function for a cosmic shear survey is usually calculated by taking the average redshift distribution of a redshift bin, weighted by the number density.
+ Ignoring that the depth is constant per pointing and therefore correlated on scales $\leq \sqrt{2}^\circ$ is equivalent to setting $E(\theta)\equiv 0$.
+Note that there is still a correlation between $N$ and $W$ for the same galaxy.
+%For the calculation of the reference correlation functions $\xi_\pm^{ij}(\theta)$ we distribute the \textit{same} galaxies into our survey, only this time we will not order their weightings $W$ or their number densities $N$ by pointing.
+We can imagine this by cutting the footprint into infinitesimal elements $\d^2\b\theta$, and redistributing those at random.
+When we calculate the correlation function of this survey, we note that $\la n^i(\bth)\ra \la n^j(\bthp)\ra = 0$ holds for $\b\theta\neq \b 0$, as the two corresponding infinitesimal elements have uncorrelated weighting and number density.
+This is equivalent to setting $E(\theta)\equiv 0$.
+ Performing the same calculations as above, this yields a relation between the correlation function of constant optical depth $\xi_\pm^{ij,\rm{const}}$ and the modelled one $\xi_\pm^{ij}$:
+\begin{equation}
+\xi_\pm^{ij}(\theta) = \left(1+\la n^iw^i\ra + \la n^jw^j\ra \right)\xi_\pm^{ij,\rm{const}}(\theta)\, .
+\end{equation}
+The ratio of modelled and observed correlation function thus becomes: \begin{equation}
+\frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} \approx \frac{1+\la n^iw^i\ra+\la n^jw^j\ra + E(\theta)\la n^in^j\ra}{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}
+\, .
+\end{equation}
+It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales.
+
+While this model serves as a good, intuitive first approximation, it completely ignores any effects from the large scale structure (LSS) between the closest and the most distant galaxy.
+Therefore, we do not expect this model to yield reliable, quantitative results for cosmic shear surveys.
+
+However, we will now derive a more sophisticated model that includes the effects of the LSS.
+While it is computationally more expensive, it yields accurate results for cosmic shear surveys, which are sensitive to the exact redshift distributions of sources as well as the underlying cosmology.
+%-------------------------------------------------
+%Given a set of average redshifts, following \citet{2006APh....26...91V}, we can estimate 
+%\[
+%\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
+%\]
+%We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts.
+We thus want to construct a model that is valid for an arbitrary distribution of redshifts and does not rely on the assumption of a single lens plane.
+\subsection{Using a semi-analytic Model}
+\todo{It feels like some kind of introductory sentence is missing here, right now I can not think of one, though...}
+The analysis of data from the Kilo-Degree Survey showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band.
+We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e.
+if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
+For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H17\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
+Due to this we account for different weighting of galaxies on the shear correlation functions as well as on the average redshift distribution.}.
+Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{10.1093/mnras/stx2082}.
+Among other quantities, it calculates the shear correlation functions for a given cosmology and source redshift distribution.
+For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (compare H17).
+If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$.
+This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions.
+Formally, we define \[
+\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} P_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} P_{mn}^{ij}(\theta)}\, ,
+\label{eq:def_xiobs}
+\]
+where $P_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.} In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
+We will later discuss the validity of these assumptions as well as possible mitigation strategies.
+
+To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1,\d^2\b\theta_2$ of separation $\theta$ on the sky.
+For the case $m\neq n$ we know that a pair of galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ has to lie in different pointings, else they would automatically be of the same percentile.
+The probability that the imagined surface elements are within different pointings is $[1-E(\theta)]$.
+Furthermore, the first element $\d^2\b\theta_1$ has to lie in percentile $m$, the probability of which is $1/10$.
+The pointing of the second element $\d^2\b\theta_2$ has to be of percentile $n$; the probability of that is also equal to $1/10$.
+The probability that a galaxy pair populates those surface elements is proportional to the weighted number of galaxies $N_m^i,N_n^j$.
+We get for $n\neq m$: \[
+\mathcal{P}_{mn}^{ij}(\theta) = [1-E(\theta)]\frac{1}{100} N_m^i N_n^j\, .
+\label{eq:pmnij_corr1}
+\]
+For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxy lies in the same pointing [accounted for by the factor $E(\theta)$], it automatically is of the same percentile.
+We therefore set \[
+\mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
+\label{eq:pmnij_corr2}
+\]
+We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \[
+\mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
+\label{eq:pmnij_uncorr}
+\]
+where $\delta_{mn}$ denotes the Kronecker delta.
+Inserting this into Eq.\,\eqref{eq:def_xiobs}, we compute
+\begin{align}
+\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\sum_{m=1}^{10} N_m^i \left\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
+\label{eq:correctionfunction1}
+\end{align}
+with the normalization
+\[
+C = \sum_{m=1}^{10} N_m^i \bigg[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\bigg]\, .
+\]
+A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
+
+If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive).
+However, if we examine Eq.\,\eqref{eq:lenseff}, we see that the comoving distance distribution of sources factors in linearly.
+This in turn implies that in Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions factor in linearly.
+This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
+In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average redshift distribution} $p^i(z)$ of tomographic bin $i$ as \[
+N^i\equiv\sum_m N_m^i\, , \qquad p^i(z) = \frac{\sum_m N_m^i p_m^i(z)}{\sum_m N_m^i} \, .
+\]
+If we define $\xi^{ij}_\pm$ as the correlation functions between the average redshift distributions $p^i(z)$ and $p^j(z)$, then we observe: \[
+\sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = N^iN^j\xi^{ij}_\pm\, .
+\]
+Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
+\begin{equation}
+\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{C}\left\{ E(\theta)\left[\sum_{m=1}^{10} N_m^iN_m^j \xi_{\pm,mm}^{ij}(\theta)\right] +\frac{\big[1-E(\theta)\big]}{10}\xi_\pm^{ij}(\theta)N^iN^j\right\}\, .
+\label{eq:correctionfunction2}
+\end{equation}
+For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
+
+%-------------------------------------------------------------------
+
+\section{Results}
+\label{sec:results}
+We applied both our methods to data from the KV450 survey and computed the ratio of observed and modeled correlation functions.\todo{Probably I should include some specifications of the KV450 survey here, like introduce the tomographic bins, etc.
+Or could I just link to Hendrik's paper?} Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
+For each tomographic redshift bin of each percentile, galaxies were placed to trace the respective redshift distribution.
+Afterwards, their expected shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included).
+This was compared to a set of simulations where the galaxies were simply distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, is this what you did?
+If you are unhappy with any of these explanations, or feel like I missed something, please feel free to add it :)}.
+As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
+The result can be seen in Figure \todo{For the analytic model, describe how we get to $W$ (either van Waerbecke (2006) or taking a value of $\xi_\pm$.}\ref{fig:all_xis}.
+	\begin{figure}
+	\centering
+	\includegraphics[width=1\textwidth]{images/allxis_0111.pdf}
+	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
+The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.}
+	\label{fig:all_xis}
+	\end{figure}
+We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
+We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk?
+Maybe in the appendix to avoid too many Figures?}\footnote{We also observe that in the semi-analytic model, $\xi_-$ seems to be much stronger affected by this effect: Following Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
+This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$.
+However, $\xi_-$ is obtained by filtering with the 4-th order Bessel function, which peaks at approximately $\ell\theta\approx 5$, so for different $\theta$ this function is sensitive to varying parts of the convergence power spectrum.
+A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}
+
+The simulations seem to be in rough agreement with the models, but there are some significant differences.
+After a thorough analysis we explain these discrepancies the following way: The simulations were performed on a $100\,\rm{deg}^2$ field, which means that shot-noise of the fields plays a significant role.
+After performing the same simulations for a different distribution of depth between the pointings and obtaining completely different results, we are quite certain that this is the dominating effect.
+The implications of this and possible mitigation strategies will be discussed in Section \ref{sec:discussion}.
+
+Calculating the correction for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$ reveals a nontrivial dependency on the cosmology, which can be observed in Figure \ref{fig:comparecosmo}.
+
+As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model.
+Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
+As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.
+As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties.
+However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area.
+As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.
+
+To estimate the B-Modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare \citet{2010A&A...520A.116S}), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
+We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
+We also note that the difference in E-Modes is as large as the B-Modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-Modes.
+
+\begin{figure}
+\centering
+\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/eandbmodes0p5t100.pdf}
+\caption{Difference in the logarithmic E- and B-modes between the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=100\arcmin$.}
+\label{fig:bmodes_cosebi}
+\end{figure}
+
+%-------------------------------------------------------------------
+
+\section{Discussion}
+\label{sec:discussion}
+With our semi-analytic model we try to describe the impacts of varying depth in ground-based surveys. During our analysis we have assumed a few simplifications, which we will discuss.
+\begin{enumerate}
+\item In the most general terms, we are analysing the effects of a position-based selection function on cosmic shear surveys.
+In our analysis, this selection function was governed by the $r$-band depth of a pointing.
+This neglects a number of other effects: The depth in different bands and the seeing of a pointing will also modify the number densities and redshift distributions on the scale of a pointing, whereas dithering strategies as well as imperfections in the telescope and CCD cause modifications on sub-pointing scales.
+However, we believe that these effects are subdominant compared to the variations caused by the $r$-band depth.
+
+\item We have assumed an infinitely large survey area with an uncorrelated distribution of the depth-function.
+While the boundary effects arising from a finite survey footprint would have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has less neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the shot noise of the depth-distribution.
+We have assumed that the probability that a neighbouring pointing is of percentile $n$ is exactly the expectation value, namely $1/10$.
+While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, Figure \ref{fig:all_xis} clearly shows that it is not valid for a $100\,\rm{deg}^2$ field.
+Whether our assumption holds true for the $450\,\rm{deg}^2$ footprint of the KV450 survey, or even the $1350\,\rm{deg}^2$ footprint of the final survey is an important question.
+Also, we have assumed an uncorrelated distribution of the depth-function, both in the simulations as well as in the models.
+While this is likely true as a rough approximation (very few pointings of the survey were taken on the same night and thus under the same weather conditions), effects like airmass, lunar phase, Galactic extinction and seasonal weather are likely to influence the depth on scales larger than one pointing.
+
+A strategy for the mitigation of finite field effects, boundaries and a correlated distribution of depth is given in Appendix \ref{sec:expand_eoftheta}.
+We find that finite field effects are not significant for a $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$-field, if the distribution of depth is uncorrelated.
+
+\item In our MCMC simulations we did not account for degeneracies with other cosmological parameters
+% (apart from $\Omega_{\rm m}, \sigma_8, w_0$ and $w_a$)
+ or observational effects.
+Especially intrinsic alignments and baryonic feedback also modify the correlation functions especially on small scales, so they are probably degenerate with the effect of varying depth.
+In an actual MCMC simulation that accounts for these effects, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, and the impact on cosmological parameters is actually smaller than in our results.
+Also, possible degeneracies between $S_8$ and other cosmological parameters might bias the resulting values.
+%Furthermore, when including the effects of dark energy we notice that our observation of $S_8$ being constant is no longer valid: For a `Euclid-like' survey we notice a bias of $\sim 0.8\sigma$.
+This gives rise to the assumption that the results of an MCMC with the full parameter space, including observational effects, will differ from our results.
+\end{enumerate}
+
+Despite these repercussions, we are confident to say that the effects of varying depth are not significant for the KV450 survey.
+The cosmological parameters did not change significantly and the main parameter, $S_8$, is especially robust against this effect.
+In particular this means that a varying depth can not explain the discrepancy between observations of the local Universe and results from analysis of the CMB.
+
+We have shown that this effect can create B-modes.
+However, \citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
+Those B-modes are at least one order of magnitude larger and still consistent with zero, so it is safe to say that the modes created by varying depth are negligible.
+An interesting observation is that the change in E-modes is as big as the created B-modes (compare Figure \ref{fig:cosebis_eandb}).
+This means that as soon as this effect causes significant biases in the cosmological parameters, it will also create significant B-modes\footnote{While this is no big surprise, it is not trivial.
+It could be possible that a systematic effect only creates E-modes and no B-modes, which would be extremely unfortunate as it could bias cosmological parameters without ever being detected by a B-mode analysis.}.
+Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey.
+
+For next-generation surveys like Euclid, this effect will be significant.
+Although Euclid is a space-based telescope, the photometric redshift determination will still be done by ground-based telescopes and therefore suffer from the same effects.
+While we did not yet perform a quantitative study of this effect for Euclid, we are certain that a such a study should be conducted.
+
+While the cosmology dependency (compare Fig.
+\ref{fig:comparecosmo}) is not significant for the KV450 survey, it will be relevant for the Euclid survey.
+In that case, a calculation of the correction for this effect is necessary for every cosmology in the MCMC simulation, underlining the necessity for a fast, analytic model.
+
+%As an outlook it would be interesting to perform a full MCMC simulation, including both cosmological and nuisance parameters.
+One might also check the most popular extensions to the standard model of cosmology, and see whether varying depth could cause a bias towards one of these models.
+Furthermore, the method developed in Appendix \ref{sec:expand_eoftheta} could be applied to the actual footprint of the KV450 survey to see whether finite field effects or a correlated distribution of $r$-band depth are significant.
+Additionally is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$, which is not isotropic.
+Therefore, it would be possible to observe a direction-dependent correlation function $\xi_\pm^{ij,\rm{obs}}(\b\theta)$ in future surveys.
+An anisotropy in the observed correlation function could be a sign for the influence of varying depth.
+\todo{Should we give an outlook?}
+
 %--------------------------------------------------------------------
@@
 \begin{appendix}
-\include{appendix}
+\section{Detailed Calculations}
+\subsection{Calculation of the power spectrum}
+In this Section we will perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$.
+For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$.
+In reality, finite field effects would play a role here.
+We begin with the calculation of the correlation for the Fourier transformed shear:
+\begin{align}
+& \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\nonumber\\
+ &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta')\ra\nonumber\\
+ &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta') \int \frac{\text{d}^2 k}{(2\pi)^2}\int \frac{\text{d}^2 \ell}{(2\pi)^2}\, \tilde{\gamma}(\b k)\tilde{\gamma}^*(\b \ell)\exp(-\i \b k\b \theta+\i \b \ell\b \theta')\ra \nonumber\\
+&\qquad = \la \int \text{d}^2 \theta \int \text{d}^2 \theta' \int \frac{\text{d}^2 k}{(2\pi)^2} \int \frac{\text{d}^2 \ell}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b \ell) \exp[\i (\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b \ell\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
+  &\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \int \text{d}^2 \theta\, W(\b \theta)\exp[\i\b \theta(\b \ell-\b k)]\int \text{d}^2 \theta'\, W(\b \theta') \exp[-\i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
+  &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k)\widetilde{W}(\b \ell-\b k)\widetilde{W}^* (\b \ell'-\b k)\ra
+\end{align}
+It is important to keep in mind that the ensemble averages of the weight function are independent of the ensemble averages of the shear values, meaning $\la W(\b \theta)\gamma(\b \theta)\ra = \la W(\b \theta)\ra \la \gamma(\b \theta)\ra$.
+We can define $W(\b \theta)=1+w(\b\theta)$ with $\la w(\b \theta)\ra = 0$, which leads to the expession
+\begin{align}
+& \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \nonumber\\
+ &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \tilde{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \tilde{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]\right.\right.
+\nonumber\\
+ & \quad\qquad \left.\left. + \tilde{w}(\b \ell-\b k)\tilde{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
+ &\qquad =  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \left[ \la \tilde{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \tilde{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\right] + \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
+& \qquad \overset{(*)}{=}  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
+\label{eq:pobs1}
+\end{align}
+where in $(*)$ we have used that the average $\la \tilde{w}(\b \ell)\ra$ vanishes.
+Up until now, we have not specified our weight-function $w$. We parametrize it as \begin{equation}
+w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
+1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
+0 \qquad \text{else}
+\end{cases}.
+\end{equation}
+Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier-Transform we compute: \begin{equation}
+\tilde{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-\i \b \ell L\b \alpha) \widetilde{\Xi}(\b \ell)\, ,
+\end{equation}
+where
+\begin{equation}
+\widetilde{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
+\end{equation}
+is a 2-dimensional sinc function.
+Assuming an uncorrelated weight-distribution $\left(\la w_{\b \alpha} w_{\b \beta}\ra = 0\text{ for }\b \alpha\neq\b \beta\right)$ and setting $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ for each $\b \alpha$, we get
+\begin{align}
+&\la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
+&\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-\i(\b \ell - \b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k) \exp[\i(\b \ell' - \b k)L\b \beta]\, \widetilde{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
+&\qquad = \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-\i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k)\widetilde{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
+\end{align}
+Using this result, we can obtain the observed power spectrum \begin{equation}
+P^{\rm{obs}}(\b\ell) = \frac{1}{(2\pi)^2}\int\d^2\ell' \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra\, ,
+\end{equation}
+by performing the $\b \ell'$-integration in \eqref{eq:pobs1}:
+\begin{align}
+P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha+\i(\b \ell'-\b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell-\b k)\widetilde{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
+= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widetilde{\Xi}^*(\b \ell'-\b k)\exp[\i(\b \ell'- \b k)L\b \alpha] \nonumber\\
+ = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widetilde{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-\i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
+ = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widetilde{\Xi}(\b \ell-\b k)P(\b k)\, ,
+\end{align}
+which is a convolution of the power spectrum and the 2-dimensional sinc function.
+\label{sec:calc of PS}
+
+\subsection{The function $E(\theta)$}
+\label{sec:model_e}
+When computing the shear correlation between a pair of galaxies, it is of central importance whether those two galaxies lie in the same pointing or not.
+We want to model the probability that a pair of galaxies with separation $\b\theta$ lie in the same pointing by the function $E(\b\theta)$, which we will derive here:
+
+{
+\def\vec{\b}
+\begin{figure}
+    \centering
+    \def\svgwidth{200pt}    
+    \hspace*{1cm}
+    \input{images/eoftheta_new.pdf_tex}  
+    \hspace*{-2cm}
+    \caption[Graphic how to obtain $E(\b\theta)$]{Graphic representation on how to obtain the function $E(\b\theta)$.
+For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
+    \label{fig:explain_etheta}
+\end{figure}
+}
+Given one square field of length $L$ (in our case $L=60\arcmin$) and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
+As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
+The volume of this square equals \begin{equation}
+V(|\b\theta|,\phi)  = \big[L-|\b\theta|\cos(\phi)\big]\,\big[L-|\b\theta|\sin(\phi)\big]\, ,
+\end{equation} where $\phi$ represents the angle of the vector $\b\theta$.
+The function $E(\b\theta)$ then simply equals $V(|\b\theta|,\phi)/L^2$.
+To exclude negative Volumes (which could occur when $|\b\theta|>1$ holds), we need to add the Heaviside theta function $\mathcal{H}$:
+\begin{equation}
+E(\b\theta)  = \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, \mathcal{H}\left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\mathcal{H}\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, .
+\label{eq:eoftheta1}
+\end{equation} 
+As $E(\b\theta)$ is not isotropic, in order to obtain the function $E(\theta) = E(|\b\theta|)$, we need to azimuthally average Equation \eqref{eq:eoftheta1} over all angles $\phi$.
+While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
+\begin{align}
+E(\theta) = & \frac{4}{2\pi}\int_0^{\frac{\pi}{2}}\d\phi\, E(\b\theta) = \frac{2}{\pi}\begin{cases}
+\int_0^{\frac{\pi}{2}} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, ,  & |\b\theta|  \leq L \\[10pt]
+\int_{\cos\inv(L/|\b\theta|)}^{\sin\inv(L/|\b\theta|)} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right] \, , \quad   & L \leq |\b\theta| \leq \sqrt{2}L \\[10pt]
+0\, , &\sqrt{2}L \leq\theta
+\end{cases} \nonumber\\[10pt]
+ = & \begin{cases}
+\frac{1}{L^2 \pi}\left[L^2\pi - (4L-\theta) \theta\right]\, ,  & \theta \leq L \\[10pt]
+\frac{2}{\pi}\,\left[4\sqrt{\frac{\theta^2}{L^2}-1} -1 - \frac{\theta^2}{2L^2} - \cos\inv\left(\frac{L}{\theta}\right) + \sin\inv\left(\frac{L}{\theta}\right)\right]\, ,  & L  \leq \theta \leq \sqrt{2}L \\[10pt]
+0\, ,  & \sqrt{2}L \leq \theta
+\end{cases}\, .
+\end{align}
+
+\subsection{Calculation of the shear correlation functions}
+\label{sec:calc of xipm}
+Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation functions via \begin{equation}
+\xi^{ij}_+(\theta) = \frac{\sum_{a,b}w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*}\Delta(|\b\theta_a^i-\b\theta_b^i|)}{\sum_{a,b}w_a^iw_b^j\Delta(|\b\theta_a^i-\b\theta_b^i|)}\, .
+\label{eq:xip_from_observations}
+\end{equation}
+Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky. We have defined the function $\Delta$ as \[
+\Delta(|\b\theta_a^i-\b\theta_b^i|) = \begin{cases}
+1, \,\, & |\b\theta_a^i-\b\theta_b^j| \in [\theta,\theta+{\rm d}\theta] \\
+0, & \text{ else}
+\end{cases}\, ,
+\]
+where we assume ${\rm d}\theta \ll \theta$.
+We define $N$ as the number of pointings in the survey and $F_k^i$ as the set of galaxies in pointing $k$ and tomographic bin $i$.
+The numerator in Equation \eqref{eq:xip_from_observations} then transforms to: \begin{align}
+& \sum_{k,\ell=1}^N \sum_{a\in F_k^i}\sum_{b\in F_{\ell}^j} w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*} \Delta(|\b\theta_a^i-\b\theta_b^i|) \nonumber\\
+ = & \sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \sum_{\ell=1}^N \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} \nonumber\\
+  = & \sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \left[\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} + \sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*}\right] \, .
+\end{align}
+When we denote the probability that pointing $k$ is of percentile $m$ by $\mathcal{P}_m^k$ and assume that the product $\epsilon_a^i\epsilon_b^{j*}$ always equals its expectation value, we can set the numerator as \[
+\sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \sum_m \mathcal{P}_m^k \left[\overbrace{\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.a)}}\,  \xi_{+,mm}^{ij}(\theta) + \overbrace{\sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.b)}} \sum_n \mathcal{P}_n^{\ell} \xi_{+,mn}^{ij}(\theta)\right] \, .
+\label{eq:numerator1}
+\]
+The term (\ref{eq:numerator1}.a) denotes all galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a$, and are in the same pointing as galaxy $a$.
+This term is equal to the (weighted) number density of galaxies in the pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$.
+
+The term (\ref{eq:numerator1}.b) denotes all galaxies within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a$, that are \textit{not} in the same pointing as galaxy $a$.
+This is equal to the number density of galaxies in the respective pointings multiplied by $2\pi\theta\, {\rm d}\theta\, [1-E(\theta)]$.
+
+If we assume that said number density in a pointing is equal to the number density in the percentile it belongs to, $N_n^j$, and set $\mathcal{P}_n^\ell=1/10$, the numerator becomes \begin{align}
+\sum_{k=1}^N \sum_{a\in F_k^i} w_a^i \sum_m P^k_m \left[2\pi\theta\,\d\theta\,E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + 2\pi\theta\,\d\theta\,\frac{1-E(\theta)}{10}\, \sum_n N_n^j \xi_{+,mn}^{ij}(\theta) \right] \, .
+\end{align}
+Now the term $\sum_{a\in F_k^i} w_a^i$ denotes the (weighted) number of galaxies in pointing $k$, which we set as the number density of galaxies in the respective percentile multiplied with the area $A$ of the pointing.
+Applying this and setting $\mathcal{P}_m^k=1/10$, the numerator reads
+\begin{align}
+\frac{2\pi\theta\,\d\theta}{10} \sum_{k=1}^N \sum_m N_m^i A &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \nonumber\\
+ =  \, \frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \, .
+\end{align}
+%
+ The same line of argumentation can be applied to the denominator, which then reads: \[
+\frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i \left[ E(\theta) N_m^j + \frac{1-E(\theta)}{10}\sum_n N_n^j\right]\, .
+ \]
+Taking the ratio of the two quantities, we see that Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} are the same\footnote{Note that while here $N_m^i$ denotes a number density, in Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} it denotes the total (weighted) number of galaxies.
+However, the difference is just a multiplication with the area $A$ of the pointings, which appears both in the numerator and the denominator and is thus cancelled out.}.
+\section{Finite field effects}
+\label{sec:expand_eoftheta}
+\begin{figure}
+    \centering
+    \def\svgwidth{200pt}    
+%    \hspace*{1cm}
+    \input{images/expand_eoftheta.pdf_tex}  
+%    \hspace*{-2cm}
+    \caption{Graphic representation of the definitions of $E_{ab}(\theta)$.
+When the first galaxy is in the bottom left pointing, the probability to find the second galaxy in a pointing of distance $(a,b)$ is $E_{ab}(\theta)$.}
+    \label{fig:expand_etheta}
+\end{figure}
+In this chapter we will outline how to calculate the correction of the correlation functions for a finite survey with a potentially correlated distribution of depth between pointings.
+Essentially, this boils down to the calculation of $\mathcal{P}_{mn}^{ij}(\theta)$ from Equation \eqref{eq:def_xiobs}.
+We calculate this weighting by the geometrical probability that a pair of galaxies of separation $\theta$ is of percentiles $m$ and $n$, $\mathcal{P}(m,n|\theta)$, weighted by the respective number of galaxies in the percentiles $N_m^i,N_n^j$: \[
+\mathcal{P}_{mn}^{ij}(\theta) = N_m^iN_n^j\mathcal{P}(m,n|\theta)\, .
+\label{eq:pmnij1}
+\]
+ At first we define Functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$.
+This situation is depicted in Figure \ref{fig:expand_etheta}.
+Due to symmetry, for the azimuthal average of the functions, $E_{ab}(\theta) = E_{-ab}(\theta) = E_{ba}(\theta)$ holds for all combinations of $a$ and $b$.
+Note that $E_{00}(\theta)=E(\theta)$ and $\sum_{a,b}E_{ab}(\theta)\equiv 1$.
+
+Let $\mathcal{P}^*(m,n|a,b)$ denote the probability that two pointings of distance $(a,b)$ are of percentile $m$ and $n$ (which is directly calculable from a given survey footprint). 
+Then the following equation holds: \[
+\mathcal{P}(m,n|\theta) = \sum_{a,b} E_{ab}(\theta)\mathcal{P}^*(m,n|a,b)\, .
+\label{eq:pmntheta}
+\]
+Note that the expectation value of $\mathcal{P}^*(m,n|a,b)$ for uncorrelated distributions is \[
+\la \mathcal{P}^*(m,n|a,b)\ra = \begin{cases}
+0.1\,\delta_{mn},\qquad & \text{for }(a,b)=(0,0) \\
+0.01, & \text{else}
+\end{cases}\, ,
+\label{eq:pmnabstar}
+\]
+where $\delta_{mn}$ denotes the Kronecker delta. Keeping in mind that \[
+\sum_{(a,b)\neq (0,0)} E_{ab}(\theta) = 1-E(\theta)\, ,
+\]
+we can use the expectation value \eqref{eq:pmnabstar} to calculate \eqref{eq:pmntheta} as a consistency check.
+In that case, we receive the same value for the coefficients in \eqref{eq:pmnij1} as we have in Equation \eqref{eq:pmnij_uncorr} in Chapter \ref{sec:xipm_semianalytic} for the case of an infinite footprint and uncorrelated distribution of depth.
+
+\begin{figure}
+\centering
+\begin{subfigure}[c]{0.49\textwidth}
+\def\svgwidth{100pt}
+\hspace*{2cm}
+\input{images/e_1.pdf_tex}
+\subcaption{For $\theta\sin(\phi)<L$ the volume of the dashed rectangle is $V(\theta,\phi)=\theta\sin(\phi)[L-\theta\cos(\phi)]$.}
+\label{fig:e01thetaa}
+\end{subfigure}
+\begin{subfigure}[c]{0.49\textwidth}
+\def\svgwidth{100pt}
+\hspace*{2cm}
+\input{images/e_2.pdf_tex}
+\subcaption{For $\theta\sin(\phi)>L$ the volume of the dashed rectangle is $V(\theta,\phi)=[2L-\theta\sin(\phi)]\, [L-\theta\cos(\phi)]$.}
+\label{fig:e01thetab}
+\end{subfigure}
+\caption[How to calculate $E_{01}(\theta)$]{How to calculate $E_{01}(\theta)$ for different values of $\theta$.}
+\label{fig:e01theta}
+\end{figure}
+
+The $E_{ab}$ can all be calculated analytically, similar to our method in Chapter \ref{sec:model_e}.
+We again assume a selection of square fields with side length $L$, and later set $L=60\arcmin$ to adapt to the KV450 survey.
+As an example, for $E_{01}$ we have several possible situations, depicted in Figure \ref{fig:e01theta}.
+Again setting $E_{ab}(\b\theta) = V(\theta,\phi)/L^2$, we define \begin{align}
+E_{01}^{(a)}(\b\theta) & \equiv \frac{\theta}{L}\sin(\phi)[1-\frac{\theta}{L}\cos(\phi)] \nonumber\\
+E_{01}^{(b)}(\b\theta) & \equiv [2-\frac{\theta}{L}\sin(\phi)]\, [1-\frac{\theta}{L}\cos(\phi)]
+\end{align}
+With some geometric considerations, we compute:
+{
+\begingroup
+\addtolength{\jot}{1em}
+\begin{align}
+E_{01}(\theta) = & \begin{cases}
+\frac{1}{\pi}\int_0^{\frac{\pi}{2}} \d\phi\, E_{01}^{(a)}(\b\theta), & \frac{\theta}{L} < 1 \\[10pt]
+ \frac{1}{\pi}  \left[\int_{\cos\inv(L/\theta)}^{\sin\inv(L/\theta)}\d\phi\,E_{01}^{(a)}(\b\theta) + \int_{\sin\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) \right],  & 1 < \frac{\theta}{L} < \sqrt{2} \\[10pt]
+ \frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta), & \sqrt{2}<\frac{\theta}{L}<2 \\[10pt]
+\frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\sin\inv(2L/\theta)}\d\phi\, E_{01}^{(b)}(\b\theta), & 2<\frac{\theta}{L}<\sqrt{5} \\[10pt]
+ 0, & \sqrt{5}<\frac{\theta}{L}
+\end{cases}\nonumber\\
+ = & \begin{cases}
+ \frac{(2L-\theta)\theta}{2\pi L^2}, & \frac{\theta}{L} < 1 \\[10pt]
+ \frac{1}{\pi}\left[\frac{3}{2}- 2\frac{\theta}{L}+\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-1}+2\rm{sec\inv}\left(\frac{\theta}{L}\right)\right], & 1<\frac{\theta}{L}<\sqrt{2} \\[10pt]
+ \frac{1}{2\pi}\left[-1-4\frac{\theta}{L}+4\sqrt{\frac{\theta^2}{L^2}-1}+4\rm{csc\inv}\left(\frac{\theta}{L}\right)\right], & \sqrt{2} < \frac{\theta}{L} < 2 \\[10pt]
+ \frac{1}{2\pi}\left[-5-\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-4}+4\sqrt{\frac{\theta^2}{L^2}-1}-4\rm{sec\inv}\left(\frac{\theta}{L}\right)+4\sin\inv\left(\frac{2L}{\theta}\right)\right], & 2 < \frac{\theta}{L} < \sqrt{5} \\[10pt]
+ 0, & \sqrt{5}<\frac{\theta}{L}
+ \end{cases}\, .
+\end{align}
+\endgroup
+}
+
+\begin{figure}
+\centering
+\def\svgwidth{120pt}
+\input{images/drawing.pdf_tex}
+\caption[Visualisation of the numerical computation for $E_{01}(\theta)$.]{Visualisation of the numerical computation for $E_{01}(\theta)$.
+For a circle of radius $\theta$, the length of the red arc divided by $2\pi$ represents the fraction of galaxies within the respective pointing.
+This value needs to be integrated for all possible centers of the circle in the pointing.
+That procedure is straightforward to expand for other $E_{ab}(\theta)$.}
+\label{fig:eoftheta_sim}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width = 0.8\textwidth]{images/eab.pdf}
+\caption{The functions $E_{ab}(\theta)$ for the first few possible combinations.}
+\label{fig:eab}
+\end{figure}
+Naturally, to calculate those functions for all possible combinations would be rather tedious, however they are simple to determine numerically (compare Figure \ref{fig:eoftheta_sim}).
+A plot of these functions can be found in Figure \ref{fig:eab}.
+
+When we now simulate random distributions of the depth-function for a $100\,\rm{deg}^2$-field, a $450\,\rm{deg}^2$-field and a $1000\,\rm{deg}^2$-field, we can compare how they differ from each other and estimate how important finite-field effects are.
+As can be seen from Figures \ref{fig:100degsqr}, \ref{fig:450degsqr} and \ref{fig:1000degsqr}, the effect is quite significant for a $100\,\rm{deg}^2$-field, but almost negligible for a $1000\,\rm{deg}^2$-field.
+This leads to the assumption that both for the KiDS- as for the Euclid-survey, finite field effects do not need to be accounted for.
+However, if the distribution of depth is correlated in the surveys, that might have a noticeable impact on the results.
+
+\section{Additional Figures}
+\subsection{Results of the MCMC}
+\begin{figure}[h]
+\centering
+	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
+	\caption{Bias in the parameters for a KiDS-like Survey.}
+	\label{fig:mcmc_kids}
+\end{figure}  
+\begin{figure}[h]
+\centering
+	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
+	\caption{Bias in the parameters for a Euclid-like Survey.}
+	\label{fig:mcmc_euclid}
+\end{figure}  
+\clearpage
+\subsection{Finite field effects}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/100degtwofoot_final.pdf}
+\caption[Correction of the correlation functions for a $100\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $100\,\rm{deg}^2$-field.}
+\label{fig:100degsqr}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/450degtwofoot_final.pdf}
+\caption[Correction of the correlation functions for a $450\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $450\,\rm{deg}^2$-field.}
+\label{fig:450degsqr}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/1000degtwofoot_final.pdf}
+\caption[Correction of the correlation functions for a $1000\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $1000\,\rm{deg}^2$-field.}
+\label{fig:1000degsqr}
+\end{figure}
+
+\subsection{Cosmology Dependency of the Results}
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/compare_cosmos.pdf}
+\caption{Correction to the correlation functions in varying cosmologies. Depicted here are three flat sample cosmologies, where values within the 98\% CL of the KV450 survey were sampled.}
+\label{fig:comparecosmo}
+\end{figure}
 \end{appendix}

### 2019-06-06 paperdraft.tex
Added references

@@
    We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.
-Due to the cosmology dependency, further analyses require a fast, analytic model for this effect.}
+Due to the cosmology dependency, further analyses require a fast, analytical model for this effect.}
 
@@
 For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[compare][hereafter H17]{2017MNRAS.465.1454H}.
-With next-generation surveys like the Large Synoptic Survey Telescope and Euclid \todo{Could someone please point me to papers to cite for these surveys?} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
+With next-generation surveys like the Large Synoptic Survey Telescope\citep{Ivezic:2008} and Euclid\citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
 %\todo{Citations..
@@
 \end{equation}
-we define the observed power spectrum via \begin{equation}
+where $\hat{\gamma}$ denotes the Fourier transform of $\gamma$, we define the observed power spectrum via \begin{equation}
 P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell)\, \gammaoh {}^*(\b \ell')\ra \, .
 \end{equation}
-Here, and throughout the rest of this paper, $\hat{\gamma}$ denotes the Fourier transform of $\gamma$.
 Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
@@
 %-------------------------------------------------
-%Given a set of average redshifts, following \citet{2006APh....26...91V}, we can estimate 
-%\[
-%\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
-%\]
-%We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts.
-We thus want to construct a model that is valid for an arbitrary distribution of redshifts and does not rely on the assumption of a single lens plane.
+
 \subsection{Using a semi-analytic Model}
+\label{sec:xipm_semianalytic}
 \todo{It feels like some kind of introductory sentence is missing here, right now I can not think of one, though...}
@@
 Formally, we define \[
-\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} P_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} P_{mn}^{ij}(\theta)}\, ,
+\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)}\, ,
 \label{eq:def_xiobs}
 \]
-where $P_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.} In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
+where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.} In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
 We will later discuss the validity of these assumptions as well as possible mitigation strategies.
@@
 \]
-A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
+A mathematically more rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
 
@@
 \label{sec:results}
-We applied both our methods to data from the KV450 survey and computed the ratio of observed and modeled correlation functions.\todo{Probably I should include some specifications of the KV450 survey here, like introduce the tomographic bins, etc.
-Or could I just link to Hendrik's paper?} Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
+We want to apply both methods to data from the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018}.
+While the application of the semi-analytic method is straightforward, for the analytic method we need to decide how to estimate the weight function $W$ from given redshift data.
+Following the separation of a survey into percentiles as in Sect.
+\ref{sec:xipm_semianalytic}, we define $W(\b\theta)\equiv W_n$ whenever $\b\theta$ is in a pointing of percentile $n$.
+For the determination of $W_n$ we tried two approaches:
+ As a first method, following \citet{2006APh....26...91V}, we estimate 
+\[
+W_n \propto \la z_n \ra ^{0.85}\, ,
+\]
+where $\la z_n\ra$ is the average redshift of percentile $n$. As a second method we define \[
+W_n \propto \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta') + \la \gamma_\times\gamma_\times\ra (\theta') = \sqrt{\xi_{+,nn}^{ij}(\theta')}\, ,
+\]
+\todo{Maybe we set $W_n\propto \sqrt[4]{\la \gamma_t\gamma_t\ra^2 + \la \gamma_\times\gamma_\times\ra^2 } \propto \sqrt[4]{\xi_+^2 + \xi_-^2}$?}
+where the $\xi_{+,nn}^{ij}(\theta')$ denotes the model correlation function defined in Sect. \ref{sec:xipm_semianalytic}, evaluated at a characteristic scale $\theta'$.
+
+While the first method suffers from the fact that the power-law index is redshift-dependent, the second method is sensitive to the angular range $\theta$, at which the shear correlation functions are evaluated, which is completely arbitrary.
+
+We applied both analytic methods and the semianalytic one to data from the KV450 survey, following the separation into tomographic bins as in H18, and computed the ratio of observed and modeled correlation functions.\todo{Probably I should include some more specifications of the KV450 survey here?} Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
 For each tomographic redshift bin of each percentile, galaxies were placed to trace the respective redshift distribution.
 Afterwards, their expected shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included).
-This was compared to a set of simulations where the galaxies were simply distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, is this what you did?
-If you are unhappy with any of these explanations, or feel like I missed something, please feel free to add it :)}.
-As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
-The result can be seen in Figure \todo{For the analytic model, describe how we get to $W$ (either van Waerbecke (2006) or taking a value of $\xi_\pm$.}\ref{fig:all_xis}.
+This was compared to a set of simulations where the galaxies were simply distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, I feel like I am grossly oversimplifying what you did.
+Maybe you could write a short paragraph about the simulations?}.
+As in H18, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
+The result can be seen in Fig.~\ref{fig:all_xis}.
 	\begin{figure}
@@
 	\includegraphics[width=1\textwidth]{images/allxis_0111.pdf}
-	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
+	\caption{The ratio of observed to modelled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
 The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.}

### 2019-06-07 paperdraft.tex
Minor changes, added new figure for both analytical models

@@
 For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[compare][hereafter H17]{2017MNRAS.465.1454H}.
-With next-generation surveys like the Large Synoptic Survey Telescope\citep{Ivezic:2008} and Euclid\citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
+With next-generation surveys like the Large Synoptic Survey Telescope \citep{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
 %\todo{Citations..
@@
 where $\la z_n\ra$ is the average redshift of percentile $n$. As a second method we define \[
-W_n \propto \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta') + \la \gamma_\times\gamma_\times\ra (\theta') = \sqrt{\xi_{+,nn}^{ij}(\theta')}\, ,
+W_n \propto \sqrt{ \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta') + \la \gamma_\times\gamma_\times\ra (\theta')} = \sqrt{\xi_{+,nn}^{ij}(\theta')}\, ,
 \]
@@
 Maybe you could write a short paragraph about the simulations?}.
-As in H18, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins.
-The result can be seen in Fig.~\ref{fig:all_xis}.
+The results can be seen in Fig.~\ref{fig:all_xis}.
 	\begin{figure}
 	\centering
-	\includegraphics[width=1\textwidth]{images/allxis_0111.pdf}
-	\caption{The ratio of observed to modelled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
-The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.}
+	\includegraphics[width=1\textwidth]{images/xis_all.pdf}
+	\caption{The ratio of observed to modelled correlation functions for the analytic methods (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
+The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
+For the characteristic scale $\theta'$ of the second analytic method we chose $\theta' = 0.\!
+'5$.}
 	\label{fig:all_xis}
 	\end{figure}
-We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
-We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk?
-Maybe in the appendix to avoid too many Figures?}\footnote{We also observe that in the semi-analytic model, $\xi_-$ seems to be much stronger affected by this effect: Following Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
+%We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
+We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.
+We observe that for high redshift bins, both analytic methods as well as the semi-analytic one yield consistent results.
+Due to the redshift-dependent index in the power law of the first analytic method, it is not able to sufficiently describe the effect for low redshift bins.
+The second analytic method, however, matches the semi-analytic one for all $\xi_+$.
+As $\xi_-$ is affected much stronger by this effect, the analytic method is not able to trace this change.\todo{Should I include the plot number density vs average redshift from the talk?
+Maybe in the appendix to avoid too many Figures?}\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
 This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$.
@@
 After performing the same simulations for a different distribution of depth between the pointings and obtaining completely different results, we are quite certain that this is the dominating effect.
-The implications of this and possible mitigation strategies will be discussed in Section \ref{sec:discussion}.
-
-Calculating the correction for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$ reveals a nontrivial dependency on the cosmology, which can be observed in Figure \ref{fig:comparecosmo}.
+The implications of this and possible mitigation strategies will be discussed in Sect.~\ref{sec:discussion}.
 
@@
 As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.
+
+Calculating the correction for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$ reveals a nontrivial dependency on the cosmology, which can be observed in Figure \ref{fig:comparecosmo}.
+However, as for the computation of the correction we need to calculate 165 correlation functions, we did not yet account for that in our MCMC analysis.
 
@@
 While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, Figure \ref{fig:all_xis} clearly shows that it is not valid for a $100\,\rm{deg}^2$ field.
-Whether our assumption holds true for the $450\,\rm{deg}^2$ footprint of the KV450 survey, or even the $1350\,\rm{deg}^2$ footprint of the final survey is an important question.
+Whether our assumption holds true for the $450\,\rm{deg}^2$ footprint of the KV450 survey, or even the $1350\,\rm{deg}^2$ footprint of the final survey, is an important question.
 Also, we have assumed an uncorrelated distribution of the depth-function, both in the simulations as well as in the models.
@@
  or observational effects.
-Especially intrinsic alignments and baryonic feedback also modify the correlation functions especially on small scales, so they are probably degenerate with the effect of varying depth.
+Especially intrinsic alignments and baryonic feedback also modify the correlation functions especially on small scales, so they are probably degenerate with the effect of varying depth \citep{Troxel:2015}.
 In an actual MCMC simulation that accounts for these effects, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, and the impact on cosmological parameters is actually smaller than in our results.
@@
 Those B-modes are at least one order of magnitude larger and still consistent with zero, so it is safe to say that the modes created by varying depth are negligible.
-An interesting observation is that the change in E-modes is as big as the created B-modes (compare Figure \ref{fig:cosebis_eandb}).
-This means that as soon as this effect causes significant biases in the cosmological parameters, it will also create significant B-modes\footnote{While this is no big surprise, it is not trivial.
+An interesting observation is that the change in E-modes is as big as the created B-modes (compare Figure \ref{fig:bmodes_cosebi}).
+This means that as soon as this effect causes a significant bias in the cosmological parameters, it will also create significant B-modes\footnote{While this is no big surprise, it is not trivial.
 It could be possible that a systematic effect only creates E-modes and no B-modes, which would be extremely unfortunate as it could bias cosmological parameters without ever being detected by a B-mode analysis.}.
@@
 In that case, a calculation of the correction for this effect is necessary for every cosmology in the MCMC simulation, underlining the necessity for a fast, analytic model.
+\todo{For that example I took value from the 95\% CL of KV450 from H18.
+As the parameter constraints in Euclid are going to be much tighter, this is probably no longer true...}
 
@@
 An anisotropy in the observed correlation function could be a sign for the influence of varying depth.
-\todo{Should we give an outlook?}
+\todo{Should we give an outlook? I.e. calculate covariances (I am trying to come up with something for that), apply to real KV450 footprint, ...}
 

### 2019-06-21 kourier/main.tex
cleanup

\documentclass[a4paper]{scrartcl}
\usepackage{graphicx}

\begin{document}
We investigate the effects of a pointing-based varying depth, caused i.e. by changes in weather between observing nights, in cosmic shear surveys. We separate KV450 data into 10 percentiles, ordered by r-band depth, and extract the galaxy number density and redshift distribution for each percentile. We develop two models to estimate the impact on the shear correlation functions: A purely analytic one that solely relies on the correlations between number density and average redshift between different pointings, and a semi-analytic model that uses the exact redshift distributions of sources to calculate the change of the correlation functions. We compare our models with simulations and find that this effect causes a bias in the shear correlation functions of the order of a few percent on small scales, but the bias on the cosmological parameters is not significant. We also extract COSEBIs of the correlation functions and find that the effect can create B-modes, but not to a degree that is significant for KiDS. We find that the varying depth affects E- and B-modes to the same degree. We further discuss how to implement a correlated distribution of depth between separate pointings as well as the shape of a footprint.

We hope to register the draft with the collaboration by the end of June. The submission is planned at the beginning of August.

Attached figure: The ratio of observed to modelled correlation functions for the analytic methods (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins. The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of xi_+, whereas the lower right triangle depicts the ratios of xi_-.
\end{document}

### 2019-06-21 paperdraft.tex
cleanup

@@
           \and Marika Asgari\inst{3}
-          \todo{order of authors?, KiDS-Authors?}
           }
@@
 Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany \and
-Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de}
+Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de, peter@astro.uni-bonn.de}
              }
@@
 To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
+The most useful E- and B-mode decomposition is provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs, compare][]{2010A&A...520A.116S}, as it can easily be applied to real data.
 Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
@@
 In this work we assume the specifications of the Kilo-Degree Survey, namely an assembly of $1\,\text{deg}^2$ square fields.
+
+The depth of a pointing primarily influences the number density as well as the average redshift of galaxies, meaning that a variation in depth is responsible for a correlation between those two quantities (compare Fig.
+\ref{fig:nz_of_meanz}).
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\linewidth]{images/cov_nz_meanz.pdf}
+\caption{Galaxy number density $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
+Details on how the data was obtained are described in Sec.
+\ref{sec:xipm_semianalytic}.}
+\label{fig:nz_of_meanz}
+\end{figure}
 
@@
 The shear correlation functions are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions.
-Given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation functions from the underlying matter power spectrum $P_\delta(\ell,\chi)$ via \citep[compare][]{1992ApJ...388..272K} \begin{align}
-\label{eq:xipm-pkappa}
-\xi_\pm^{ij}(\theta) =& \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta)\, P^{ij}(\ell)\, , \\
-\label{eq:pkappa-pdelta/lenseff}
-P^{ij}(\ell) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_{\rm{H}}} {\rm d}\chi\, \frac{g^i(\chi)g^j(\chi)}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)\, , \\
-\label{eq:lenseff}
-g^i(\chi) =& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, p_i(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
-\end{align}
-Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is chosen such that $p_i(\chi)=0$ holds for all $\chi>\chi_{\rm{H}}$.
 \subsection{Using an analytic model}
@@
 Due to this we account for different weighting of galaxies on the shear correlation functions as well as on the average redshift distribution.}.
+Asserting an arbitrary cosmological model, we can transform the source redshift distributions $p^i_m(z)$ into comoving distance probability distributions $\mathcal{L}^i_m(\chi)$.
+
+Given two comoving distance probability distributions of sources $\mathcal{L}^i_m(\chi),\mathcal{L}^j_n(\chi)$, we can compute the shear correlation functions from the underlying matter power spectrum $P(\ell,\chi)$ via \citep[compare][]{1992ApJ...388..272K} \begin{align}
+\label{eq:xipm-pkappa}
+\xi_{\pm,mn}^{ij}(\theta) =& \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta)\, P^{ij}_{\kappa,mn}(\ell)\, , \\
+\label{eq:pkappa-pdelta/lenseff}
+P^{ij}_{\kappa,mn}(\ell) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_{\rm{H}}} {\rm d}\chi\, \frac{g^i_m(\chi)g^j_n(\chi)}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)\, , \\
+\label{eq:lenseff}
+g^i_m(\chi) =& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \mathcal{L}^i_m(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
+\end{align}
+Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is chosen such that $p_i(\chi)=0$ holds for all $\chi>\chi_{\rm{H}}$.
+
 Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{10.1093/mnras/stx2082}.
@@
 We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \[
-\mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
+\mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
 \label{eq:pmnij_uncorr}
@@
 
-If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive).
-However, if we examine Eq.\,\eqref{eq:lenseff}, we see that the comoving distance distribution of sources factors in linearly.
-This in turn implies that in Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions factor in linearly.
-This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
-In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average redshift distribution} $p^i(z)$ of tomographic bin $i$ as \[
-N^i\equiv\sum_m N_m^i\, , \qquad p^i(z) = \frac{\sum_m N_m^i p_m^i(z)}{\sum_m N_m^i} \, .
+If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and coadding them, thus yielding potential numerical errors (apart from being computationally expensive).
+However, if we examine Eq.\,\eqref{eq:lenseff}, we see that the comoving distance distribution of sources enters linearly.
+This in turn implies that in Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
+In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average comoving distance probability distribution} $\mathcal{L}^i(\chi)$ of tomographic bin $i$ as \[
+N^i\equiv\sum_m N_m^i\, , \qquad \mathcal{L}^i(\chi) = \frac{\sum_m N_m^i \mathcal{L}_m^i(\chi)}{\sum_m N_m^i} \, .
 \]
-If we define $\xi^{ij}_\pm$ as the correlation functions between the average redshift distributions $p^i(z)$ and $p^j(z)$, then we observe: \[
-\sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = N^iN^j\xi^{ij}_\pm\, .
-\]
+If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, then we observe: \begin{align}
+\sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = & \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \\
+& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \mathcal{L}^i_m(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}
+\int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \mathcal{L}^j_n(\chi'') \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \\
+ = & \,N^i N^j \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \\
+& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \frac{\sum_m N_m^i \mathcal{L}^i_m(\chi')}{N^i} \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}
+\int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \frac{\sum_n N_n^j \mathcal{L}^j_n(\chi'')}{N^j}  \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \\
+ = & \, N^iN^j\xi^{ij}_\pm\, ,
+\end{align}
+where $\xi^{ij}_\pm$ denotes the correlation function for the average comoving distance probability distributions of redshift bins $i$ and $j$.
 Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
@@
 \end{equation}
-For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
+For each pair of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
 
@@
 \centering
-	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
+	\includegraphics[width=0.7\textwidth]{images/mcmc_kids.pdf}
 	\caption{Bias in the parameters for a KiDS-like Survey.}
@@
 \centering
-	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
+	\includegraphics[width=0.7\textwidth]{images/mcmc_euclid.pdf}
 	\caption{Bias in the parameters for a Euclid-like Survey.}
@@
 \centering
-\includegraphics[width=\textwidth]{images/100degtwofoot_final.pdf}
+\includegraphics[width=\textwidth]{images/finite_footprint.pdf}
 \caption[Correction of the correlation functions for a $100\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $100\,\rm{deg}^2$-field.}
 \label{fig:100degsqr}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{images/450degtwofoot_final.pdf}
-\caption[Correction of the correlation functions for a $450\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $450\,\rm{deg}^2$-field.}
-\label{fig:450degsqr}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{images/1000degtwofoot_final.pdf}
-\caption[Correction of the correlation functions for a $1000\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $1000\,\rm{deg}^2$-field.}
-\label{fig:1000degsqr}
 \end{figure}

### 2019-06-21 paperdraft.tex
nicer figures

@@
 \caption{Galaxy number density $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
-Details on how the data was obtained are described in Sec.
+Details on how the data were obtained are described in Sec.
 \ref{sec:xipm_semianalytic}.}
@@
 For the determination of $W_n$ we tried two approaches:
- As a first method, following \citet{2006APh....26...91V}, we estimate 
+ As a first method, following \citet{2006APh....26...91V,1997A&A...322....1B}, we estimate 
 \[
@@
 where $\la z_n\ra$ is the average redshift of percentile $n$. As a second method we define \[
-W_n \propto \sqrt{ \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta') + \la \gamma_\times\gamma_\times\ra (\theta')} = \sqrt{\xi_{+,nn}^{ij}(\theta')}\, ,
+W_n \propto \sqrt{ \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta_{\rm{ref}}) + \la \gamma_\times\gamma_\times\ra (\theta_{\rm{ref}})} = \sqrt{\xi_{+,nn}^{ij}(\theta_{\rm{ref}})}\, ,
 \]
-\todo{Maybe we set $W_n\propto \sqrt[4]{\la \gamma_t\gamma_t\ra^2 + \la \gamma_\times\gamma_\times\ra^2 } \propto \sqrt[4]{\xi_+^2 + \xi_-^2}$?}
-where the $\xi_{+,nn}^{ij}(\theta')$ denotes the model correlation function defined in Sect. \ref{sec:xipm_semianalytic}, evaluated at a characteristic scale $\theta'$.
+where the $\xi_{+,nn}^{ij}(\theta_{\rm{ref}})$ denotes the model correlation function defined in Sect. \ref{sec:xipm_semianalytic}, evaluated at a characteristic scale $\theta_{\rm{ref}}$.
 
-While the first method suffers from the fact that the power-law index is redshift-dependent, the second method is sensitive to the angular range $\theta$, at which the shear correlation functions are evaluated, which is completely arbitrary.
+While the first method suffers from the fact that the power-law index only holds for sources of redshifts $1\lesssim z \lesssim 2$, the second method is sensitive to the angular range $\theta$, at which the shear correlation functions are evaluated, which is fairly arbitrary.
 
@@
 The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
-For the characteristic scale $\theta'$ of the second analytic method we chose $\theta' = 0.\!
-'5$.}
+For the characteristic scale $\theta_{\rm{ref}}$ of the second analytic method we chose $\theta_{\rm{ref}} \approx 11'$.}
 	\label{fig:all_xis}
@@
 As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model.
-Then we ran a Markov-Chain Monte Carlo simulation\footnote{The code for this was developed by Jan-Luca van den Busch and used in a modified version.} to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
+Then we ran a Markov-Chain Monte Carlo simulation to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
 As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.
-As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is noticeable, but insignificant compared to the uncertainties.
+As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is barely noticeable and insignificant compared to the uncertainties.
 However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area.
-As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is extremely robust against this effect.
+As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is considerably more robust against this effect.
+
+\begin{figure}
+\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
+	\caption{Bias for a KiDS-like Survey.}
+	\label{fig:mcmc_kids}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
+	\caption{Bias for a 'Euclid-like' Survey.}
+	\label{fig:mcmc_euclid}
+\end{subfigure}
+\caption{Estimation of the bias caused by a variation of depth in a cosmic shear survey. Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
+\end{figure}
 
@@
 \includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/eandbmodes0p5t100.pdf}
-\caption{Difference in the logarithmic E- and B-modes between the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=100\arcmin$.}
+\caption{Logarithmic E-modes of the reference correlation functions as well as difference in the E- and B-modes between the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=100\arcmin$.}
 \label{fig:bmodes_cosebi}
@@
 \begin{acknowledgements}
-Something should probably be put in here...
-\end{acknowledgements}
+We want to thank Jan-Luca van den Busch for his permission to use and modify his code for an MCMC simulation.\end{acknowledgements}
 
@@
 we can use the expectation value \eqref{eq:pmnabstar} to calculate \eqref{eq:pmntheta} as a consistency check.
-In that case, we receive the same value for the coefficients in \eqref{eq:pmnij1} as we have in Equation \eqref{eq:pmnij_uncorr} in Chapter \ref{sec:xipm_semianalytic} for the case of an infinite footprint and uncorrelated distribution of depth.
+In that case, we receive the same value for the coefficients in \eqref{eq:pmnij1} as we have in Eq.
+\eqref{eq:pmnij_uncorr} in Sec.
+\ref{sec:xipm_semianalytic} for the case of an infinite footprint and uncorrelated distribution of depth.
 
@@
 
-The $E_{ab}$ can all be calculated analytically, similar to our method in Chapter \ref{sec:model_e}.
+The $E_{ab}$ can all be calculated analytically, similar to our method in Sec.
+\ref{sec:model_e}.
 We again assume a selection of square fields with side length $L$, and later set $L=60\arcmin$ to adapt to the KV450 survey.
-As an example, for $E_{01}$ we have several possible situations, depicted in Figure \ref{fig:e01theta}.
-Again setting $E_{ab}(\b\theta) = V(\theta,\phi)/L^2$, we define \begin{align}
+As an example, for $E_{01}$ we have several possible situations, depicted in Fig.
+\ref{fig:e01theta}.
+Setting $E_{ab}(\b\theta) = V(\theta,\phi)/L^2$, we define \begin{align}
 E_{01}^{(a)}(\b\theta) & \equiv \frac{\theta}{L}\sin(\phi)[1-\frac{\theta}{L}\cos(\phi)] \nonumber\\
@@
 
-When we now simulate random distributions of the depth-function for a $100\,\rm{deg}^2$-field, a $450\,\rm{deg}^2$-field and a $1000\,\rm{deg}^2$-field, we can compare how they differ from each other and estimate how important finite-field effects are.
-As can be seen from Figures \ref{fig:100degsqr}, \ref{fig:450degsqr} and \ref{fig:1000degsqr}, the effect is quite significant for a $100\,\rm{deg}^2$-field, but almost negligible for a $1000\,\rm{deg}^2$-field.
-This leads to the assumption that both for the KiDS- as for the Euclid-survey, finite field effects do not need to be accounted for.
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{images/finite_footprint.pdf}
+\caption{$2\sigma$-contours of the corrections for the correlation functions for a $100\,\rm{deg}^2$ field (blue), a $450\,\rm{deg}^2$ field (red) and a $1000\,\rm{deg}^2$ field (blue).}
+\label{fig:finite_footprint}
+\end{figure}
+
+We sampled several realizations of a random depth-distribution for a $100\,\rm{deg}^2$-field, a $450\,\rm{deg}^2$-field and a $1000\,\rm{deg}^2$-field and computed the variance of the resulting correlation functions.
+As can be seen from Fig.
+\ref{fig:finite_footprint}, the effect is quite significant for a $100\,\rm{deg}^2$-field, but almost negligible for a $1000\,\rm{deg}^2$-field.
+This leads to the assumption that both for the KV450 survey as well as for all next-generation cosmic shear surveys, finite field effects do not need to be accounted for.
 However, if the distribution of depth is correlated in the surveys, that might have a noticeable impact on the results.
@@
 \section{Additional Figures}
-\subsection{Results of the MCMC}
-\begin{figure}[h]
-\centering
-	\includegraphics[width=0.7\textwidth]{images/mcmc_kids.pdf}
-	\caption{Bias in the parameters for a KiDS-like Survey.}
-	\label{fig:mcmc_kids}
-\end{figure}  
-\begin{figure}[h]
-\centering
-	\includegraphics[width=0.7\textwidth]{images/mcmc_euclid.pdf}
-	\caption{Bias in the parameters for a Euclid-like Survey.}
-	\label{fig:mcmc_euclid}
-\end{figure}  
-\clearpage
-\subsection{Finite field effects}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{images/finite_footprint.pdf}
-\caption[Correction of the correlation functions for a $100\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $100\,\rm{deg}^2$-field.}
-\label{fig:100degsqr}
-\end{figure}
 

### 2019-06-21 paperdraft.tex
applied second batch of modifications

@@
 If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and coadding them, thus yielding potential numerical errors (apart from being computationally expensive).
-However, if we examine Eq.\,\eqref{eq:lenseff}, we see that the comoving distance distribution of sources enters linearly.
-This in turn implies that in Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
+However, if we examine Eq.~\eqref{eq:lenseff}, we see that the comoving distance distribution of sources enters linearly.
+This in turn implies that in Eqs.~\eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
 In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average comoving distance probability distribution} $\mathcal{L}^i(\chi)$ of tomographic bin $i$ as \[
@@
 
-We applied both analytic methods and the semianalytic one to data from the KV450 survey, following the separation into tomographic bins as in H18, and computed the ratio of observed and modeled correlation functions.\todo{Probably I should include some more specifications of the KV450 survey here?} Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
-For each tomographic redshift bin of each percentile, galaxies were placed to trace the respective redshift distribution.
-Afterwards, their expected shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included).
-This was compared to a set of simulations where the galaxies were simply distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, I feel like I am grossly oversimplifying what you did.
+We applied both analytic methods and the semianalytic one to data from the KV450 survey, following the separation into tomographic bins as in H18, and computed the ratio of observed and modeled correlation functions.
+Furthermore, we conducted numerical simulations, where a $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
+For each tomographic redshift bin of each percentile, source galaxies were distributed according to the respective redshift distribution and their shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included).
+This was compared to a set of simulations where the galaxies were distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, I feel like I am grossly oversimplifying what you did.
 Maybe you could write a short paragraph about the simulations?}.
@@
 	\includegraphics[width=1\textwidth]{images/xis_all.pdf}
-	\caption{The ratio of observed to modelled correlation functions for the analytic methods (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
+	\caption{The ratio of observed to modelled correlation functions for the analytic methods (green), the semi-analytic method (blue) and one realization of the numerical simulations (red) for a cross-correlation of all redshift bins.
 The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
@@
 We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.
-We observe that for high redshift bins, both analytic methods as well as the semi-analytic one yield consistent results.
-Due to the redshift-dependent index in the power law of the first analytic method, it is not able to sufficiently describe the effect for low redshift bins.
-The second analytic method, however, matches the semi-analytic one for all $\xi_+$.
-As $\xi_-$ is affected much stronger by this effect, the analytic method is not able to trace this change.\todo{Should I include the plot number density vs average redshift from the talk?
-Maybe in the appendix to avoid too many Figures?}\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
+We observe that for high-redshift bins, both analytic methods as well as the semi-analytic one yield consistent results.
+Due to the redshift-dependent index in the power law of the first analytic method, it is not able to accurately describe the effect for low redshift bins.
+The second analytic method, however, traces the semi-analytic one pretty well for $\xi_+$.
+As $\xi_-$ is affected much stronger by this effect, the analytic method is not able to trace this change.\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
 This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$.
@@
 
-The simulations seem to be in rough agreement with the models, but there are some significant differences.
-After a thorough analysis we explain these discrepancies the following way: The simulations were performed on a $100\,\rm{deg}^2$ field, which means that shot-noise of the fields plays a significant role.
-After performing the same simulations for a different distribution of depth between the pointings and obtaining completely different results, we are quite certain that this is the dominating effect.
+The simulations and the models seem to be in rough agreement, but there are some significant differences.
+After a thorough analysis we explain these discrepancies the following way: The simulations shown in Fig.~\ref{fig:all_xis} were performed on a single $100\,\rm{deg}^2$ field, which means that sample variance of the depth distribution of the fields plays a significant role.
+Performing the same simulations for a different realization of depth between the pointings, we obtained completely different results.
 The implications of this and possible mitigation strategies will be discussed in Sect.~\ref{sec:discussion}.
+\todo{I will probably completely rewrite this paragraph in case it is possible to conduct a few more simulations.}
 
-As the next step we computed a reference correlation function given a fiducial cosmology for each combination of redshift bins, and modified said correlation function according to our semi-analytic model.
-Then we ran a Markov-Chain Monte Carlo simulation to check for a potential bias in the cosmological parameters, using the covariance-matrix computed in \citet{2017MNRAS.465.1454H}.
+In Sec.~\ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm,\rm{obs}}^{ij}$ for a specific survey footprint.
+With this model we can estimate the impacts of a correlated distribution of depth, the sample variance of the depth-distribution and boundary effects.
+We find that for quadratic footprint of $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$ with an uncorrelated depth-distribution, finite field effects are negligible.
+
+As the next step we chose a fiducial cosmology $\b \Phi$ and computed a reference correlation function $\xi_\pm^{ij}(\theta,\b\Phi)$ for each pair of redshift bins $i,j$.
+Using those, we calculated the observed correlation function $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ according to our semi-analytic model in Sect.~\ref{sec:xipm_semianalytic}.
+Then we ran a Markov-Chain Monte Carlo simulation to check for the resulting bias in the inferred cosmological parameters, using the covariance-matrix computed in H18.
 As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.
 As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is barely noticeable and insignificant compared to the uncertainties.
-However, to get a rough estimate for the impact on a Euclid-like survey, we divided the used covariance-matrix by 30, to account for the increased survey area.
-As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant, however it seems that the parameter $S_8$ is considerably more robust against this effect.
+To get a rough estimate for the impact on future surveys, we divided our covariance-matrix by a factor of 30, to approximately account for the increased survey area of LSST and Euclid with respect to KV450.
+As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant.
+Conveniently it seems that the parameter $S_8$ is considerably more robust against this effect.
 
@@
 
-Calculating the correction for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$ reveals a nontrivial dependency on the cosmology, which can be observed in Figure \ref{fig:comparecosmo}.
-However, as for the computation of the correction we need to calculate 165 correlation functions, we did not yet account for that in our MCMC analysis.
+Calculating the correction $\xi_\pm^{ij}/\xi_\pm^{ij,\rm{obs}}$ for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$ reveals a nontrivial dependence on the cosmology, which can be seen in Figure \ref{fig:comparecosmo}.
 
-To estimate the B-Modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare \citet{2010A&A...520A.116S}), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
-We report a consistent B-Mode pattern across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-We also note that the difference in E-Modes is as large as the B-Modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-Modes.
+To estimate the B-modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} \citep[COSEBIS, compare][]{2010A&A...520A.116S}, once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
+We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
+It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.
 
@@
 \label{sec:discussion}
-With our semi-analytic model we try to describe the impacts of varying depth in ground-based surveys. During our analysis we have assumed a few simplifications, which we will discuss.
+With our semi-analytic model we try to describe the impacts of varying depth in ground-based cosmic shear surveys. During our analysis we have made several simplifications, which we discuss below.
 \begin{enumerate}
-\item In the most general terms, we are analysing the effects of a position-based selection function on cosmic shear surveys.
-In our analysis, this selection function was governed by the $r$-band depth of a pointing.
+\item In the most general terms, we are analysing the effects of a position-dependent selection function on cosmic shear surveys.
+In our analysis, this selection function was governed by the KiDS $r$-band depth of a pointing.
 This neglects a number of other effects: The depth in different bands and the seeing of a pointing will also modify the number densities and redshift distributions on the scale of a pointing, whereas dithering strategies as well as imperfections in the telescope and CCD cause modifications on sub-pointing scales.
@@
 \item We have assumed an infinitely large survey area with an uncorrelated distribution of the depth-function.
-While the boundary effects arising from a finite survey footprint would have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has less neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the shot noise of the depth-distribution.
-We have assumed that the probability that a neighbouring pointing is of percentile $n$ is exactly the expectation value, namely $1/10$.
-While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, Figure \ref{fig:all_xis} clearly shows that it is not valid for a $100\,\rm{deg}^2$ field.
-Whether our assumption holds true for the $450\,\rm{deg}^2$ footprint of the KV450 survey, or even the $1350\,\rm{deg}^2$ footprint of the final survey, is an important question.
-Also, we have assumed an uncorrelated distribution of the depth-function, both in the simulations as well as in the models.
+While the boundary effects arising from a finite survey footprint would have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has less neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the sample variance of the depth-distribution.
+We have assumed that the probability that any pointing is of percentile $n$ is exactly the expectation value, namely $1/10$.
+While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, it does not necessarily hold for a real survey.
+However, our analysis in Sec.~\ref{sec:expand_eoftheta} suggests that these effects are not significant for the KV450 survey.
+We have also assumed an uncorrelated distribution of the depth-function, both in the simulations as well as in the models.
 While this is likely true as a rough approximation (very few pointings of the survey were taken on the same night and thus under the same weather conditions), effects like airmass, lunar phase, Galactic extinction and seasonal weather are likely to influence the depth on scales larger than one pointing.
-
-A strategy for the mitigation of finite field effects, boundaries and a correlated distribution of depth is given in Appendix \ref{sec:expand_eoftheta}.
-We find that finite field effects are not significant for a $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$-field, if the distribution of depth is uncorrelated.
 

### 2019-06-23 paperdraft.tex
added data from marika

@@
 
-While this model serves as a good, intuitive first approximation, it completely ignores any effects from the large scale structure (LSS) between the closest and the most distant galaxy.
-Therefore, we do not expect this model to yield reliable, quantitative results for cosmic shear surveys.
-
-However, we will now derive a more sophisticated model that includes the effects of the LSS.
-While it is computationally more expensive, it yields accurate results for cosmic shear surveys, which are sensitive to the exact redshift distributions of sources as well as the underlying cosmology.
 %-------------------------------------------------
@@
 \todo{It feels like some kind of introductory sentence is missing here, right now I can not think of one, though...}
+The previously derived analytic model describes how varying depth between pointings modifies the correlation function due to the correlation between number density and average redshift of source galaxies.
+While this model serves as a good, intuitive first approximation, it completely ignores any effects from the large scale structure (LSS) between the closest and the most distant galaxy.
+Therefore, we do not expect this model to yield reliable, quantitative results for cosmic shear surveys.
+
+Below we derive a more sophisticated model that includes the effects of the LSS.
+While it is computationally more expensive, it yields accurate results for cosmic shear surveys, which are sensitive to the exact redshift distributions of sources as well as the underlying cosmology.
+
 The analysis of data from the Kilo-Degree Survey showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band.
@@
 We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.
+It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.\todo{add reference in the figure as soon as marika's paper is on arxiv}
 
@@
 \centering
-\includegraphics[width = \textwidth, trim = {0 1.5cm 2.5cm 0}, clip]{images/eandbmodes0p5t100.pdf}
-\caption{Logarithmic E-modes of the reference correlation functions as well as difference in the E- and B-modes between the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=100\arcmin$.}
+\includegraphics[width = \textwidth]{images/ebmodes0p5t72.pdf}
+\caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.
+For comparison: Total E-modes of the reference correlation function $E_n$ (top left) and B-modes measured in the KV450 survey by Asgari et al.
+$B_n^{\rm{KV450}}$.}
 \label{fig:bmodes_cosebi}
@@
  or observational effects.
-Especially intrinsic alignments and baryonic feedback also modify the correlation functions especially on small scales, so they are probably degenerate with the effect of varying depth \citep{Troxel:2015}.
-In an actual MCMC simulation that accounts for these effects, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, and the impact on cosmological parameters is actually smaller than in our results.
+Especially intrinsic alignments and baryonic feedback also modify the correlation functions primarily on small scales, so they are likely to be degenerate with the effect of varying depth \citep{Troxel:2015}.
+In an actual MCMC simulation that accounts for these effects, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, so that the impact on cosmological parameters is actually smaller than in our results.
 Also, possible degeneracies between $S_8$ and other cosmological parameters might bias the resulting values.
@@
 Despite these repercussions, we are confident to say that the effects of varying depth are not significant for the KV450 survey.
-The cosmological parameters did not change significantly and the main parameter, $S_8$, is especially robust against this effect.
+The cosmological parameters did not change and the main parameter, $S_8$, is especially robust against this effect.
 In particular this means that a varying depth can not explain the discrepancy between observations of the local Universe and results from analysis of the CMB.
@@
 We have shown that this effect can create B-modes.
-However, \citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
-Those B-modes are at least one order of magnitude larger and still consistent with zero, so it is safe to say that the modes created by varying depth are negligible.
-An interesting observation is that the change in E-modes is as big as the created B-modes (compare Figure \ref{fig:bmodes_cosebi}).
+However, \todo{cite new asgari et al.
+here as soon as it is on arxiv}\citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
+Those B-modes are greater than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern, so it is safe to say that the B-modes in the KV450 survey are not created by varying depth.
+An interesting observation is that the change in E-modes is as big as the created B-modes (compare Fig.~\ref{fig:bmodes_cosebi}).
 This means that as soon as this effect causes a significant bias in the cosmological parameters, it will also create significant B-modes\footnote{While this is no big surprise, it is not trivial.
@@
 \ref{fig:comparecosmo}) is not significant for the KV450 survey, it will be relevant for the Euclid survey.
-In that case, a calculation of the correction for this effect is necessary for every cosmology in the MCMC simulation, underlining the necessity for a fast, analytic model.
+In that case, a calculation of the correction for this effect is necessary for various cosmologies, underlining the necessity for a fast, analytic model.
 \todo{For that example I took value from the 95\% CL of KV450 from H18.
@@
 Furthermore, the method developed in Appendix \ref{sec:expand_eoftheta} could be applied to the actual footprint of the KV450 survey to see whether finite field effects or a correlated distribution of $r$-band depth are significant.
-Additionally is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$, which is not isotropic.
+Additionally is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$ derived in Sec.~\ref{sec:model_e}, which is not isotropic.
 Therefore, it would be possible to observe a direction-dependent correlation function $\xi_\pm^{ij,\rm{obs}}(\b\theta)$ in future surveys.
@@
 Given one square field of length $L$ (in our case $L=60\arcmin$) and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
-As depicted in Figure \ref{fig:explain_etheta}, the dashed square represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
+The dashed square in Fig.~\ref{fig:explain_etheta} represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
 The volume of this square equals \begin{equation}
@@
 \end{equation} 
-As $E(\b\theta)$ is not isotropic, in order to obtain the function $E(\theta) = E(|\b\theta|)$, we need to azimuthally average Equation \eqref{eq:eoftheta1} over all angles $\phi$.
-While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can eliminate the other cases by simple symmetry.
+As $E(\b\theta)$ is not isotropic, in order to obtain the function $E(\theta) = E(|\b\theta|)$, we need to calculate the azimuthal average of Eq.~\eqref{eq:eoftheta1} over all angles $\phi$.
+While the case $\theta_1,\theta_2\geq 0$ certainly does not hold for all angles $\phi$, we can omit the other cases by making use of the symmetry of the problem.
 \begin{align}
@@
 \label{sec:calc of xipm}
-Following \citet{2017MNRAS.465.1454H}, given a set of galaxies we calculate the shear correlation functions via \begin{equation}
+Following H17, given a set of galaxies we calculate the shear correlation function $\xi_+^{ij}$ via \begin{equation}
 \xi^{ij}_+(\theta) = \frac{\sum_{a,b}w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*}\Delta(|\b\theta_a^i-\b\theta_b^i|)}{\sum_{a,b}w_a^iw_b^j\Delta(|\b\theta_a^i-\b\theta_b^i|)}\, .
@@
 where we assume ${\rm d}\theta \ll \theta$.
-We define $N$ as the number of pointings in the survey and $F_k^i$ as the set of galaxies in pointing $k$ and tomographic bin $i$.
-The numerator in Equation \eqref{eq:xip_from_observations} then transforms to: \begin{align}
-& \sum_{k,\ell=1}^N \sum_{a\in F_k^i}\sum_{b\in F_{\ell}^j} w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*} \Delta(|\b\theta_a^i-\b\theta_b^i|) \nonumber\\
- = & \sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \sum_{\ell=1}^N \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} \nonumber\\
-  = & \sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \left[\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} + \sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*}\right] \, .
+We define $\mathcal{N}$ as the number of pointings in the survey and $F_k^i$ as the set of galaxies in pointing $k$ and tomographic redshift bin $i$.
+The numerator in Eq.~\eqref{eq:xip_from_observations} then transforms to: \begin{align}
+& \sum_{k,\ell=1}^\mathcal{N} \sum_{a\in F_k^i}\sum_{b\in F_{\ell}^j} w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*} \Delta(|\b\theta_a^i-\b\theta_b^i|) \nonumber\\
+ = & \sum_{k=1}^\mathcal{N}\sum_{a\in F_k^i}w_a^i \sum_{\ell=1}^\mathcal{N} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} \nonumber\\
+  = & \sum_{k=1}^\mathcal{N}\sum_{a\in F_k^i}w_a^i \left[\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*} + \sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)\, \epsilon_a^i\epsilon_b^{j*}\right] \, .
 \end{align}
 When we denote the probability that pointing $k$ is of percentile $m$ by $\mathcal{P}_m^k$ and assume that the product $\epsilon_a^i\epsilon_b^{j*}$ always equals its expectation value, we can set the numerator as \[
-\sum_{k=1}^N\sum_{a\in F_k^i}w_a^i \sum_m \mathcal{P}_m^k \left[\overbrace{\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.a)}}\,  \xi_{+,mm}^{ij}(\theta) + \overbrace{\sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.b)}} \sum_n \mathcal{P}_n^{\ell} \xi_{+,mn}^{ij}(\theta)\right] \, .
+\sum_{k=1}^\mathcal{N}\sum_{a\in F_k^i}w_a^i \sum_m \mathcal{P}_m^k \left[\overbrace{\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.a)}}\,  \xi_{+,mm}^{ij}(\theta) + \overbrace{\sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.b)}} \sum_n \mathcal{P}_n^{\ell} \xi_{+,mn}^{ij}(\theta)\right] \, .
 \label{eq:numerator1}
@@
 If we assume that said number density in a pointing is equal to the number density in the percentile it belongs to, $N_n^j$, and set $\mathcal{P}_n^\ell=1/10$, the numerator becomes \begin{align}
-\sum_{k=1}^N \sum_{a\in F_k^i} w_a^i \sum_m P^k_m \left[2\pi\theta\,\d\theta\,E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + 2\pi\theta\,\d\theta\,\frac{1-E(\theta)}{10}\, \sum_n N_n^j \xi_{+,mn}^{ij}(\theta) \right] \, .
+\sum_{k=1}^\mathcal{N} \sum_{a\in F_k^i} w_a^i \sum_m P^k_m \left[2\pi\theta\,\d\theta\,E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + 2\pi\theta\,\d\theta\,\frac{1-E(\theta)}{10}\, \sum_n N_n^j \xi_{+,mn}^{ij}(\theta) \right] \, .
 \end{align}
-Now the term $\sum_{a\in F_k^i} w_a^i$ denotes the (weighted) number of galaxies in pointing $k$, which we set as the number density of galaxies in the respective percentile multiplied with the area $A$ of the pointing.
+The term $\sum_{a\in F_k^i} w_a^i$ denotes the number of galaxies in pointing $k$, which we set as the number density of galaxies in the respective percentile multiplied with the area $A$ of the pointing.
 Applying this and setting $\mathcal{P}_m^k=1/10$, the numerator reads
 \begin{align}
-\frac{2\pi\theta\,\d\theta}{10} \sum_{k=1}^N \sum_m N_m^i A &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \nonumber\\
+\frac{2\pi\theta\,\d\theta}{10} \sum_{k=1}^\mathcal{N} \sum_m N_m^i A &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \nonumber\\
  =  \, \frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \, .
@@
  At first we define Functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$.
-This situation is depicted in Figure \ref{fig:expand_etheta}.
+This situation is depicted in Fig.~\ref{fig:expand_etheta}.
 Due to symmetry, for the azimuthal average of the functions, $E_{ab}(\theta) = E_{-ab}(\theta) = E_{ba}(\theta)$ holds for all combinations of $a$ and $b$.
@@
 \end{figure}
-Naturally, to calculate those functions for all possible combinations would be rather tedious, however they are simple to determine numerically (compare Figure \ref{fig:eoftheta_sim}).
-A plot of these functions can be found in Figure \ref{fig:eab}.
+Naturally, to calculate those functions for all possible combinations would be rather tedious, however they are simple to determine numerically (compare Fig.~\ref{fig:eoftheta_sim}).
+A plot of these functions can be found in Fig.~\ref{fig:eab}.
 
@@
 \includegraphics[width=\textwidth]{images/finite_footprint.pdf}
-\caption{$2\sigma$-contours of the corrections for the correlation functions for a $100\,\rm{deg}^2$ field (blue), a $450\,\rm{deg}^2$ field (red) and a $1000\,\rm{deg}^2$ field (blue).}
+\caption{$2\sigma$-contours of the corrections for the correlation functions for a $100\,\rm{deg}^2$ field (blue), a $450\,\rm{deg}^2$ field (red) and a $1000\,\rm{deg}^2$ field (green).}
 \label{fig:finite_footprint}
@@
 
-\subsection{Cosmology Dependency of the Results}
 \begin{figure}[h]

### 2019-06-23 paperdraft.tex
minor corrections

@@
 \def\bth{\b \theta'}
+\def\i{\rm{i}}
 
@@
 % aims
-   Since ground-based surveys are subject to a variation in depth, we investigate and quantify the resulting effects.
+   Ground-based surveys are subject to a variation in depth caused by varying atmospherical conditions; we investigate and quantify the resulting effects.
 In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
@@
 % results
-   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$.
-However, the parameter $S_8$ is robust against this modification.
+   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales.
+We find that the resulting bias in $\Omega_{\rm m}$ and $\sigma_8$ will be significant in next-generation cosmic shear surveys.
+The parameter $S_8$ is especially robust against this modification.
 We find that the dependency of this effect on the underlying cosmology is not negligible.
-We also report the occurrence of B-modes, although not at a significant level.
+We also report the occurrence of B-modes, although at a not yet significant level.
 % conclusions (optional)
@@
 \section{Introduction}
-The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the Standard Model of Cosmology and to determine its parameters.
-Contrary to the analysis of the Cosmic Microwave Background (CMB) by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology.
-Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
+The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the standard model of cosmology and to determine its parameters.
+Contrary to the analysis of the Cosmic Microwave Background (CMB) by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model.
+Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
 It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
@@
 For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[compare][hereafter H17]{2017MNRAS.465.1454H}.
-With next-generation surveys like the Large Synoptic Survey Telescope \citep{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
+With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
 %\todo{Citations..
@@
 To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
-The most useful E- and B-mode decomposition is provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs, compare][]{2010A&A...520A.116S}, as it can easily be applied to real data.
+The most useful E- and B-mode decomposition for cosmic shear surveys is provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs, compare][hereafter S10]{2010A&A...520A.116S}, as it can easily be applied to real data.
 Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
@@
 While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions that are found in ground-based surveys.
-To first order, this variation can be modelled by a piece-wise constant depth function which varies from pointing to pointing.
+To first order, this variation can be modelled by a piece-wise constant depth function, which varies from pointing to pointing.
 In this work we assume the specifications of the Kilo-Degree Survey, namely an assembly of $1\,\text{deg}^2$ square fields.
@@
 Here, $\gamma_t$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[compare][]{2002A&A...396....1S}.
-The shear correlation functions are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions.
+The shear correlation functions are the prime estimators to quantify a cosmic-shear signal, since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint or masked regions.
 \subsection{Using an analytic model}
@@
 \xi^{ij,\text{obs}}_\pm(\theta) = & \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_{\rm t}(\bth)\gamma^{j,\rm{obs}}_{\rm t}(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \pm \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_\times(\bth)\gamma^{j,\rm{obs}}_\times(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \nonumber\\
- = & \frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i(\bth)N^j(\bthp)\ra} \xi_{\pm}^{ij,\rm{const}}(\theta) \, ,
+ = & \frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i(\bth)N^j(\bthp)\ra} \xi_{\pm}^{ij,\rm{uni}}(\theta) \, ,
  \label{eq:xipmblub1}
@@
 We want to denote the probability that a random galaxy pair of separation $\theta$ lies in the same pointing, by $E(\theta)$.
-This function is depicted in Figure \ref{fig:eoftheta_lin}, and an analytical expression is derived in \ref{sec:model_e}.
+This function is depicted in Figure \ref{fig:eoftheta_lin}, and an analytical expression is derived in Appendix \ref{sec:model_e}.
 
@@
  \begin{align}
- \xi^{ij,\rm{obs}}_\pm(\theta) = \frac{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}{1+E(\theta)\la n^i n^j\ra }\xi^{ij,\rm{const}}_\pm (\theta) \, .
+ \xi^{ij,\rm{obs}}_\pm(\theta) = \frac{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}{1+E(\theta)\la n^i n^j\ra }\xi^{ij,\rm{uni}}_\pm (\theta) \, .
  \end{align}
@@
 This is equivalent to setting $E(\theta)\equiv 0$.
- Performing the same calculations as above, this yields a relation between the correlation function of constant optical depth $\xi_\pm^{ij,\rm{const}}$ and the modelled one $\xi_\pm^{ij}$:
+ Performing the same calculations as above, this yields a relation between the correlation function of uniform depth $\xi_\pm^{ij,\rm{uni}}$ and the modelled one $\xi_\pm^{ij}$:
 \begin{equation}
@@
 \label{sec:xipm_semianalytic}
-\todo{It feels like some kind of introductory sentence is missing here, right now I can not think of one, though...}
 The previously derived analytic model describes how varying depth between pointings modifies the correlation function due to the correlation between number density and average redshift of source galaxies.
-While this model serves as a good, intuitive first approximation, it completely ignores any effects from the large scale structure (LSS) between the closest and the most distant galaxy.
+While this model serves as an intuitive first approximation, it completely ignores any effects from the large scale structure (LSS) between the closest and the most distant galaxy.
 Therefore, we do not expect this model to yield reliable, quantitative results for cosmic shear surveys.
@@
 For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H17\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
-Due to this we account for different weighting of galaxies on the shear correlation functions as well as on the average redshift distribution.}.
+Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.}.
 Asserting an arbitrary cosmological model, we can transform the source redshift distributions $p^i_m(z)$ into comoving distance probability distributions $\mathcal{L}^i_m(\chi)$.
@@
 \]
-where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.} In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
+where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.}.
+In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
 We will later discuss the validity of these assumptions as well as possible mitigation strategies.
@@
 
-If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and coadding them, thus yielding potential numerical errors (apart from being computationally expensive).
+If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate and coadd 1275 correlation functions, thus yielding potential numerical errors (apart from being computationally expensive).
 However, if we examine Eq.~\eqref{eq:lenseff}, we see that the comoving distance distribution of sources enters linearly.
-This in turn implies that in Eqs.~\eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
+This in turn implies that in Eqs.~\eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa}, both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
 In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average comoving distance probability distribution} $\mathcal{L}^i(\chi)$ of tomographic bin $i$ as \[
@@
 \]
-If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, then we observe: \begin{align}
+If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, we observe: \begin{align}
 \sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = & \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \\
@@
 \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \frac{\sum_n N_n^j \mathcal{L}^j_n(\chi'')}{N^j}  \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \\
- = & \, N^iN^j\xi^{ij}_\pm\, ,
+ = & \, N^iN^j\xi^{ij}_\pm\, .
 \end{align}
-where $\xi^{ij}_\pm$ denotes the correlation function for the average comoving distance probability distributions of redshift bins $i$ and $j$.
 Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
@@
 
-While the first method suffers from the fact that the power-law index only holds for sources of redshifts $1\lesssim z \lesssim 2$, the second method is sensitive to the angular range $\theta$, at which the shear correlation functions are evaluated, which is fairly arbitrary.
+While the first method suffers from the fact that the power-law index only holds for sources of redshifts $1\lesssim z \lesssim 2$, the second method is sensitive to the angular range $\theta_{\rm{ref}}$, at which the shear correlation functions are evaluated, which is fairly arbitrary.
 
@@
 
-In Sec.~\ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm,\rm{obs}}^{ij}$ for a specific survey footprint.
+In Appendix \ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
 With this model we can estimate the impacts of a correlated distribution of depth, the sample variance of the depth-distribution and boundary effects.
-We find that for quadratic footprint of $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$ with an uncorrelated depth-distribution, finite field effects are negligible.
+We find that for a quadratic footprint of $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$ with an uncorrelated depth-distribution, finite field effects are negligible.
 
-As the next step we chose a fiducial cosmology $\b \Phi$ and computed a reference correlation function $\xi_\pm^{ij}(\theta,\b\Phi)$ for each pair of redshift bins $i,j$.
-Using those, we calculated the observed correlation function $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ according to our semi-analytic model in Sect.~\ref{sec:xipm_semianalytic}.
+As the next step we chose a fiducial cosmology $\b \Phi$ and computed reference correlation functions $\xi_\pm^{ij}(\theta,\b\Phi)$ for each pair of redshift bins $i,j$.
+Using our semi-analytic model in Sect.~\ref{sec:xipm_semianalytic}, we derived the observed correlation function $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ from those.
 Then we ran a Markov-Chain Monte Carlo simulation to check for the resulting bias in the inferred cosmological parameters, using the covariance-matrix computed in H18.
 As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.
-As can be seen in Figure \ref{fig:mcmc_kids}, the impact of varying depth is barely noticeable and insignificant compared to the uncertainties.
+As can be seen in Fig.~\ref{fig:mcmc_kids}, the impact of varying depth is insignificant compared to the uncertainties.
 To get a rough estimate for the impact on future surveys, we divided our covariance-matrix by a factor of 30, to approximately account for the increased survey area of LSST and Euclid with respect to KV450.
-As can be seen in Figure \ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant.
+As can be seen in Fig.~\ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant.
 Conveniently it seems that the parameter $S_8$ is considerably more robust against this effect.
@@
 
-To estimate the B-modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} \citep[COSEBIS, compare][]{2010A&A...520A.116S}, once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
+To estimate the B-modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare S10), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
 We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
@@
 \includegraphics[width = \textwidth]{images/ebmodes0p5t72.pdf}
-\caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.
+\caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions.
 For comparison: Total E-modes of the reference correlation function $E_n$ (top left) and B-modes measured in the KV450 survey by Asgari et al.
-$B_n^{\rm{KV450}}$.}
+$B_n^{\rm{KV450}}$ (bottom right).
+All E- and B-modes were calculated using the logarithmic COSEBIS in S10 for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.}
 \label{fig:bmodes_cosebi}
@@
 \label{sec:discussion}
-With our semi-analytic model we try to describe the impacts of varying depth in ground-based cosmic shear surveys. During our analysis we have made several simplifications, which we discuss below.
+With our semi-analytic model we describe the impacts of varying depth in ground-based cosmic shear surveys. During our analysis we have made several simplifications, which we discuss below.
 \begin{enumerate}
@@
 While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, it does not necessarily hold for a real survey.
-However, our analysis in Sec.~\ref{sec:expand_eoftheta} suggests that these effects are not significant for the KV450 survey.
+However, our analysis in Appendix \ref{sec:expand_eoftheta} suggests that these effects are not significant for the KV450 survey.
 We have also assumed an uncorrelated distribution of the depth-function, both in the simulations as well as in the models.
@@
  &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta')\ra\nonumber\\
- &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta') \int \frac{\text{d}^2 k}{(2\pi)^2}\int \frac{\text{d}^2 \ell}{(2\pi)^2}\, \tilde{\gamma}(\b k)\tilde{\gamma}^*(\b \ell)\exp(-\i \b k\b \theta+\i \b \ell\b \theta')\ra \nonumber\\
+ &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta') \int \frac{\text{d}^2 k}{(2\pi)^2}\int \frac{\text{d}^2 \ell}{(2\pi)^2}\, \hat{\gamma}(\b k)\hat{\gamma}^*(\b \ell)\exp(-\i \b k\b \theta+\i \b \ell\b \theta')\ra \nonumber\\
 &\qquad = \la \int \text{d}^2 \theta \int \text{d}^2 \theta' \int \frac{\text{d}^2 k}{(2\pi)^2} \int \frac{\text{d}^2 \ell}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b \ell) \exp[\i (\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b \ell\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
   &\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \int \text{d}^2 \theta\, W(\b \theta)\exp[\i\b \theta(\b \ell-\b k)]\int \text{d}^2 \theta'\, W(\b \theta') \exp[-\i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
-  &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k)\widetilde{W}(\b \ell-\b k)\widetilde{W}^* (\b \ell'-\b k)\ra
+  &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k)\widehat{W}(\b \ell-\b k)\widehat{W}^* (\b \ell'-\b k)\ra
 \end{align}
@@
 & \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \nonumber\\
- &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \tilde{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \tilde{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]\right.\right.
+ &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]\right.\right.
 \nonumber\\
- & \quad\qquad \left.\left. + \tilde{w}(\b \ell-\b k)\tilde{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
- &\qquad =  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \left[ \la \tilde{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \tilde{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\right] + \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
-& \qquad \overset{(*)}{=}  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
+ & \quad\qquad \left.\left. + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
+ &\qquad =  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \left[ \la \hat{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \hat{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\right] + \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
+& \qquad \overset{(*)}{=}  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
 \label{eq:pobs1}
 \end{align}
-where in $(*)$ we have used that the average $\la \tilde{w}(\b \ell)\ra$ vanishes.
+where in $(*)$ we have used that the average $\la \hat{w}(\b \ell)\ra$ vanishes.
 Up until now, we have not specified our weight-function $w$. We parametrize it as \begin{equation}
@@
 \end{equation}
-Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier-Transform we compute: \begin{equation}
-\tilde{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-\i \b \ell L\b \alpha) \widetilde{\Xi}(\b \ell)\, ,
+Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier transform we compute: \begin{equation}
+\hat{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-\i \b \ell L\b \alpha) \widehat{\Xi}(\b \ell)\, ,
 \end{equation}
@@
 \begin{equation}
-\widetilde{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
+\widehat{\Xi}(\b\ell) = \frac{4\sin\left(\frac{L\ell_1}{2}\right)\sin\left(\frac{L\ell_2}{2}\right)}{\ell_1\ell_2}\, ,
+\label{eq:sinc}
 \end{equation}
@@
 \begin{align}
-&\la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \tilde{w}(\b \ell-\b k)\tilde{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
-&\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-\i(\b \ell - \b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k) \exp[\i(\b \ell' - \b k)L\b \beta]\, \widetilde{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
-&\qquad = \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-\i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k)\widetilde{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
+&\la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
+&\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-\i(\b \ell - \b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k) \exp[\i(\b \ell' - \b k)L\b \beta]\, \widehat{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
+&\qquad = \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-\i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)\widehat{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
 \end{align}
@@
 \begin{align}
-P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha+\i(\b \ell'-\b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell-\b k)\widetilde{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
-= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha]\, \widetilde{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widetilde{\Xi}^*(\b \ell'-\b k)\exp[\i(\b \ell'- \b k)L\b \alpha] \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widetilde{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-\i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widetilde{\Xi}(\b \ell-\b k)P(\b k)\, ,
+P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha+\i(\b \ell'-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell-\b k)\widehat{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
+= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widehat{\Xi}^*(\b \ell'-\b k)\exp[\i(\b \ell'- \b k)L\b \alpha] \nonumber\\
+ = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widehat{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-\i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
+ = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widehat{\Xi}(\b \ell-\b k)P(\b k)\, ,
 \end{align}
-which is a convolution of the power spectrum and the 2-dimensional sinc function.
+which is a convolution of the power spectrum and the 2-dimensional sinc function \eqref{eq:sinc}.
 \label{sec:calc of PS}

### 2019-07-10 paperdraft.tex
applied marikas corrections, added new simulations

@@
 Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
-It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
+It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep[DES,][]{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
+Combined analyses of DES and KiDS data \citep{Joudaki:2019} yields even higher tension with the value determined for $S_8$ by the Planck Collaboration\todo{cite marikas new paper here as soon as it is there}.
 This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2016MNRAS.459..971K}.
@@
 
-For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[compare][hereafter H17]{2017MNRAS.465.1454H}.
+For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[][hereafter H17]{2017MNRAS.465.1454H}.
 With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
@@
 To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
-The most useful E- and B-mode decomposition for cosmic shear surveys is provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs, compare][hereafter S10]{2010A&A...520A.116S}, as it can easily be applied to real data.
+The most useful E- and B-mode decomposition for cosmic shear surveys is provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs,][hereafter S10]{2010A&A...520A.116S}, as it can easily be applied to real data.
 Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
@@
 To first order, this variation can be modelled by a piece-wise constant depth function, which varies from pointing to pointing.
-In this work we assume the specifications of the Kilo-Degree Survey, namely an assembly of $1\,\text{deg}^2$ square fields.
+In this work we assume the specifications of the Kilo-Degree Survey \citep[KiDS,][]{Kuijken:2015}, namely an assembly of $1\,\text{deg}^2$ square fields.
 
-The depth of a pointing primarily influences the number density as well as the average redshift of galaxies, meaning that a variation in depth is responsible for a correlation between those two quantities (compare Fig.
+The depth of a pointing primarily influences the number density as well as the average redshift of galaxies, meaning that a variation in depth is responsible for a correlation between those two quantities (see Fig.
 \ref{fig:nz_of_meanz}).
-
+\todo{I see why you would like to move this further down.
+However, I feel like this plot would make a nice Fig.
+1, that captures the essence of what this paper is trying to analyse -- The effect of an artificial correlation between number density and redshift.
+I feel like the confusion caused by how exactly the plot is calculated is worth it to not have Fig.
+2 (which is not that essential) as new Fig.
+1.
+However, if you still feel like this figure would be better off further down, I will move it.}
+%
 \begin{figure}
@@
 \includegraphics[width=0.7\linewidth]{images/cov_nz_meanz.pdf}
-\caption{Galaxy number density $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
+\caption{Galaxy number density $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018} survey in pointings of different depth for each of the five tomographic bins used in H18.
+Each colour corresponds to one redshift bin of H18, the fainter points denote pointings of shallower depth.
 Details on how the data were obtained are described in Sec.
@@
 \end{figure}
-
+%
 In Sect.
@@
 \label{sec:modelling_single_lens}
-For our first analysis we will further simplify our assumptions: We imagine that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
+For our first analysis we assume that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
 If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm{ds}}/D_{\rm s}$.
@@
 
-Assuming that the depth, and thus the source redshift populations, varies between pointings, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of average depth.
+Assuming that the depth, and thus the source redshift populations, varies between pointings of the camera, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of average depth.
 We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
@@
 \la \hat{\gamma}(\b\ell)\,\hat{\gamma}^*(\b\ell')\ra = (2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) \, ,
+\label{eq:original_power_spectrum}
 \end{equation}
@@
 where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function and $\hat{\Xi}$ is the Fourier transform of a box-function, which is a 2-dimensional sinc-function (compare \ref{sec:calc of PS}).
-The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with a sinc-function, scaling with the variance of the function $w(\b\theta)$.
+The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P(\ell)$ from Eq.
+\eqref{eq:original_power_spectrum}, plus a convolution of the power spectrum with a sinc-function, scaling with the variance of the function $w(\b\theta)$.
 In particular, the power spectrum is not isotropic anymore.
@@
 \]
-Here, $\gamma_t$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[compare][]{2002A&A...396....1S}.
-The shear correlation functions are the prime estimators to quantify a cosmic-shear signal, since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint or masked regions.
+Here, $\gamma_t$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[see][]{2002A&A...396....1S}.
+The shear correlation functions are the prime estimators to quantify a cosmic-shear signal, since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint or masked regions, or model the noise contribution.
 \subsection{Using an analytic model}
@@
 For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal, in the sense that the shear field for a deeper redshift distribution gets multiplied by a weight $W>1$.
+This is equivalent to the assumption that all matter between source and observer is concentrated in a single lens plane from the previous Section.
 While this is not true for a 3-dimensional lensing matter distribution, it should be a reasonable first approximation for small variations in mean source redshift.
@@
 Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
-The observed correlation functions $\xi^{ij,\text{obs}}_\pm(\theta)$ now change from one of uniform depth $\xi_\pm^{ij,\rm{uni}}(\theta)$ via (compare H17)
+The observed correlation functions $\xi^{ij,\text{obs}}_\pm(\theta)$ now change from one of uniform depth, $\xi_\pm^{ij,\rm{uni}}(\theta)$, via \citep[see][]{2002A&A...396....1S}
 \begin{align}
@@
 We want to denote the probability that a random galaxy pair of separation $\theta$ lies in the same pointing, by $E(\theta)$.
-This function is depicted in Figure \ref{fig:eoftheta_lin}, and an analytical expression is derived in Appendix \ref{sec:model_e}.
+This function is depicted in Fig.
+\ref{fig:eoftheta_lin}, and an analytical expression is derived in App.
+\ref{sec:model_e}.
 
@@
 
-To compute the modified shear correlation functions, we parametrize the number densities \linebreak$N^{i}(\b \theta)=\la N^{i} \ra [1+n^{i}(\b \theta)]$ and the weight $W^{i}(\b \theta)=1+w^{i}(\b \theta)$ and, as in \eqref{eq:defweightf}, interpret $n^{i}(\b \theta)$ as a function with average $\la n^{i} \ra = 0$ that is constant on each pointing.
-We can see that $\la n^i(\bth)n^j(\bthp)\ra = E(\theta)\la n^i(\bth)n^j(\bth)\ra \equiv E(\theta)\la n^i n^j \ra$ holds and compute:
+To compute the modified shear correlation functions, we parametrize the number densities \linebreak$N^{i}(\b \theta)=\la N^{i} \ra [1+n^{i}(\b \theta)]$ and the weight $W^{i}(\b \theta)=1+w^{i}(\b \theta)$ and, as in Eq.
+\eqref{eq:defweightf}, interpret $n^{i}(\b \theta)$ as a function with average $\la n^{i} \ra = 0$ that is constant on each pointing.
+We can see that $\la n^i(\bth)n^j(\bthp)\ra = E(\theta)\la n^i(\bth)n^j(\bth)\ra = E(\theta)\la n^i n^j \ra$ holds and compute:
 \begin{align}
@@
 Ignoring correlations higher than second order in $n^i$ and $w^i$,\footnote{It is not inherently obvious that this is a valid assumption.
-However, after performing calculations with and without higher order correlations, we noticed no difference between the outcomes of both equations.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
+However, after performing calculations with and without higher order correlations, the highest difference between the outcomes of both equations was less then $5\times 10^{-4}$.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
  \begin{align}
@@
  A model correlation function for a cosmic shear survey is usually calculated by taking the average redshift distribution of a redshift bin, weighted by the number density.
- Ignoring that the depth is constant per pointing and therefore correlated on scales $\leq \sqrt{2}^\circ$ is equivalent to setting $E(\theta)\equiv 0$.
+ Ignoring that the depth is correlated on scales of one pointing (here at $\theta \leq \sqrt{2}^\circ$) is equivalent to setting $E(\theta)\equiv 0$.
 Note that there is still a correlation between $N$ and $W$ for the same galaxy.
@@
 This is equivalent to setting $E(\theta)\equiv 0$.
- Performing the same calculations as above, this yields a relation between the correlation function of uniform depth $\xi_\pm^{ij,\rm{uni}}$ and the modelled one $\xi_\pm^{ij}$:
+ Performing the same calculations as above, this yields a relation between the correlation function of uniform depth $\xi_\pm^{ij,\rm{uni}}$ and the one that is usually modelled, $\xi_\pm^{ij}$:
 \begin{equation}
-\xi_\pm^{ij}(\theta) = \left(1+\la n^iw^i\ra + \la n^jw^j\ra \right)\xi_\pm^{ij,\rm{const}}(\theta)\, .
+\xi_\pm^{ij}(\theta) = \left(1+\la n^iw^i\ra + \la n^jw^j\ra \right)\xi_\pm^{ij,\rm{uni}}(\theta)\, .
 \end{equation}
-The ratio of modelled and observed correlation function thus becomes: \begin{equation}
+When an observer now calculates the model correlation functions $\xi^{ij}_\pm$ without accounting for varying depth between pointings, the ratio between modelled and observed correlation functions becomes: \begin{equation}
 \frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} \approx \frac{1+\la n^iw^i\ra+\la n^jw^j\ra + E(\theta)\la n^in^j\ra}{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}
@@
 \end{equation}
-It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, meaning that the correlation function is not affected for large angular scales.
+It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, so we expect the observed and the modelled correlation functions to be equivalent on scales where the depth is uncorrelated.
 
@@
 
-The analysis of data from the Kilo-Degree Survey showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band.
+An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band\todo{This is basically from unpublished data of a KV450 WG telecon.
+Should/can I cite something here?}.
 We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e.
@@
 
-If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate and coadd 1275 correlation functions, thus yielding potential numerical errors (apart from being computationally expensive).
+If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate and coadd 1275 correlation functions\footnote{For each of the 15 pairs redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
+Since we are investigating an effect that is of the order of a percent, even small numerical errors can add up, skewing the calculations.
+Additionally, calculating $10^3$ correlation functions is computationally expensive.
 However, if we examine Eq.~\eqref{eq:lenseff}, we see that the comoving distance distribution of sources enters linearly.
@@
 \]
-If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, we observe: \begin{align}
+If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, we find: \begin{align}
 \sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = & \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \\
@@
 \label{sec:results}
-We want to apply both methods to data from the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018}.
+Here we apply both the analytic and the semi-analytic method to model the data from the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018}.
 While the application of the semi-analytic method is straightforward, for the analytic method we need to decide how to estimate the weight function $W$ from given redshift data.
@@
 \]
-where the $\xi_{+,nn}^{ij}(\theta_{\rm{ref}})$ denotes the model correlation function defined in Sect. \ref{sec:xipm_semianalytic}, evaluated at a characteristic scale $\theta_{\rm{ref}}$.
+where the $\xi_{+,nn}^{ij}(\theta_{\rm{ref}})$ denotes the model correlation function defined in Sect.
+\ref{sec:xipm_semianalytic}, evaluated at a characteristic scale $\theta_{\rm{ref}}$, that needs to be chosen.
 
@@
 
-We applied both analytic methods and the semianalytic one to data from the KV450 survey, following the separation into tomographic bins as in H18, and computed the ratio of observed and modeled correlation functions.
-Furthermore, we conducted numerical simulations, where a $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles.
-For each tomographic redshift bin of each percentile, source galaxies were distributed according to the respective redshift distribution and their shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included).
-This was compared to a set of simulations where the galaxies were distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, I feel like I am grossly oversimplifying what you did.
-Maybe you could write a short paragraph about the simulations?}.
+We applied both analytic methods and the semianalytic one to data from KV450, following the separation into tomographic bins as in H18, and computed the ratio between our model for the observed correlation function $\xi_{\pm}^{\rm{obs}}$, and the model correlation function ignoring variations in depth, $\xi_{\pm}$.
+We compare our models to the results measured from numerical simulations.
+Using a modified version (Joachimi, Lin, et al.
+in prep.) of Full-sky Lognormal Astro-fields Simulation Kit \citep[FLASK,][]{Xavier:2016}, we generated galaxy mocks with coherent clustering and lensing signals from lognormal fields.
+For each lognormal field, one mock with uniform depth and another one with variable depth were generated.
+In the variable case, we measured the depth of tiles in the KiDS-1000 data \citep{Kuijken:2019} and performed an analogous separation into 10 bins\todo{Was this separation done tile-based, or did you make the bins pixel-based (such that several bins could be present in a single pointing)?}.
+Each depth bin can then be associated with a tomographic redshift set and the galaxy redshifts were sampled accordingly from one of the 10 distributions\todo{Did you also sample the number density?}.
+In the uniform case, redshifts were sampled from the average of these 10 tomographic sets.
+Finally, we compute the ratio of the average lensing signals from the two mocks.
+The number of realizations is 2000.
+Shape noise is omitted.
 The results can be seen in Fig.~\ref{fig:all_xis}.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{images/xis_all.pdf}
-	\caption{The ratio of observed to modelled correlation functions for the analytic methods (green), the semi-analytic method (blue) and one realization of the numerical simulations (red) for a cross-correlation of all redshift bins.
+	\includegraphics[width=1\textwidth]{images/xis_all1.pdf}
+	\caption{The ratio of observed to modelled correlation functions for the analytic methods (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
 The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
@@
 
-The simulations and the models seem to be in rough agreement, but there are some significant differences.
-After a thorough analysis we explain these discrepancies the following way: The simulations shown in Fig.~\ref{fig:all_xis} were performed on a single $100\,\rm{deg}^2$ field, which means that sample variance of the depth distribution of the fields plays a significant role.
-Performing the same simulations for a different realization of depth between the pointings, we obtained completely different results.
-The implications of this and possible mitigation strategies will be discussed in Sect.~\ref{sec:discussion}.
-\todo{I will probably completely rewrite this paragraph in case it is possible to conduct a few more simulations.}
+The simulations and the models seem to be in rough agreement, but there are some differences.
+It is noticeable that in the simulations, the value $\xi_\pm/\xi_\pm^{\rm{obs}}$ consistently stays below unity, which can be attributed to the fact that the depth of different pointings is not completely uncorrelated, as was assumed in the models.
+Furthermore, we notice some strong features in the simulations at lower values of $\theta$.
+As the noise of the simulated correlation functions increases for decreasing $\theta$,\footnote{The logarithmic bins for the correlation functions were chosen in H17 such that the signal-to-noise ratio is roughly equal for each bin.
+However, in the simulations we ignore shape-noise, such that our only noise contribution is sample variance, which increases at lower $\theta$.} and we take the ratio of two functions that are subject to noise, these features can be attributed to sample variance.
+In general, the semi-analytic model seems to over-estimate the effect compared to the simulations, which take the full distribution of depth into account.
+This slight discrepancy could be attributed to the fact that the simulations make use of the whole KiDS-1000 data, whereas the models rely on distributions extracted from KV450 data.
+Additionlly, the simulations take the full variations in depth into account, which include both scales smaller than one pointing (especially dithering strategies) and scales larger than one pointing.
 
+An additional difference between the models and simulations is that in the models we assume an infinite footprint, whereas the simulations were performed with the actual KiDS-1000 footprint.
 In Appendix \ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
@@
 While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, it does not necessarily hold for a real survey.
-However, our analysis in Appendix \ref{sec:expand_eoftheta} suggests that these effects are not significant for the KV450 survey.
-We have also assumed an uncorrelated distribution of the depth-function, both in the simulations as well as in the models.
-While this is likely true as a rough approximation (very few pointings of the survey were taken on the same night and thus under the same weather conditions), effects like airmass, lunar phase, Galactic extinction and seasonal weather are likely to influence the depth on scales larger than one pointing.
+However, our analysis in App.~\ref{sec:expand_eoftheta} suggests that these effects are not significant for the KV450 survey.
+In the models, we have also assumed an uncorrelated distribution of the depth-function.
+As can be seen in Fig \ref{fig:all_xis}, this approximation introduces a small error when compared to the simulations.
 
-\item In our MCMC simulations we did not account for degeneracies with other cosmological parameters
-% (apart from $\Omega_{\rm m}, \sigma_8, w_0$ and $w_a$)
- or observational effects.
-Especially intrinsic alignments and baryonic feedback also modify the correlation functions primarily on small scales, so they are likely to be degenerate with the effect of varying depth \citep{Troxel:2015}.
+\item In our MCMC simulations we did not account for degeneracies with other cosmological parameters or observational effects.
+Especially intrinsic alignments and baryon feedback also modify the correlation functions primarily on small scales, so they are likely to be degenerate with the effect of varying depth \citep{Troxel:2015}.
 In an actual MCMC simulation that accounts for these effects, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, so that the impact on cosmological parameters is actually smaller than in our results.
@@
 Furthermore, the method developed in Appendix \ref{sec:expand_eoftheta} could be applied to the actual footprint of the KV450 survey to see whether finite field effects or a correlated distribution of $r$-band depth are significant.
-Additionally is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$ derived in Sec.~\ref{sec:model_e}, which is not isotropic.
+Additionally, it is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$ derived in Sec.~\ref{sec:model_e}, which is not isotropic.
 Therefore, it would be possible to observe a direction-dependent correlation function $\xi_\pm^{ij,\rm{obs}}(\b\theta)$ in future surveys.

### 2019-07-11 paperdraft.tex
added coauthors; please check your affiliations

@@
           \and Marika Asgari\inst{3}
+          \and Chieh-An Lin\inst{3,5,6}
+          \and B.~Joachimi\inst{4}
+          \and T.~Tr\"{o}ster\inst{3}
           }
@@
 \and 
-Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany \and
-Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de, peter@astro.uni-bonn.de}
+Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany 
+\and
+Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK
+\and
+Department of Physics and Astronomy, University College London, Gower Street, London WC1E 6BT, UK
+\and
+Service d'Astrophysique, CEA Saclay, Orme des Merisiers, B\^at 709, 91191 Gif-sur-Yvette, France
+\and 
+Fenglin Veteran Hospital, 2 Zhongzheng Rd. Sec. 1, Fenglin Township, Hualien 97544, Taiwan
+\\ \email{sven@astro.uni-bonn.de, peter@astro.uni-bonn.de}
              }

### 2019-07-11 paperdraft.tex
added coauthors; please check your affiliations
minor modifications

@@
 
-   \author{S. Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
+   \author{Sven Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
           \and Peter Schneider\inst{1} 
@@
           \and Chieh-An Lin\inst{3,5,6}
-          \and B.~Joachimi\inst{4}
-          \and T.~Tr\"{o}ster\inst{3}
+          \and Benjamin Joachimi\inst{4}
+          \and Tilman Tr\"{o}ster\inst{3}
           }
@@
 We applied both analytic methods and the semianalytic one to data from KV450, following the separation into tomographic bins as in H18, and computed the ratio between our model for the observed correlation function $\xi_{\pm}^{\rm{obs}}$, and the model correlation function ignoring variations in depth, $\xi_{\pm}$.
+
 We compare our models to the results measured from numerical simulations.
@@
 For each lognormal field, one mock with uniform depth and another one with variable depth were generated.
-In the variable case, we measured the depth of tiles in the KiDS-1000 data \citep{Kuijken:2019} and performed an analogous separation into 10 bins\todo{Was this separation done tile-based, or did you make the bins pixel-based (such that several bins could be present in a single pointing)?}.
-Each depth bin can then be associated with a tomographic redshift set and the galaxy redshifts were sampled accordingly from one of the 10 distributions\todo{Did you also sample the number density?}.
-In the uniform case, redshifts were sampled from the average of these 10 tomographic sets.
+In the variable case, we measured the depth of tiles in the KiDS-1000 data \citep{Kuijken:2019} and performed an analogous separation into 10 bins.
+Each depth bin can then be associated with a tomographic redshift set and the galaxy redshifts were sampled accordingly from one of the 10 distributions.
+We observed that the relation between depth and effective number density, as well as the one between depth and shape noise, is linear, so we sampled both quantities for each bin from a linear fit.
+In the uniform case, redshifts, number densities and shape noise were sampled from the average of these 10 tomographic sets.
 Finally, we compute the ratio of the average lensing signals from the two mocks.

### 2019-07-11 paperdraft.tex
minor modifications
fixed stuff

@@
 Each depth bin can then be associated with a tomographic redshift set and the galaxy redshifts were sampled accordingly from one of the 10 distributions.
-We observed that the relation between depth and effective number density, as well as the one between depth and shape noise, is linear, so we sampled both quantities for each bin from a linear fit.
+We observed that the relation between depth and effective number density is linear, so we sampled the number density of a pointing from a linear fit of this relation.
 In the uniform case, redshifts, number densities and shape noise were sampled from the average of these 10 tomographic sets.
@@
 This slight discrepancy could be attributed to the fact that the simulations make use of the whole KiDS-1000 data, whereas the models rely on distributions extracted from KV450 data.
-Additionlly, the simulations take the full variations in depth into account, which include both scales smaller than one pointing (especially dithering strategies) and scales larger than one pointing.
+% Additionlly, the simulations take the full variations in depth into account, which include both scales smaller than one pointing (especially dithering strategies) and scales larger than one pointing.
 

### 2019-07-13 paperdraft.tex
new explanation for simulations

@@
 For each lognormal field, one mock with uniform depth and another one with variable depth were generated.
-In the variable case, we measured the depth of tiles in the KiDS-1000 data \citep{Kuijken:2019} and performed an analogous separation into 10 bins.
-Each depth bin can then be associated with a tomographic redshift set and the galaxy redshifts were sampled accordingly from one of the 10 distributions.
-We observed that the relation between depth and effective number density is linear, so we sampled the number density of a pointing from a linear fit of this relation.
-In the uniform case, redshifts, number densities and shape noise were sampled from the average of these 10 tomographic sets.
-Finally, we compute the ratio of the average lensing signals from the two mocks.
+In the variable case, the depth of KiDS-1000 data \citep{Kuijken:2019} was binned by magnitude into roughly 20 bins.
+Afterwards, a linear relation between deph and effective number density was extracted.
+The KiDS-1000 survey was put on a Healpix grid, and for each pixel the limiting magnitude was calculated.
+According to this limiting magnitude, an effective number density was assigned, using the linear relation extracted above.
+Each pixel lies in one of the depth bins defined in this work and can thus be assigned an average source redshift distribution for each tomographic redshift bin.
+
+In the uniform case, redshifts and number densities were sampled from the average of these tomographic sets.
+Finally, the ratio of the average lensing signals from the two mocks was computed.
 The number of realizations is 2000.
@@
 
-The simulations and the models seem to be in rough agreement, but there are some differences.
+The simulations and the models seem to be in relatively good agreement, but there are some differences.
 It is noticeable that in the simulations, the value $\xi_\pm/\xi_\pm^{\rm{obs}}$ consistently stays below unity, which can be attributed to the fact that the depth of different pointings is not completely uncorrelated, as was assumed in the models.
@@
 This slight discrepancy could be attributed to the fact that the simulations make use of the whole KiDS-1000 data, whereas the models rely on distributions extracted from KV450 data.
-% Additionlly, the simulations take the full variations in depth into account, which include both scales smaller than one pointing (especially dithering strategies) and scales larger than one pointing.
+Additionlly, the simulations take the full variations in depth into account, which include both scales smaller than one pointing (especially chip positions and dithering strategies) and scales larger than one pointing.
 

### 2019-07-30 paperdraft.tex
new explanation for simulations
minor changes

@@
 In the variable case, the depth of KiDS-1000 data \citep{Kuijken:2019} was binned by magnitude into roughly 20 bins.
-Afterwards, a linear relation between deph and effective number density was extracted.
+Afterwards, a linear relation between depth and effective number density was extracted.
 The KiDS-1000 survey was put on a Healpix grid, and for each pixel the limiting magnitude was calculated.
 According to this limiting magnitude, an effective number density was assigned, using the linear relation extracted above.
-Each pixel lies in one of the depth bins defined in this work and can thus be assigned an average source redshift distribution for each tomographic redshift bin.
-
+For each pixel and each tomographic redshift bin we used the same limiting magnitude to assign an average source redshift distribution from the ones extracted in this work.
 In the uniform case, redshifts and number densities were sampled from the average of these tomographic sets.
@@
 Shape noise is omitted.
+
 The results can be seen in Fig.~\ref{fig:all_xis}.

### 2019-07-30 paperdraft.tex
removed cosebis of reference function

@@
 
-To estimate the B-modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare S10), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth.
+To estimate the B-modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare S10)
+%, once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then 
+ for the correlation functions $\xi_\pm^{\rm{obs}}$ that have been modified under the semi-analytic model.
 We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.

### 2019-09-03 paperdraft.tex
added marika's paper

@@
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
-Combined analyses of DES and KiDS data \citep{Joudaki:2019} yields even higher tension with the value determined for $S_8$ by the Planck Collaboration\todo{cite marikas new paper here as soon as it is there}.
+Combined analyses of DES and KiDS data \citep{Joudaki:2019,2019A&A...624A.134A} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration.
 This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2016MNRAS.459..971K}.
@@
 \caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions.
-For comparison: Total E-modes of the reference correlation function $E_n$ (top left) and B-modes measured in the KV450 survey by Asgari et al.
-$B_n^{\rm{KV450}}$ (bottom right).
+For comparison: Total E-modes of the reference correlation function $E_n$ (top left) and B-modes measured in the KV450 survey by \citet{2019A&A...624A.134A} $B_n^{\rm{KV450}}$ (bottom right).
 All E- and B-modes were calculated using the logarithmic COSEBIS in S10 for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.}
@@
 We have shown that this effect can create B-modes.
-However, \todo{cite new asgari et al.
-here as soon as it is on arxiv}\citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
+However, \citet{2019A&A...624A.134A} measured the B-modes of the KV450 survey in the same $\theta$-range.
 Those B-modes are greater than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern, so it is safe to say that the B-modes in the KV450 survey are not created by varying depth.

### 2019-09-04 paperdraft.tex
changed format to regular aa paper

--- 2019-07-30 paperdraft.tex
@@
-\documentclass[referee]{aa} % for a referee version
+%\documentclass[referee]{aa} % for a referee version
 %\documentclass[onecolumn]{aa} % for a paper on 1 column  
@@
 %
-%\documentclass{aa}  
+\documentclass{aa}  
 \newcommand{\bea}{\begin{eqnarray}}
@@
 \usepackage{todonotes}
-%\renewcommand{\todo}{\emph}
+\renewcommand{\todo}{\emph}
 \begin{document}
@@
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
-Combined analyses of DES and KiDS data \citep{Joudaki:2019} yields even higher tension with the value determined for $S_8$ by the Planck Collaboration\todo{cite marikas new paper here as soon as it is there}.
+Combined analyses of DES and KiDS data \citep{Joudaki:2019} yields even higher tension with the value determined for $S_8$ by the Planck Collaboration \todo{we should cite marikas new paper here as soon as it is there}.
 This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2016MNRAS.459..971K}.
@@
 \ref{fig:nz_of_meanz}).
-\todo{I see why you would like to move this further down.
+\todo{I see why you would like to move this figure further down.
 However, I feel like this plot would make a nice Fig.
@@
 \centering
-\includegraphics[width=0.7\linewidth]{images/cov_nz_meanz.pdf}
+\includegraphics[width=\linewidth]{images/cov_nz_meanz.pdf}
 \caption{Galaxy number density $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018} survey in pointings of different depth for each of the five tomographic bins used in H18.
@@
 To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as
-\begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
+\begin{align}
+w(\b \theta) = & \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \\
+\Xi(\b \theta) = & \begin{cases}
 1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
@@
 \label{eq:defweightf}
-\end{equation}
+\end{align}
 where $L$ is the length of one pointing.
@@
 \begin{align}
-\xi^{ij,\text{obs}}_\pm(\theta) = & \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_{\rm t}(\bth)\gamma^{j,\rm{obs}}_{\rm t}(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \pm \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_\times(\bth)\gamma^{j,\rm{obs}}_\times(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \nonumber\\
+\xi^{ij,\text{obs}}_\pm(\theta) = & \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_{\rm t}(\bth)\gamma^{j,\rm{obs}}_{\rm t}(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \\
+ & \pm \frac{\la N^i(\bth)N^j(\bthp)\gamma^{i,\rm{obs}}_\times(\bth)\gamma^{j,\rm{obs}}_\times(\bthp)\ra }{\la N^i(\bth)N^j(\bthp)\ra} \nonumber\\
  = & \frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i(\bth)N^j(\bthp)\ra} \xi_{\pm}^{ij,\rm{uni}}(\theta) \, ,
@@
  \centering
- \includegraphics[width=0.5\textwidth]{images/eoftheta.pdf}
+ \includegraphics[width=0.9\linewidth]{images/eoftheta.pdf}
  \caption{Probability $E(\theta)$ that a random pair of galaxies of distance $\theta$ lie in the same $1\deg ^2$ pointing.}
@@
 &\frac{\la N^i(\bth)N^j(\bthp)W^i(\bth)W^j(\bthp)\ra}{\la N^i\ra \la N^j\ra } \nonumber\\
-&\qquad =  1 + \la n^iw^i\ra + \la n^j w^j\ra + E(\theta)\left[ \la n^in^j\ra + \la n^i w^j \ra  + \la n^jw^i\ra + \la w^iw^j\ra + \la n^in^jw^i\ra + \la n^in^jw^j\ra + \la n^iw^iw^j\ra \right.
-\nonumber\\
-&\qquad\quad \left. + \la n^jw^iw^j\ra + \la n^in^jw^iw^j\ra  \right] \, .
+&\qquad =  1 + \la n^iw^i\ra + \la n^j w^j\ra + E(\theta)\left[ \la n^in^j\ra + \la n^i w^j \ra  + \la n^jw^i\ra \right. \nonumber\\
+& \qquad\quad + \la w^iw^j\ra + \la n^in^jw^i\ra + \la n^in^jw^j\ra + \la n^iw^iw^j\ra 
++ \la n^jw^iw^j\ra \nonumber\\
+& \qquad\quad\left.+ \la n^in^jw^iw^j\ra  \right] \, .
  \end{align}
@@
  \begin{align}
- \xi^{ij,\rm{obs}}_\pm(\theta) = \frac{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}{1+E(\theta)\la n^i n^j\ra }\xi^{ij,\rm{uni}}_\pm (\theta) \, .
+ \xi^{ij,\rm{obs}}_\pm(\theta) = & \left[ 1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left(\la n^in^j\ra + \la n^iw^j\ra \right.\right. \nonumber\\
+ &\left.\left. + \la n^j w^i\ra + \la w^iw^j\ra\right)\right]\, \left[1+E(\theta)\la n^i n^j\ra \right]\inv\xi^{ij,\rm{uni}}_\pm (\theta) \, .
  \end{align}
@@
 \end{equation}
-When an observer now calculates the model correlation functions $\xi^{ij}_\pm$ without accounting for varying depth between pointings, the ratio between modelled and observed correlation functions becomes: \begin{equation}
-\frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} \approx \frac{1+\la n^iw^i\ra+\la n^jw^j\ra + E(\theta)\la n^in^j\ra}{1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left[\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right]}
+When an observer now calculates the model correlation functions $\xi^{ij}_\pm$ without accounting for varying depth between pointings, the ratio between modelled and observed correlation functions becomes: \begin{align}
+\frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} \approx &  \left[1+\la n^iw^i\ra +\la n^jw^j\ra + E(\theta)\la n^in^j\ra\right]\,\left[1 + \la n^iw^i\ra \right. \nonumber\\
+ & \left.+ \la n^jw^j\ra + E(\theta)\left(\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right)\right]
 \, .
-\end{equation}
+\end{align}
 It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, so we expect the observed and the modelled correlation functions to be equivalent on scales where the depth is uncorrelated.
@@
 \]
-where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.}.
+where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$ \todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.}.
 In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
@@
 If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, we find: \begin{align}
-\sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = & \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \\
-& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \mathcal{L}^i_m(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}
-\int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \mathcal{L}^j_n(\chi'') \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \\
- = & \,N^i N^j \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \\
-& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \frac{\sum_m N_m^i \mathcal{L}^i_m(\chi')}{N^i} \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}
-\int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \frac{\sum_n N_n^j \mathcal{L}^j_n(\chi'')}{N^j}  \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \\
- = & \, N^iN^j\xi^{ij}_\pm\, .
+& \sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \nonumber\\
+& \qquad \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)
+\int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \mathcal{L}^i_m(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')} \nonumber\\
+& \qquad \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \mathcal{L}^j_n(\chi'') \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \nonumber\\
+ & \quad =  \,N^i N^j \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \nonumber\\
+& \qquad \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \frac{\sum_m N_m^i \mathcal{L}^i_m(\chi')}{N^i} \, \frac{f_K(\chi'-\chi)}{f_K(\chi')} \nonumber\\
+& \qquad \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \frac{\sum_n N_n^j \mathcal{L}^j_n(\chi'')}{N^j}  \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \nonumber\\
+& \quad =  \, N^iN^j\xi^{ij}_\pm\, .
 \end{align}
@@
 The results can be seen in Fig.~\ref{fig:all_xis}.
-	\begin{figure}
+	\begin{figure*}
 	\centering
-	\includegraphics[width=1\textwidth]{images/xis_all1.pdf}
+	\includegraphics[width=0.9\linewidth]{images/xis_all1.pdf}
 	\caption{The ratio of observed to modelled correlation functions for the analytic methods (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
@@
 	\label{fig:all_xis}
-	\end{figure}
+	\end{figure*}
 %We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
@@
 
-\begin{figure}
-\begin{subfigure}{0.5\textwidth}
+\begin{figure*}
+\begin{subfigure}{0.45\textwidth}
 	\includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.45\textwidth}
 	\includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
@@
 \caption{Estimation of the bias caused by a variation of depth in a cosmic shear survey. Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
-\end{figure}
+\end{figure*}
 
@@
 We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.\todo{add reference in the figure as soon as marika's paper is on arxiv}
+It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.\todo{I will add a reference in the figure as soon as marika's paper is on arxiv}
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width = \textwidth]{images/ebmodes0p5t72.pdf}
+\includegraphics[width = 0.9\linewidth]{images/ebmodes0p5t72.pdf}
 \caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions.
@@
 \label{fig:bmodes_cosebi}
-\end{figure}
+\end{figure*}
 
@@
 We have shown that this effect can create B-modes.
-However, \todo{cite new asgari et al.
-here as soon as it is on arxiv}\citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
+However, \todo{New asgari et al.
+comes here as soon as it is on arxiv}\citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
 Those B-modes are greater than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern, so it is safe to say that the B-modes in the KV450 survey are not created by varying depth.
@@
 \begin{appendix}
+\onecolumn
 \section{Detailed Calculations}
@@
 \centering
-\includegraphics[width = 0.8\textwidth]{images/eab.pdf}
+\includegraphics[width = 0.6\linewidth]{images/eab.pdf}
 \caption{The functions $E_{ab}(\theta)$ for the first few possible combinations.}
@@
 \centering
-\includegraphics[width=\textwidth]{images/finite_footprint.pdf}
+\includegraphics[width=0.8\linewidth]{images/finite_footprint.pdf}
 \caption{$2\sigma$-contours of the corrections for the correlation functions for a $100\,\rm{deg}^2$ field (blue), a $450\,\rm{deg}^2$ field (red) and a $1000\,\rm{deg}^2$ field (green).}
@@
 \centering
-\includegraphics[width=\textwidth]{images/compare_cosmos.pdf}
+\includegraphics[width=0.8\linewidth]{images/compare_cosmos.pdf}
 \caption{Correction to the correlation functions in varying cosmologies. Depicted here are three flat sample cosmologies, where values within the 98\% CL of the KV450 survey were sampled.}

### 2019-09-06 paperdraft.tex
applied most of hendrik's suggestions

@@
           \and Hendrik Hildebrandt\inst{2,1}
-          \and Catherine Heymans\inst{3} 
+          \and Catherine Heymans\inst{3,2} 
           \and Marika Asgari\inst{3}
+          \and Jan Luca Van den Busch\inst{2,1}
           \and Chieh-An Lin\inst{3,5,6}
@@
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
-Combined analyses of DES and KiDS data \citep{Joudaki:2019} yields even higher tension with the value determined for $S_8$ by the Planck Collaboration \todo{we should cite marikas new paper here as soon as it is there}.
+Combined analyses of DES and KiDS data \citep{Joudaki:2019} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration \todo{we should cite marikas new paper here as soon as it is there}.
 This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2016MNRAS.459..971K}.
@@
 In Sect.
-\ref{sec:discussion} we will discuss our results and comment on the impacts of our used simplifications.
+\ref{sec:discussion} we will discuss our results and comment on the impact of our used simplifications.
 We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
@@
 
-Assuming that the depth, and thus the source redshift populations, varies between pointings of the camera, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of average depth.
+Assuming that the depth, and thus the source redshift population, varies between pointings of the camera, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of the average depth.
 We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
@@
  where the average $\la\ldots\ra$ represents both an ensemble average as well as an average over the position $\bth$.
- Assuming that depth of different pointings is uncorrelated implies that the same holds for the functions $W$ and $N$.
+ Assuming that the depth of different pointings is uncorrelated implies that the same holds for the functions $W$ and $N$.
 This means that the only important property of a galaxy pair is whether or not they lie in the same pointing.
@@
 Ignoring correlations higher than second order in $n^i$ and $w^i$,\footnote{It is not inherently obvious that this is a valid assumption.
-However, after performing calculations with and without higher order correlations, the highest difference between the outcomes of both equations was less then $5\times 10^{-4}$.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
+However, after performing calculations with and without higher order correlations, the highest relative difference between the outcomes of both equations was less then $5\times 10^{-4}$.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
  \begin{align}
@@
 if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H17\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
+For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H18\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
 Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.}.
-Asserting an arbitrary cosmological model, we can transform the source redshift distributions $p^i_m(z)$ into comoving distance probability distributions $\mathcal{L}^i_m(\chi)$.
+The weighted numbers of Galaxies can be seen in Fig.
+\ref{fig:nz_of_meanz}, whereas the source redshift distributions are depicted in Fig.
+\ref{fig:nofz_percentiles}.
+%
+\begin{figure}
+\centering
+\includegraphics[trim = {1cm 0 1.2cm 0.1cm}, clip, width=\linewidth]{images/dist_z_all.pdf}
+\caption{The source redshift distributions $p^i_m(z)$ for the best, average, and worst percentile in each tomographic redshift bin.}
+\label{fig:nofz_percentiles}
+\end{figure}
+% Asserting an arbitrary cosmological model, we can transform the source redshift distributions $p^i_m(z)$ into comoving distance probability distributions $\mathcal{L}^i_m(\chi)$.
 
@@
 
-If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate and coadd 1275 correlation functions\footnote{For each of the 15 pairs redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
+If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate and coadd 1275 correlation functions\footnote{For each of the 15 pairs of redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
 Since we are investigating an effect that is of the order of a percent, even small numerical errors can add up, skewing the calculations.
@@
 \ref{sec:xipm_semianalytic}, we define $W(\b\theta)\equiv W_n$ whenever $\b\theta$ is in a pointing of percentile $n$.
-For the determination of $W_n$ we tried two approaches:
+For the determination of $W_n$ we test two approaches:
  As a first method, following \citet{2006APh....26...91V,1997A&A...322....1B}, we estimate 
@@
 Using a modified version (Joachimi, Lin, et al.
-in prep.) of Full-sky Lognormal Astro-fields Simulation Kit \citep[FLASK,][]{Xavier:2016}, we generated galaxy mocks with coherent clustering and lensing signals from lognormal fields.
-For each lognormal field, one mock with uniform depth and another one with variable depth were generated.
-In the variable case, the depth of KiDS-1000 data \citep{Kuijken:2019} was binned by magnitude into roughly 20 bins.
-Afterwards, a linear relation between depth and effective number density was extracted.
-The KiDS-1000 survey was put on a Healpix grid, and for each pixel the limiting magnitude was calculated.
-According to this limiting magnitude, an effective number density was assigned, using the linear relation extracted above.
-For each pixel and each tomographic redshift bin we used the same limiting magnitude to assign an average source redshift distribution from the ones extracted in this work.
-In the uniform case, redshifts and number densities were sampled from the average of these tomographic sets.
-Finally, the ratio of the average lensing signals from the two mocks was computed.
+in prep.) of Full-sky Lognormal Astro-fields Simulation Kit \citep[FLASK,][]{Xavier:2016}, we generate galaxy mocks with coherent clustering and lensing signals from lognormal fields.
+For each lognormal field, one mock with uniform depth and another one with variable depth is generated.
+In the variable case, the depth of KiDS-1000 data \citep{Kuijken:2019} is binned by magnitude into roughly 20 bins.
+Afterwards, a linear relation between depth and effective number density is extracted.
+The KiDS-1000 survey is put on a Healpix grid, and for each pixel the limiting magnitude is calculated.
+According to this limiting magnitude, an effective number density can be assigned, using the linear relation extracted above.
+For each pixel and each tomographic redshift bin we use the same limiting magnitude to assign an average source redshift distribution from the ones extracted in this work.
+In the uniform case, redshifts and number densities are sampled from the average of these tomographic sets.
+Finally, the ratio of the average lensing signals from the two mocks is computed.
 The number of realizations is 2000.
@@
 In Appendix \ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
-With this model we can estimate the impacts of a correlated distribution of depth, the sample variance of the depth-distribution and boundary effects.
+With this model we can estimate the impact of a correlated distribution of depth, the sample variance of the depth-distribution and boundary effects.
 We find that for a quadratic footprint of $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$ with an uncorrelated depth-distribution, finite field effects are negligible.
 
-As the next step we chose a fiducial cosmology $\b \Phi$ and computed reference correlation functions $\xi_\pm^{ij}(\theta,\b\Phi)$ for each pair of redshift bins $i,j$.
-Using our semi-analytic model in Sect.~\ref{sec:xipm_semianalytic}, we derived the observed correlation function $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ from those.
-Then we ran a Markov-Chain Monte Carlo simulation to check for the resulting bias in the inferred cosmological parameters, using the covariance-matrix computed in H18.
-As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restricted our analysis to those two parameters.
+As the next step we choose a fiducial cosmology $\b \Phi$ and compute reference correlation functions $\xi_\pm^{ij}(\theta,\b\Phi)$ for each pair of redshift bins $i,j$.
+Using our semi-analytic model in Sect.~\ref{sec:xipm_semianalytic}, we derive the observed correlation function $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ from those.
+Then we run a Markov-Chain Monte Carlo simulation to check for the resulting bias in the inferred cosmological parameters, using the covariance-matrix computed in H18.
+As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restrict our analysis to those two parameters.
+All other parameters are taken to be fixed as the best-fit values from H17.
 As can be seen in Fig.~\ref{fig:mcmc_kids}, the impact of varying depth is insignificant compared to the uncertainties.
-To get a rough estimate for the impact on future surveys, we divided our covariance-matrix by a factor of 30, to approximately account for the increased survey area of LSST and Euclid with respect to KV450.
-As can be seen in Fig.~\ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant.
+To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30, to approximately account for the increased survey area of LSST and Euclid with respect to KV450.
+As can be seen in Fig.~\ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant at the level of approx.~$1\sigma$.
 Conveniently it seems that the parameter $S_8$ is considerably more robust against this effect.
@@
 
-To estimate the B-modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare S10)
+To estimate the B-modes created by this effect, we extract the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare S10)
 %, once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then 
- for the correlation functions $\xi_\pm^{\rm{obs}}$ that have been modified under the semi-analytic model.
+ for the correlation functions $\xi_\pm^{\rm{obs}}$ that have been modified under the semi-analytic model and for a reference set of correlation functions $\xi_\pm$.
 We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
@@
 \caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions.
-For comparison: Total E-modes of the reference correlation function $E_n$ (top left) and B-modes measured in the KV450 survey by Asgari et al.
-$B_n^{\rm{KV450}}$ (bottom right).
+For comparison: Total E-modes of the reference correlation function $E_n$ and B-modes measured in the KV450 survey by Asgari et al.
+(in prep.) $B_n^{\rm{KV450}}$.
 All E- and B-modes were calculated using the logarithmic COSEBIS in S10 for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.}
@@
 \label{sec:discussion}
-With our semi-analytic model we describe the impacts of varying depth in ground-based cosmic shear surveys. During our analysis we have made several simplifications, which we discuss below.
+With our semi-analytic model we describe the impact of varying depth in ground-based cosmic shear surveys. During our analysis we have made several simplifications, which we discuss below.
 \begin{enumerate}
@@
 In our analysis, this selection function was governed by the KiDS $r$-band depth of a pointing.
-This neglects a number of other effects: The depth in different bands and the seeing of a pointing will also modify the number densities and redshift distributions on the scale of a pointing, whereas dithering strategies as well as imperfections in the telescope and CCD cause modifications on sub-pointing scales.
+This neglects a number of other effects: The depth in different bands and the seeing of a pointing will also modify the number densities and redshift distributions on the scale of a pointing (although those variations are also correlated with $r$-band depth and thus at least partly accounted for), whereas dithering strategies as well as imperfections in the telescope and CCD cause modifications on sub-pointing scales.
 However, we believe that these effects are subdominant compared to the variations caused by the $r$-band depth.
@@
 Although Euclid is a space-based telescope, the photometric redshift determination will still be done by ground-based telescopes and therefore suffer from the same effects.
-While we did not yet perform a quantitative study of this effect for Euclid, we are certain that a such a study should be conducted.
+While we did not yet perform a quantitative study of this effect for Euclid, we are certain that such a study should be conducted.
 

### 2019-09-17 paperdraft.tex
added jan lucas changes

@@
           \and Marika Asgari\inst{3}
-          \and Jan Luca Van den Busch\inst{2,1}
+          \and Jan Luca van den Busch\inst{2,1}
           \and Chieh-An Lin\inst{3,5,6}
@@
 
-Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{10.1093/mnras/stx2082}.
+Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{2009A&A...497..677K}.~%\citep{10.1093/mnras/stx2082}.
 Among other quantities, it calculates the shear correlation functions for a given cosmology and source redshift distribution.
@@
 
-As the next step we choose a fiducial cosmology $\b \Phi$ and compute reference correlation functions $\xi_\pm^{ij}(\theta,\b\Phi)$ for each pair of redshift bins $i,j$.
-Using our semi-analytic model in Sect.~\ref{sec:xipm_semianalytic}, we derive the observed correlation function $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ from those.
-Then we run a Markov-Chain Monte Carlo simulation to check for the resulting bias in the inferred cosmological parameters, using the covariance-matrix computed in H18.
-As our main interest lies in the $\Omega_{\rm m}$ - $\sigma_8$ combination, we restrict our analysis to those two parameters.
-All other parameters are taken to be fixed as the best-fit values from H17.
+As the next step we want to assess how the observational depth variations propagate to cosmological parameters inferred from $\xi_\pm^{ij,\rm{obs}}$ compared to $\xi_\pm^{ij}$.
+For this test we choose the best fit values from H17 as our a fiducial cosmology $\b \Phi$ and determine the relative change in $\Omega_{\rm m}$ and $\sigma_8$ compared to a reference setup with uniform depth.
+All other cosmological parameters we keep fixed.
+First, we compute the reference correlation functions $\xi_\pm^{ij}(\theta,\b\Phi)$ for each pair of redshift bins $i,j$ using the \textsc{Nicaea}-code \citep{2009A&A...497..677K} as described in section~\ref{sec:xipm_semianalytic}.
+Then we derive the observed correlation functions $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ from Eq.~(\ref{eq:correctionfunction2}) and compute the $\chi^2$ between these and $\xi_\pm^{ij}(\theta,\b\Phi)$ using the data covariance-matrix computed in H18.
+The last step we repeat in a Markov-Chain Monte Carlo simulation to find the cosmology $\b \Phi^\mathrm{obs}$ that minimizes the $\chi^2$ and gives us an estimate of the shift in $\Omega_{\rm m}$ and $\sigma_8$ introduced by varying depth.
+
 As can be seen in Fig.~\ref{fig:mcmc_kids}, the impact of varying depth is insignificant compared to the uncertainties.

### 2019-09-17 paperdraft.tex
applied peter's suggestions

@@
 
-   \title{The Effects of Varying Depth in Cosmic Shear Surveys}
+   \title{The effects of varying depth in cosmic shear surveys}
 
@@
    {Cosmic shear proves to be a powerful tool to study the properties of the Universe.
-The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases.
+The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the cosmic microwave background motivates further investigation of yet unaccounted systematic biases.
 % aims
@@
    For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales.
-We find that the resulting bias in $\Omega_{\rm m}$ and $\sigma_8$ will be significant in next-generation cosmic shear surveys.
-The parameter $S_8$ is especially robust against this modification.
-We find that the dependency of this effect on the underlying cosmology is not negligible.
+We find that the resulting bias in $\Omega_{\rm m}$ and $\sigma_8$ will be significant in next-generation cosmic shear surveys, but that the parameter $S_8$ is surprisingly robust against this modification.
+We find that the dependence of this effect on the underlying cosmology is not negligible.
 We also report the occurrence of B-modes, although at a not yet significant level.
 % conclusions (optional)
-   We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.
-Due to the cosmology dependency, further analyses require a fast, analytical model for this effect.}
+   We conclude that the effects of varying depth for current cosmic shear surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}
 
@@
 \section{Introduction}
-The discovery of cosmic shear has provided us with a new and powerful cosmological tool to investigate the standard model of cosmology and to determine its parameters.
-Contrary to the analysis of the Cosmic Microwave Background (CMB) by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model.
-Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
-It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep[DES,][]{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
+The discovery of cosmic shear has provided us with a new and powerful cosmological tool to empirically test the standard model of cosmology and to determine its parameters.
+Contrary to the analysis of the cosmic microwave background \citet[CMB, e.g.][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model.
+Current cosmic shear surveys are particularly sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ characterizes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density parameter.
+It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis by \citet{2018arXiv180706209P}.
+While their analysis determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from an analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data, and the Dark Energy Survey \citep[DES,][]{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
-Combined analyses of DES and KiDS data \citep{Joudaki:2019} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration \todo{we should cite marikas new paper here as soon as it is there}.
+After reweighting the obtained redshift of data from DES and combining this with KiDS data \citep{Joudaki:2019} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration \todo{we should cite marikas new paper here as soon as it is there}.
 This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2016MNRAS.459..971K}.
@@
 \includegraphics[width=\linewidth]{images/cov_nz_meanz.pdf}
-\caption{Galaxy number density $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018} survey in pointings of different depth for each of the five tomographic bins used in H18.
+\caption{Weighted number of galaxies $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
 Each colour corresponds to one redshift bin of H18, the fainter points denote pointings of shallower depth.
-Details on how the data were obtained are described in Sec.
+Details on how the data were obtained are described in Sect.
 \ref{sec:xipm_semianalytic}.}
@@
 %-------------------------------------------------------------------
+\section{Simple, analytic toy models}
+For our first analysis we assume that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
+If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm{ds}}/D_{\rm s}$, where $D_{\rm{ds}}$ is the distance between the lens plane and the respective source.
 
-\section{Modelling the power spectrum}
+Assuming that the depth, and thus the source redshift population, varies between pointings of the camera, an observer will measure a shear signal that is modified by a step-like depth-function, $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of the average depth.
+We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
+\subsection{Modelling the power spectrum}
 \label{sec:modelling_single_lens}
-For our first analysis we assume that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
-If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm{ds}}/D_{\rm s}$.
+In our first model we describe the impact of varying depth on the power spectrum, following the simplifications described above.
 % Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
@@
 
-Assuming that the depth, and thus the source redshift population, varies between pointings of the camera, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of the average depth.
-We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
 In accordance to the definition of the shear power spectrum \begin{equation}
@@
 \end{equation}
-Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
+Note that due to the depth-function, both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
 To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as
 \begin{align}
-w(\b \theta) = & \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \\
+w(\b \theta) = & \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the box-function } \\
 \Xi(\b \theta) = & \begin{cases}
@@
 \end{align}
-where $L$ is the length of one pointing.
+where $L$ is the sidelength of one pointing.
 Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
@@
 
-\section{Modelling the shear correlation functions}
-\label{sec:xipm}
-Convenient measures to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
+\subsection{Modelling the shear correlation functions}
+\label{sec:xipm_analytic}
+More convenient measures to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
 \xi_\pm(\theta) = \la \gamma_{\rm t}\gamma_{\rm t}\ra(\theta) \pm \la \gamma_\times\gamma_\times\ra(\theta) \, .
 \]
-Here, $\gamma_t$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[see][]{2002A&A...396....1S}.
+Here, $\gamma_{\rm{t}}$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[see][]{2002A&A...396....1S}.
 The shear correlation functions are the prime estimators to quantify a cosmic-shear signal, since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint or masked regions, or model the noise contribution.
-\subsection{Using an analytic model}
-\label{sec:xipm_analytic}
-For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal, in the sense that the shear field for a deeper redshift distribution gets multiplied by a weight $W>1$.
-This is equivalent to the assumption that all matter between source and observer is concentrated in a single lens plane from the previous Section.
+For this analysis we will follow the assumption that a deeper pointing shows a stronger shear signal $\gamma^{\rm{obs}}(\b\theta) = W(\b\theta)\gamma(\b\theta)$ as described above.
 While this is not true for a 3-dimensional lensing matter distribution, it should be a reasonable first approximation for small variations in mean source redshift.
@@
 This means that the only important property of a galaxy pair is whether or not they lie in the same pointing.
-We want to denote the probability that a random galaxy pair of separation $\theta$ lies in the same pointing, by $E(\theta)$.
+We want to denote the probability that a random galaxy pair of separation $\theta$ lies in the same pointing by $E(\theta)$.
 This function is depicted in Fig.
@@
 Ignoring correlations higher than second order in $n^i$ and $w^i$,\footnote{It is not inherently obvious that this is a valid assumption.
-However, after performing calculations with and without higher order correlations, the highest relative difference between the outcomes of both equations was less then $5\times 10^{-4}$.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
+However, after performing calculations with and without higher-order correlations, the largest relative difference between the outcomes of both equations was less then $5\times 10^{-4}$.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
  \begin{align}
@@
 When an observer now calculates the model correlation functions $\xi^{ij}_\pm$ without accounting for varying depth between pointings, the ratio between modelled and observed correlation functions becomes: \begin{align}
-\frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} \approx &  \left[1+\la n^iw^i\ra +\la n^jw^j\ra + E(\theta)\la n^in^j\ra\right]\,\left[1 + \la n^iw^i\ra \right. \nonumber\\
- & \left.+ \la n^jw^j\ra + E(\theta)\left(\la n^in^j\ra + \la n^iw^j\ra + \la n^j w^i\ra + \la w^iw^j\ra\right)\right]
+\frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} \approx &  \left[1+\la n^iw^i\ra +\la n^jw^j\ra + E(\theta)\la n^in^j\ra\right] \nonumber\\
+& \times \left[1 + \la n^iw^i\ra + \la n^jw^j\ra + E(\theta)\left(\la n^in^j\ra + \la n^iw^j\ra \right.\right. \nonumber\\
+& \left.\left. + \la n^j w^i\ra + \la w^iw^j\ra\right)\right]\inv
 \, .
@@
 
-\subsection{Using a semi-analytic Model}
+\section{A semi-analytic model}
 \label{sec:xipm_semianalytic}
@@
 While this model serves as an intuitive first approximation, it completely ignores any effects from the large scale structure (LSS) between the closest and the most distant galaxy.
-Therefore, we do not expect this model to yield reliable, quantitative results for cosmic shear surveys.
+Therefore, we do not expect this model to yield accurate, quantitative results for cosmic shear surveys.
 
@@
 
-An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band\todo{This is basically from unpublished data of a KV450 WG telecon.
-Should/can I cite something here?}.
+An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band (compare Fig.
+\ref{fig:nz_of_meanz}).
 We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e.
 if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H18\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
+For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the DIR method of H18\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
 Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.}.
@@
 
-Given two comoving distance probability distributions of sources $\mathcal{L}^i_m(\chi),\mathcal{L}^j_n(\chi)$, we can compute the shear correlation functions from the underlying matter power spectrum $P(\ell,\chi)$ via \citep[compare][]{1992ApJ...388..272K} \begin{align}
+Given two comoving distance probability distributions of sources $\mathcal{L}^i_m(\chi),\mathcal{L}^j_n(\chi)$, we can compute the shear correlation functions from the underlying matter power spectrum $P_\delta(k,\chi)$ via \citep[compare][]{1992ApJ...388..272K} \begin{align}
 \label{eq:xipm-pkappa}
@@
 \end{align}
-Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is chosen such that $p_i(\chi)=0$ holds for all $\chi>\chi_{\rm{H}}$.
+Here, $J_n$ denote the $n$-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is the comoving horizon.
 
-Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{2009A&A...497..677K}.~%\citep{10.1093/mnras/stx2082}.
+Using Eq.~\eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{2009A&A...497..677K}.~%\citep{10.1093/mnras/stx2082}.
 Among other quantities, it calculates the shear correlation functions for a given cosmology and source redshift distribution.
@@
 \]
-where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$ \todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.}.
+where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.
 In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
@@
 To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1,\d^2\b\theta_2$ of separation $\theta$ on the sky.
-For the case $m\neq n$ we know that a pair of galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ has to lie in different pointings, else they would automatically be of the same percentile.
-The probability that the imagined surface elements are within different pointings is $[1-E(\theta)]$.
+For the case $m\neq n$ we know that the two galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ have to lie in different pointings, else they would automatically be in the same percentile.
+The probability that the surface elements are within different pointings is $[1-E(\theta)]$.
 Furthermore, the first element $\d^2\b\theta_1$ has to lie in percentile $m$, the probability of which is $1/10$.
@@
 \]
-For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxy lies in the same pointing [accounted for by the factor $E(\theta)$], it automatically is of the same percentile.
-We therefore set \[
+For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxies lie in the same pointing [accounted for by the factor $E(\theta)$], they automatically are in the same percentile.
+We therefore obtain \[
 \mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
@@
 \begin{align}
-\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\sum_{m=1}^{10} N_m^i \left\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
+\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \left.\frac{1}{C}\sum_{m=1}^{10} N_m^i \right\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) \nonumber\\
+ & \left. + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
 \label{eq:correctionfunction1}
@@
 \[
-C = \sum_{m=1}^{10} N_m^i \bigg[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\bigg]\, .
+C = \sum_{m=1}^{10} N_m^i \left[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\right]\, .
 \]
@@
 If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, we find: \begin{align}
-& \sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \nonumber\\
-& \qquad \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)
+& \sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn}(\theta) = \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \nonumber\\
+& \qquad\times \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)
 \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \mathcal{L}^i_m(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')} \nonumber\\
-& \qquad \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \mathcal{L}^j_n(\chi'') \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \nonumber\\
+& \qquad\times \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \mathcal{L}^j_n(\chi'') \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \nonumber\\
  & \quad =  \,N^i N^j \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \nonumber\\
-& \qquad \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \frac{\sum_m N_m^i \mathcal{L}^i_m(\chi')}{N^i} \, \frac{f_K(\chi'-\chi)}{f_K(\chi')} \nonumber\\
-& \qquad \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \frac{\sum_n N_n^j \mathcal{L}^j_n(\chi'')}{N^j}  \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \nonumber\\
-& \quad =  \, N^iN^j\xi^{ij}_\pm\, .
+& \qquad\times \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \frac{\sum_m N_m^i \mathcal{L}^i_m(\chi')}{N^i} \, \frac{f_K(\chi'-\chi)}{f_K(\chi')} \nonumber\\
+& \qquad\times \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \frac{\sum_n N_n^j \mathcal{L}^j_n(\chi'')}{N^j}  \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \nonumber\\
+& \quad =  \, N^iN^j\xi^{ij}_\pm(\theta)\, .
 \end{align}
 Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
-\begin{equation}
-\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{C}\left\{ E(\theta)\left[\sum_{m=1}^{10} N_m^iN_m^j \xi_{\pm,mm}^{ij}(\theta)\right] +\frac{\big[1-E(\theta)\big]}{10}\xi_\pm^{ij}(\theta)N^iN^j\right\}\, .
+\begin{align}
+\xi_{\pm}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\left\{ E(\theta)\left[\sum_{m=1}^{10} N_m^iN_m^j \xi_{\pm,mm}^{ij}(\theta)\right]\right.\nonumber\\
+& \left.\vphantom{\sum_{m=1}^10}+\frac{\big[1-E(\theta)\big]}{10}\xi_\pm^{ij}(\theta)N^iN^j\right\}\, .
 \label{eq:correctionfunction2}
-\end{equation}
+\end{align}
 For each pair of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
@@
 \[
-W_n \propto \la z_n \ra ^{0.85}\, ,
+W_n \propto \la z \ra _n^{0.85}\, ,
 \]
-where $\la z_n\ra$ is the average redshift of percentile $n$. As a second method we define \[
+where $\la z\ra_n$ is the average redshift of percentile $n$. As a second method we define \[
 W_n \propto \sqrt{ \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta_{\rm{ref}}) + \la \gamma_\times\gamma_\times\ra (\theta_{\rm{ref}})} = \sqrt{\xi_{+,nn}^{ij}(\theta_{\rm{ref}})}\, ,
@@
 
-We applied both analytic methods and the semianalytic one to data from KV450, following the separation into tomographic bins as in H18, and computed the ratio between our model for the observed correlation function $\xi_{\pm}^{\rm{obs}}$, and the model correlation function ignoring variations in depth, $\xi_{\pm}$.
+We applied both analytic methods and the semianalytic one to data from KV450, following the separation into tomographic bins as in H18, and computed the ratio between our model for the observed correlation functions $\xi_{\pm}^{\rm{obs}}$, and the model correlation functions ignoring variations in depth, $\xi_{\pm}$.
 
@@
 The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
+The semi-analytic model was computed for the best-fit cosmology of H18.
 For the characteristic scale $\theta_{\rm{ref}}$ of the second analytic method we chose $\theta_{\rm{ref}} \approx 11'$.}
@@
 However, $\xi_-$ is obtained by filtering with the 4-th order Bessel function, which peaks at approximately $\ell\theta\approx 5$, so for different $\theta$ this function is sensitive to varying parts of the convergence power spectrum.
-A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}
+A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.} Furthermore we note that the effect seems to be strongest in the first redshift bin, which is not surprising, as there the average redshift between pointings varies the most (compare Fig.
+\ref{fig:nz_of_meanz}).
 
 The simulations and the models seem to be in relatively good agreement, but there are some differences.
-It is noticeable that in the simulations, the value $\xi_\pm/\xi_\pm^{\rm{obs}}$ consistently stays below unity, which can be attributed to the fact that the depth of different pointings is not completely uncorrelated, as was assumed in the models.
+It is noticeable that in the simulations, the value $\xi_\pm/\xi_\pm^{\rm{obs}}$ consistently stays below unity at large scales, which can be attributed to the fact that the depth of different pointings is not completely uncorrelated, as was assumed in the models.
 Furthermore, we notice some strong features in the simulations at lower values of $\theta$.
@@
 This slight discrepancy could be attributed to the fact that the simulations make use of the whole KiDS-1000 data, whereas the models rely on distributions extracted from KV450 data.
-Additionlly, the simulations take the full variations in depth into account, which include both scales smaller than one pointing (especially chip positions and dithering strategies) and scales larger than one pointing.
+Additionally, the simulations take the full variations in depth into account, which include both scales smaller than one pointing (especially chip positions and dithering strategies) and scales larger than one pointing.
 
@@
 We find that for a quadratic footprint of $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$ with an uncorrelated depth-distribution, finite field effects are negligible.
+
+\begin{figure*}
+\begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
+\end{subfigure}
+\begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
+\end{subfigure}
+\caption{Results of the MCMC simultation to estimate the bias caused by a variation of depth in a cosmic shear survey for a KiDS-like (left) and 'Euclid-like' survey (right).
+The left simulation was computed using the covariance matrix of H18.
+As Euclid will survey approx.
+$15\,000\,\rm{deg}^2$, the covariance matrix of the 'Euclid-like' survey is the one of H18 divided by 30.
+Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
+\label{fig:mcmc_results}
+\end{figure*}
 
@@
 
-As can be seen in Fig.~\ref{fig:mcmc_kids}, the impact of varying depth is insignificant compared to the uncertainties.
+As can be seen in Fig.~\ref{fig:mcmc_results}, the impact of varying depth is insignificant compared to the uncertainties.
 To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30, to approximately account for the increased survey area of LSST and Euclid with respect to KV450.
-As can be seen in Fig.~\ref{fig:mcmc_euclid}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant at the level of approx.~$1\sigma$.
+As can be seen in Fig.~\ref{fig:mcmc_results}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant at the level of approx.~$1\sigma$.
 Conveniently it seems that the parameter $S_8$ is considerably more robust against this effect.
-
-\begin{figure*}
-\begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
-  \caption{Bias for a KiDS-like Survey.}
-  \label{fig:mcmc_kids}
-\end{subfigure}
-\begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
-  \caption{Bias for a 'Euclid-like' Survey.}
-  \label{fig:mcmc_euclid}
-\end{subfigure}
-\caption{Estimation of the bias caused by a variation of depth in a cosmic shear survey. Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
-\end{figure*}
 
@@
 \item We have assumed an infinitely large survey area with an uncorrelated distribution of the depth-function.
-While the boundary effects arising from a finite survey footprint would have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has less neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the sample variance of the depth-distribution.
-We have assumed that the probability that any pointing is of percentile $n$ is exactly the expectation value, namely $1/10$.
+While the boundary effects arising from a finite survey footprint would have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has fewer neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the sample variance of the depth-distribution.
+We have assumed that the probability for any pointing to be in percentile $n$ is exactly the expectation value, namely $1/10$.
 While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, it does not necessarily hold for a real survey.
@@
 comes here as soon as it is on arxiv}\citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
-Those B-modes are greater than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern, so it is safe to say that the B-modes in the KV450 survey are not created by varying depth.
-An interesting observation is that the change in E-modes is as big as the created B-modes (compare Fig.~\ref{fig:bmodes_cosebi}).
+Those B-modes are larger than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern.
+Thus it is safe to say that the B-modes in the KV450 survey are not created by varying depth.
+An interesting observation is that the change in E-modes is as large as the created B-modes (compare Fig.~\ref{fig:bmodes_cosebi}).
 This means that as soon as this effect causes a significant bias in the cosmological parameters, it will also create significant B-modes\footnote{While this is no big surprise, it is not trivial.
@@
 For next-generation surveys like Euclid, this effect will be significant.
-Although Euclid is a space-based telescope, the photometric redshift determination will still be done by ground-based telescopes and therefore suffer from the same effects.
+Although Euclid is a space-based telescope, the photometric redshift determination will still be done using ground-based data and therefore suffer from the same effects.
 While we did not yet perform a quantitative study of this effect for Euclid, we are certain that such a study should be conducted.
 
-While the cosmology dependency (compare Fig.
+While the cosmology dependence (compare Fig.
 \ref{fig:comparecosmo}) is not significant for the KV450 survey, it will be relevant for the Euclid survey.
-In that case, a calculation of the correction for this effect is necessary for various cosmologies, underlining the necessity for a fast, analytic model.
-\todo{For that example I took value from the 95\% CL of KV450 from H18.
-As the parameter constraints in Euclid are going to be much tighter, this is probably no longer true...}
+In that case, a calculation of the correction for this effect is necessary for various cosmologies.
 
@@
 Furthermore, the method developed in Appendix \ref{sec:expand_eoftheta} could be applied to the actual footprint of the KV450 survey to see whether finite field effects or a correlated distribution of $r$-band depth are significant.
-Additionally, it is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$ derived in Sec.~\ref{sec:model_e}, which is not isotropic.
+Additionally, it is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$ derived in Sect.~\ref{sec:model_e}, which is not isotropic.
 Therefore, it would be possible to observe a direction-dependent correlation function $\xi_\pm^{ij,\rm{obs}}(\b\theta)$ in future surveys.
@@
 \begin{acknowledgements}
-We want to thank Jan-Luca van den Busch for his permission to use and modify his code for an MCMC simulation.\end{acknowledgements}
+I feel like something should be put here.
+\end{acknowledgements}
 
@@
 \subsection{Calculation of the power spectrum}
-In this Section we will perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$.
+In this section we will perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$.
 For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$.
@@
 & \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \nonumber\\
- &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left[ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]\right.\right.
+ &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left\{ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]\right.\right.
 \nonumber\\
- & \quad\qquad \left.\left. + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right] \right. \bigg> \nonumber\\
+ & \quad\qquad \left.\vphantom{\int\frac{\text{d}^2 k}{(2\pi)^2}}\left.\vphantom{(2\pi)^4} + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right\} \right> \nonumber\\
  &\qquad =  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \left[ \la \hat{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \hat{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\right] + \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
-& \qquad \overset{(*)}{=}  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
+& \qquad = (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \, ,
 \label{eq:pobs1}
 \end{align}
-where in $(*)$ we have used that the average $\la \hat{w}(\b \ell)\ra$ vanishes.
+where in the final step we have used that the average $\la \hat{w}(\b \ell)\ra$ vanishes.
 Up until now, we have not specified our weight-function $w$. We parametrize it as \begin{equation}
-w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
+w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the box-function } \Xi(\b \theta) = \begin{cases}
 1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
@@
 Here, the $w_{\b \alpha}$ are random variables, drawn from the random distribution describing the survey depths. For the Fourier transform we compute: \begin{equation}
-\hat{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-\i \b \ell L\b \alpha) \widehat{\Xi}(\b \ell)\, ,
+\hat{w}(\b \ell) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \exp(-\i L \b \ell \cdot\b \alpha) \widehat{\Xi}(\b \ell)\, ,
 \end{equation}
@@
 &\la \int \frac{\text{d}^2 k}{(2\pi)^2}\, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
-&\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-\i(\b \ell - \b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k) \exp[\i(\b \ell' - \b k)L\b \beta]\, \widehat{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
-&\qquad = \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-\i(\b \ell - \b k)L\b \alpha + i(\b \ell' - \b k) L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)\widehat{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
+&\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha,\b \beta}w_{\b \alpha}w_{\b \beta} \exp[-\i L(\b \ell - \b k)\cdot\b \alpha]\, \widehat{\Xi}(\b \ell - \b k) \exp[\i L(\b \ell' - \b k)\cdot\b \beta]\, \widehat{\Xi}^*(\b \ell' - \b k)P(\b k)\ra \nonumber\\
+&\qquad = \int \frac{\text{d}^2 k}{(2\pi)^2} \sum_{\b \alpha} \la w^2\ra \exp[-\i L(\b \ell - \b k)\cdot\b \alpha + \i L(\b \ell' - \b k) \cdot\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)\widehat{\Xi}^*(\b \ell' - \b k)P(\b k) \, .
 \end{align}
@@
 \begin{align}
-P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha+\i(\b \ell'-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell-\b k)\widehat{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
-= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i(\b \ell-\b k)L\b \alpha]\, \widehat{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widehat{\Xi}^*(\b \ell'-\b k)\exp[\i(\b \ell'- \b k)L\b \alpha] \nonumber\\
- = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widehat{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-\i(\b \ell - \b k)L\b \alpha]\,\Xi(L\b \alpha) \nonumber\\
+P^{\text{obs}}(\b \ell) = & P(\b \ell)+\int \frac{\text{d}^2\b \ell'}{(2\pi)^2} \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i L (\b \ell-\b k)\cdot\b \alpha+\i L(\b \ell'-\b k) \cdot \b \alpha]\, \widehat{\Xi}(\b \ell-\b k)\widehat{\Xi}(\b \ell' - \b k) P(\b k) \nonumber\\
+= & P(\b \ell)+ \int\frac{\text{d}^2\b k}{(2\pi)^2}\sum_{\b \alpha}\la w^2\ra \exp[-\i L (\b \ell-\b k) \cdot \b \alpha]\, \widehat{\Xi}(\b \ell - \b k)P(k) \int\frac{\text{d}^2\b \ell}{(2\pi)^2}\, \widehat{\Xi}^*(\b \ell'-\b k)\exp[\i L (\b \ell'- \b k)\cdot\b \alpha] \nonumber\\
+ = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\, \widehat{\Xi}(\b \ell-\b k)P(\b k) \sum_{\b \alpha}\exp[-\i L (\b \ell - \b k) \cdot \b \alpha]\,\Xi(L\b \alpha) \nonumber\\
  = & P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\widehat{\Xi}(\b \ell-\b k)P(\b k)\, ,
@@
 \begin{figure}
+    \sidecaption
     \centering
@@
     \hspace*{-2cm}
-    \caption[Graphic how to obtain $E(\b\theta)$]{Graphic representation on how to obtain the function $E(\b\theta)$.
+    \caption{Graphic representation on how to obtain the function $E(\b\theta)$.
 For a separation vector $\b\theta$, the dashed square represents the area of galaxies that have their partner in the same pointing.}
@@
 }
-Given one square field of length $L$ (in our case $L=60\arcmin$) and a separation vector $\b\theta$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
+Given one square field of length $L$ (in our case $L=60\arcmin$) and a separation vector $\b\theta = (\theta_1,\theta_2)$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
 The dashed square in Fig.~\ref{fig:explain_etheta} represents all possible positions that the first galaxy can take, such that the second galaxy is still within the same pointing.
@@
 V(|\b\theta|,\phi)  = \big[L-|\b\theta|\cos(\phi)\big]\,\big[L-|\b\theta|\sin(\phi)\big]\, ,
-\end{equation} where $\phi$ represents the angle of the vector $\b\theta$.
+\end{equation} where $\phi$ represents the polar angle of the vector $\b\theta$.
 The function $E(\b\theta)$ then simply equals $V(|\b\theta|,\phi)/L^2$.
-To exclude negative Volumes (which could occur when $|\b\theta|>1$ holds), we need to add the Heaviside theta function $\mathcal{H}$:
+To exclude negative volumes (which could occur when $|\b\theta|>1$ holds), we need to add the Heaviside step function $\mathcal{H}$:
 \begin{equation}
@@
 \int_0^{\frac{\pi}{2}} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right]\, ,  & |\b\theta|  \leq L \\[10pt]
-\int_{\cos\inv(L/|\b\theta|)}^{\sin\inv(L/|\b\theta|)} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right] \, , \quad   & L \leq |\b\theta| \leq \sqrt{2}L \\[10pt]
+\int_{\arccos(L/|\b\theta|)}^{\arcsin(L/|\b\theta|)} \d\phi\, \left[1-\frac{|\b\theta|}{L}\cos(\phi)\right]\,\left[1-\frac{|\b\theta|}{L}\sin(\phi)\right] \, , \quad   & L \leq |\b\theta| \leq \sqrt{2}L \\[10pt]
 0\, , &\sqrt{2}L \leq\theta
@@
 \frac{1}{L^2 \pi}\left[L^2\pi - (4L-\theta) \theta\right]\, ,  & \theta \leq L \\[10pt]
-\frac{2}{\pi}\,\left[4\sqrt{\frac{\theta^2}{L^2}-1} -1 - \frac{\theta^2}{2L^2} - \cos\inv\left(\frac{L}{\theta}\right) + \sin\inv\left(\frac{L}{\theta}\right)\right]\, ,  & L  \leq \theta \leq \sqrt{2}L \\[10pt]
+\frac{2}{\pi}\,\left[4\sqrt{\frac{\theta^2}{L^2}-1} -1 - \frac{\theta^2}{2L^2} - \arccos\left(\frac{L}{\theta}\right) + \arcsin\left(\frac{L}{\theta}\right)\right]\, ,  & L  \leq \theta \leq \sqrt{2}L \\[10pt]
 0\, ,  & \sqrt{2}L \leq \theta
@@
 This term is equal to the (weighted) number density of galaxies in the pointing multiplied by $2\pi\theta\, {\rm d}\theta\, E(\theta)$.
-
+\\
 The term (\ref{eq:numerator1}.b) denotes all galaxies within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a$, that are \textit{not} in the same pointing as galaxy $a$.
@@
 
-If we assume that said number density in a pointing is equal to the number density in the percentile it belongs to, $N_n^j$, and set $\mathcal{P}_n^\ell=1/10$, the numerator becomes \begin{align}
-\sum_{k=1}^\mathcal{N} \sum_{a\in F_k^i} w_a^i \sum_m P^k_m \left[2\pi\theta\,\d\theta\,E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + 2\pi\theta\,\d\theta\,\frac{1-E(\theta)}{10}\, \sum_n N_n^j \xi_{+,mn}^{ij}(\theta) \right] \, .
+If we assume that said number density in a pointing is equal to the number density in the percentile it belongs to, $\hat{n}_n^j$, and set $\mathcal{P}_n^\ell=1/10$, the numerator becomes \begin{align}
+\sum_{k=1}^\mathcal{N} \sum_{a\in F_k^i} w_a^i \sum_m P^k_m \left[2\pi\theta\,\d\theta\,E(\theta) \hat{n}_m^j \xi_{+,mm}^{ij}(\theta) + 2\pi\theta\,\d\theta\,\frac{1-E(\theta)}{10}\, \sum_n \hat{n}_n^j \xi_{+,mn}^{ij}(\theta) \right] \, .
 \end{align}
@@
 \begin{align}
-\frac{2\pi\theta\,\d\theta}{10} \sum_{k=1}^\mathcal{N} \sum_m N_m^i A &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \nonumber\\
- =  \, \frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n N_n^j\xi_{+,mn}^{ij}(\theta)\right] \, .
+\frac{2\pi\theta\,\d\theta}{10} \sum_{k=1}^\mathcal{N} \sum_m \hat{n}_m^i A &\left[ E(\theta) N_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n \hat{n}_n^j\xi_{+,mn}^{ij}(\theta)\right] \nonumber\\
+ =  \, \frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m \hat{n}_m^i &\left[ E(\theta) \hat{n}_m^j \xi_{+,mm}^{ij}(\theta) + \frac{1-E(\theta)}{10}\sum_n \hat{n}_n^j\xi_{+,mn}^{ij}(\theta)\right] \, .
 \end{align}
@@
  The same line of argumentation can be applied to the denominator, which then reads: \[
-\frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m N_m^i \left[ E(\theta) N_m^j + \frac{1-E(\theta)}{10}\sum_n N_n^j\right]\, .
+\frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m \hat{n}_m^i \left[ E(\theta) \hat{n}_m^j + \frac{1-E(\theta)}{10}\sum_n \hat{n}_n^j\right]\, .
  \]
-Taking the ratio of the two quantities, we see that Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} are the same\footnote{Note that while here $N_m^i$ denotes a number density, in Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} it denotes the total (weighted) number of galaxies.
-However, the difference is just a multiplication with the area $A$ of the pointings, which appears both in the numerator and the denominator and is thus cancelled out.}.
+Taking the ratio of the two quantities, and setting $N_n^i = A\hat{n}_n^i$ we see that Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} are the same.
 \section{Finite field effects}
@@
 In this chapter we will outline how to calculate the correction of the correlation functions for a finite survey with a potentially correlated distribution of depth between pointings.
-Essentially, this boils down to the calculation of $\mathcal{P}_{mn}^{ij}(\theta)$ from Equation \eqref{eq:def_xiobs}.
+Essentially, this boils down to the calculation of $\mathcal{P}_{mn}^{ij}(\theta)$ from Eq.~\eqref{eq:def_xiobs}.
 We calculate this weighting by the geometrical probability that a pair of galaxies of separation $\theta$ is of percentiles $m$ and $n$, $\mathcal{P}(m,n|\theta)$, weighted by the respective number of galaxies in the percentiles $N_m^i,N_n^j$: \[
@@
 \]
- At first we define Functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$.
+ At first we define functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$.
 This situation is depicted in Fig.~\ref{fig:expand_etheta}.
@@
 \centering
-\begin{subfigure}[c]{0.49\textwidth}
+\sidecaption
+\begin{subfigure}[c]{6cm}
 \def\svgwidth{100pt}
-\hspace*{2cm}
+\hspace*{1cm}
 \input{images/e_1.pdf_tex}
-\subcaption{For $\theta\sin(\phi)<L$ the volume of the dashed rectangle is $V(\theta,\phi)=\theta\sin(\phi)[L-\theta\cos(\phi)]$.}
-\label{fig:e01thetaa}
 \end{subfigure}
-\begin{subfigure}[c]{0.49\textwidth}
+\begin{subfigure}[c]{6cm}
 \def\svgwidth{100pt}
-\hspace*{2cm}
+\hspace*{1cm}
 \input{images/e_2.pdf_tex}
-\subcaption{For $\theta\sin(\phi)>L$ the volume of the dashed rectangle is $V(\theta,\phi)=[2L-\theta\sin(\phi)]\, [L-\theta\cos(\phi)]$.}
-\label{fig:e01thetab}
 \end{subfigure}
-\caption[How to calculate $E_{01}(\theta)$]{How to calculate $E_{01}(\theta)$ for different values of $\theta$.}
+\caption[How to calculate $E_{01}(\theta)$]{Representation of how to calculate $E_{01}(\theta)$ for different values of $\theta$.
+For $\theta\sin(\phi)<L$, as depicted in the left part, the volume of the dashed rectangle is $V(\theta,\phi)=\theta\sin(\phi)[L-\theta\cos(\phi)]$.
+For $\theta\sin(\phi)>L$, as depicted in the right part, the volume of the dashed rectangle is $V(\theta,\phi)=[2L-\theta\sin(\phi)]\, [L-\theta\cos(\phi)]$.}
 \label{fig:e01theta}
@@
 Setting $E_{ab}(\b\theta) = V(\theta,\phi)/L^2$, we define \begin{align}
-E_{01}^{(a)}(\b\theta) & \equiv \frac{\theta}{L}\sin(\phi)[1-\frac{\theta}{L}\cos(\phi)] \nonumber\\
-E_{01}^{(b)}(\b\theta) & \equiv [2-\frac{\theta}{L}\sin(\phi)]\, [1-\frac{\theta}{L}\cos(\phi)]
+E_{01}^{(a)}(\b\theta) & \equiv \frac{\theta}{L}\sin(\phi)\left[1-\frac{\theta}{L}\cos(\phi)\right] \nonumber\\
+E_{01}^{(b)}(\b\theta) & \equiv \left[2-\frac{\theta}{L}\sin(\phi)\right]\, \left[1-\frac{\theta}{L}\cos(\phi)\right]
 \end{align}
@@
 \frac{1}{\pi}\int_0^{\frac{\pi}{2}} \d\phi\, E_{01}^{(a)}(\b\theta), & \frac{\theta}{L} < 1 \\[10pt]
- \frac{1}{\pi}  \left[\int_{\cos\inv(L/\theta)}^{\sin\inv(L/\theta)}\d\phi\,E_{01}^{(a)}(\b\theta) + \int_{\sin\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) \right],  & 1 < \frac{\theta}{L} < \sqrt{2} \\[10pt]
- \frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta), & \sqrt{2}<\frac{\theta}{L}<2 \\[10pt]
-\frac{1}{\pi} \int_{\cos\inv(L/\theta)}^{\sin\inv(2L/\theta)}\d\phi\, E_{01}^{(b)}(\b\theta), & 2<\frac{\theta}{L}<\sqrt{5} \\[10pt]
+ \frac{1}{\pi}  \left[\int_{\arccos(L/\theta)}^{\arcsin(L/\theta)}\d\phi\,E_{01}^{(a)}(\b\theta) + \int_{\arcsin(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta) \right],  & 1 < \frac{\theta}{L} < \sqrt{2} \\[10pt]
+ \frac{1}{\pi} \int_{\arccos(L/\theta)}^{\frac{\pi}{2}}\d\phi\, E_{01}^{(b)}(\b\theta), & \sqrt{2}<\frac{\theta}{L}<2 \\[10pt]
+\frac{1}{\pi} \int_{\arccos(L/\theta)}^{\arcsin(2L/\theta)}\d\phi\, E_{01}^{(b)}(\b\theta), & 2<\frac{\theta}{L}<\sqrt{5} \\[10pt]
  0, & \sqrt{5}<\frac{\theta}{L}
@@
  \frac{(2L-\theta)\theta}{2\pi L^2}, & \frac{\theta}{L} < 1 \\[10pt]
- \frac{1}{\pi}\left[\frac{3}{2}- 2\frac{\theta}{L}+\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-1}+2\rm{sec\inv}\left(\frac{\theta}{L}\right)\right], & 1<\frac{\theta}{L}<\sqrt{2} \\[10pt]
- \frac{1}{2\pi}\left[-1-4\frac{\theta}{L}+4\sqrt{\frac{\theta^2}{L^2}-1}+4\rm{csc\inv}\left(\frac{\theta}{L}\right)\right], & \sqrt{2} < \frac{\theta}{L} < 2 \\[10pt]
- \frac{1}{2\pi}\left[-5-\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-4}+4\sqrt{\frac{\theta^2}{L^2}-1}-4\rm{sec\inv}\left(\frac{\theta}{L}\right)+4\sin\inv\left(\frac{2L}{\theta}\right)\right], & 2 < \frac{\theta}{L} < \sqrt{5} \\[10pt]
+ \frac{1}{\pi}\left[\frac{3}{2}- 2\frac{\theta}{L}+\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-1}+2\arcsin\left(\frac{L}{\theta}\right)\right], & 1<\frac{\theta}{L}<\sqrt{2} \\[10pt]
+ \frac{1}{2\pi}\left[-1-4\frac{\theta}{L}+4\sqrt{\frac{\theta^2}{L^2}-1}+4\arccos\left(\frac{L}{\theta}\right)\right], & \sqrt{2} < \frac{\theta}{L} < 2 \\[10pt]
+ \frac{1}{2\pi}\left[-5-\frac{\theta^2}{L^2}+2\sqrt{\frac{\theta^2}{L^2}-4}+4\sqrt{\frac{\theta^2}{L^2}-1}-4\arcsin\left(\frac{L}{\theta}\right)+4\arcsin\left(\frac{2L}{\theta}\right)\right], & 2 < \frac{\theta}{L} < \sqrt{5} \\[10pt]
  0, & \sqrt{5}<\frac{\theta}{L}
@@
 \centering
-\def\svgwidth{120pt}
+\sidecaption
+\hspace*{1cm}
+\def\svgwidth{140pt}
 \input{images/drawing.pdf_tex}
@@
 \centering
+\sidecaption
 \includegraphics[width = 0.6\linewidth]{images/eab.pdf}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{images/finite_footprint.pdf}
-\caption{$2\sigma$-contours of the corrections for the correlation functions for a $100\,\rm{deg}^2$ field (blue), a $450\,\rm{deg}^2$ field (red) and a $1000\,\rm{deg}^2$ field (green).}
+\includegraphics[width=0.9\linewidth]{images/finite_footprint.pdf}
+\caption{$2\sigma$-contours of the corrections for the correlation functions for a $100\,\rm{deg}^2$ field (blue), a $450\,\rm{deg}^2$ field (red) and a $1000\,\rm{deg}^2$ field (green).
+As can be seen, the variance of the variation is small for a $450\,\rm{deg}^2$ field and barely noticeable for a $1000\,\rm{deg}^2$ field.}
 \label{fig:finite_footprint}
@@
 
-We sampled several realizations of a random depth-distribution for a $100\,\rm{deg}^2$-field, a $450\,\rm{deg}^2$-field and a $1000\,\rm{deg}^2$-field and computed the variance of the resulting correlation functions.
+We sample several realizations of a random depth-distribution for a $100\,\rm{deg}^2$-field, a $450\,\rm{deg}^2$-field and a $1000\,\rm{deg}^2$-field.
+For each realization we extract the Function $\mathcal{P}^*(m,n|a,b)$ and, using Eq.~\eqref{eq:pmntheta}, calculate the ratio $\xi_\pm^{\rm{obs}}/\xi_\pm$.
+Afterwards, we compute the variance of these ratios.
 As can be seen from Fig.
@@
 \centering
-\includegraphics[width=0.8\linewidth]{images/compare_cosmos.pdf}
+\includegraphics[width=0.9\linewidth]{images/compare_cosmos.pdf}
 \caption{Correction to the correlation functions in varying cosmologies. Depicted here are three flat sample cosmologies, where values within the 98\% CL of the KV450 survey were sampled.}

### 2019-09-18 paperdraft.tex
minor changes

@@
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
-After reweighting the obtained redshift of data from DES and combining this with KiDS data \citep{Joudaki:2019} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration \todo{we should cite marikas new paper here as soon as it is there}.
+After reweighting the obtained redshift of data from DES and combining this with KiDS data \citep{Joudaki:2019} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration.
 This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2016MNRAS.459..971K}.
@@
 With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
-%\todo{Citations..
-\citet{2017MNRAS.464.1676A} has a few...}
 
@@
 \ref{fig:nz_of_meanz}).
-\todo{I see why you would like to move this figure further down.
-However, I feel like this plot would make a nice Fig.
-1, that captures the essence of what this paper is trying to analyse -- The effect of an artificial correlation between number density and redshift.
-I feel like the confusion caused by how exactly the plot is calculated is worth it to not have Fig.
-2 (which is not that essential) as new Fig.
-1.
-However, if you still feel like this figure would be better off further down, I will move it.}
 %
@@
 In Sect.
-\ref{sec:modelling_single_lens} we will introduce a simple toy model to understand this effect and analyze the impact on the cosmic shear power spectrum.
+\ref{sec:analytic_models} we will introduce two simple toy models to understand this effect and analyze the impact on the cosmic shear power spectrum.
 In Sect.
-\ref{sec:xipm} we will estimate the effect on the shear correlation functions $\xi_\pm$ using two different models.
+\ref{sec:xipm_semianalytic} we will estimate the effect on the shear correlation functions $\xi_\pm$ using a semi-analytic model.
 We will present our results in Sect.
@@
 \section{Simple, analytic toy models}
+\label{sec:analytic_models}
 For our first analysis we assume that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
@@
 \subsection{Modelling the power spectrum}
-\label{sec:modelling_single_lens}
+\label{sec:modelling_power_spectrum}
 In our first model we describe the impact of varying depth on the power spectrum, following the simplifications described above.
@@
 To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30, to approximately account for the increased survey area of LSST and Euclid with respect to KV450.
-As can be seen in Fig.~\ref{fig:mcmc_results}, here the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant at the level of approx.~$1\sigma$.
+Here, the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant at the level of approximately $1\sigma$.
 Conveniently it seems that the parameter $S_8$ is considerably more robust against this effect.
@@
 We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.\todo{I will add a reference in the figure as soon as marika's paper is on arxiv}
+It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.
 
@@
 We have shown that this effect can create B-modes.
-However, \todo{New asgari et al.
-comes here as soon as it is on arxiv}\citet{2018arXiv181002353A} measured the B-modes of the KV450 survey in the same $\theta$-range.
+However, Asgari et al.
+(in prep.) measured the B-modes of the KV450 survey in the same $\theta$-range.
 Those B-modes are larger than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern.
@@
 An anisotropy in the observed correlation function could be a sign for the influence of varying depth.
-\todo{Should we give an outlook? I.e. calculate covariances (I am trying to come up with something for that), apply to real KV450 footprint, ...}
 

### 2019-10-01 paperdraft.tex
added marikas changes

@@
-%\documentclass[referee]{aa} % for a referee version
-%\documentclass[onecolumn]{aa} % for a paper on 1 column  
-%\documentclass[longauth]{aa} % for the long lists of affiliations 
-%\documentclass[letter]{aa} % for the letters 
-%\documentclass[bibyear]{aa} % if the references are not structured 
-%                              according to the author-year natbib style
-%
 \documentclass{aa}
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\ben}{\begin{enumerate}}
-\newcommand{\een}{\end{enumerate}}
-\newcommand{\bi}{\begin{itemize}}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\bmi}[1]{\begin{minipage}{#1 cm}}
-\newcommand{\emi}{\end{minipage}}
-\renewcommand{\[}{\begin{equation}}
-\renewcommand{\]}{\end{equation}}
 
@@
           \and Jan Luca van den Busch\inst{2,1}
-          \and Chieh-An Lin\inst{3,5,6}
+          \and Chieh-An Lin\inst{3}
           \and Benjamin Joachimi\inst{4}
@@
 Department of Physics and Astronomy, University College London, Gower Street, London WC1E 6BT, UK
-\and
-Service d'Astrophysique, CEA Saclay, Orme des Merisiers, B\^at 709, 91191 Gif-sur-Yvette, France
-\and 
-Fenglin Veteran Hospital, 2 Zhongzheng Rd. Sec. 1, Fenglin Township, Hualien 97544, Taiwan
+% \and
+% Service d'Astrophysique, CEA Saclay, Orme des Merisiers, B\^at 709, 91191 Gif-sur-Yvette, France
+% \and 
+% Fenglin Veteran Hospital, 2 Zhongzheng Rd. Sec. 1, Fenglin Township, Hualien 97544, Taiwan
 \\ \email{sven@astro.uni-bonn.de, peter@astro.uni-bonn.de}
@@
 % aims
-   Ground-based surveys are subject to a variation in depth caused by varying atmospherical conditions; we investigate and quantify the resulting effects.
+   Ground-based surveys are subject to a variation in depth caused by varying atmospheric conditions; we investigate and quantify the resulting effects.
 In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
@@
    We construct a semi-analytic model to estimate the impact on the shear correlation functions and analyse the implications for cosmological parameters.
-Furthermore, we construct COSEBIs of the correlation functions to quantify the occurring B-modes.
+Furthermore, we construct COSEBIs from the correlation functions to quantify the occurring B-modes.
 % results
@@
 The discovery of cosmic shear has provided us with a new and powerful cosmological tool to empirically test the standard model of cosmology and to determine its parameters.
-Contrary to the analysis of the cosmic microwave background \citet[CMB, e.g.][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model.
-Current cosmic shear surveys are particularly sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ characterizes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density parameter.
+Contrary to the analysis of the cosmic microwave background \citep[CMB, e.g.~by][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model.
+Current cosmic shear surveys are particularly sensitive to the parameter $S_8=\sigma_8 (\Omega_{\rm m}/0.3)^\alpha$, where $\sigma_8$ characterizes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density parameter.
+The parameter $\alpha\approx 0.5$ depends on the exact survey properties; in this paper we will fix it to be $\alpha = 0.5$.
 It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis by \citet{2018arXiv180706209P}.
@@
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
-After reweighting the obtained redshift of data from DES and combining this with KiDS data \citep{Joudaki:2019} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration.
-This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2016MNRAS.459..971K}.
+After reweighting the obtained redshift of data from DES and combining this with KiDS data \citep[][Asgari et al.~in prep.]{Joudaki:2019} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration.
+This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2019arXiv190103686S,2019arXiv190911006T}.
 It could be interpreted as a statistical coincidence, a sign of new physics like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P}; or as the manifestation of a systematic effect, either in the cosmic shear surveys or in the Planck mission \citep{2016ApJ...818..132A}, that is not yet accounted for.
@@
 
-The depth of a pointing primarily influences the number density as well as the average redshift of galaxies, meaning that a variation in depth is responsible for a correlation between those two quantities (see Fig.
+%The depth of a pointing primarily influences the number density as well as the average redshift of galaxies, meaning that a variation in depth is responsible for a correlation between those two quantities (see Fig.
 \ref{fig:nz_of_meanz}).
 %
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{images/cov_nz_meanz.pdf}
-\caption{Weighted number of galaxies $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
-Each colour corresponds to one redshift bin of H18, the fainter points denote pointings of shallower depth.
-Details on how the data were obtained are described in Sect.
-\ref{sec:xipm_semianalytic}.}
-\label{fig:nz_of_meanz}
-\end{figure}
-%
+
 In Sect.
@@
 For our first analysis we assume that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
-If we now distribute sources at varying distances $D_{\rm s}$, then the convergence $\kappa$ varies according to $\kappa \propto D_{\rm{ds}}/D_{\rm s}$, where $D_{\rm{ds}}$ is the distance between the lens plane and the respective source.
+If we now distribute sources at varying distances $D_{\rm s}$, two effects become apparent: Firstly, the lensing efficiency $D_{\rm{ds}}/D_{\rm s}$ varies, where $D_{\rm{ds}}$ is the distance between the lens plane and the respective source.
+Secondly, and more importantly, for a more distant source \emph{more} matter is concentrated between the source and the observer, leading to a stronger shear signal.
 
-Assuming that the depth, and thus the source redshift population, varies between pointings of the camera, an observer will measure a shear signal that is modified by a step-like depth-function, $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of the average depth.
-We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
+Assuming that the depth, and thus the source redshift population, only varies between pointings of the camera, an observer will measure a shear signal that is modified by a step-like depth-function, $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of the average depth.
+We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$. This implies that $\langle w(\bm{\theta})\rangle=0$ holds, where $\langle \cdot\rangle$ denotes the average over all pointings.
 \subsection{Modelling the power spectrum}
@@
 In our first model we describe the impact of varying depth on the power spectrum, following the simplifications described above.
-% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \[
+% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \begin{equation}
 %\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
-%\]
+%\end{equation}
 
@@
 In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part.
-This allows us to separate our received signal into E- and B-modes following \[
+This allows us to separate our received signal into E- and B-modes following \begin{equation}
 % \kappa = \kappa^E+i\kappa^B\, ,
-%\]
+%\end{equation}
 %where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
@@
 Note that due to the depth-function, both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
-To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as
-\begin{align}
-w(\b \theta) = & \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the box-function } \\
-\Xi(\b \theta) = & \begin{cases}
+To model a constant depth on each individual pointing, $\b \alpha$, we can choose random variables, $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$.
+As we assume an infinite number of pointings, $\b\alpha$ can assume any two-dimensional integer value $\mathbb{Z}^2$ and we can parametrize $w(\b\theta)$ as
+\begin{equation}
+w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\, ,
+\end{equation}
+with the box-function
+\begin{equation}
+\Xi(\b \theta) = \begin{cases}
 1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
@@
 \label{eq:defweightf}
-\end{align}
+\end{equation}
 where $L$ is the sidelength of one pointing.
@@
 \begin{equation}
-P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)\, P(\b k)\, ,
+P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b \ell'}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b \ell')\, P(\b \ell')\, .
 \end{equation}
-where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function and $\hat{\Xi}$ is the Fourier transform of a box-function, which is a 2-dimensional sinc-function (compare \ref{sec:calc of PS}).
-The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P(\ell)$ from Eq.
+Here we have denoted $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ as the dispersion of the depth-function, since the statistical properties of this function do not depend on the pointing $\b\alpha$.
+The Fourier transform of the box function, $\hat{\Xi}$, is a 2-dimensional sinc-function (see \ref{sec:calc of PS}).
+The observed power spectrum, $P^{\text{obs}}$, is thus composed of the original power spectrum $P(\ell)$ from Eq.
 \eqref{eq:original_power_spectrum}, plus a convolution of the power spectrum with a sinc-function, scaling with the variance of the function $w(\b\theta)$.
-In particular, the power spectrum is not isotropic anymore.
 
@@
 \label{sec:xipm_analytic}
-More convenient measures to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
+More convenient measures to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \begin{equation}
 \xi_\pm(\theta) = \la \gamma_{\rm t}\gamma_{\rm t}\ra(\theta) \pm \la \gamma_\times\gamma_\times\ra(\theta) \, .
-\]
+\end{equation}
 Here, $\gamma_{\rm{t}}$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[see][]{2002A&A...396....1S}.
@@
 Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
-The observed correlation functions $\xi^{ij,\text{obs}}_\pm(\theta)$ now change from one of uniform depth, $\xi_\pm^{ij,\rm{uni}}(\theta)$, via \citep[see][]{2002A&A...396....1S}
+The observed correlation functions $\xi^{ij,\text{obs}}_\pm(\theta)$ now change from uniform depth, $\xi_\pm^{ij,\rm{uni}}(\theta)$, via %\citep[see][]{2002A&A...396....1S}
 \begin{align}
@@
  where the average $\la\ldots\ra$ represents both an ensemble average as well as an average over the position $\bth$.
- Assuming that the depth of different pointings is uncorrelated implies that the same holds for the functions $W$ and $N$.
-This means that the only important property of a galaxy pair is whether or not they lie in the same pointing.
+ Assuming that the depth of different pointings is uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
 We want to denote the probability that a random galaxy pair of separation $\theta$ lies in the same pointing by $E(\theta)$.
@@
 This is equivalent to setting $E(\theta)\equiv 0$.
- Performing the same calculations as above, this yields a relation between the correlation function of uniform depth $\xi_\pm^{ij,\rm{uni}}$ and the one that is usually modelled, $\xi_\pm^{ij}$:
+ Performing the same calculations as above, this yields a relation between the correlation function of uniform depth, $\xi_\pm^{ij,\rm{uni}}$, and the one that is usually modelled, $\xi_\pm^{ij}$:
 \begin{equation}
@@
 \label{sec:xipm_semianalytic}
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{images/cov_nz_meanz.pdf}
+\caption{Weighted number of galaxies $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
+Each colour corresponds to one redshift bin of H18.
+A single point represents one percentile of the respective redshift bin, where the fainter points denote pointings of shallower depth.}
+\label{fig:nz_of_meanz}
+\end{figure}
 The previously derived analytic model describes how varying depth between pointings modifies the correlation function due to the correlation between number density and average redshift of source galaxies.
@@
 
-An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band (compare Fig.
-\ref{fig:nz_of_meanz}).
+An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band.
 We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e.
 if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the DIR method of H18\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
+For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the direct spectroscopic calibration method of H18\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
 Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.}.
-The weighted numbers of Galaxies can be seen in Fig.
-\ref{fig:nz_of_meanz}, whereas the source redshift distributions are depicted in Fig.
-\ref{fig:nofz_percentiles}.
+In Fig.~\ref{fig:nz_of_meanz} the average redshift and weighted number of galaxies are plotted for each percentile of each redshift bin, whereas a selection of source redshift distributions is depicted in Fig.~\ref{fig:nofz_percentiles}.
 %
@@
 
-Given two comoving distance probability distributions of sources $\mathcal{L}^i_m(\chi),\mathcal{L}^j_n(\chi)$, we can compute the shear correlation functions from the underlying matter power spectrum $P_\delta(k,\chi)$ via \citep[compare][]{1992ApJ...388..272K} \begin{align}
+Given two comoving distance probability distributions of sources, $\mathcal{L}^i_m(\chi)$ and $\mathcal{L}^j_n(\chi)$, we can compute the shear correlation functions from the underlying matter power spectrum, $P_\delta(k,\chi)$, via \citep{1992ApJ...388..272K} \begin{align}
 \label{eq:xipm-pkappa}
@@
 \end{align}
-Here, $J_n$ denote the $n$-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is the comoving horizon.
+Here, $J_n$ denote the $n$-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is the comoving distance to the horizon.
+The parameters $H_0$ and $c$ denote the Hubble constant and the speed of light.
 
-Using Eq.~\eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{2009A&A...497..677K}.~%\citep{10.1093/mnras/stx2082}.
-Among other quantities, it calculates the shear correlation functions for a given cosmology and source redshift distribution.
-For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (compare H17).
+Using Eq.~\eqref{eq:xipm-pkappa}, we can compute the model correlation functions, $\xi_{\pm,mn}^{ij}(\theta)$, for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use \textsc{Nicaea} \citep{2009A&A...497..677K}.
+%\citep{10.1093/mnras/stx2082}.
+For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (see H17).
 If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$.
 This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions.
-Formally, we define \[
+Formally, we define \begin{equation}
 \xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)}\, ,
 \label{eq:def_xiobs}
-\]
+\end{equation}
 where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.
@@
 
-To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1,\d^2\b\theta_2$ of separation $\theta$ on the sky.
+To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1$ and $\d^2\b\theta_2$ of separation $\theta$ on the sky.
 For the case $m\neq n$ we know that the two galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ have to lie in different pointings, else they would automatically be in the same percentile.
@@
 The pointing of the second element $\d^2\b\theta_2$ has to be of percentile $n$; the probability of that is also equal to $1/10$.
-The probability that a galaxy pair populates those surface elements is proportional to the weighted number of galaxies $N_m^i,N_n^j$.
-We get for $n\neq m$: \[
+The probability that a galaxy pair populates those surface elements is proportional to the weighted number of galaxies $N_m^i$ and $N_n^j$.
+We get for $n\neq m$: \begin{equation}
 \mathcal{P}_{mn}^{ij}(\theta) = [1-E(\theta)]\frac{1}{100} N_m^i N_n^j\, .
 \label{eq:pmnij_corr1}
-\]
-For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxies lie in the same pointing [accounted for by the factor $E(\theta)$], they automatically are in the same percentile.
-We therefore obtain \[
-\mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
-\label{eq:pmnij_corr2}
-\]
-We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \[
+\end{equation}
+For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxies lie in the same pointing, they automatically are in the same percentile.
+We therefore obtain \begin{equation}
+% \mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
+% \label{eq:pmnij_corr2}
+% \end{equation}
+% We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \begin{equation}
 \mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
 \label{eq:pmnij_uncorr}
-\]
+\end{equation}
 where $\delta_{mn}$ denotes the Kronecker delta.
@@
 \begin{align}
-\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \left.\frac{1}{C}\sum_{m=1}^{10} N_m^i \right\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) \nonumber\\
+\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) =  \left.\frac{1}{C}\sum_{m=1}^{10} N_m^i \right\{ & E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) \nonumber\\
  & \left. + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
@@
 with the normalization
-\[
+\begin{equation}
 C = \sum_{m=1}^{10} N_m^i \left[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\right]\, .
-\]
+\end{equation}
 A mathematically more rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
 
-If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate and coadd 1275 correlation functions\footnote{For each of the 15 pairs of redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
-Since we are investigating an effect that is of the order of a percent, even small numerical errors can add up, skewing the calculations.
+To compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate and coadd 1275 correlation functions\footnote{For each of the 15 pairs of redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
+Since the variation in optical depth is a relatively small effect, even tiny numerical errors can add up, skewing the calculations.
 Additionally, calculating $10^3$ correlation functions is computationally expensive.
@@
 This in turn implies that in Eqs.~\eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa}, both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
-In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average comoving distance probability distribution} $\mathcal{L}^i(\chi)$ of tomographic bin $i$ as \[
+In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average comoving distance probability distribution}, $\mathcal{L}^i(\chi)$, of tomographic bin $i$ as \begin{equation}
 N^i\equiv\sum_m N_m^i\, , \qquad \mathcal{L}^i(\chi) = \frac{\sum_m N_m^i \mathcal{L}_m^i(\chi)}{\sum_m N_m^i} \, .
-\]
-If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, we find: \begin{align}
+\end{equation}
+Defining $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, we find: \begin{align}
 & \sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn}(\theta) = \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \nonumber\\
@@
 Here we apply both the analytic and the semi-analytic method to model the data from the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018}.
-While the application of the semi-analytic method is straightforward, for the analytic method we need to decide how to estimate the weight function $W$ from given redshift data.
+While the application of the semi-analytic method is straightforward, for the analytic method we need to decide how to estimate the weight function $W$ from the given redshift data.
 Following the separation of a survey into percentiles as in Sect.
@@
  As a first method, following \citet{2006APh....26...91V,1997A&A...322....1B}, we estimate 
-\[
+\begin{equation}
 W_n \propto \la z \ra _n^{0.85}\, ,
-\]
-where $\la z\ra_n$ is the average redshift of percentile $n$. As a second method we define \[
+\end{equation}
+where $\la z\ra_n$ is the average redshift of percentile $n$. As a second method we define \begin{equation}
 W_n \propto \sqrt{ \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta_{\rm{ref}}) + \la \gamma_\times\gamma_\times\ra (\theta_{\rm{ref}})} = \sqrt{\xi_{+,nn}^{ij}(\theta_{\rm{ref}})}\, ,
-\]
+\end{equation}
 where the $\xi_{+,nn}^{ij}(\theta_{\rm{ref}})$ denotes the model correlation function defined in Sect.
@@
 While the first method suffers from the fact that the power-law index only holds for sources of redshifts $1\lesssim z \lesssim 2$, the second method is sensitive to the angular range $\theta_{\rm{ref}}$, at which the shear correlation functions are evaluated, which is fairly arbitrary.
+In our case, we chose $\theta_{\rm{ref}}\approx 11'$, which is roughly in the logarithmic middle between the range of the correlation functions, $[0.\!'5,300']$.
+The choice of other values for $\theta_{\rm{ref}}$ leads to a different amplitude of the change $\xi_\pm/\xi_\pm^{\rm{obs}}$, but does not affect its shape.
+In particular, the highest amplitude of the change is at $\theta_{\rm{ref}}=0.\!'5$.
 
-We applied both analytic methods and the semianalytic one to data from KV450, following the separation into tomographic bins as in H18, and computed the ratio between our model for the observed correlation functions $\xi_{\pm}^{\rm{obs}}$, and the model correlation functions ignoring variations in depth, $\xi_{\pm}$.
+We applied both analytic methods and the semianalytic one to data from KV450, following the separation into tomographic bins as in H18, and computed the ratio between our model for the observed correlation functions, $\xi_{\pm}^{\rm{obs}}$, and the model correlation functions, $\xi_{\pm}$, ignoring variations in depth.
 
@@
   \includegraphics[width=0.9\linewidth]{images/xis_all1.pdf}
-  \caption{The ratio of observed to modelled correlation functions for the analytic methods (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
+  \caption{The ratio of modelled to observed correlation functions for the analytic methods (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
 The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
@@
 It is noticeable that in the simulations, the value $\xi_\pm/\xi_\pm^{\rm{obs}}$ consistently stays below unity at large scales, which can be attributed to the fact that the depth of different pointings is not completely uncorrelated, as was assumed in the models.
-Furthermore, we notice some strong features in the simulations at lower values of $\theta$.
-As the noise of the simulated correlation functions increases for decreasing $\theta$,\footnote{The logarithmic bins for the correlation functions were chosen in H17 such that the signal-to-noise ratio is roughly equal for each bin.
+Furthermore, we notice some strong features in the simulations at lower values of $\theta$, which arise due to the resolution limit of the simulations.
+%As the noise of the simulated correlation functions increases for decreasing $\theta$,\footnote{The logarithmic bins for the correlation functions were chosen in H17 such that the signal-to-noise ratio is roughly equal for each bin.
 However, in the simulations we ignore shape-noise, such that our only noise contribution is sample variance, which increases at lower $\theta$.} and we take the ratio of two functions that are subject to noise, these features can be attributed to sample variance.
@@
 This slight discrepancy could be attributed to the fact that the simulations make use of the whole KiDS-1000 data, whereas the models rely on distributions extracted from KV450 data.
-Additionally, the simulations take the full variations in depth into account, which include both scales smaller than one pointing (especially chip positions and dithering strategies) and scales larger than one pointing.
+Due to the fact that the discrepancies arise predominantly on small scales, the most likely reason for the discrepancy is that the simulations take the full variations in depth into account, which include scales smaller than one pointing (especially chip positions and dithering strategies).
+Several tests suggest that the small-scale effects partly negate the varying depth between pointings.
 
-An additional difference between the models and simulations is that in the models we assume an infinite footprint, whereas the simulations were performed with the actual KiDS-1000 footprint.
+An additional difference between the models and simulations is that in the models we assume an infinite footprint, whereas the simulations were performed with the KiDS-1000 footprint.
 In Appendix \ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
 With this model we can estimate the impact of a correlated distribution of depth, the sample variance of the depth-distribution and boundary effects.
-We find that for a quadratic footprint of $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$ with an uncorrelated depth-distribution, finite field effects are negligible.
+We find that for a square footprint of $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$ with an uncorrelated depth-distribution, finite field effects are negligible.
 
@@
 As the next step we want to assess how the observational depth variations propagate to cosmological parameters inferred from $\xi_\pm^{ij,\rm{obs}}$ compared to $\xi_\pm^{ij}$.
-For this test we choose the best fit values from H17 as our a fiducial cosmology $\b \Phi$ and determine the relative change in $\Omega_{\rm m}$ and $\sigma_8$ compared to a reference setup with uniform depth.
-All other cosmological parameters we keep fixed.
-First, we compute the reference correlation functions $\xi_\pm^{ij}(\theta,\b\Phi)$ for each pair of redshift bins $i,j$ using the \textsc{Nicaea}-code \citep{2009A&A...497..677K} as described in section~\ref{sec:xipm_semianalytic}.
-Then we derive the observed correlation functions $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ from Eq.~(\ref{eq:correctionfunction2}) and compute the $\chi^2$ between these and $\xi_\pm^{ij}(\theta,\b\Phi)$ using the data covariance-matrix computed in H18.
-The last step we repeat in a Markov-Chain Monte Carlo simulation to find the cosmology $\b \Phi^\mathrm{obs}$ that minimizes the $\chi^2$ and gives us an estimate of the shift in $\Omega_{\rm m}$ and $\sigma_8$ introduced by varying depth.
+For this test we choose the best fit values from H17 as our a fiducial cosmology, $\b \Phi$, and determine the relative change in $\Omega_{\rm m}$ and $\sigma_8$ compared to a reference setup with uniform depth.
+All other cosmological parameters are kept fixed.
+First, we compute the reference correlation functions, $\xi_\pm^{ij}(\theta,\b\Phi)$, for each pair of redshift bins $i,j$ using \textsc{Nicaea} as described in Sec.~\ref{sec:xipm_semianalytic}.
+Then we derive the observed correlation functions, $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$, from Eq.~(\ref{eq:correctionfunction2}).
+Using the Markov-Chain Monte Carlo sampler \textsc{emcee}, we sample correlation functions $\xi_\pm^{ij}(\theta,\b\Phi')$ for different cosmologies $\b\Phi'$ and find the likelihood distribution, given the data vector $\xi_\pm^{ij,\rm{obs}}(\theta,\b\Phi)$ and the covariance-matrix computed in H18.
+This yields an estimate of the shift in $\Omega_{\rm m}$ and $\sigma_8$ introduced by varying depth.
 
@@
 Here, the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant at the level of approximately $1\sigma$.
-Conveniently it seems that the parameter $S_8$ is considerably more robust against this effect.
+Conveniently the parameter $S_8$ is considerably more robust against this effect.
 
 Calculating the correction $\xi_\pm^{ij}/\xi_\pm^{ij,\rm{obs}}$ for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$ reveals a nontrivial dependence on the cosmology, which can be seen in Figure \ref{fig:comparecosmo}.
+For various combinations of $\Omega_{\rm{m}}$ and $\sigma_8$ within the $95\%$ confidence limit of KV450, we report a variation in $\xi_\pm/\xi_\pm^{\rm{obs}}$ of a few per cent on small scales.
 
-To estimate the B-modes created by this effect, we extract the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare S10)
+To estimate the B-modes created by this effect, we extract the COSEBIs
 %, once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then 
- for the correlation functions $\xi_\pm^{\rm{obs}}$ that have been modified under the semi-analytic model and for a reference set of correlation functions $\xi_\pm$.
+ from the correlation functions, $\xi_\pm^{\rm{obs}}$, that have been modified under the semi-analytic model and from a reference set of correlation functions $\xi_\pm$.
+To be most sensitive to the effect of varying depth, we chose logarithmic COSEBIs with an angular range of $\theta_{\rm{min}}=0.\!'5$ to $\theta_{\rm{max}}=72'$.
+As the B-modes of the reference correlation functions are zero, they are a good test for numerical errors in the calculations.
+Motivated by the discussion in \citet{2017MNRAS.464.1676A}, we calculated the COSEBIs from correlation functions binned in $400\,000$ linear bins, which yielded neglible numerical errors.
 We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.
+However, we compare the B-Modes to the ones measured by Asgari et al.~(in prep.) in KV450, which were consistent with zero.
+Since the B-modes created by varying depth are smaller than these by a factor of 50, we conclude that this effect can not create measurable B-modes in the KV450 survey.
+It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield a significant detection of B-modes.
 
@@
 \caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions.
-For comparison: Total E-modes of the reference correlation function $E_n$ and B-modes measured in the KV450 survey by Asgari et al.
-(in prep.) $B_n^{\rm{KV450}}$.
-All E- and B-modes were calculated using the logarithmic COSEBIS in S10 for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.}
+For comparison: Scaled total E-modes of the reference correlation function $E_n$ and scaled B-modes measured in the KV450 survey $B_n^{\rm{KV450}}$.
+All E- and B-modes were calculated using the logarithmic COSEBIs in S10 for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.}
 \label{fig:bmodes_cosebi}
@@
 This neglects a number of other effects: The depth in different bands and the seeing of a pointing will also modify the number densities and redshift distributions on the scale of a pointing (although those variations are also correlated with $r$-band depth and thus at least partly accounted for), whereas dithering strategies as well as imperfections in the telescope and CCD cause modifications on sub-pointing scales.
-However, we believe that these effects are subdominant compared to the variations caused by the $r$-band depth.
+However, several tests showed that these effects are subdominant compared to the variations caused by the $r$-band depth.
 
 \item We have assumed an infinitely large survey area with an uncorrelated distribution of the depth-function.
-While the boundary effects arising from a finite survey footprint would have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has fewer neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the sample variance of the depth-distribution.
+While the boundary effects arising from a finite survey footprint have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has fewer neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the sample variance of the depth-distribution.
 We have assumed that the probability for any pointing to be in percentile $n$ is exactly the expectation value, namely $1/10$.
@@
 
-\item In our MCMC simulations we did not account for degeneracies with other cosmological parameters or observational effects.
+\item In our MCMC runs we did not account for degeneracies with other cosmological parameters or observational effects.
 Especially intrinsic alignments and baryon feedback also modify the correlation functions primarily on small scales, so they are likely to be degenerate with the effect of varying depth \citep{Troxel:2015}.
-In an actual MCMC simulation that accounts for these effects, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, so that the impact on cosmological parameters is actually smaller than in our results.
-Also, possible degeneracies between $S_8$ and other cosmological parameters might bias the resulting values.
+In an MCMC run that includes these nuisance parameters, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, so that the impact on cosmological parameters will be smaller than in our results.
+Furthermore, possible degeneracies between $S_8$ and other cosmological parameters that we have kept fixed, might bias the resulting values.
 %Furthermore, when including the effects of dark energy we notice that our observation of $S_8$ being constant is no longer valid: For a `Euclid-like' survey we notice a bias of $\sim 0.8\sigma$.
@@
 (in prep.) measured the B-modes of the KV450 survey in the same $\theta$-range.
-Those B-modes are larger than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern.
-Thus it is safe to say that the B-modes in the KV450 survey are not created by varying depth.
+Those B-modes are larger than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern, yet they are consistent with zero.
+Thus it is safe to say that varying depth does not create any measurable B-modes in the KV450 survey.
 An interesting observation is that the change in E-modes is as large as the created B-modes (compare Fig.~\ref{fig:bmodes_cosebi}).
-This means that as soon as this effect causes a significant bias in the cosmological parameters, it will also create significant B-modes\footnote{While this is no big surprise, it is not trivial.
-It could be possible that a systematic effect only creates E-modes and no B-modes, which would be extremely unfortunate as it could bias cosmological parameters without ever being detected by a B-mode analysis.}.
-Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey.
+This means that as soon as this effect causes a significant bias in the cosmological parameters, it will also create significant B-modes.
+Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey \citep[see][]{2018arXiv181002353A}.
 
@@
 Although Euclid is a space-based telescope, the photometric redshift determination will still be done using ground-based data and therefore suffer from the same effects.
-While we did not yet perform a quantitative study of this effect for Euclid, we are certain that such a study should be conducted.
+Considering our quite rough assumptions regarding the variation in depth and the covariance matrix of the Euclid-survey, a study using a realistic variation of depth and covariance matrix should be conducted.
 
-While the cosmology dependence (compare Fig.
+While the cosmology dependence (Fig.
 \ref{fig:comparecosmo}) is not significant for the KV450 survey, it will be relevant for the Euclid survey.
@@
 & \la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra \nonumber\\
- &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left\{ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big]\right.\right.
-\nonumber\\
- & \quad\qquad \left.\vphantom{\int\frac{\text{d}^2 k}{(2\pi)^2}}\left.\vphantom{(2\pi)^4} + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right\} \right> \nonumber\\
+ &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \left\{ (2\pi)^4\delta(\b \ell-\b k)\delta(\b \ell'-\b k)+(2\pi)^2\big[ \hat{w}(\b \ell-\b k)\delta(\b \ell'-\b k) + \hat{w}^*(\b \ell'-\b k)\delta(\b \ell-\b k)\big] + \hat{w}(\b \ell-\b k)\hat{w}(\b \ell'-\b k) \right\} \right> \nonumber\\
  &\qquad =  (2\pi)^2\delta(\b \ell-\b \ell')P(\b \ell) + \left[ \la \hat{w}(\b \ell-\b \ell')\ra P(\b \ell')+\la \hat{w}^*(\b \ell'-\b \ell)\ra P(\b \ell)\right] + \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, \hat{w}(\b \ell-\b k)\hat{w}^*(\b \ell'-\b k)P(\b k)\ra \nonumber\\
@@
 \end{equation}
-Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky. We have defined the function $\Delta$ as \[
+Here, $w$ represents the lensing weight of the galaxy, whereas $\epsilon$ is its (complex) ellipticity and $\b \theta$ its position on the sky.
+We have defined the function $\Delta$ as \begin{equation}
 \Delta(|\b\theta_a^i-\b\theta_b^i|) = \begin{cases}
@@
 \end{cases}\, ,
-\]
+\end{equation}
 where we assume ${\rm d}\theta \ll \theta$.
@@
 \end{align}
-When we denote the probability that pointing $k$ is of percentile $m$ by $\mathcal{P}_m^k$ and assume that the product $\epsilon_a^i\epsilon_b^{j*}$ always equals its expectation value, we can set the numerator as \[
+When we denote the probability that pointing $k$ is of percentile $m$ by $\mathcal{P}_m^k$ and assume that the product $\epsilon_a^i\epsilon_b^{j*}$ always equals its expectation value, we can set the numerator as \begin{equation}
 \sum_{k=1}^\mathcal{N}\sum_{a\in F_k^i}w_a^i \sum_m \mathcal{P}_m^k \left[\overbrace{\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.a)}}\,  \xi_{+,mm}^{ij}(\theta) + \overbrace{\sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.b)}} \sum_n \mathcal{P}_n^{\ell} \xi_{+,mn}^{ij}(\theta)\right] \, .
 \label{eq:numerator1}
-\]
+\end{equation}
 The term (\ref{eq:numerator1}.a) denotes all galaxies that lie within distance interval $[\theta,\theta+{\rm d}\theta]$ of galaxy $a$, and are in the same pointing as galaxy $a$.
@@
 %
- The same line of argumentation can be applied to the denominator, which then reads: \[
+ The same line of argumentation can be applied to the denominator, which then reads: \begin{equation}
 \frac{2\pi\theta\,\d\theta \, NA}{10}  \sum_m \hat{n}_m^i \left[ E(\theta) \hat{n}_m^j + \frac{1-E(\theta)}{10}\sum_n \hat{n}_n^j\right]\, .
- \]
+ \end{equation}
 Taking the ratio of the two quantities, and setting $N_n^i = A\hat{n}_n^i$ we see that Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} are the same.
@@
 Essentially, this boils down to the calculation of $\mathcal{P}_{mn}^{ij}(\theta)$ from Eq.~\eqref{eq:def_xiobs}.
-We calculate this weighting by the geometrical probability that a pair of galaxies of separation $\theta$ is of percentiles $m$ and $n$, $\mathcal{P}(m,n|\theta)$, weighted by the respective number of galaxies in the percentiles $N_m^i,N_n^j$: \[
+We calculate this weighting by the geometrical probability that a pair of galaxies of separation $\theta$ is of percentiles $m$ and $n$, $\mathcal{P}(m,n|\theta)$, weighted by the respective number of galaxies in the percentiles $N_m^i,N_n^j$: \begin{equation}
 \mathcal{P}_{mn}^{ij}(\theta) = N_m^iN_n^j\mathcal{P}(m,n|\theta)\, .
 \label{eq:pmnij1}
-\]
+\end{equation}
  At first we define functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$.
@@
 Let $\mathcal{P}^*(m,n|a,b)$ denote the probability that two pointings of distance $(a,b)$ are of percentile $m$ and $n$ (which is directly calculable from a given survey footprint). 
-Then the following equation holds: \[
+Then the following equation holds: \begin{equation}
 \mathcal{P}(m,n|\theta) = \sum_{a,b} E_{ab}(\theta)\mathcal{P}^*(m,n|a,b)\, .
 \label{eq:pmntheta}
-\]
-Note that the expectation value of $\mathcal{P}^*(m,n|a,b)$ for uncorrelated distributions is \[
+\end{equation}
+Note that the expectation value of $\mathcal{P}^*(m,n|a,b)$ for uncorrelated distributions is \begin{equation}
 \la \mathcal{P}^*(m,n|a,b)\ra = \begin{cases}
@@
 \label{eq:pmnabstar}
-\]
-where $\delta_{mn}$ denotes the Kronecker delta. Keeping in mind that \[
+\end{equation}
+where $\delta_{mn}$ denotes the Kronecker delta. Keeping in mind that \begin{equation}
 \sum_{(a,b)\neq (0,0)} E_{ab}(\theta) = 1-E(\theta)\, ,
-\]
+\end{equation}
 we can use the expectation value \eqref{eq:pmnabstar} to calculate \eqref{eq:pmntheta} as a consistency check.

### 2019-10-02 paperdraft.tex
minor changes

@@
    For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales.
-We find that the resulting bias in $\Omega_{\rm m}$ and $\sigma_8$ will be significant in next-generation cosmic shear surveys, but that the parameter $S_8$ is surprisingly robust against this modification.
+We find that the resulting bias in $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ will be significant in next-generation cosmic shear surveys.
 We find that the dependence of this effect on the underlying cosmology is not negligible.
@@
 Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
-After reweighting the obtained redshift of data from DES and combining this with KiDS data \citep[][Asgari et al.~in prep.]{Joudaki:2019} yield even higher tension with the value determined for $S_8$ by the Planck Collaboration.
+Reweighting the obtained redshifts of data from DES and combining this with KiDS data \citep[][Asgari et al.~in prep.]{Joudaki:2019}, yields even higher tension with the value determined for $S_8$ by the Planck Collaboration.
 This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2019arXiv190103686S,2019arXiv190911006T}.
@@
 \ref{sec:discussion} we will discuss our results and comment on the impact of our used simplifications.
+App.~A is reserved for detailed calculations that can not be done in the main paper, in App.~B we introduce way to apply our model to a given survey footprint.
+App.~C is reserved for figures and tables that can not be displayed in the main body.
 We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
@@
 %\end{equation}
-
+%
 %Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate.
@@
 %2002A&A...389..729S SRC
-
+%
 In accordance to the definition of the shear power spectrum \begin{equation}
@@
 where $L$ is the sidelength of one pointing.
-Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
+Following the calculations in App.~\ref{sec:calc of PS}, we derive 
 \begin{equation}
@@
 
-Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
+Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
+Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.} per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
 The observed correlation functions $\xi^{ij,\text{obs}}_\pm(\theta)$ now change from uniform depth, $\xi_\pm^{ij,\rm{uni}}(\theta)$, via %\citep[see][]{2002A&A...396....1S}
@@
  \end{align}
- where the average $\la\ldots\ra$ represents both an ensemble average as well as an average over the position $\bth$.
+ where the average $\la\cdot\ra$ represents both an ensemble average as well as an average over the position $\bth$.
  Assuming that the depth of different pointings is uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
@@
 This function is depicted in Fig.
-\ref{fig:eoftheta_lin}, and an analytical expression is derived in App.
+\ref{fig:eoftheta_lin}, and an analytic expression is derived in App.
 \ref{sec:model_e}.
@@
 if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the direct spectroscopic calibration method of H18\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
-Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.}.
+For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the direct spectroscopic calibration method of H18.
 In Fig.~\ref{fig:nz_of_meanz} the average redshift and weighted number of galaxies are plotted for each percentile of each redshift bin, whereas a selection of source redshift distributions is depicted in Fig.~\ref{fig:nofz_percentiles}.
+A table of the limiting magnitudes for each percentile can be found in Tab.~\ref{tab:maglim}.
 %
@@
 \end{equation}
-A mathematically more rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.
+A mathematically more rigorous derivation of this function can be found in App.~\ref{sec:calc of xipm}.
 
-To compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate and coadd 1275 correlation functions\footnote{For each of the 15 pairs of redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
-Since the variation in optical depth is a relatively small effect, even tiny numerical errors can add up, skewing the calculations.
+Computing this for all 5 redshift bins of the KV450-survey, forces us to calculate and coadd 1275 correlation functions\footnote{For each of the 15 pairs of redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
+Since the variation in depth is a relatively small effect, even tiny numerical errors can add up, skewing the calculations.
 Additionally, calculating $10^3$ correlation functions is computationally expensive.
@@
 The second analytic method, however, traces the semi-analytic one pretty well for $\xi_+$.
-As $\xi_-$ is affected much stronger by this effect, the analytic method is not able to trace this change.\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
+As $\xi_-$ is affected much stronger by this effect, the analytic method is not able to trace this change\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
 This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$.
 However, $\xi_-$ is obtained by filtering with the 4-th order Bessel function, which peaks at approximately $\ell\theta\approx 5$, so for different $\theta$ this function is sensitive to varying parts of the convergence power spectrum.
-A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.} Furthermore we note that the effect seems to be strongest in the first redshift bin, which is not surprising, as there the average redshift between pointings varies the most (compare Fig.
+A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}.
+Furthermore we note that the effect seems to be strongest in the first redshift bin, which is not surprising, as there the average redshift between pointings varies the most (compare Fig.
 \ref{fig:nz_of_meanz}).
@@
 In general, the semi-analytic model seems to over-estimate the effect compared to the simulations, which take the full distribution of depth into account.
-This slight discrepancy could be attributed to the fact that the simulations make use of the whole KiDS-1000 data, whereas the models rely on distributions extracted from KV450 data.
+This slight discrepancy could be attributed to the fact that the simulations follow a finer magnitude-binning for the number densities of galaxies.
 Due to the fact that the discrepancies arise predominantly on small scales, the most likely reason for the discrepancy is that the simulations take the full variations in depth into account, which include scales smaller than one pointing (especially chip positions and dithering strategies).
-Several tests suggest that the small-scale effects partly negate the varying depth between pointings.
+Several tests suggest that both small-scale effects and a finer magnitude binning partly negate the varying depth between pointings.
 
 An additional difference between the models and simulations is that in the models we assume an infinite footprint, whereas the simulations were performed with the KiDS-1000 footprint.
-In Appendix \ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
+In App.~\ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
 With this model we can estimate the impact of a correlated distribution of depth, the sample variance of the depth-distribution and boundary effects.
@@
 As the next step we want to assess how the observational depth variations propagate to cosmological parameters inferred from $\xi_\pm^{ij,\rm{obs}}$ compared to $\xi_\pm^{ij}$.
-For this test we choose the best fit values from H17 as our a fiducial cosmology, $\b \Phi$, and determine the relative change in $\Omega_{\rm m}$ and $\sigma_8$ compared to a reference setup with uniform depth.
+For this test we choose a fiducial cosmology, $\b \Phi$, and determine the relative change in $\Omega_{\rm m}$ and $\sigma_8$ compared to a reference setup with uniform depth.
 All other cosmological parameters are kept fixed.
@@
 Calculating the correction $\xi_\pm^{ij}/\xi_\pm^{ij,\rm{obs}}$ for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$ reveals a nontrivial dependence on the cosmology, which can be seen in Figure \ref{fig:comparecosmo}.
-For various combinations of $\Omega_{\rm{m}}$ and $\sigma_8$ within the $95\%$ confidence limit of KV450, we report a variation in $\xi_\pm/\xi_\pm^{\rm{obs}}$ of a few per cent on small scales.
+For various combinations of $\Omega_{\rm{m}}$ and $\sigma_8$ within the $95\%$ confidence limit of KV450, we report a variation in $\xi_\pm/\xi_\pm^{\rm{obs}}$ of a few percentage points on small scales.
 
@@
 %, once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then 
- from the correlation functions, $\xi_\pm^{\rm{obs}}$, that have been modified under the semi-analytic model and from a reference set of correlation functions $\xi_\pm$.
+ from the correlation functions, $\xi_\pm^{\rm{obs}}$, that have been modified under the semi-analytic model, and from a reference set of correlation functions $\xi_\pm$.
 To be most sensitive to the effect of varying depth, we chose logarithmic COSEBIs with an angular range of $\theta_{\rm{min}}=0.\!'5$ to $\theta_{\rm{max}}=72'$.
@@
 Especially intrinsic alignments and baryon feedback also modify the correlation functions primarily on small scales, so they are likely to be degenerate with the effect of varying depth \citep{Troxel:2015}.
-In an MCMC run that includes these nuisance parameters, we suspect that the parameters for intrinsic alignments and baryonic feedback change to mitigate this effect, so that the impact on cosmological parameters will be smaller than in our results.
-Furthermore, possible degeneracies between $S_8$ and other cosmological parameters that we have kept fixed, might bias the resulting values.
+In an MCMC run that includes these nuisance parameters, we suspect that the parameters for intrinsic alignments and baryon feedback change to mitigate this effect, so that the impact on cosmological parameters will be smaller than in our results.
+Furthermore, possible degeneracies between $S_8$ and other cosmological parameters that we have kept fixed might bias the resulting values.
 %Furthermore, when including the effects of dark energy we notice that our observation of $S_8$ being constant is no longer valid: For a `Euclid-like' survey we notice a bias of $\sim 0.8\sigma$.
@@
 Despite these repercussions, we are confident to say that the effects of varying depth are not significant for the KV450 survey.
-The cosmological parameters did not change and the main parameter, $S_8$, is especially robust against this effect.
 In particular this means that a varying depth can not explain the discrepancy between observations of the local Universe and results from analysis of the CMB.
@@
 \subsection{Calculation of the power spectrum}
-In this section we will perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$.
+Here we will perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$.
 For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$.
-In reality, finite field effects would play a role here.
+In reality, finite field effects would play a role.
 We begin with the calculation of the correlation for the Fourier transformed shear:
@@
 
-\section{Additional Figures}
-
+\section{Additional Figures and Tables}
+\begin{table}[h]
+\centering
+\caption{Limiting magnitudes for the ten percentiles}
+\label{tab:maglim}
+\begin{tabular}{r c}
+\hline\hline
+Percentile & $r$-band depth \\
+\hline
+0 & 25.76 \\
+10 & 26.06 \\
+20 & 26.15 \\
+30 & 26.19 \\
+40 & 26.23 \\
+50 & 26.27 \\
+60 & 26.31 \\
+70 & 26.34 \\
+80 & 26.39 \\
+90 & 26.44 \\
+100 & 26.60 \\
+\hline
+\end{tabular}
+\end{table}
 \begin{figure}[h]

### 2019-10-02 paperdraft.tex
minor changes
added link to paper in abstract

@@
 \documentclass{aa}  
+\usepackage{hyperref}
 
@@
 \usepackage{subcaption}
+%\usepackage{hyperref}
 
@@
           \and Hendrik Hildebrandt\inst{2,1}
+          \and Marika Asgari\inst{3}
           \and Catherine Heymans\inst{3,2} 
-          \and Marika Asgari\inst{3}
+          \and Benjamin Joachimi\inst{4}
+          \and Chieh-An Lin\inst{3}
+          \and Tilman Tr\"{o}ster\inst{3}
           \and Jan Luca van den Busch\inst{2,1}
-          \and Chieh-An Lin\inst{3}
-          \and Benjamin Joachimi\inst{4}
-          \and Tilman Tr\"{o}ster\inst{3}
           }
@@
   \abstract
-% context (optional)
    {Cosmic shear proves to be a powerful tool to study the properties of the Universe.
 The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the cosmic microwave background motivates further investigation of yet unaccounted systematic biases.
-% aims
    Ground-based surveys are subject to a variation in depth caused by varying atmospheric conditions; we investigate and quantify the resulting effects.
 In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
-% methods
    We construct a semi-analytic model to estimate the impact on the shear correlation functions and analyse the implications for cosmological parameters.
 Furthermore, we construct COSEBIs from the correlation functions to quantify the occurring B-modes.
-% results
    For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales.
@@
 We also report the occurrence of B-modes, although at a not yet significant level.
-% conclusions (optional)
-   We conclude that the effects of varying depth for current cosmic shear surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}
+   We conclude that the effects of varying depth for current cosmic shear surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.
+\textcolor{blue}{\href{https://docs.google.com/document/d/13j7fUE8jrK5HOVbf4p0HdQs6c14jbWtm9Yq8CtLZCK4/edit?usp=sharing}{[Link to the current google doc]}}}
 

### 2019-10-02 paperdraft.tex
added some acknowledgements

@@
 \begin{acknowledgements}
-I feel like something should be put here.
+The KV450 results in this paper are based on data products from observations
+made with ESO Telescopes at the La Silla Paranal Observatory under programme
+IDs 177.A-3016, 177.A-3017 and 177.A-3018, and on data products produced by
+Target/OmegaCEN, INAF-OACN, INAF-OAPD and the KiDS production team,
+on behalf of the KiDS consortium.
+\\
+This research has made use of NASA's Astrophysics Data System and adstex (\url{https://github.com/yymao/adstex}).
 \end{acknowledgements}

### 2019-10-03 paperdraft.tex
added some acknowledgements
updated figues

@@
 In an MCMC run that includes these nuisance parameters, we suspect that the parameters for intrinsic alignments and baryon feedback change to mitigate this effect, so that the impact on cosmological parameters will be smaller than in our results.
-Furthermore, possible degeneracies between $S_8$ and other cosmological parameters that we have kept fixed might bias the resulting values.
 %Furthermore, when including the effects of dark energy we notice that our observation of $S_8$ being constant is no longer valid: For a `Euclid-like' survey we notice a bias of $\sim 0.8\sigma$.
@@
 on behalf of the KiDS consortium.
+\\
+\emph{Author contributions:} All authors contributed to the development and writing of this paper.
+The authorship list is given in two groups: the lead authors (SH, PS, HHi) followed by key contributors to either the scientific analysis or the data products in alphabetical order.
 \\

### 2019-10-04 paperdraft.tex
changes

@@
 In this work we assume the specifications of the Kilo-Degree Survey \citep[KiDS,][]{Kuijken:2015}, namely an assembly of $1\,\text{deg}^2$ square fields.
+To quantify the depth, we chose the limiting magnitude of the $r$-band, as defined in \citet{2017A&A...604A.134D}, since it serves as the detection band and is thus most important for determining source galaxies.
 
@@
 
-An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band.
+An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the limiting magnitude in the $r$-band.
 We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e.

### 2019-10-04 paperdraft.tex
cleanup

@@
 %
-In accordance to the definition of the shear power spectrum \begin{equation}
+In accordance with the definition of the shear power spectrum \begin{equation}
 \la \hat{\gamma}(\b\ell)\,\hat{\gamma}^*(\b\ell')\ra = (2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) \, ,
@@
 While this is not true for a 3-dimensional lensing matter distribution, it should be a reasonable first approximation for small variations in mean source redshift.
-Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
+Additionally, we assume that a greater depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
 
@@
 \includegraphics[trim = {1cm 0 1.2cm 0.1cm}, clip, width=\linewidth]{images/dist_z_all.pdf}
-\caption{The source redshift distributions $p^i_m(z)$ for the best, average, and worst percentile in each tomographic redshift bin.}
+\caption{The source redshift distributions $p^i_m(z)$ for a selection of very shallow pointings (blue), average pointings (yellow) and very deep pointings (green).
+The percentage points in the legend denote to which percentile a pointing belongs, when all are ordered by their depth.}
 \label{fig:nofz_percentiles}
@@
 where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.
-In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth.
+In this analysis, we will assume an uncorrelated distribution of depth and neglect boundary effects as well as the sample variance of the depth-distribution between pointings.
 We will later discuss the validity of these assumptions as well as possible mitigation strategies.
@@
 
-An additional difference between the models and simulations is that in the models we assume an infinite footprint, whereas the simulations were performed with the KiDS-1000 footprint.
+An additional difference between the models and simulations is that in the models we neglect boundary effects and the sample-variance of the depth-distribution between pointings, whereas the simulations were performed with the KiDS-1000 footprint.
 In App.~\ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
@@
 
-\item We have assumed an infinitely large survey area with an uncorrelated distribution of the depth-function.
+\item We have assumed an uncorrelated distribution of the depth-function and neglected boundary effects as well as the sample variance of the depth-distribution between pointings.
 While the boundary effects arising from a finite survey footprint have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has fewer neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the sample variance of the depth-distribution.
 We have assumed that the probability for any pointing to be in percentile $n$ is exactly the expectation value, namely $1/10$.
-While this is true for an infinitely large survey with an uncorrelated distribution of the depth-function, it does not necessarily hold for a real survey.
+While this would be true for an infinitely large survey with an uncorrelated distribution of the depth-function, it does not necessarily hold for a real survey.
 However, our analysis in App.~\ref{sec:expand_eoftheta} suggests that these effects are not significant for the KV450 survey.

### 2019-10-04 paperdraft.tex
applied changes suggested by benjamin

@@
    {Cosmic shear proves to be a powerful tool to study the properties of the Universe.
-The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the cosmic microwave background motivates further investigation of yet unaccounted systematic biases.
+The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the low-redshift large-scale structure and the cosmic microwave background motivates further investigation of yet unaccounted systematic biases.
    Ground-based surveys are subject to a variation in depth caused by varying atmospheric conditions; we investigate and quantify the resulting effects.
@@
    For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales.
-We find that the resulting bias in $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ will be significant in next-generation cosmic shear surveys.
+We find that the resulting bias in $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ will be significant at the level of about $1\sigma$ in next-generation cosmic shear surveys.
 We find that the dependence of this effect on the underlying cosmology is not negligible.
-We also report the occurrence of B-modes, although at a not yet significant level.
+We also report the occurrence of B-modes, although at a level that is more than one order of magnitude below the current statistical uncertainties.
    We conclude that the effects of varying depth for current cosmic shear surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.
@@
 The discovery of cosmic shear has provided us with a new and powerful cosmological tool to empirically test the standard model of cosmology and to determine its parameters.
-Contrary to the analysis of the cosmic microwave background \citep[CMB, e.g.~by][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model.
+Contrary to the analysis of the cosmic microwave background \citep[CMB, e.g.~by][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the low-redshift large-scale Structure and thus provides an excellent consistency check for the standard model.
 Current cosmic shear surveys are particularly sensitive to the parameter $S_8=\sigma_8 (\Omega_{\rm m}/0.3)^\alpha$, where $\sigma_8$ characterizes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density parameter.
@@
 To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}.
-To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
+To leading order, B-modes cannot be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
 The most useful E- and B-mode decomposition for cosmic shear surveys is provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs,][hereafter S10]{2010A&A...520A.116S}, as it can easily be applied to real data.
@@
 \ref{sec:discussion} we will discuss our results and comment on the impact of our used simplifications.
-App.~A is reserved for detailed calculations that can not be done in the main paper, in App.~B we introduce way to apply our model to a given survey footprint.
-App.~C is reserved for figures and tables that can not be displayed in the main body.
+App.~A is reserved for detailed calculations that cannot be done in the main paper, in App.~B we introduce way to apply our model to a given survey footprint.
+App.~C is reserved for figures and tables that cannot be displayed in the main body.
 We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
@@
 %\end{equation}
-%where $B$-Modes can not be generated by a lensing signal and are thus a tracer of remaining systematics.
+%where $B$-Modes cannot be generated by a lensing signal and are thus a tracer of remaining systematics.
 %2002A&A...389..729S SRC
@@
 Each colour corresponds to one redshift bin of H18.
-A single point represents one percentile of the respective redshift bin, where the fainter points denote pointings of shallower depth.}
+A single point represents one quantile of the respective redshift bin, where the fainter points denote pointings of shallower depth.}
 \label{fig:nz_of_meanz}
@@
 An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the limiting magnitude in the $r$-band.
-We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e.
-if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on.
-For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the direct spectroscopic calibration method of H18.
-In Fig.~\ref{fig:nz_of_meanz} the average redshift and weighted number of galaxies are plotted for each percentile of each redshift bin, whereas a selection of source redshift distributions is depicted in Fig.~\ref{fig:nofz_percentiles}.
-A table of the limiting magnitudes for each percentile can be found in Tab.~\ref{tab:maglim}.
+We thus chose to separate the survey into 10 quantiles, sorted by $r$-band depth, i.e.
+if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first quantile, and so on.
+For each quantile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the direct spectroscopic calibration method of H18.
+In Fig.~\ref{fig:nz_of_meanz} the average redshift and weighted number of galaxies are plotted for each quantile of each redshift bin, whereas a selection of source redshift distributions is depicted in Fig.~\ref{fig:nofz_quantiles}.
+A table of the limiting magnitudes for each quantile can be found in Tab.~\ref{tab:maglim}.
 %
@@
 \caption{The source redshift distributions $p^i_m(z)$ for a selection of very shallow pointings (blue), average pointings (yellow) and very deep pointings (green).
-The percentage points in the legend denote to which percentile a pointing belongs, when all are ordered by their depth.}
-\label{fig:nofz_percentiles}
+The percentage points in the legend denote to which quantile a pointing belongs, when all are ordered by their depth.}
+\label{fig:nofz_quantiles}
 \end{figure}
@@
 
-Using Eq.~\eqref{eq:xipm-pkappa}, we can compute the model correlation functions, $\xi_{\pm,mn}^{ij}(\theta)$, for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use \textsc{Nicaea} \citep{2009A&A...497..677K}.
+Using Eq.~\eqref{eq:xipm-pkappa}, we can compute the model correlation functions, $\xi_{\pm,mn}^{ij}(\theta)$, for each pair of quantiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use \textsc{Nicaea} \citep{2009A&A...497..677K}.
 %\citep{10.1093/mnras/stx2082}.
 For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (see H17).
-If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$.
+If, for a single pair of galaxies, one galaxy lies in the $m$-th quantile of redshift bin $i$ and the second one lies in the $n$-th quantile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$.
 This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions.
@@
 \end{equation}
-where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.
+where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from quantiles $m$ and $n$.
 In this analysis, we will assume an uncorrelated distribution of depth and neglect boundary effects as well as the sample variance of the depth-distribution between pointings.
@@
 To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1$ and $\d^2\b\theta_2$ of separation $\theta$ on the sky.
-For the case $m\neq n$ we know that the two galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ have to lie in different pointings, else they would automatically be in the same percentile.
+For the case $m\neq n$ we know that the two galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ have to lie in different pointings, else they would automatically be in the same quantile.
 The probability that the surface elements are within different pointings is $[1-E(\theta)]$.
-Furthermore, the first element $\d^2\b\theta_1$ has to lie in percentile $m$, the probability of which is $1/10$.
-The pointing of the second element $\d^2\b\theta_2$ has to be of percentile $n$; the probability of that is also equal to $1/10$.
+Furthermore, the first element $\d^2\b\theta_1$ has to lie in quantile $m$, the probability of which is $1/10$.
+The pointing of the second element $\d^2\b\theta_2$ has to be of quantile $n$; the probability of that is also equal to $1/10$.
 The probability that a galaxy pair populates those surface elements is proportional to the weighted number of galaxies $N_m^i$ and $N_n^j$.
@@
 \end{equation}
-For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxies lie in the same pointing, they automatically are in the same percentile.
+For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxies lie in the same pointing, they automatically are in the same quantile.
 We therefore obtain \begin{equation}
@@
 While the application of the semi-analytic method is straightforward, for the analytic method we need to decide how to estimate the weight function $W$ from the given redshift data.
-Following the separation of a survey into percentiles as in Sect.
-\ref{sec:xipm_semianalytic}, we define $W(\b\theta)\equiv W_n$ whenever $\b\theta$ is in a pointing of percentile $n$.
+Following the separation of a survey into quantiles as in Sect.
+\ref{sec:xipm_semianalytic}, we define $W(\b\theta)\equiv W_n$ whenever $\b\theta$ is in a pointing of quantile $n$.
 For the determination of $W_n$ we test two approaches:
@@
 \end{equation}
-where $\la z\ra_n$ is the average redshift of percentile $n$. As a second method we define \begin{equation}
+where $\la z\ra_n$ is the average redshift of quantile $n$. As a second method we define \begin{equation}
 W_n \propto \sqrt{ \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta_{\rm{ref}}) + \la \gamma_\times\gamma_\times\ra (\theta_{\rm{ref}})} = \sqrt{\xi_{+,nn}^{ij}(\theta_{\rm{ref}})}\, ,
@@
   \includegraphics[width=0.9\linewidth]{images/xis_all1.pdf}
-  \caption{The ratio of modelled to observed correlation functions for the analytic methods (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins.
+  \caption{The ratio of modelled to observed correlation functions for a cross-correlation of all redshift bins.
+Plotted are the semi-analytic method (blue), the numerical simulations (red) as well as the analytic method (green) with the first and second method of estimating the weight function, as described in the beginning of Sec.~\ref{sec:results}.
+The dashed part of the red line represents the region in which the limited resulution affects the simulations by more than 10\%.
 The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
@@
 Due to the fact that the discrepancies arise predominantly on small scales, the most likely reason for the discrepancy is that the simulations take the full variations in depth into account, which include scales smaller than one pointing (especially chip positions and dithering strategies).
-Several tests suggest that both small-scale effects and a finer magnitude binning partly negate the varying depth between pointings.
+While it is impossible to include the entire sub-pointing variations in depth into our models, we tested a sub-division of one pointing into four smaller ones, all of which have a similar depth; this lowered the tension between models and simulation.
+Furthermore, we tested a coarser magnitude-binning in our models, which increased the tension.
+These tests suggest that both small-scale effects and a finer magnitude binning at least partly negate the varying depth between pointings.
 
@@
 To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30, to approximately account for the increased survey area of LSST and Euclid with respect to KV450.
-Here, the impact on both $\Omega_{\rm m}$ and $\sigma_8$ is significant at the level of approximately $1\sigma$.
-Conveniently the parameter $S_8$ is considerably more robust against this effect.
+Here, the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$.
+It should be noted that while Euclid is a space-based mission, the photometric redshift determination will be performed using several ground-based telescopes, which means that Euclid will suffer from variations in depth that are at least as large as in KiDS.
+While the data from LSST will be practically free of variations in depth after 10 years of observations, their first-year data will equally suffer from this effect.
 
@@
 However, we compare the B-Modes to the ones measured by Asgari et al.~(in prep.) in KV450, which were consistent with zero.
-Since the B-modes created by varying depth are smaller than these by a factor of 50, we conclude that this effect can not create measurable B-modes in the KV450 survey.
+Since the B-modes created by varying depth are smaller than these by a factor of 50, we conclude that this effect cannot create measurable B-modes in the KV450 survey.
 It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield a significant detection of B-modes.
@@
 While the boundary effects arising from a finite survey footprint have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has fewer neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the sample variance of the depth-distribution.
-We have assumed that the probability for any pointing to be in percentile $n$ is exactly the expectation value, namely $1/10$.
+We have assumed that the probability for any pointing to be in quantile $n$ is exactly the expectation value, namely $1/10$.
 While this would be true for an infinitely large survey with an uncorrelated distribution of the depth-function, it does not necessarily hold for a real survey.
@@
 Despite these repercussions, we are confident to say that the effects of varying depth are not significant for the KV450 survey.
-In particular this means that a varying depth can not explain the discrepancy between observations of the local Universe and results from analysis of the CMB.
+In particular this means that a varying depth cannot explain the discrepancy between observations of the low-redshift Universe and results from analysis of the CMB.
 
@@
 (in prep.) measured the B-modes of the KV450 survey in the same $\theta$-range.
-Those B-modes are larger than the ones created by varying depth by a factor of approx.~$50$ and show a completely different pattern, yet they are consistent with zero.
+The results are consistent with zero, yet their statistical fluctuations are larger than the B-modes created by varying depth by a factor of approx.~$50$.
 Thus it is safe to say that varying depth does not create any measurable B-modes in the KV450 survey.
@@
 For next-generation surveys like Euclid, this effect will be significant.
-Although Euclid is a space-based telescope, the photometric redshift determination will still be done using ground-based data and therefore suffer from the same effects.
 Considering our quite rough assumptions regarding the variation in depth and the covariance matrix of the Euclid-survey, a study using a realistic variation of depth and covariance matrix should be conducted.
@@
 An anisotropy in the observed correlation function could be a sign for the influence of varying depth.
+
+The variation in depth will also affect the covariance of a survey, both because they modify the signal and because they introduce an additional term of sample variance in terms of the distribution of depth.
+This effect will be investigated in a forthcoming publication.
 
@@
 \end{align}
-When we denote the probability that pointing $k$ is of percentile $m$ by $\mathcal{P}_m^k$ and assume that the product $\epsilon_a^i\epsilon_b^{j*}$ always equals its expectation value, we can set the numerator as \begin{equation}
+When we denote the probability that pointing $k$ is of quantile $m$ by $\mathcal{P}_m^k$ and assume that the product $\epsilon_a^i\epsilon_b^{j*}$ always equals its expectation value, we can set the numerator as \begin{equation}
 \sum_{k=1}^\mathcal{N}\sum_{a\in F_k^i}w_a^i \sum_m \mathcal{P}_m^k \left[\overbrace{\sum_{b\in F_{k}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.a)}}\,  \xi_{+,mm}^{ij}(\theta) + \overbrace{\sum_{\ell\neq k} \sum_{b\in F_{\ell}^j} w_b^j \Delta(|\b\theta_a^i-\b\theta_b^i|)}^{\rm{(\ref{eq:numerator1}.b)}} \sum_n \mathcal{P}_n^{\ell} \xi_{+,mn}^{ij}(\theta)\right] \, .
@@
 
-If we assume that said number density in a pointing is equal to the number density in the percentile it belongs to, $\hat{n}_n^j$, and set $\mathcal{P}_n^\ell=1/10$, the numerator becomes \begin{align}
+If we assume that said number density in a pointing is equal to the number density in the quantile it belongs to, $\hat{n}_n^j$, and set $\mathcal{P}_n^\ell=1/10$, the numerator becomes \begin{align}
 \sum_{k=1}^\mathcal{N} \sum_{a\in F_k^i} w_a^i \sum_m P^k_m \left[2\pi\theta\,\d\theta\,E(\theta) \hat{n}_m^j \xi_{+,mm}^{ij}(\theta) + 2\pi\theta\,\d\theta\,\frac{1-E(\theta)}{10}\, \sum_n \hat{n}_n^j \xi_{+,mn}^{ij}(\theta) \right] \, .
 \end{align}
-The term $\sum_{a\in F_k^i} w_a^i$ denotes the number of galaxies in pointing $k$, which we set as the number density of galaxies in the respective percentile multiplied with the area $A$ of the pointing.
+The term $\sum_{a\in F_k^i} w_a^i$ denotes the number of galaxies in pointing $k$, which we set as the number density of galaxies in the respective quantile multiplied with the area $A$ of the pointing.
 Applying this and setting $\mathcal{P}_m^k=1/10$, the numerator reads
@@
 Essentially, this boils down to the calculation of $\mathcal{P}_{mn}^{ij}(\theta)$ from Eq.~\eqref{eq:def_xiobs}.
-We calculate this weighting by the geometrical probability that a pair of galaxies of separation $\theta$ is of percentiles $m$ and $n$, $\mathcal{P}(m,n|\theta)$, weighted by the respective number of galaxies in the percentiles $N_m^i,N_n^j$: \begin{equation}
+We calculate this weighting by the geometrical probability that a pair of galaxies of separation $\theta$ is of quantiles $m$ and $n$, $\mathcal{P}(m,n|\theta)$, weighted by the respective number of galaxies in the quantiles $N_m^i,N_n^j$: \begin{equation}
 \mathcal{P}_{mn}^{ij}(\theta) = N_m^iN_n^j\mathcal{P}(m,n|\theta)\, .
@@
 
-Let $\mathcal{P}^*(m,n|a,b)$ denote the probability that two pointings of distance $(a,b)$ are of percentile $m$ and $n$ (which is directly calculable from a given survey footprint). 
+Let $\mathcal{P}^*(m,n|a,b)$ denote the probability that two pointings of distance $(a,b)$ are of quantile $m$ and $n$ (which is directly calculable from a given survey footprint). 
 Then the following equation holds: \begin{equation}
@@
 \centering
-\caption{Limiting magnitudes for the ten percentiles}
+\caption{Limiting magnitudes for the ten quantiles}
 \label{tab:maglim}
@@
 \hline\hline
-Percentile & $r$-band depth \\
+quantile & $r$-band depth \\
 \hline

### 2019-10-05 paperdraft.tex
minor changes

@@
           \and Benjamin Joachimi\inst{4}
+          \and Konrad Kuijken\inst{5}
           \and Chieh-An Lin\inst{3}
@@
 Department of Physics and Astronomy, University College London, Gower Street, London WC1E 6BT, UK
+\and
+Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, The Netherlands
 % \and
@@
 For this analysis we will follow the assumption that a deeper pointing shows a stronger shear signal $\gamma^{\rm{obs}}(\b\theta) = W(\b\theta)\gamma(\b\theta)$ as described above.
-While this is not true for a 3-dimensional lensing matter distribution, it should be a reasonable first approximation for small variations in mean source redshift.
+In general, this is certainly not true.
+This assumption implies that a higher redshift just increases the amplitude of the shear signal, but as can clearly be seen by inspecting shear correlation functions of different redshift distributions, the change of the signal is extremely scale-dependent and not just a multiplication with a constant factor.
+However, it should serve as a reasonable first approximation for small variations in mean source redshift.
 Additionally, we assume that a greater depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
@@
 Plotted are the semi-analytic method (blue), the numerical simulations (red) as well as the analytic method (green) with the first and second method of estimating the weight function, as described in the beginning of Sec.~\ref{sec:results}.
-The dashed part of the red line represents the region in which the limited resulution affects the simulations by more than 10\%.
+The dashed part of the red line represents the region in which the limited resolution affects the simulations by more than 10\%.
 The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.

### 2019-10-09 paperdraft.tex
minor modifications

@@
 \and 
-Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany 
+The German Centre for Cosmological Lensing, Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany 
 \and
@@
 The discovery of cosmic shear has provided us with a new and powerful cosmological tool to empirically test the standard model of cosmology and to determine its parameters.
-Contrary to the analysis of the cosmic microwave background \citep[CMB, e.g.~by][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the low-redshift large-scale Structure and thus provides an excellent consistency check for the standard model.
-Current cosmic shear surveys are particularly sensitive to the parameter $S_8=\sigma_8 (\Omega_{\rm m}/0.3)^\alpha$, where $\sigma_8$ characterizes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density parameter.
-The parameter $\alpha\approx 0.5$ depends on the exact survey properties; in this paper we will fix it to be $\alpha = 0.5$.
+Contrary to the analysis of the cosmic microwave background \citep[CMB, e.g.~by][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the low-redshift large-scale structure and thus provides an excellent consistency check for the standard model.
+Current cosmic shear surveys are particularly sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ characterizes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density parameter.
+Constraints on $S_8$ from the three current major cosmic shear results are all consistent with the CMB analysis by \citet{2018arXiv180706209P}.
+It is interesting to note, however, that they all favour values that are slightly lower than the Planck constraints of $S_8 = 0.830 \pm 0.013$.
+\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from an analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data, and \citet{2018PhRvD..98d3528T} constrain $S_8=0.782\pm 0.027$ using the Dark Energy Survey (DES).
+Combined analyses of DES and KiDS data \citep{Joudaki:2019, asgari/etal:2019} results in a $\sim 3 \sigma S_8$ tension with the CMB value.
+If this tension is not the manifestation of an unaccounted systematic effect, in either the cosmic shear surveys \citep{Mandelbaum:2019} or the Planck mission \citep{2016ApJ...818..132A}, it certainly merits attention.
+It could be interpreted as a sign of new physics with examples like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P} and coupling within the dark sector \citep{Kumar:2019}.
+It could also, however, be a simple statistical coincidence.
+
 It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis by \citet{2018arXiv180706209P}.
@@
 
-For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[][hereafter H17]{2017MNRAS.465.1454H}.
+For current cosmic shear surveys, the estimated systematic error is becoming comparable in size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[][hereafter H17]{2017MNRAS.465.1454H}.
 With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
@@
 
-One systematic effect is the variation of depth in a survey.
-While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions that are found in ground-based surveys.
-To first order, this variation can be modelled by a piece-wise constant depth function, which varies from pointing to pointing.
-In this work we assume the specifications of the Kilo-Degree Survey \citep[KiDS,][]{Kuijken:2015}, namely an assembly of $1\,\text{deg}^2$ square fields.
-To quantify the depth, we chose the limiting magnitude of the $r$-band, as defined in \citet{2017A&A...604A.134D}, since it serves as the detection band and is thus most important for determining source galaxies.
+In this paper we focus on systematic effects induced by variation in survey depth that is so far unaccounted for in cosmic shear analyses \citep{Vale:2004}.
+For a fixed exposure time survey, varying atmospheric conditions, dithering strategies and galactic extinction all contribute to an inhomogeneous limiting magnitude as a function of sky position.
+In order to assess the impact of variable depth for current and future surveys we build an analytical model for the effect based on the survey specifications of the Kilo-Degree Survey \citep[KiDS,][]{Kuijken:2015}.
+To first order, the depth variation in KiDS can be modelled by a piece-wise constant depth function, which varies between each $1\,\text{deg}^2$ square pointing.
+KiDS object detection is defined in the $r-band$ as these images were chosen to be significantly deeper in comparison to the other optical and near-infra red filters.
+We therefore quantify survey depth with the limiting $r$-band magnitude, as defined in \citet{2017A&A...604A.134D}.
+We defer the study of multi-band variable depth and its impact on photometric redshift accuracy for future work.
 
@@
 \ref{sec:discussion} we will discuss our results and comment on the impact of our used simplifications.
-App.~A is reserved for detailed calculations that cannot be done in the main paper, in App.~B we introduce way to apply our model to a given survey footprint.
+In the appendices we present the full derivation of our model for finite field surveys.
+%App.~A is reserved for detailed calculations that cannot be done in the main paper, in App.~B we introduce way to apply our model to a given survey footprint.
 App.~C is reserved for figures and tables that cannot be displayed in the main body.
@@
 \label{sec:analytic_models}
-For our first analysis we assume that all the matter between sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
+For our first analysis we assume that all the matter between the sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
 If we now distribute sources at varying distances $D_{\rm s}$, two effects become apparent: Firstly, the lensing efficiency $D_{\rm{ds}}/D_{\rm s}$ varies, where $D_{\rm{ds}}$ is the distance between the lens plane and the respective source.
@@
 
-Assuming that the depth, and thus the source redshift population, only varies between pointings of the camera, an observer will measure a shear signal that is modified by a step-like depth-function, $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of the average depth.
+Assuming that the depth, and thus the source redshift population, only varies between pointings of the camera, an observer will measure a shear signal that is modified by a step-like depth-function, $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would experience if it were of the average depth.
 We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$. This implies that $\langle w(\bm{\theta})\rangle=0$ holds, where $\langle \cdot\rangle$ denotes the average over all pointings.

### 2019-10-09 paperdraft.tex
minor modifications

@@
 For this analysis we will follow the assumption that a deeper pointing shows a stronger shear signal $\gamma^{\rm{obs}}(\b\theta) = W(\b\theta)\gamma(\b\theta)$ as described above.
-In general, this is certainly not true.
 This assumption implies that a higher redshift just increases the amplitude of the shear signal, but as can clearly be seen by inspecting shear correlation functions of different redshift distributions, the change of the signal is extremely scale-dependent and not just a multiplication with a constant factor.
-However, it should serve as a reasonable first approximation for small variations in mean source redshift.
+In other words, not just the average shear changes as a function of redshift, but also its entire two-point statistics.
+However, this should serve as a reasonable first approximation for small variations in mean source redshift.
 Additionally, we assume that a greater depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.
 
-Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17.
+Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies\footnote{Instead of using the actual number of galaxies, we take the effective number density times respective area, as defined in \citet{Kuijken:2015}.
 Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.} per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
@@
 Ignoring correlations higher than second order in $n^i$ and $w^i$,\footnote{It is not inherently obvious that this is a valid assumption.
-However, after performing calculations with and without higher-order correlations, the largest relative difference between the outcomes of both equations was less then $5\times 10^{-4}$.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we get
+However, after performing calculations with and without the inclusion of higher-order correlations, the largest relative difference between the outcomes of both equations was less than $5\times 10^{-4}$.} and performing the same calculation for the denominator of Eq.\,\eqref{eq:xipmblub1}, we find
  \begin{align}
@@
 \end{figure}
-The previously derived analytic model describes how varying depth between pointings modifies the correlation function due to the correlation between number density and average redshift of source galaxies.
+The previously derived analytic model describes how varying depth between pointings modifies the correlation function due to the correlation between number density and the average redshift of source galaxies.
 While this model serves as an intuitive first approximation, it completely ignores any effects from the large scale structure (LSS) between the closest and the most distant galaxy.
@@
 Below we derive a more sophisticated model that includes the effects of the LSS.
-While it is computationally more expensive, it yields accurate results for cosmic shear surveys, which are sensitive to the exact redshift distributions of sources as well as the underlying cosmology.
+While it is computationally more expensive, it improves the accuracy of the model for cosmic shear surveys, which are sensitive to the exact redshift distributions of sources as well as the underlying cosmology.
 
@@
 \end{align}
-Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
+Consequently, we can apply this to Eq.~\eqref{eq:correctionfunction1}, yielding
 \begin{align}
@@
   \includegraphics[width=0.9\linewidth]{images/xis_all1.pdf}
-  \caption{The ratio of modelled to observed correlation functions for a cross-correlation of all redshift bins.
-Plotted are the semi-analytic method (blue), the numerical simulations (red) as well as the analytic method (green) with the first and second method of estimating the weight function, as described in the beginning of Sec.~\ref{sec:results}.
-The dashed part of the red line represents the region in which the limited resolution affects the simulations by more than 10\%.
-The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
+  \caption{The ratio of correlation functions measured for a uniform depth survey, $\xi_\pm$, and a KiDS-like variable depth survey, $\xi_\pm^{\rm obs}$, cross-correlating five tomographic bins (as denoted in the upper left corner of each panel).
+Results from mock KiDS-like data (red) can be compared to analytic models from Sect.~2 (average redshift weighting in green-solid, and auto-correlation $\xi_+$ weighting in green-dashed) and the semi-analytic model from Sect.~4 (blue).
+Mock data is limited to the angular regime which is not significantly impacted by resolution effects.The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
 The semi-analytic model was computed for the best-fit cosmology of H18.

### 2019-10-09 paperdraft.tex
minor modifications

@@
 
-It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis by \citet{2018arXiv180706209P}.
+%It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis by \citet{2018arXiv180706209P}.
 While their analysis determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from an analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data, and the Dark Energy Survey \citep[DES,][]{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
@@
 Reweighting the obtained redshifts of data from DES and combining this with KiDS data \citep[][Asgari et al.~in prep.]{Joudaki:2019}, yields even higher tension with the value determined for $S_8$ by the Planck Collaboration.
-This discrepancy has received a lot of attention \citep{2017MNRAS.471.1259J,2019arXiv190103686S,2019arXiv190911006T}.
+This discrepancy has received a lot of attention.
 It could be interpreted as a statistical coincidence, a sign of new physics like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P}; or as the manifestation of a systematic effect, either in the cosmic shear surveys or in the Planck mission \citep{2016ApJ...818..132A}, that is not yet accounted for.

### 2019-10-09 paperdraft.tex
minor modifications

@@
 \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from an analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data, and \citet{2018PhRvD..98d3528T} constrain $S_8=0.782\pm 0.027$ using the Dark Energy Survey (DES).
-Combined analyses of DES and KiDS data \citep{Joudaki:2019, asgari/etal:2019} results in a $\sim 3 \sigma S_8$ tension with the CMB value.
+Combined analyses of DES and KiDS data \citep{Joudaki:2019, asgari/etal:2019} results in a $\sim 3 \sigma$ tension with the CMB value for $S_8$.
 If this tension is not the manifestation of an unaccounted systematic effect, in either the cosmic shear surveys \citep{Mandelbaum:2019} or the Planck mission \citep{2016ApJ...818..132A}, it certainly merits attention.
@@
 
+\subsection{Effect on the shear correlation functions}
+
 We applied both analytic methods and the semianalytic one to data from KV450, following the separation into tomographic bins as in H18, and computed the ratio between our model for the observed correlation functions, $\xi_{\pm}^{\rm{obs}}$, and the model correlation functions, $\xi_{\pm}$, ignoring variations in depth.
@@
 
+\subsection{Impact on cosmological parameter constraints}
+
 As the next step we want to assess how the observational depth variations propagate to cosmological parameters inferred from $\xi_\pm^{ij,\rm{obs}}$ compared to $\xi_\pm^{ij}$.
@@
 Here, the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$.
-It should be noted that while Euclid is a space-based mission, the photometric redshift determination will be performed using several ground-based telescopes, which means that Euclid will suffer from variations in depth that are at least as large as in KiDS.
-While the data from LSST will be practically free of variations in depth after 10 years of observations, their first-year data will equally suffer from this effect.
+We note that even though Euclid is a space-based mission, and therefore will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.
+Placing a selection criteria on redshift estimation success will therefore lead to depth variations in the source galaxy sample.
+While the data from LSST will be practically free of variations in depth after 10 years of observations, the first few years data will include significant depth variation.
+The impact may be even stronger than the KiDS-like analysis presented here as the multi-band KiDS depth variation was minimised using seeing-dependent data acquisition.
+This is in contrast to the seeing-agnostic multi-band cadence of LSST.
 
@@
 For various combinations of $\Omega_{\rm{m}}$ and $\sigma_8$ within the $95\%$ confidence limit of KV450, we report a variation in $\xi_\pm/\xi_\pm^{\rm{obs}}$ of a few percentage points on small scales.
+
+\subsection{Variable depth contribution to B-modes}
 
@@
 We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
-However, we compare the B-Modes to the ones measured by Asgari et al.~(in prep.) in KV450, which were consistent with zero.
+However, we compare the B-Modes to the ones measured by \citet{asgari/etal:2019} in KV450, which were consistent with zero.
 Since the B-modes created by varying depth are smaller than these by a factor of 50, we conclude that this effect cannot create measurable B-modes in the KV450 survey.
@@
 We have shown that this effect can create B-modes.
-However, Asgari et al.
-(in prep.) measured the B-modes of the KV450 survey in the same $\theta$-range.
+However, \citet{asgari/etal:2019} measured the B-modes of the KV450 survey in the same $\theta$-range.
 The results are consistent with zero, yet their statistical fluctuations are larger than the B-modes created by varying depth by a factor of approx.~$50$.
@@
 
-For next-generation surveys like Euclid, this effect will be significant.
-Considering our quite rough assumptions regarding the variation in depth and the covariance matrix of the Euclid-survey, a study using a realistic variation of depth and covariance matrix should be conducted.
-
-While the cosmology dependence (Fig.
-\ref{fig:comparecosmo}) is not significant for the KV450 survey, it will be relevant for the Euclid survey.
-In that case, a calculation of the correction for this effect is necessary for various cosmologies.
+For next-generation surveys like Euclid and LSST we have demonstrated that if variable depth in unaccounted for in the analysis, the resulting bias is likely to be significant.
+A detailed LSST and Euclid study that uses a realistic variation of depth should therefore be conducted.
+If these studies reach a similar conclusion, variable-depth bias could be circumvented in likelihood analyses by including a cosmology-dependent correction for this effect using the semi-analytical model presented in this paper (see Fig.
+\ref{fig:comparecosmo}).
 
@@
 
-The variation in depth will also affect the covariance of a survey, both because they modify the signal and because they introduce an additional term of sample variance in terms of the distribution of depth.
-This effect will be investigated in a forthcoming publication.
+The variations in depth will also affect the covariance of a survey, both because they modify the signal and because they introduce an additional term of sample variance in terms of the distribution of depth.
+This effect will be investigated in a forthcoming publication (Joachimi, Lin, et al.
+in prep.).
 

### 2019-10-09 paperdraft.tex
added the first batch of catherine's suggestion

@@
 With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
-
-To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}.
-To leading order, B-modes cannot be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
-The most useful E- and B-mode decomposition for cosmic shear surveys is provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs,][hereafter S10]{2010A&A...520A.116S}, as it can easily be applied to real data.
-Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
 
@@
 It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, so we expect the observed and the modelled correlation functions to be equivalent on scales where the depth is uncorrelated.
+One thing left to determine is how to define the weight-function $W(\b\theta)$.
+For this, we will refer the reader to the beginning of Sec.~\ref{sec:results}.
 
@@
 
-We compare our models to the results measured from numerical simulations.
-Using a modified version (Joachimi, Lin, et al.
-in prep.) of Full-sky Lognormal Astro-fields Simulation Kit \citep[FLASK,][]{Xavier:2016}, we generate galaxy mocks with coherent clustering and lensing signals from lognormal fields.
-For each lognormal field, one mock with uniform depth and another one with variable depth is generated.
-In the variable case, the depth of KiDS-1000 data \citep{Kuijken:2019} is binned by magnitude into roughly 20 bins.
-Afterwards, a linear relation between depth and effective number density is extracted.
-The KiDS-1000 survey is put on a Healpix grid, and for each pixel the limiting magnitude is calculated.
-According to this limiting magnitude, an effective number density can be assigned, using the linear relation extracted above.
-For each pixel and each tomographic redshift bin we use the same limiting magnitude to assign an average source redshift distribution from the ones extracted in this work.
-In the uniform case, redshifts and number densities are sampled from the average of these tomographic sets.
-Finally, the ratio of the average lensing signals from the two mocks is computed.
-The number of realizations is 2000.
-Shape noise is omitted.
+We compare our models to mock KiDS-like data created using a modified version of the Full-sky Lognormal Astro-fields Simulation Kit \citep[\sc{FLASK},][Joachimi, Lin, et al.
+in prep.]{Xavier:2016}.
+Using {\sc{FLASK}} lognormal fields, we generate galaxy mocks with coherent clustering and lensing signals.
+Adopting a linear relation between the limiting $r$-band magnitude and the effective number density, fit to the KiDS data, we imprint the variable depth of the full KiDS-1000 footprint \citep{Kuijken:2019} on a {\sc{Healpix}}\footnote{\url{https://healpix.sourceforge.io}} grid of Nside=4096 (add cite for Healpix).
+Our resolution choice represents a compromise between minimising the mock computation time and maximising the accuracy of the recovered shear signal at small angular scales.
+With Nside=4096 $\xi_+$ is accurate to 7\% above ~1 arcmin, and $\xi_-$ is accurate to 10\% above ~6 arcmin.
+For each \sc{Healpix} pixel in the KiDS-1000 data, the limiting $r$-band magnitude defines the effective number density of sources, and the average source redshift distribution for each tomographic redshift bin (see Fig.~\ref{fig:nofz_quantiles}).
+In the uniform depth case, redshifts and number densities are sampled from the average of these tomographic sets.
+The ratio of the lensing signals from the two mocks is computed, averaged over 2000 shape-noise-free realizations, and is shown in Fig.~\ref{fig:all_xis} (red).
 
@@
 
+To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}.
+To leading order, B-modes cannot be created by astrophysical phenomena and are thus an excellent test for remaining systematics.
+Direct E- and B-mode decomposition for cosmic shear surveys can be provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs,][hereafter S10]{2010A&A...520A.116S}, as they can easily be applied to real data.
+Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
 To estimate the B-modes created by this effect, we extract the COSEBIs
@@
 It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield a significant detection of B-modes.
+Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey \citep[see][]{2018arXiv181002353A}.
 
@@
 
-We have shown that this effect can create B-modes.
-However, \citet{asgari/etal:2019} measured the B-modes of the KV450 survey in the same $\theta$-range.
-The results are consistent with zero, yet their statistical fluctuations are larger than the B-modes created by varying depth by a factor of approx.~$50$.
-Thus it is safe to say that varying depth does not create any measurable B-modes in the KV450 survey.
-An interesting observation is that the change in E-modes is as large as the created B-modes (compare Fig.~\ref{fig:bmodes_cosebi}).
-This means that as soon as this effect causes a significant bias in the cosmological parameters, it will also create significant B-modes.
-Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey \citep[see][]{2018arXiv181002353A}.
-
 For next-generation surveys like Euclid and LSST we have demonstrated that if variable depth in unaccounted for in the analysis, the resulting bias is likely to be significant.
@@
 \begin{acknowledgements}
-The KV450 results in this paper are based on data products from observations
-made with ESO Telescopes at the La Silla Paranal Observatory under programme
-IDs 177.A-3016, 177.A-3017 and 177.A-3018, and on data products produced by
-Target/OmegaCEN, INAF-OACN, INAF-OAPD and the KiDS production team,
-on behalf of the KiDS consortium.
+The results in this paper are based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 177.A-3016, 177.A-3017, 177.A-3018 and 179.A-2004, and on data products produced by the KiDS consortium.
+The KiDS production team acknowledges support from: Deutsche Forschungsgemeinschaft, ERC, NOVA and NWO-M grants; Target; the University of Padova, and the University Federico II (Naples).
 \\
 \emph{Author contributions:} All authors contributed to the development and writing of this paper.
-The authorship list is given in two groups: the lead authors (SH, PS, HHi) followed by key contributors to either the scientific analysis or the data products in alphabetical order.
+The authorship list is given in two groups: the lead authors (SH, PS, HHi) followed by key contributors to the scientific analysis in alphabetical order.
+\\
+H. Hildebrandt is supported by a Heisenberg grant of the Deutsche Forschungsgemeinschaft (Hi 1495/5-1) as well as an ERC Consolidator Grant (No. 770935).
+\\
+KK acknowledges support by the Alexander von Humboldt Foundation.
+\\
+Some of the results in this paper have been derived using the HEALPix \citep{2005ApJ...622..759G} package.
 \\
@@
 \label{sec:calc of xipm}
-Following H17, given a set of galaxies we calculate the shear correlation function $\xi_+^{ij}$ via \begin{equation}
+Given a set of galaxies we calculate the shear correlation function $\xi_+^{ij}$ via \begin{equation}
 \xi^{ij}_+(\theta) = \frac{\sum_{a,b}w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*}\Delta(|\b\theta_a^i-\b\theta_b^i|)}{\sum_{a,b}w_a^iw_b^j\Delta(|\b\theta_a^i-\b\theta_b^i|)}\, .
@@
 \end{figure}
-In this chapter we will outline how to calculate the correction of the correlation functions for a finite survey with a potentially correlated distribution of depth between pointings.
+In this appendix we will outline how to calculate the correction of the correlation functions for a finite survey with a potentially correlated distribution of depth between pointings.
 Essentially, this boils down to the calculation of $\mathcal{P}_{mn}^{ij}(\theta)$ from Eq.~\eqref{eq:def_xiobs}.

### 2019-10-10 paperdraft.tex
added the first batch of catherine's suggestion

@@
 
-Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies\footnote{Instead of using the actual number of galaxies, we take the effective number density times respective area, as defined in \citet{Kuijken:2015}.
+Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies\footnote{Instead of using the actual number of galaxies, we take the effective number density, as defined in \citet{Kuijken:2015}, scaled by the respective survey area.
 Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.} per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
@@
 \, .
+\label{eq:xipm_analytic}
 \end{align}
@@
 \label{sec:results}
-Here we apply both the analytic and the semi-analytic method to model the data from the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018}.
+We compare the analytic and semi-analytic models for a variable-depth cosmic shear measurement in a KiDS-like survey.
 While the application of the semi-analytic method is straightforward, for the analytic method we need to decide how to estimate the weight function $W$ from the given redshift data.
@@
 
-We applied both analytic methods and the semianalytic one to data from KV450, following the separation into tomographic bins as in H18, and computed the ratio between our model for the observed correlation functions, $\xi_{\pm}^{\rm{obs}}$, and the model correlation functions, $\xi_{\pm}$, ignoring variations in depth.
+In this Section we calculate both the analytic (Eq.~\ref{eq:xipm_analytic}) and semi-analytic (Eq.~\ref{eq:correctionfunction2}) models for the shear correlation function from a KiDS-like variable depth survey.
+We adopt the tomographic bins defined in H18 and their resulting best-fit cosmological parameters to present, in Fig.~\ref{fig:all_xis}, the ratio between our models for the observed correlation functions $\xi_\pm^{\rm{obs}}$, and the standard theoretical prediction that assumes uniform depth.
+We find that the level of variation in the depth of the KiDS survey increases the amplitude of the observed shear correlation function, on sub-pointing scales, by up to 5\% relative to the uniform-depth case.
 
@@
 With Nside=4096 $\xi_+$ is accurate to 7\% above ~1 arcmin, and $\xi_-$ is accurate to 10\% above ~6 arcmin.
-For each \sc{Healpix} pixel in the KiDS-1000 data, the limiting $r$-band magnitude defines the effective number density of sources, and the average source redshift distribution for each tomographic redshift bin (see Fig.~\ref{fig:nofz_quantiles}).
+For each {\sc{Healpix}} pixel in the KiDS-1000 data, the limiting $r$-band magnitude defines the effective number density of sources, and the average source redshift distribution for each tomographic redshift bin (see Fig.~\ref{fig:nofz_quantiles}).
 In the uniform depth case, redshifts and number densities are sampled from the average of these tomographic sets.

### 2019-10-11 paperdraft.tex
added the second batch of catherine's suggestion

@@
 Results from mock KiDS-like data (red) can be compared to analytic models from Sect.~2 (average redshift weighting in green-solid, and auto-correlation $\xi_+$ weighting in green-dashed) and the semi-analytic model from Sect.~4 (blue).
-Mock data is limited to the angular regime which is not significantly impacted by resolution effects.The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
+Mock data is limited to the angular regime which is not significantly impacted by resolution effects.The upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
 The semi-analytic model was computed for the best-fit cosmology of H18.
-For the characteristic scale $\theta_{\rm{ref}}$ of the second analytic method we chose $\theta_{\rm{ref}} \approx 11'$.}
+For the characteristic scale $\theta_{\rm{ref}}$ of the second analytic method we chose $\theta_{\rm{ref}} \approx 11'$.
+Note that the seemingly better agreement between the mocks and the analytic method is purely coincidental.}
   \label{fig:all_xis}
@@
 Due to the redshift-dependent index in the power law of the first analytic method, it is not able to accurately describe the effect for low redshift bins.
-The second analytic method, however, traces the semi-analytic one pretty well for $\xi_+$.
-As $\xi_-$ is affected much stronger by this effect, the analytic method is not able to trace this change\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
+%The second analytic method, however, traces the semi-analytic one pretty well for $\xi_+$.
+The second analytic model is entirely dependent on the choice of $\theta_{\rm{ref}}$.
+For $\theta_{\rm{ref}}=11'$, as chosen here, both analytic models agree very well for all redshift bins.
+For $\theta_{\rm{ref}}=0.\!'5$, the second analytic method agrees with the semi-analytic one pretty well for $\xi_+$.
+As $\xi_-$ is affected much stronger by this effect\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
 This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$.
 However, $\xi_-$ is obtained by filtering with the 4-th order Bessel function, which peaks at approximately $\ell\theta\approx 5$, so for different $\theta$ this function is sensitive to varying parts of the convergence power spectrum.
-A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}.
+A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}, the analytic method is not able to trace this change for any choice of $\theta_{\rm{ref}}$.
 Furthermore we note that the effect seems to be strongest in the first redshift bin, which is not surprising, as there the average redshift between pointings varies the most (compare Fig.
@@
 It is noticeable that in the simulations, the value $\xi_\pm/\xi_\pm^{\rm{obs}}$ consistently stays below unity at large scales, which can be attributed to the fact that the depth of different pointings is not completely uncorrelated, as was assumed in the models.
-Furthermore, we notice some strong features in the simulations at lower values of $\theta$, which arise due to the resolution limit of the simulations.
+%Furthermore, we notice some strong features in the simulations at lower values of $\theta$, which arise due to the resolution limit of the simulations.
 %As the noise of the simulated correlation functions increases for decreasing $\theta$,\footnote{The logarithmic bins for the correlation functions were chosen in H17 such that the signal-to-noise ratio is roughly equal for each bin.
@@
 These tests suggest that both small-scale effects and a finer magnitude binning at least partly negate the varying depth between pointings.
+Note that the seemingly better agreement between mocks and the analytic method is purely coincidental.
 
@@
 \end{subfigure}
-\caption{Results of the MCMC simultation to estimate the bias caused by a variation of depth in a cosmic shear survey for a KiDS-like (left) and 'Euclid-like' survey (right).
+\caption{Results of the MCMC simultation to estimate the bias caused by a variation of depth in a cosmic shear survey for a KiDS450-like (left) and KiDS$15\,000$-like survey (right).
 The left simulation was computed using the covariance matrix of H18.
-As Euclid will survey approx.
-$15\,000\,\rm{deg}^2$, the covariance matrix of the 'Euclid-like' survey is the one of H18 divided by 30.
-Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
+As Euclid will cover approx.
+$15\,000\,\rm{deg}^2$, the covariance matrix of the KiDS$15\,000$-like survey is the one of H18 divided by 30.
+Note that this does not include the higher number density and better shape measurements of Euclid, so that thi Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
 \label{fig:mcmc_results}
@@
 As can be seen in Fig.~\ref{fig:mcmc_results}, the impact of varying depth is insignificant compared to the uncertainties.
-To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30, to approximately account for the increased survey area of LSST and Euclid with respect to KV450.
+To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30 to model a a KiDS$15\,000$-like survey, which approximately accounts for the increased survey area of LSST and Euclid with respect to KV450.
 Here, the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$.
+As our modified covariance-matrix does not account for higher number densities and better shape measurements, this is just a lower estimate; the real effect will probably be up to twice as big.
 We note that even though Euclid is a space-based mission, and therefore will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.
@@
 H. Hildebrandt is supported by a Heisenberg grant of the Deutsche Forschungsgemeinschaft (Hi 1495/5-1) as well as an ERC Consolidator Grant (No. 770935).
+\\
+CH acknowledges support from the European Research Council under grant number 647112, and support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
 \\

### 2019-10-11 paperdraft.tex
added the second batch of catherine's suggestion

@@
 Note that due to the depth-function, both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
+This estimator provides a natural extension to the definition of the regular power spectrum and, in the case of a homogeneous depth distribution, reduces back to the original estimator.
 To model a constant depth on each individual pointing, $\b \alpha$, we can choose random variables, $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$.
@@
 The choice of other values for $\theta_{\rm{ref}}$ leads to a different amplitude of the change $\xi_\pm/\xi_\pm^{\rm{obs}}$, but does not affect its shape.
-In particular, the highest amplitude of the change is at $\theta_{\rm{ref}}=0.\!'5$.
+Generally, a smaller $\theta_{\rm{ref}}$ leads to a stronger effect, in particular, the highest amplitude of the change is at $\theta_{\rm{ref}}=0.\!'5$.
 

### 2019-10-11 paperdraft.tex
added the second batch of catherine's suggestion

@@
 Using {\sc{FLASK}} lognormal fields, we generate galaxy mocks with coherent clustering and lensing signals.
-Adopting a linear relation between the limiting $r$-band magnitude and the effective number density, fit to the KiDS data, we imprint the variable depth of the full KiDS-1000 footprint \citep{Kuijken:2019} on a {\sc{Healpix}}\footnote{\url{https://healpix.sourceforge.io}} grid of Nside=4096 (add cite for Healpix).
+Adopting a linear relation between the limiting $r$-band magnitude and the effective number density, fit to the KiDS data, we imprint the variable depth of the full KiDS-1000 footprint \citep{Kuijken:2019} on a {\sc{Healpix}}\footnote{\url{https://healpix.sourceforge.io}} grid of Nside=4096.
 Our resolution choice represents a compromise between minimising the mock computation time and maximising the accuracy of the recovered shear signal at small angular scales.
-With Nside=4096 $\xi_+$ is accurate to 7\% above ~1 arcmin, and $\xi_-$ is accurate to 10\% above ~6 arcmin.
+With Nside=4096, $\xi_+$ is accurate to 7\% above $\sim 1$ arcmin, and $\xi_-$ is accurate to 10\% above $\sim6$ arcmin.
 For each {\sc{Healpix}} pixel in the KiDS-1000 data, the limiting $r$-band magnitude defines the effective number density of sources, and the average source redshift distribution for each tomographic redshift bin (see Fig.~\ref{fig:nofz_quantiles}).

### 2019-10-11 paperdraft.tex
added the second batch of catherine's suggestion

@@
 $15\,000\,\rm{deg}^2$, the covariance matrix of the KiDS$15\,000$-like survey is the one of H18 divided by 30.
-Note that this does not include the higher number density and better shape measurements of Euclid, so that thi Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
+Note that this does not include the higher number density and better shape measurements of Euclid, so that this figure constitutes an extremely conservative estimate on this effect for Euclid.
+Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
 \label{fig:mcmc_results}
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width = 0.9\linewidth]{images/ebmodes0p5t72.pdf}
+\caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions.
+For comparison: Scaled total E-modes of the reference correlation function $E_n$ and scaled B-modes measured in the KV450 survey $B_n^{\rm{KV450}}$.
+All E- and B-modes were calculated using the logarithmic COSEBIs in S10 for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.}
+\label{fig:bmodes_cosebi}
+\end{figure*}
+
 To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}.
@@
 Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey \citep[see][]{2018arXiv181002353A}.
-
-\begin{figure*}
-\centering
-\includegraphics[width = 0.9\linewidth]{images/ebmodes0p5t72.pdf}
-\caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions.
-For comparison: Scaled total E-modes of the reference correlation function $E_n$ and scaled B-modes measured in the KV450 survey $B_n^{\rm{KV450}}$.
-All E- and B-modes were calculated using the logarithmic COSEBIs in S10 for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.}
-\label{fig:bmodes_cosebi}
-\end{figure*}
 

### 2019-10-11 paperdraft.tex
corrected more things

--- 2019-10-11 paperdraft.tex
@@
   \abstract
-   {Cosmic shear proves to be a powerful tool to study the properties of the Universe.
-The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the low-redshift large-scale structure and the cosmic microwave background motivates further investigation of yet unaccounted systematic biases.
-   Ground-based surveys are subject to a variation in depth caused by varying atmospheric conditions; we investigate and quantify the resulting effects.
-In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
-   We construct a semi-analytic model to estimate the impact on the shear correlation functions and analyse the implications for cosmological parameters.
-Furthermore, we construct COSEBIs from the correlation functions to quantify the occurring B-modes.
-   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales.
-We find that the resulting bias in $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ will be significant at the level of about $1\sigma$ in next-generation cosmic shear surveys.
-We find that the dependence of this effect on the underlying cosmology is not negligible.
-We also report the occurrence of B-modes, although at a level that is more than one order of magnitude below the current statistical uncertainties.
-   We conclude that the effects of varying depth for current cosmic shear surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.
+   {We present a semi-analytic model for the shear two-point correlation function of a cosmic shear survey with non-uniform depth.
+Ground-based surveys are subject to depth variations that primarily arise through varying atmospheric conditions.
+For a survey like the Kilo-Degree Survey (KiDS), we find that the measured depth variation increases the amplitude of the observed shear correlation function at the level of a few percent out to degree-scales, relative to the assumed uniform-depth case.
+The impact on the inferred cosmological parameters is shown to be insignificant for a KiDS-like survey.
+For next-generation cosmic shear experiments, however, we conclude that variable depth should be accounted for.
 \textcolor{blue}{\href{https://docs.google.com/document/d/13j7fUE8jrK5HOVbf4p0HdQs6c14jbWtm9Yq8CtLZCK4/edit?usp=sharing}{[Link to the current google doc]}}}
@@
 
-For current cosmic shear surveys, the estimated systematic error is becoming comparable in size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[][hereafter H17]{2017MNRAS.465.1454H}.
-With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}.
+For current cosmic shear surveys, the estimated systematic error is becoming comparable in size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary.
+With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep[see][and references therein]{Mandelbaum:2019}.
 
@@
 To first order, the depth variation in KiDS can be modelled by a piece-wise constant depth function, which varies between each $1\,\text{deg}^2$ square pointing.
-KiDS object detection is defined in the $r-band$ as these images were chosen to be significantly deeper in comparison to the other optical and near-infra red filters.
+KiDS object detection is defined in the $r$-band as these images were chosen to be significantly deeper in comparison to the other optical and near-infra red filters.
 We therefore quantify survey depth with the limiting $r$-band magnitude, as defined in \citet{2017A&A...604A.134D}.
@@
 %\citep{10.1093/mnras/stx2082}.
-For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (see H17).
+For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies \citep[see][]{2017MNRAS.465.1454H}.
 If, for a single pair of galaxies, one galaxy lies in the $m$-th quantile of redshift bin $i$ and the second one lies in the $n$-th quantile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$.
@@
 
-We compare our models to mock KiDS-like data created using a modified version of the Full-sky Lognormal Astro-fields Simulation Kit \citep[\sc{FLASK},][Joachimi, Lin, et al.
+We compare our models to mock KiDS-like data created using a modified version of the Full-sky Lognormal Astro-fields Simulation Kit \citep[\textsc{FLASK},][Joachimi, Lin, et al.
 in prep.]{Xavier:2016}.
@@
   \end{figure*}
-%We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge.
-We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.
-We observe that for high-redshift bins, both analytic methods as well as the semi-analytic one yield consistent results.
-Due to the redshift-dependent index in the power law of the first analytic method, it is not able to accurately describe the effect for low redshift bins.
-%The second analytic method, however, traces the semi-analytic one pretty well for $\xi_+$.
-The second analytic model is entirely dependent on the choice of $\theta_{\rm{ref}}$.
+We observe that for high-redshift bins, all methods yield consistent results.
+For low-redshift bins, there are some serious discrepancies between the different models.
+The average-redshift weighted analytic model is only valid for high redshifts, whereas the auto-correlation $\xi_+$ weighted model is entirely dependent on the choice of $\theta_{\rm{ref}}$.
 For $\theta_{\rm{ref}}=11'$, as chosen here, both analytic models agree very well for all redshift bins.
@@
 \end{subfigure}
-\caption{Results of the MCMC simultation to estimate the bias caused by a variation of depth in a cosmic shear survey for a KiDS450-like (left) and KiDS$15\,000$-like survey (right).
+\caption{Recovered cosmological parameters for a variable-depth (Observed) and uniform-depth (Reference) KiDS-$450$-like (left) and KiDS-$15\,000$-like survey (right).
 The left simulation was computed using the covariance matrix of H18.
-As Euclid will cover approx.
-$15\,000\,\rm{deg}^2$, the covariance matrix of the KiDS$15\,000$-like survey is the one of H18 divided by 30.
-Note that this does not include the higher number density and better shape measurements of Euclid, so that thi Both simulations were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
+For the KiDS$15\,000$-like survey, we divided the one of H18 by 30.
+This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and better shape measurements, so that this figure constitutes a conservative estimate on this effect for Euclid and LSST.
+Both figures were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
 \label{fig:mcmc_results}
@@
 
-As can be seen in Fig.~\ref{fig:mcmc_results}, the impact of varying depth is insignificant compared to the uncertainties.
-To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30 to model a a KiDS$15\,000$-like survey, which approximately accounts for the increased survey area of LSST and Euclid with respect to KV450.
+As can be seen in Fig.~\ref{fig:mcmc_results}, the impact of varying depth is insignificant compared to the uncertainties for a KiDS-$450$-like survey.
+To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30 to model a KiDS-$15\,000$-like survey, which approximately accounts for the increased survey area of LSST and Euclid with respect to KiDS-450.
 Here, the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$.
-As our modified covariance-matrix does not account for higher number densities and better shape measurements, this is just a lower estimate; the real effect will probably be up to twice as big.
+As our modified covariance-matrix does not account for the factor of $\sim 4$ expected increase in galaxy number density for LSST and Euclid , we note that this likely to be a lower estimate for the significance of the effect.
  We note that even though Euclid is a space-based mission, and therefore will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.
@@
 \subsection{Variable depth contribution to B-modes}
+
+\begin{figure*}
+\centering
+\includegraphics[width = 0.9\linewidth]{images/ebmodes0p5t72.pdf}
+\caption{Difference in the E-modes (top left) and B-modes (bottom right) between the reference and the observed correlation functions.
+For comparison: Scaled total E-modes of the reference correlation function $E_n$ and scaled B-modes measured in the KV450 survey $B_n^{\rm{KV450}}$.
+All E- and B-modes were calculated using the logarithmic COSEBIs in S10 for an angular range of $\theta_{\rm{min}}=0.\!^\prime 5,\,\theta_{\rm{max}}=72\arcmin$.}
+\label{fig:bmodes_cosebi}
+\end{figure*}
 
@@
 Despite these repercussions, we are confident to say that the effects of varying depth are not significant for the KV450 survey.
-In particular this means that a varying depth cannot explain the discrepancy between observations of the low-redshift Universe and results from analysis of the CMB.
+In particular this means that a varying depth cannot explain the tension between observations of the low-redshift Universe and results from analysis of the CMB.
 
@@
 \\
-\emph{Author contributions:} All authors contributed to the development and writing of this paper.
-The authorship list is given in two groups: the lead authors (SH, PS, HHi) followed by key contributors to the scientific analysis in alphabetical order.
+We acknowledge support from the European Research Council under grant numbers 770935 (HH,JLvdB) and 647112 (CH,MA,CL).
 \\
-H. Hildebrandt is supported by a Heisenberg grant of the Deutsche Forschungsgemeinschaft (Hi 1495/5-1) as well as an ERC Consolidator Grant (No. 770935).
+H. Hildebrandt is supported by a Heisenberg grant of the Deutsche Forschungsgemeinschaft (Hi 1495/5-1).
 \\
-CH acknowledges support from the European Research Council under grant number 647112, and support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
+CH acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
 \\
@@
 This research has made use of NASA's Astrophysics Data System and adstex (\url{https://github.com/yymao/adstex}).
+\\
+\emph{Author contributions:} All authors contributed to the development and writing of this paper.
+The authorship list is given in two groups: the lead authors (SH, PS, HHi) followed by key contributors to the scientific analysis in alphabetical order.
 \end{acknowledgements}

### 2019-10-11 paperdraft.tex
corrected more things

@@
 We observe that for high-redshift bins, all methods yield consistent results.
-For low-redshift bins, there are some serious discrepancies between the different models.
-The average-redshift weighted analytic model is only valid for high redshifts, whereas the auto-correlation $\xi_+$ weighted model is entirely dependent on the choice of $\theta_{\rm{ref}}$.
+For low-redshift bins, there are discrepancies between the different models.
+However, the average-redshift weighted analytic model is only valid for high redshifts, whereas the auto-correlation $\xi_+$ weighted model is entirely dependent on the choice of $\theta_{\rm{ref}}$.
 For $\theta_{\rm{ref}}=11'$, as chosen here, both analytic models agree very well for all redshift bins.
-For $\theta_{\rm{ref}}=0.\!'5$, the second analytic method agrees with the semi-analytic one pretty well for $\xi_+$.
+For $\theta_{\rm{ref}}=0.\!'5$, the auto-correlation weighted method agrees with the semi-analytic one pretty well for $\xi_+$.
 As $\xi_-$ is affected much stronger by this effect\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
@@
 \caption{Recovered cosmological parameters for a variable-depth (Observed) and uniform-depth (Reference) KiDS-$450$-like (left) and KiDS-$15\,000$-like survey (right).
-The left simulation was computed using the covariance matrix of H18.
-For the KiDS$15\,000$-like survey, we divided the one of H18 by 30.
-This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and better shape measurements, so that this figure constitutes a conservative estimate on this effect for Euclid and LSST.
+The KiDS-$450$-like figure was computed using the covariance matrix of H18.
+For the KiDS-$15\,000$-like survey, we divided the one of H18 by 30.
+This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and better shape measurements.
+Therefore, this figure constitutes a conservative estimate of this effect for Euclid and LSST.
 Both figures were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}

### 2019-10-11 paperdraft.tex
corrected more things

@@
 This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and better shape measurements.
-Therefore, this figure constitutes a conservative estimate of this effect for Euclid and LSST.
+Therefore, this figure constitutes a conservative estimate for the effect of variable depth for Euclid and LSST.
 Both figures were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
@@
 Here, the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$.
-As our modified covariance-matrix does not account for the factor of $\sim 4$ expected increase in galaxy number density for LSST and Euclid , we note that this likely to be a lower estimate for the significance of the effect.
- We note that even though Euclid is a space-based mission, and therefore will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.
+As our modified covariance-matrix does not account for the factor of $\sim \!
+4$ expected increase in galaxy number density for LSST and Euclid, we note that this likely to be a lower estimate for the significance of the effect.
+ Even though Euclid is a space-based mission, and therefore will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.
 Placing a selection criteria on redshift estimation success will therefore lead to depth variations in the source galaxy sample.

### 2019-10-11 paperdraft.tex
corrected more things

@@
 \label{sec:xipm_semianalytic}
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{images/cov_nz_meanz.pdf}
-\caption{Weighted number of galaxies $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
-Each colour corresponds to one redshift bin of H18.
-A single point represents one quantile of the respective redshift bin, where the fainter points denote pointings of shallower depth.}
-\label{fig:nz_of_meanz}
-\end{figure}
 The previously derived analytic model describes how varying depth between pointings modifies the correlation function due to the correlation between number density and the average redshift of source galaxies.
@@
 %
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{images/cov_nz_meanz.pdf}
+\caption{Weighted number of galaxies $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
+Each colour corresponds to one redshift bin of H18.
+A single point represents one quantile of the respective redshift bin, where the fainter points denote pointings of shallower depth.}
+\label{fig:nz_of_meanz}
+\end{figure}
+
 \begin{figure}
@@
  &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\gamma(\b \theta)\gamma^*(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta')\ra\nonumber\\
- &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta') \int \frac{\text{d}^2 k}{(2\pi)^2}\int \frac{\text{d}^2 \ell}{(2\pi)^2}\, \hat{\gamma}(\b k)\hat{\gamma}^*(\b \ell)\exp(-\i \b k\b \theta+\i \b \ell\b \theta')\ra \nonumber\\
-&\qquad = \la \int \text{d}^2 \theta \int \text{d}^2 \theta' \int \frac{\text{d}^2 k}{(2\pi)^2} \int \frac{\text{d}^2 \ell}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b \ell) \exp[\i (\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b \ell\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
-  &\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \int \text{d}^2 \theta\, W(\b \theta)\exp[\i\b \theta(\b \ell-\b k)]\int \text{d}^2 \theta'\, W(\b \theta') \exp[-\i\b \theta(\b \ell'-\b k)] \ra \nonumber\\
+ &\qquad = \la\int\text{d}^2 \theta\int\text{d}^2 \theta'\,W(\b \theta)W(\b \theta')\exp(\i \b \ell\b \theta-\i \b \ell'\b \theta') \int \frac{\text{d}^2 k}{(2\pi)^2}\int \frac{\text{d}^2 k'}{(2\pi)^2}\, \hat{\gamma}(\b k)\hat{\gamma}^*(\b k')\exp(-\i \b k\b \theta+\i \b k'\b \theta')\ra \nonumber\\
+&\qquad = \la \int \text{d}^2 \theta \int \text{d}^2 \theta' \int \frac{\text{d}^2 k}{(2\pi)^2} \int \frac{\text{d}^2 k'}{(2\pi)^2}\, P(\b k)(2\pi)^2 \delta(\b k-\b k') \exp[\i (\b \ell\b \theta-\b \ell'\b \theta'-\b k\b \theta+\b k'\b \theta')]W(\b \theta)W(\b \theta')\ra \nonumber\\
+  &\qquad = \la \int \frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k) \int \text{d}^2 \theta\, W(\b \theta)\exp[\i\b \theta(\b \ell-\b k)]\int \text{d}^2 \theta'\, W(\b \theta') \exp[-\i\b \theta'(\b \ell'-\b k)] \ra \nonumber\\
   &\qquad = \la \int\frac{\text{d}^2 k}{(2\pi)^2} \, P(\b k)\widehat{W}(\b \ell-\b k)\widehat{W}^* (\b \ell'-\b k)\ra

### 2019-10-16 paperdraft.tex
added ack
minor changes

@@
 For $\theta_{\rm{ref}}=11'$, as chosen here, both analytic models agree very well for all redshift bins.
-For $\theta_{\rm{ref}}=0.\!'5$, the auto-correlation weighted method agrees with the semi-analytic one pretty well for $\xi_+$.
+For $\theta_{\rm{ref}}=0.\!'5$ (not shown), the auto-correlation weighted method agrees with the semi-analytic one pretty well for $\xi_+$.
 As $\xi_-$ is affected much stronger by this effect\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
@@
 The KiDS-$450$-like figure was computed using the covariance matrix of H18.
-For the KiDS-$15\,000$-like survey, we divided the one of H18 by 30.
-This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and better shape measurements.
-Therefore, this figure constitutes a conservative estimate for the effect of variable depth for Euclid and LSST.
+For the KiDS-$15\,000$-like survey, we divided the covariance matrix of H18 by 30.
+This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and higher redshifts.
+Therefore, this figure constitutes a lower estimate for the effect of variable depth for Euclid and LSST.
 Both figures were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
@@
 KK acknowledges support by the Alexander von Humboldt Foundation.
+\\
+TT acknowledges funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sk{l}odowska-Curie grant agreement No 797794.
 \\

### 2019-10-17 paperdraft.tex
minor changes

@@
 This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and higher redshifts.
-Therefore, this figure constitutes a lower estimate for the effect of variable depth for Euclid and LSST.
+Hence, this exercise probably still underestimates the significance of varying depth effects in stage IV surveys.
 Both figures were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
@@
 which is a convolution of the power spectrum and the 2-dimensional sinc function \eqref{eq:sinc}.
+
+Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail.
+In particular, the Fourier transform of the observed power spectrum yields $\langle \gamma(\b 0)\gamma^*(\b\theta)\rangle$, but not the shear correlation function.
 \label{sec:calc of PS}

### 2019-10-18 paperdraft.tex
minor changes
added new explanation for discrepancy

@@
 \usepackage{verbatim}
+\usepackage{xcolor}
 %
@@
 For the characteristic scale $\theta_{\rm{ref}}$ of the second analytic method we chose $\theta_{\rm{ref}} \approx 11'$.
-Note that the seemingly better agreement between the mocks and the analytic method is purely coincidental.}
+Note that the seemingly better agreement between the mocks and the analytic method is purely coincidental; as the mocks only take galaxies with $z<2$ into account, they slightly underestimate the effect.}
   \label{fig:all_xis}
@@
 However, in the simulations we ignore shape-noise, such that our only noise contribution is sample variance, which increases at lower $\theta$.} and we take the ratio of two functions that are subject to noise, these features can be attributed to sample variance.
-In general, the semi-analytic model seems to over-estimate the effect compared to the simulations, which take the full distribution of depth into account.
+%In general, the semi-analytic model seems to over-estimate the effect compared to the simulations, which take the full distribution of depth into account.
 This slight discrepancy could be attributed to the fact that the simulations follow a finer magnitude-binning for the number densities of galaxies.
@@
 
+\textcolor{blue}{In general, the semi-analytic model predicts a stronger effect than the mocks.
+This is due to the fact that the mocks are subject to a redshift-cutoff at $z=2$, meaning that they do not take the high-redshift tail of galaxies into account.
+When the same cutoff is applied to the models, the agreement on sub-pointing scales is striking (compare Fig.~\ref{fig:redshift_cutoff} in the Appendix).}
+
 \begin{figure*}
@@
 This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and higher redshifts.
-Hence, this exercise probably still underestimates the significance of varying depth effects in stage IV surveys.
+Hence, this exercise provides a rough indication of the significance of varying depth effects in stage IV surveys.
 Both figures were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
@@
 \centering
+\includegraphics[width=0.9\linewidth]{images/xis_all_cutoff.pdf}
+\caption{The same Figure as Fig.~\ref{fig:all_xis}, but in this case the redshift distributions $p_n^i(z)$ were set equal to zero for $z>2$ in the models to mimick the redshift-cutoff in the mocks.}
+\label{fig:redshift_cutoff}
+\end{figure}
+\begin{figure}[h]
+\centering
 \includegraphics[width=0.9\linewidth]{images/compare_cosmos.pdf}

### 2019-10-18 paperdraft.tex
added new explanation for discrepancy

@@
 \includegraphics[width=0.9\linewidth]{images/xis_all_cutoff.pdf}
-\caption{The same Figure as Fig.~\ref{fig:all_xis}, but in this case the redshift distributions $p_n^i(z)$ were set equal to zero for $z>2$ in the models to mimick the redshift-cutoff in the mocks.}
+\caption{The same Figure as Fig.~\ref{fig:all_xis}, but in this case the redshift distributions $p_n^i(z)$ were set equal to zero for $z>2$ in the models to mimick the redshift-cutoff in the mocks.
+Any residual differences are explained by the sub-pointing depth variations that are accounted for in the mocks, but not in the models.
+These variations slightly reduce the effect of varying depth.}
 \label{fig:redshift_cutoff}

### 2019-10-21 paperdraft.tex
added peter's suggestions

@@
 \documentclass{aa}
-\usepackage{hyperref}
+
+%\documentclass[referee]{aa}
+\pdfoutput=1
+
+\usepackage[hidelinks]{hyperref}
 
@@
 This is due to the fact that the mocks are subject to a redshift-cutoff at $z=2$, meaning that they do not take the high-redshift tail of galaxies into account.
-When the same cutoff is applied to the models, the agreement on sub-pointing scales is striking (compare Fig.~\ref{fig:redshift_cutoff} in the Appendix).}
+This is of particular importance in the first redshift bin, where this feature is especially pronounced (compare Fig.~\ref{fig:nofz_quantiles}).
+When the same cutoff is applied to the models, the agreement on sub-pointing scales is striking (compare Fig.~\ref{fig:redshift_cutoff} in the Appendix).
+In particular this means that the mocks slightly underestimate the effect of varying depth.}
 
@@
 The KiDS production team acknowledges support from: Deutsche Forschungsgemeinschaft, ERC, NOVA and NWO-M grants; Target; the University of Padova, and the University Federico II (Naples).
-\\
 We acknowledge support from the European Research Council under grant numbers 770935 (HH,JLvdB) and 647112 (CH,MA,CL).
-\\
+SH acknowledges support from the German Research Foundation (DFG SCHN 342/13).
 H. Hildebrandt is supported by a Heisenberg grant of the Deutsche Forschungsgemeinschaft (Hi 1495/5-1).
-\\
 CH acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
-\\
 KK acknowledges support by the Alexander von Humboldt Foundation.
-\\
 TT acknowledges funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sk{l}odowska-Curie grant agreement No 797794.
-\\
 Some of the results in this paper have been derived using the HEALPix \citep{2005ApJ...622..759G} package.
-\\
 This research has made use of NASA's Astrophysics Data System and adstex (\url{https://github.com/yymao/adstex}).

### 2019-10-21 paperdraft.tex
added peter's suggestions

@@
 Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail.
-In particular, the Fourier transform of the observed power spectrum yields $\langle \gamma(\b 0)\gamma^*(\b\theta)\rangle$, but not the shear correlation function.
+In particular, $\langle \gamma(\theta)\gamma^*(\theta')\rangle$ does not only depend on the separation vector $\theta'-\theta$, but also on the position $\theta$.
+For example, the Fourier transform of the observed power spectrum yields $\langle \gamma(\b 0)\gamma^*(\b\theta)\rangle$, but not the shear correlation function.
 \label{sec:calc of PS}

### 2019-10-21 paperdraft.tex
added peter's suggestions

@@
 \usepackage[hidelinks]{hyperref}
+% \usepackage[section]{placeins}
 
@@
 which is a convolution of the power spectrum and the 2-dimensional sinc function \eqref{eq:sinc}.
-
 Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail.
@@
 \label{sec:model_e}
-When computing the shear correlation between a pair of galaxies, it is of central importance whether those two galaxies lie in the same pointing or not.
-We want to model the probability that a pair of galaxies with separation $\b\theta$ lie in the same pointing by the function $E(\b\theta)$, which we will derive here:
-
 {
@@
 }
+When computing the shear correlation between a pair of galaxies, it is of central importance whether those two galaxies lie in the same pointing or not.
+We want to model the probability that a pair of galaxies with separation $\b\theta$ lie in the same pointing by the function $E(\b\theta)$, which we will derive here:
 Given one square field of length $L$ (in our case $L=60\arcmin$) and a separation vector $\b\theta = (\theta_1,\theta_2)$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
@@
 
-\begin{figure}
+\begin{figure}[!htb]
 \centering
@@
 
+% \clearpage
 \section{Additional Figures and Tables}
-\begin{table}[h]
+\begin{table}[!htb]
 \centering
@@
 \end{table}
-\begin{figure}[h]
+\begin{figure}[!htb]
 \centering
@@
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[!htb]
 \centering

### 2019-10-22 paperdraft.tex
added peter's suggestions

@@
 
-%\documentclass[referee]{aa}
+% \documentclass[referee]{aa}
 \pdfoutput=1
@@
 
-   \date{Received XXX; accepted XXX}
+   \date{Received 21 October 2019; accepted XXX}
 
@@
 The impact on the inferred cosmological parameters is shown to be insignificant for a KiDS-like survey.
-For next-generation cosmic shear experiments, however, we conclude that variable depth should be accounted for.
-\textcolor{blue}{\href{https://docs.google.com/document/d/13j7fUE8jrK5HOVbf4p0HdQs6c14jbWtm9Yq8CtLZCK4/edit?usp=sharing}{[Link to the current google doc]}}}
+For next-generation cosmic shear experiments, however, we conclude that variable depth should be accounted for.}
 
-   \keywords{gravitational lensing --
-                weak lensing --
-                cosmic shear
-               }
-
+   % \keywords{gravitational lensing --
+   %              weak lensing --
+   %              cosmic shear
+   %             }
+   \keywords{gravitational lensing: weak -- cosmology: miscellaneous}
    \maketitle
@@
 
-\textcolor{blue}{In general, the semi-analytic model predicts a stronger effect than the mocks.
+In general, the semi-analytic model predicts a stronger effect than the mocks.
 This is due to the fact that the mocks are subject to a redshift-cutoff at $z=2$, meaning that they do not take the high-redshift tail of galaxies into account.
@@
 When the same cutoff is applied to the models, the agreement on sub-pointing scales is striking (compare Fig.~\ref{fig:redshift_cutoff} in the Appendix).
-In particular this means that the mocks slightly underestimate the effect of varying depth.}
+In particular this means that the mocks slightly underestimate the effect of varying depth.
 
@@
 Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail.
-In particular, $\langle \gamma(\theta)\gamma^*(\theta')\rangle$ does not only depend on the separation vector $\theta'-\theta$, but also on the position $\theta$.
+In particular, $\langle \gamma(\b \theta)\gamma^*(\b \theta')\rangle$ does not only depend on the separation vector $\b \theta'-\b \theta$, but also on the position $\b \theta$.
 For example, the Fourier transform of the observed power spectrum yields $\langle \gamma(\b 0)\gamma^*(\b\theta)\rangle$, but not the shear correlation function.

### 2019-10-23 paperdraft.tex
typo

@@
 
-For next-generation surveys like Euclid and LSST we have demonstrated that if variable depth in unaccounted for in the analysis, the resulting bias is likely to be significant.
+For next-generation surveys like Euclid and LSST we have demonstrated that if variable depth is unaccounted for in the analysis, the resulting bias is likely to be significant.
 A detailed LSST and Euclid study that uses a realistic variation of depth should therefore be conducted.

### 2019-10-23 paperdraft_ver2.tex
added ver2, showing the alternative Fig 4

--- 2019-10-23 paperdraft.tex
@@
 While the first method suffers from the fact that the power-law index only holds for sources of redshifts $1\lesssim z \lesssim 2$, the second method is sensitive to the angular range $\theta_{\rm{ref}}$, at which the shear correlation functions are evaluated, which is fairly arbitrary.
-In our case, we chose $\theta_{\rm{ref}}\approx 11'$, which is roughly in the logarithmic middle between the range of the correlation functions, $[0.\!'5,300']$.
+For $\theta_{\rm{ref}}\approx 11'$, which is roughly in the logarithmic middle between the range of the correlation functions, $[0.\!'5,300']$, the two calibration methods agree pretty well.
 The choice of other values for $\theta_{\rm{ref}}$ leads to a different amplitude of the change $\xi_\pm/\xi_\pm^{\rm{obs}}$, but does not affect its shape.
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/xis_all1.pdf}
+  \includegraphics[width=0.9\linewidth]{images/xis_all2.pdf}
   \caption{The ratio of correlation functions measured for a uniform depth survey, $\xi_\pm$, and a KiDS-like variable depth survey, $\xi_\pm^{\rm obs}$, cross-correlating five tomographic bins (as denoted in the upper left corner of each panel).
-Results from mock KiDS-like data (red) can be compared to analytic models from Sect.~2 (average redshift weighting in green-solid, and auto-correlation $\xi_+$ weighting in green-dashed) and the semi-analytic model from Sect.~4 (blue).
-Mock data is limited to the angular regime which is not significantly impacted by resolution effects.The upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
-The semi-analytic model was computed for the best-fit cosmology of H18.
-For the characteristic scale $\theta_{\rm{ref}}$ of the second analytic method we chose $\theta_{\rm{ref}} \approx 11'$.
-Note that the seemingly better agreement between the mocks and the analytic method is purely coincidental; as the mocks only take galaxies with $z<2$ into account, they slightly underestimate the effect.}
+The upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
+Results from mock KiDS-like data (red) can be compared to analytic models from Sect.~2 (average redshift weighting, green), and the semi-analytic model from Sect.~3 (blue solid).
+Mock data is limited to the angular regime which is not significantly impacted by resolution effects.
+As the mocks only take galaxies with $z<2$ into account, they slightly underestimate the effect.
+Applying the same redshift-cutoff to the semi-analytical model (blue dashed) yields a near-perfect agreement on sub-pointing scales.
+Therefore, the seemingly better agreement between the mocks and the analytic method is purely coincidental.
+The semi-analytic model was computed for the best-fit cosmology of H18.}
   \label{fig:all_xis}
@@
 For low-redshift bins, there are discrepancies between the different models.
-However, the average-redshift weighted analytic model is only valid for high redshifts, whereas the auto-correlation $\xi_+$ weighted model is entirely dependent on the choice of $\theta_{\rm{ref}}$.
-For $\theta_{\rm{ref}}=11'$, as chosen here, both analytic models agree very well for all redshift bins.
-For $\theta_{\rm{ref}}=0.\!'5$ (not shown), the auto-correlation weighted method agrees with the semi-analytic one pretty well for $\xi_+$.
+However, the average-redshift weighted analytic model, as shown here, is only valid for high redshifts, whereas the auto-correlation $\xi_+$ weighted model (not shown) is entirely dependent on the choice of $\theta_{\rm{ref}}$.
+For $\theta_{\rm{ref}}=11'$, both analytic models agree very well for all redshift bins.
+For $\theta_{\rm{ref}}=0.\!'5$, the auto-correlation weighted method agrees with the semi-analytic one pretty well for $\xi_+$.
 As $\xi_-$ is affected much stronger by this effect\footnote{The effect on $\xi_-$ is much stronger due to the fact that in Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function.
@@
 This is of particular importance in the first redshift bin, where this feature is especially pronounced (compare Fig.~\ref{fig:nofz_quantiles}).
-When the same cutoff is applied to the models, the agreement on sub-pointing scales is striking (compare Fig.~\ref{fig:redshift_cutoff} in the Appendix).
+When the same cutoff is applied to the models, the agreement on sub-pointing scales is striking.
 In particular this means that the mocks slightly underestimate the effect of varying depth.
@@
 \centering
-\includegraphics[width=0.9\linewidth]{images/xis_all_cutoff.pdf}
-\caption{The same Figure as Fig.~\ref{fig:all_xis}, but in this case the redshift distributions $p_n^i(z)$ were set equal to zero for $z>2$ in the models to mimick the redshift-cutoff in the mocks.
-Any residual differences are explained by the sub-pointing depth variations that are accounted for in the mocks, but not in the models.
-These variations slightly reduce the effect of varying depth.}
-\label{fig:redshift_cutoff}
-\end{figure}
-\begin{figure}[!htb]
-\centering
 \includegraphics[width=0.9\linewidth]{images/compare_cosmos.pdf}

### 2019-11-19 Heydenreich_et_al.tex
added referee comments

--- 2019-10-23 paperdraft_ver2.tex
@@
 \usepackage{txfonts}
-\usepackage{subcaption}
+% \usepackage{subcaption}
 %\usepackage{hyperref}
@@
 We defer the study of multi-band variable depth and its impact on photometric redshift accuracy for future work.
+
+{\bf So far the effects of varying depth have not been extensively studied: \citet{Guzik:2005} investigate the effect of a general, position-dependent multiplicative shear bias on the shear power spectrum through simulations, but do not perform a quantitative analysis.
+Furthermore, varying depth was one of the effects included in mock catalogs in the Subaru Hyper Suprime-Cam Survey \citep{Shirasaki:2019}, but they did not discuss its implications in detail.
+}
 
@@
 While the first method suffers from the fact that the power-law index only holds for sources of redshifts $1\lesssim z \lesssim 2$, the second method is sensitive to the angular range $\theta_{\rm{ref}}$, at which the shear correlation functions are evaluated, which is fairly arbitrary.
-For $\theta_{\rm{ref}}\approx 11'$, which is roughly in the logarithmic middle between the range of the correlation functions, $[0.\!'5,300']$, the two calibration methods agree pretty well.
-The choice of other values for $\theta_{\rm{ref}}$ leads to a different amplitude of the change $\xi_\pm/\xi_\pm^{\rm{obs}}$, but does not affect its shape.
+{\bf For $\theta_{\rm{ref}}\approx 11'$, which is roughly in the logarithmic middle between the range of the correlation functions, $[0.\!'5,300']$, the two calibration methods agree.} The choice of other values for $\theta_{\rm{ref}}$ leads to a different amplitude of the change $\xi_\pm/\xi_\pm^{\rm{obs}}$, but does not affect its shape.
 Generally, a smaller $\theta_{\rm{ref}}$ leads to a stronger effect, in particular, the highest amplitude of the change is at $\theta_{\rm{ref}}=0.\!'5$.
@@
 Using {\sc{FLASK}} lognormal fields, we generate galaxy mocks with coherent clustering and lensing signals.
-Adopting a linear relation between the limiting $r$-band magnitude and the effective number density, fit to the KiDS data, we imprint the variable depth of the full KiDS-1000 footprint \citep{Kuijken:2019} on a {\sc{Healpix}}\footnote{\url{https://healpix.sourceforge.io}} grid of Nside=4096.
+Adopting a linear relation between the limiting $r$-band magnitude and the effective number density, fit to the KiDS data, we imprint the variable depth of the full KiDS-1000 footprint \citep{Kuijken:2019} on a {\sc{Healpix}}\footnote{\url{https://healpix.sourceforge.io}} grid of $\text{Nside}=4096$.
 Our resolution choice represents a compromise between minimising the mock computation time and maximising the accuracy of the recovered shear signal at small angular scales.
-With Nside=4096, $\xi_+$ is accurate to 7\% above $\sim 1$ arcmin, and $\xi_-$ is accurate to 10\% above $\sim6$ arcmin.
+With $\text{Nside}=4096$, $\xi_+$ is accurate to 7\% above $\sim 1$ arcmin, and $\xi_-$ is accurate to 10\% above $\sim6$ arcmin.
 For each {\sc{Healpix}} pixel in the KiDS-1000 data, the limiting $r$-band magnitude defines the effective number density of sources, and the average source redshift distribution for each tomographic redshift bin (see Fig.~\ref{fig:nofz_quantiles}).
@@
   \includegraphics[width=0.9\linewidth]{images/xis_all2.pdf}
-  \caption{The ratio of correlation functions measured for a uniform depth survey, $\xi_\pm$, and a KiDS-like variable depth survey, $\xi_\pm^{\rm obs}$, cross-correlating five tomographic bins (as denoted in the upper left corner of each panel).
+  \caption{\bf The ratio of correlation functions measured for a uniform depth survey, $\xi_\pm$, and a KiDS-like variable depth survey, $\xi_\pm^{\rm{obs}}$, cross-correlating five tomographic bins (as denoted in the upper left corner of each panel).
 The upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
@@
 Therefore, the seemingly better agreement between the mocks and the analytic method is purely coincidental.
-The semi-analytic model was computed for the best-fit cosmology of H18.}
+The models adopt the best-fit cosmology of H18.}
   \label{fig:all_xis}
@@
 For low-redshift bins, there are discrepancies between the different models.
-However, the average-redshift weighted analytic model, as shown here, is only valid for high redshifts, whereas the auto-correlation $\xi_+$ weighted model (not shown) is entirely dependent on the choice of $\theta_{\rm{ref}}$.
-For $\theta_{\rm{ref}}=11'$, both analytic models agree very well for all redshift bins.
+However, the average-redshift weighted analytic model, {\bf as shown here, is only valid for high redshifts, whereas the auto-correlation-$\xi_+$-weighted model (not shown) is entirely dependent on the choice of $\theta_{\rm{ref}}$.} For $\theta_{\rm{ref}}=11'$, both analytic models agree very well for all redshift bins.
 For $\theta_{\rm{ref}}=0.\!'5$, the auto-correlation weighted method agrees with the semi-analytic one pretty well for $\xi_+$.
@@
 \begin{figure*}
-\begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
-\end{subfigure}
-\begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
-\end{subfigure}
+% \begin{subfigure}{0.45\textwidth}
+$
+\begin{array}{cc}
+\includegraphics[width=0.45\textwidth]{images/mcmc_kids.pdf}&
+% \end{subfigure}
+% \begin{subfigure}{0.45\textwidth}
+\includegraphics[width=0.45\textwidth]{images/mcmc_euclid.pdf}
+% \end{subfigure}
+\end{array}$
 \caption{Recovered cosmological parameters for a variable-depth (Observed) and uniform-depth (Reference) KiDS-$450$-like (left) and KiDS-$15\,000$-like survey (right).
@@
 
+{\bf Although the analytic model (Eq.~\ref{eq:xipm_analytic}) does not fully describe the effect, it can be used as a valid approximation to estimate the importance of varying depth for an arbitrary survey: As can be seen in Fig.~\ref{fig:nz_of_meanz}, in the KiDS-survey the characteristic changes both in redshift and number density for the third redshift bin are about $0.1$.
+Setting $\la n^in^j\ra=\la w^iw^j\ra=\la n^iw^j\ra = 0.01$ yields $\xi^{ij}_\pm/\xi_\pm^{ij,\rm{obs}}(0)\approx 0.97$, which roughly agrees with the actual results (see Fig.~\ref{fig:all_xis}).
+For a survey with only half the variation in depth, one gets $\xi^{ij}_\pm/\xi_\pm^{ij,\rm{obs}}(0)\approx 0.993$.
+This method allows us to estimate a threshold for an acceptable variation of depth, given a required precision for the shear correlation functions.}
+
 %As an outlook it would be interesting to perform a full MCMC simulation, including both cosmological and nuisance parameters.
@@
 \begin{acknowledgements}
+{\bf We thank the anonymous referee for very constructive and helpful comments.}
 The results in this paper are based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 177.A-3016, 177.A-3017, 177.A-3018 and 179.A-2004, and on data products produced by the KiDS consortium.
@@
 \sidecaption
-\begin{subfigure}[c]{6cm}
+$
+\begin{array}{cc}
+% \begin{subfigure}[c]{6cm}
 \def\svgwidth{100pt}
 \hspace*{1cm}
-\input{images/e_1.pdf_tex}
-\end{subfigure}
-\begin{subfigure}[c]{6cm}
+\input{images/e_1.pdf_tex}&
+% \end{subfigure}
+% \begin{subfigure}[c]{6cm}
 \def\svgwidth{100pt}
@@
 \input{images/e_2.pdf_tex}
-\end{subfigure}
+% \end{subfigure}
+\end{array}$
 \caption[How to calculate $E_{01}(\theta)$]{Representation of how to calculate $E_{01}(\theta)$ for different values of $\theta$.

### 2019-11-19 Heydenreich_et_al.tex
added referee comments
added catherine's suggestion

@@
 \usepackage{txfonts}
+\usepackage[section]{placeins}
 % \usepackage{subcaption}
@@
 
-{\bf So far the effects of varying depth have not been extensively studied: \citet{Guzik:2005} investigate the effect of a general, position-dependent multiplicative shear bias on the shear power spectrum through simulations, but do not perform a quantitative analysis.
-Furthermore, varying depth was one of the effects included in mock catalogs in the Subaru Hyper Suprime-Cam Survey \citep{Shirasaki:2019}, but they did not discuss its implications in detail.
+{\bf This work is complementary to the analysis of \citet{Guzik:2005} who investigate the effect of a general, position-dependent multiplicative shear bias on the shear power spectrum.
+In principle the varying depth of the source galaxy sample that we study here could be recast as a varying effective shear bias.
+The inclusion of an inhomogeneous distribution of source galaxies has also been explored using mock catalogs of the Subaru Hyper Suprime-Cam Survey \citep{Shirasaki:2019}, with a focus on resulting estimation of the cosmic shear covariance matrix.
+
 }

### 2019-12-16 Heydenreich_et_al.tex
accepted version

@@
 
-   \date{Received 21 October 2019; accepted XXX}
+   \date{Received 21 October 2019; accepted 02 December 2019}
 
@@
 The discovery of cosmic shear has provided us with a new and powerful cosmological tool to empirically test the standard model of cosmology and to determine its parameters.
-Contrary to the analysis of the cosmic microwave background \citep[CMB, e.g.~by][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the low-redshift large-scale structure and thus provides an excellent consistency check for the standard model.
+Contrary to the analysis of the cosmic microwave background \citep[CMB, e.g.,~by][]{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the low-redshift large-scale structure and, thus, provides an excellent consistency check for the standard model.
 Current cosmic shear surveys are particularly sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ characterizes the normalization of the matter power spectrum and $\Omega_{\rm m}$ is the matter density parameter.
 Constraints on $S_8$ from the three current major cosmic shear results are all consistent with the CMB analysis by \citet{2018arXiv180706209P}.
-It is interesting to note, however, that they all favour values that are slightly lower than the Planck constraints of $S_8 = 0.830 \pm 0.013$.
+It is interesting to note, however, that they all favor values that are slightly lower than the Planck constraints of $S_8 = 0.830 \pm 0.013$.
 \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from an analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data, and \citet{2018PhRvD..98d3528T} constrain $S_8=0.782\pm 0.027$ using the Dark Energy Survey (DES).
-Combined analyses of DES and KiDS data \citep{Joudaki:2019, asgari/etal:2019} results in a $\sim 3 \sigma$ tension with the CMB value for $S_8$.
+Combined analyses of DES and KiDS data \citep{Joudaki:2019, asgari/etal:2019} result in a $\sim 3 \sigma$ tension with the CMB value for $S_8$.
 If this tension is not the manifestation of an unaccounted systematic effect, in either the cosmic shear surveys \citep{Mandelbaum:2019} or the Planck mission \citep{2016ApJ...818..132A}, it certainly merits attention.
-It could be interpreted as a sign of new physics with examples like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P} and coupling within the dark sector \citep{Kumar:2019}.
-It could also, however, be a simple statistical coincidence.
+It could be interpreted as a sign of new physics exemplified by massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy, or modified gravity \citep{2016A&A...594A..14P} and coupling within the dark sector \citep{Kumar:2019}.
+It could also, however, prove to be a simple statistical coincidence.
 
@@
 
-For current cosmic shear surveys, the estimated systematic error is becoming comparable in size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary.
-With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep[see][and references therein]{Mandelbaum:2019}.
+For current cosmic shear surveys, the estimated systematic error is becoming comparable in magnitude to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary.
+With surveys like the Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic:2008} and Euclid \citep{Laureijs:2011} soon to begin, systematic effects in gravitational lensing have received a large amount of attention \citep[see][and references therein]{Mandelbaum:2019}.
 
-In this paper we focus on systematic effects induced by variation in survey depth that is so far unaccounted for in cosmic shear analyses \citep{Vale:2004}.
-For a fixed exposure time survey, varying atmospheric conditions, dithering strategies and galactic extinction all contribute to an inhomogeneous limiting magnitude as a function of sky position.
-In order to assess the impact of variable depth for current and future surveys we build an analytical model for the effect based on the survey specifications of the Kilo-Degree Survey \citep[KiDS,][]{Kuijken:2015}.
-To first order, the depth variation in KiDS can be modelled by a piece-wise constant depth function, which varies between each $1\,\text{deg}^2$ square pointing.
+In this paper, we focus on systematic effects induced by variation in survey depth that is so far unaccounted for in cosmic shear analyses \citep{Vale:2004}.
+For a survey with a fixed exposure time, varying atmospheric conditions, dithering strategies and galactic extinction all contribute to an inhomogeneous limiting magnitude as a function of sky position.
+In order to assess the impact of variable depth for current and future surveys, we build an analytical model for the effect based on the survey specifications of the Kilo-Degree Survey \citep[KiDS,][]{Kuijken:2015}.
+To the first order, the depth variation in KiDS can be modeled by a piece-wise constant depth function, which varies between each $1\,\text{deg}^2$ square pointing.
 KiDS object detection is defined in the $r$-band as these images were chosen to be significantly deeper in comparison to the other optical and near-infra red filters.
-We therefore quantify survey depth with the limiting $r$-band magnitude, as defined in \citet{2017A&A...604A.134D}.
-We defer the study of multi-band variable depth and its impact on photometric redshift accuracy for future work.
+We, therefore, quantify survey depth with the limiting $r$-band magnitude, as defined in \citet{2017A&A...604A.134D}.
+We defer the study of multi-band variable depth and its impact on photometric redshift accuracy for a future work.
 
-{\bf This work is complementary to the analysis of \citet{Guzik:2005} who investigate the effect of a general, position-dependent multiplicative shear bias on the shear power spectrum.
-In principle the varying depth of the source galaxy sample that we study here could be recast as a varying effective shear bias.
+This work is complementary to the analysis of \citet{Guzik:2005}, who investigate the effect of a general, position-dependent multiplicative shear bias on the shear power spectrum.
+In principle, the varying depth of the source galaxy sample that we study here could be recast as a varying effective shear bias.
 The inclusion of an inhomogeneous distribution of source galaxies has also been explored using mock catalogs of the Subaru Hyper Suprime-Cam Survey \citep{Shirasaki:2019}, with a focus on resulting estimation of the cosmic shear covariance matrix.
-
-}
 
@@
 In Sect.
-\ref{sec:analytic_models} we will introduce two simple toy models to understand this effect and analyze the impact on the cosmic shear power spectrum.
+\ref{sec:analytic_models}, we will introduce two simple toy models to understand this effect and analyze the impact on the cosmic shear power spectrum.
 In Sect.
-\ref{sec:xipm_semianalytic} we will estimate the effect on the shear correlation functions $\xi_\pm$ using a semi-analytic model.
+\ref{sec:xipm_semianalytic}, we will estimate the effect on the shear correlation functions $\xi_\pm$ using a semi-analytic model.
 We will present our results in Sect.
@@
 In Sect.
-\ref{sec:discussion} we will discuss our results and comment on the impact of our used simplifications.
-In the appendices we present the full derivation of our model for finite field surveys.
+\ref{sec:discussion}, we will discuss our results and comment on the impact of our used simplifications.
+In the appendices, we present the full derivation of our model for finite field surveys.
 %App.~A is reserved for detailed calculations that cannot be done in the main paper, in App.~B we introduce way to apply our model to a given survey footprint.
 App.~C is reserved for figures and tables that cannot be displayed in the main body.
-We will assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
+We assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
 
@@
 \label{sec:analytic_models}
-For our first analysis we assume that all the matter between the sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
-If we now distribute sources at varying distances $D_{\rm s}$, two effects become apparent: Firstly, the lensing efficiency $D_{\rm{ds}}/D_{\rm s}$ varies, where $D_{\rm{ds}}$ is the distance between the lens plane and the respective source.
-Secondly, and more importantly, for a more distant source \emph{more} matter is concentrated between the source and the observer, leading to a stronger shear signal.
+For our first analysis, we assume that all the matter between the sources and observer is concentrated in a single lens plane of distance $D_{\rm d}$ from the observer.
+If we then distribute sources at varying distances $D_{\rm s}$, two effects become apparent: firstly, the lensing efficiency $D_{\rm{ds}}/D_{\rm s}$ varies, where $D_{\rm{ds}}$ is the distance between the lens plane and the respective source.
+Secondly, and more importantly, for a more distant source, more matter is concentrated between the source and the observer, leading to a stronger shear signal.
 
-Assuming that the depth, and thus the source redshift population, only varies between pointings of the camera, an observer will measure a shear signal that is modified by a step-like depth-function, $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would experience if it were of the average depth.
+Assuming that the depth and, thus, the source redshift population, only varies between pointings of the camera, an observer will measure a shear signal that is modified by a step-like depth-function, $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would experience if it were of the average depth.
 We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$. This implies that $\langle w(\bm{\theta})\rangle=0$ holds, where $\langle \cdot\rangle$ denotes the average over all pointings.
+
 \subsection{Modelling the power spectrum}
 \label{sec:modelling_power_spectrum}
-In our first model we describe the impact of varying depth on the power spectrum, following the simplifications described above.
+In our first model, we describe the impact of varying depth on the power spectrum, following the simplifications described above.
 % Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \begin{equation}
@@
 \end{equation}
-Note that due to the depth-function, both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
-This estimator provides a natural extension to the definition of the regular power spectrum and, in the case of a homogeneous depth distribution, reduces back to the original estimator.
+We note that due to the depth-function, both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
+This estimator provides a natural extension to the definition of the regular power spectrum and, in the case of a homogeneous depth distribution, is reduced back to the original estimator.
 To model a constant depth on each individual pointing, $\b \alpha$, we can choose random variables, $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$.
@@
 
-\subsection{Modelling the shear correlation functions}
+\subsection{Modeling the shear correlation functions}
 \label{sec:xipm_analytic}
-More convenient measures to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \begin{equation}
+Measures that are more convenient for the inference of cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \begin{equation}
 \xi_\pm(\theta) = \la \gamma_{\rm t}\gamma_{\rm t}\ra(\theta) \pm \la \gamma_\times\gamma_\times\ra(\theta) \, .
 \end{equation}
-Here, $\gamma_{\rm{t}}$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[see][]{2002A&A...396....1S}.
+Here, $\gamma_{\rm{t}}$ and $\gamma_\times$, denote the tangential and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[see][]{2002A&A...396....1S}.
 The shear correlation functions are the prime estimators to quantify a cosmic-shear signal, since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint or masked regions, or model the noise contribution.
-For this analysis we will follow the assumption that a deeper pointing shows a stronger shear signal $\gamma^{\rm{obs}}(\b\theta) = W(\b\theta)\gamma(\b\theta)$ as described above.
+For this analysis, we follow the assumption that a deeper pointing shows a stronger shear signal $\gamma^{\rm{obs}}(\b\theta) = W(\b\theta)\gamma(\b\theta)$ as described above.
 This assumption implies that a higher redshift just increases the amplitude of the shear signal, but as can clearly be seen by inspecting shear correlation functions of different redshift distributions, the change of the signal is extremely scale-dependent and not just a multiplication with a constant factor.
@@
 
-Let $N^i(\b \theta),N^j(\b\theta)$ be the average weighted number of galaxies\footnote{Instead of using the actual number of galaxies, we take the effective number density, as defined in \citet{Kuijken:2015}, scaled by the respective survey area.
-Due to this we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.} per pointing in redshift bins $i$ and $j$ and let $W^i(\b \theta),W^j(\b\theta)$ be the weighting of average shear.
+We denote by $N^i(\b \theta)$ the average weighted number of galaxies\footnote{Instead of using the actual number of galaxies, we take the effective number density, as defined in \citet{Kuijken:2015}, scaled by the respective survey area.
+Due to this, we account for different weighting of galaxies in the shear correlation functions as well as in the average redshift distribution.} per pointing in redshift bin $i$ and by $W^i(\b \theta)$ the weighting of average shear.
 The observed correlation functions $\xi^{ij,\text{obs}}_\pm(\theta)$ now change from uniform depth, $\xi_\pm^{ij,\rm{uni}}(\theta)$, via %\citep[see][]{2002A&A...396....1S}
@@
  \end{align}
- where the average $\la\cdot\ra$ represents both an ensemble average as well as an average over the position $\bth$.
+ where the average, $\la\cdot\ra$, represents both an ensemble average as well as an average over the position $\bth$.
  Assuming that the depth of different pointings is uncorrelated, the only important property of a galaxy pair is whether or not they lie in the same pointing.
-We want to denote the probability that a random galaxy pair of separation $\theta$ lies in the same pointing by $E(\theta)$.
+We denote the probability that a random galaxy pair of separation $\theta$ lies in the same pointing by $E(\theta)$.
 This function is depicted in Fig.
@@
  Ignoring that the depth is correlated on scales of one pointing (here at $\theta \leq \sqrt{2}^\circ$) is equivalent to setting $E(\theta)\equiv 0$.
-Note that there is still a correlation between $N$ and $W$ for the same galaxy.
+We note that there is still a correlation between $N$ and $W$ for the same galaxy.
 %For the calculation of the reference correlation functions $\xi_\pm^{ij}(\theta)$ we distribute the \textit{same} galaxies into our survey, only this time we will not order their weightings $W$ or their number densities $N$ by pointing.
@@
 This is equivalent to setting $E(\theta)\equiv 0$.
- Performing the same calculations as above, this yields a relation between the correlation function of uniform depth, $\xi_\pm^{ij,\rm{uni}}$, and the one that is usually modelled, $\xi_\pm^{ij}$:
+ Performing the same calculations as above, this yields a relation between the correlation function of uniform depth, $\xi_\pm^{ij,\rm{uni}}$, and the one that is usually modeled, $\xi_\pm^{ij}$:
 \begin{equation}
@@
 \end{equation}
-When an observer now calculates the model correlation functions $\xi^{ij}_\pm$ without accounting for varying depth between pointings, the ratio between modelled and observed correlation functions becomes: \begin{align}
+When an observer now calculates the model correlation functions $\xi^{ij}_\pm$ without accounting for varying depth between pointings, the ratio between modeled and observed correlation functions becomes: \begin{align}
 \frac{\xi^{ij}_\pm(\theta)}{\xi_\pm^{ij,\rm{obs}}(\theta)} \approx &  \left[1+\la n^iw^i\ra +\la n^jw^j\ra + E(\theta)\la n^in^j\ra\right] \nonumber\\
@@
 \end{align}
-It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, so we expect the observed and the modelled correlation functions to be equivalent on scales where the depth is uncorrelated.
+It is interesting to note that $\xi^{ij}_\pm = \xi_\pm^{ij,\rm{obs}}$ holds wherever $E(\theta)=0$, so we expect the observed and the modeled correlation functions to be equivalent on scales where the depth is uncorrelated.
 One thing left to determine is how to define the weight-function $W(\b\theta)$.
@@
 \label{sec:xipm_semianalytic}
-The previously derived analytic model describes how varying depth between pointings modifies the correlation function due to the correlation between number density and the average redshift of source galaxies.
+The previously derived analytic model describes, how varying depth between pointings modifies the correlation function due to the correlation between number density and the average redshift of source galaxies.
 While this model serves as an intuitive first approximation, it completely ignores any effects from the large scale structure (LSS) between the closest and the most distant galaxy.
@@
 An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the limiting magnitude in the $r$-band.
-We thus chose to separate the survey into 10 quantiles, sorted by $r$-band depth, i.e.
-if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first quantile, and so on.
+We thus chose to separate the survey into ten quantiles, sorted by $r$-band depth, that is, if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first quantile, and so on.
 For each quantile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the direct spectroscopic calibration method of H18.
-In Fig.~\ref{fig:nz_of_meanz} the average redshift and weighted number of galaxies are plotted for each quantile of each redshift bin, whereas a selection of source redshift distributions is depicted in Fig.~\ref{fig:nofz_quantiles}.
+In Fig.~\ref{fig:nz_of_meanz}, the average redshift and weighted number of galaxies are plotted for each quantile of each redshift bin, whereas a selection of source redshift distributions is depicted in Fig.~\ref{fig:nofz_quantiles}.
 A table of the limiting magnitudes for each quantile can be found in Tab.~\ref{tab:maglim}.
@@
 \caption{Weighted number of galaxies $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 survey \citep[KV450,][]{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18.
-Each colour corresponds to one redshift bin of H18.
+Each color corresponds to one redshift bin of H18.
 A single point represents one quantile of the respective redshift bin, where the fainter points denote pointings of shallower depth.}
@@
 \includegraphics[trim = {1cm 0 1.2cm 0.1cm}, clip, width=\linewidth]{images/dist_z_all.pdf}
-\caption{The source redshift distributions $p^i_m(z)$ for a selection of very shallow pointings (blue), average pointings (yellow) and very deep pointings (green).
+\caption{Source redshift distributions $p^i_m(z)$ for a selection of very shallow pointings (blue), average pointings (yellow) and very deep pointings (green).
 The percentage points in the legend denote to which quantile a pointing belongs, when all are ordered by their depth.}
@@
 
-Given two comoving distance probability distributions of sources, $\mathcal{L}^i_m(\chi)$ and $\mathcal{L}^j_n(\chi)$, we can compute the shear correlation functions from the underlying matter power spectrum, $P_\delta(k,\chi)$, via \citep{1992ApJ...388..272K} \begin{align}
+Given the two comoving distance probability distributions of sources, $\mathcal{L}^i_m(\chi)$ and $\mathcal{L}^j_n(\chi)$, we can compute the shear correlation functions from the underlying matter power spectrum, $P_\delta(k,\chi)$, via \citep{1992ApJ...388..272K} \begin{align}
 \label{eq:xipm-pkappa}
@@
 \end{align}
-Here, $J_n$ denote the $n$-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is the comoving distance to the horizon.
+Here, $J_n$ denotes the $n$-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is the comoving distance to the horizon.
 The parameters $H_0$ and $c$ denote the Hubble constant and the speed of light.
@@
 If, for a single pair of galaxies, one galaxy lies in the $m$-th quantile of redshift bin $i$ and the second one lies in the $n$-th quantile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$.
-This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions.
+This means that, if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions.
 Formally, we define \begin{equation}
@@
 
-To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1$ and $\d^2\b\theta_2$ of separation $\theta$ on the sky.
-For the case $m\neq n$ we know that the two galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ have to lie in different pointings, else they would automatically be in the same quantile.
+To calculate $\mathcal{P}_{mn}^{ij}(\theta)$, we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1$ and $\d^2\b\theta_2$ of separation $\theta$ on the sky.
+For the case $m\neq n$, we know that the two galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ have to lie in different pointings, else they would automatically be in the same quantile.
 The probability that the surface elements are within different pointings is $[1-E(\theta)]$.
@@
 \end{equation}
-For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxies lie in the same pointing, they automatically are in the same quantile.
+For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$, we have to account for a different possibility: In case that the galaxies lie in the same pointing, they automatically are in the same quantile.
 We therefore obtain \begin{equation}
@@
 
-Computing this for all 5 redshift bins of the KV450-survey, forces us to calculate and coadd 1275 correlation functions\footnote{For each of the 15 pairs of redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
+Computing this for all five redshift bins of the KV450-survey, forces us to calculate and co-add 1275 correlation functions\footnote{For each of the 15 pairs of redshift bins we need to calculate 100 correlation functions, except for the pairs of bins with the same redshift, where only 55 correlation functions need to be calculated due to symmetry.}.
 Since the variation in depth is a relatively small effect, even tiny numerical errors can add up, skewing the calculations.
@@
 However, if we examine Eq.~\eqref{eq:lenseff}, we see that the comoving distance distribution of sources enters linearly.
-This in turn implies that in Eqs.~\eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa}, both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
+This, in turn, implies that in Eqs.~\eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa}, both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that.
 In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average comoving distance probability distribution}, $\mathcal{L}^i(\chi)$, of tomographic bin $i$ as \begin{equation}
@@
 \end{align}
-For each pair of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
+For each pair of redshift bins we, thus, only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.
 
@@
 \end{equation}
-where $\la z\ra_n$ is the average redshift of quantile $n$. As a second method we define \begin{equation}
+where $\la z\ra_n$ is the average redshift of quantile $n$. As a second method, we define \begin{equation}
 W_n \propto \sqrt{ \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta_{\rm{ref}}) + \la \gamma_\times\gamma_\times\ra (\theta_{\rm{ref}})} = \sqrt{\xi_{+,nn}^{ij}(\theta_{\rm{ref}})}\, ,
@@
 While the first method suffers from the fact that the power-law index only holds for sources of redshifts $1\lesssim z \lesssim 2$, the second method is sensitive to the angular range $\theta_{\rm{ref}}$, at which the shear correlation functions are evaluated, which is fairly arbitrary.
-{\bf For $\theta_{\rm{ref}}\approx 11'$, which is roughly in the logarithmic middle between the range of the correlation functions, $[0.\!'5,300']$, the two calibration methods agree.} The choice of other values for $\theta_{\rm{ref}}$ leads to a different amplitude of the change $\xi_\pm/\xi_\pm^{\rm{obs}}$, but does not affect its shape.
+For $\theta_{\rm{ref}}\approx 11'$, which is roughly in the logarithmic middle between the range of the correlation functions, $[0.\!'5,300']$, the two calibration methods agree.
+The choice of other values for $\theta_{\rm{ref}}$ leads to a different amplitude of the change $\xi_\pm/\xi_\pm^{\rm{obs}}$, but does not affect its shape.
 Generally, a smaller $\theta_{\rm{ref}}$ leads to a stronger effect, in particular, the highest amplitude of the change is at $\theta_{\rm{ref}}=0.\!'5$.
@@
 
-In this Section we calculate both the analytic (Eq.~\ref{eq:xipm_analytic}) and semi-analytic (Eq.~\ref{eq:correctionfunction2}) models for the shear correlation function from a KiDS-like variable depth survey.
+In this Section, we calculate both the analytic (Eq.~\ref{eq:xipm_analytic}) and semi-analytic (Eq.~\ref{eq:correctionfunction2}) models for the shear correlation function from a KiDS-like variable depth survey.
 We adopt the tomographic bins defined in H18 and their resulting best-fit cosmological parameters to present, in Fig.~\ref{fig:all_xis}, the ratio between our models for the observed correlation functions $\xi_\pm^{\rm{obs}}$, and the standard theoretical prediction that assumes uniform depth.
@@
 
-We compare our models to mock KiDS-like data created using a modified version of the Full-sky Lognormal Astro-fields Simulation Kit \citep[\textsc{FLASK},][Joachimi, Lin, et al.
-in prep.]{Xavier:2016}.
+We compare our models to mock KiDS-like data created using a modified version of the Full-sky Lognormal Astro-fields Simulation Kit \citep[\textsc{FLASK},][Joachimi, Lin, et al., in prep.]{Xavier:2016}.
 Using {\sc{FLASK}} lognormal fields, we generate galaxy mocks with coherent clustering and lensing signals.
@@
   \includegraphics[width=0.9\linewidth]{images/xis_all2.pdf}
-  \caption{\bf The ratio of correlation functions measured for a uniform depth survey, $\xi_\pm$, and a KiDS-like variable depth survey, $\xi_\pm^{\rm{obs}}$, cross-correlating five tomographic bins (as denoted in the upper left corner of each panel).
+  \caption{Ratio of correlation functions measured for a uniform depth survey, $\xi_\pm$, and a KiDS-like variable depth survey, $\xi_\pm^{\rm{obs}}$, cross-correlating five tomographic bins (as denoted in the upper left corner of each panel).
 The upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.
@@
 For low-redshift bins, there are discrepancies between the different models.
-However, the average-redshift weighted analytic model, {\bf as shown here, is only valid for high redshifts, whereas the auto-correlation-$\xi_+$-weighted model (not shown) is entirely dependent on the choice of $\theta_{\rm{ref}}$.} For $\theta_{\rm{ref}}=11'$, both analytic models agree very well for all redshift bins.
+However, the average-redshift weighted analytic model, as shown here, is only valid for high redshifts, whereas the auto-correlation-$\xi_+$-weighted model (not shown) is entirely dependent on the choice of $\theta_{\rm{ref}}$.
+For $\theta_{\rm{ref}}=11'$, both analytic models agree very well for all redshift bins.
 For $\theta_{\rm{ref}}=0.\!'5$, the auto-correlation weighted method agrees with the semi-analytic one pretty well for $\xi_+$.
@@
 A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}, the analytic method is not able to trace this change for any choice of $\theta_{\rm{ref}}$.
-Furthermore we note that the effect seems to be strongest in the first redshift bin, which is not surprising, as there the average redshift between pointings varies the most (compare Fig.
+Furthermore we note, that the effect seems to be strongest in the first redshift bin, which is not surprising, as there the average redshift between pointings varies the most (compare Fig.
 \ref{fig:nz_of_meanz}).
@@
 
-An additional difference between the models and simulations is that in the models we neglect boundary effects and the sample-variance of the depth-distribution between pointings, whereas the simulations were performed with the KiDS-1000 footprint.
-In App.~\ref{sec:expand_eoftheta} we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
-With this model we can estimate the impact of a correlated distribution of depth, the sample variance of the depth-distribution and boundary effects.
+An additional difference between the models and simulations is, that in the models we neglect boundary effects and the sample-variance of the depth-distribution between pointings, whereas the simulations were performed with the KiDS-1000 footprint.
+In App.~\ref{sec:expand_eoftheta}, we develop a model to extract the correction $\xi_\pm^{ij}/\xi_{\pm}^{ij,\rm{obs}}$ for a specific survey footprint.
+With this model, we can estimate the impact of a correlated distribution of depth, the sample variance of the depth-distribution and boundary effects.
 We find that for a square footprint of $450\,\rm{deg}^2$ or $1000\,\rm{deg}^2$ with an uncorrelated depth-distribution, finite field effects are negligible.
@@
 
-As the next step we want to assess how the observational depth variations propagate to cosmological parameters inferred from $\xi_\pm^{ij,\rm{obs}}$ compared to $\xi_\pm^{ij}$.
-For this test we choose a fiducial cosmology, $\b \Phi$, and determine the relative change in $\Omega_{\rm m}$ and $\sigma_8$ compared to a reference setup with uniform depth.
+As the next step, we assess how the observational depth variations propagate to cosmological parameters inferred from $\xi_\pm^{ij,\rm{obs}}$ compared to $\xi_\pm^{ij}$.
+For this test, we choose a fiducial cosmology, $\b \Phi$, and determine the relative change in $\Omega_{\rm m}$ and $\sigma_8$ compared to a reference setup with uniform depth.
 All other cosmological parameters are kept fixed.
@@
 To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30 to model a KiDS-$15\,000$-like survey, which approximately accounts for the increased survey area of LSST and Euclid with respect to KiDS-450.
-Here, the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$.
+Here the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$.
 As our modified covariance-matrix does not account for the factor of $\sim \!
-4$ expected increase in galaxy number density for LSST and Euclid, we note that this likely to be a lower estimate for the significance of the effect.
- Even though Euclid is a space-based mission, and therefore will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.
-Placing a selection criteria on redshift estimation success will therefore lead to depth variations in the source galaxy sample.
+4$ expected increase in galaxy number density for LSST and Euclid, we note that this is likely to be a lower estimate for the significance of the effect.
+ Even though Euclid is a space-based mission and, therefore, will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.
+Placing a selection criteria on redshift estimation success, will therefore lead to depth variations in the source galaxy sample.
 While the data from LSST will be practically free of variations in depth after 10 years of observations, the first few years data will include significant depth variation.
@@
 
-Calculating the correction $\xi_\pm^{ij}/\xi_\pm^{ij,\rm{obs}}$ for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$ reveals a nontrivial dependence on the cosmology, which can be seen in Figure \ref{fig:comparecosmo}.
+Calculating the correction $\xi_\pm^{ij}/\xi_\pm^{ij,\rm{obs}}$ for varying values of $\Omega_{\rm{m}}$ and $\sigma_8$, reveals a nontrivial dependence on the cosmology, which can be seen in Fig.~\ref{fig:comparecosmo}.
 For various combinations of $\Omega_{\rm{m}}$ and $\sigma_8$ within the $95\%$ confidence limit of KV450, we report a variation in $\xi_\pm/\xi_\pm^{\rm{obs}}$ of a few percentage points on small scales.
@@
 Direct E- and B-mode decomposition for cosmic shear surveys can be provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs,][hereafter S10]{2010A&A...520A.116S}, as they can easily be applied to real data.
-Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
+We note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
 To estimate the B-modes created by this effect, we extract the COSEBIs
@@
  from the correlation functions, $\xi_\pm^{\rm{obs}}$, that have been modified under the semi-analytic model, and from a reference set of correlation functions $\xi_\pm$.
-To be most sensitive to the effect of varying depth, we chose logarithmic COSEBIs with an angular range of $\theta_{\rm{min}}=0.\!'5$ to $\theta_{\rm{max}}=72'$.
+To be most sensitive to the effect of varying depth, we choose logarithmic COSEBIs with an angular range of $\theta_{\rm{min}}=0.\!'5$ to $\theta_{\rm{max}}=72'$.
 As the B-modes of the reference correlation functions are zero, they are a good test for numerical errors in the calculations.
 Motivated by the discussion in \citet{2017MNRAS.464.1676A}, we calculated the COSEBIs from correlation functions binned in $400\,000$ linear bins, which yielded neglible numerical errors.
-We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}.
+We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Fig.~\ref{fig:bmodes_cosebi}.
 However, we compare the B-Modes to the ones measured by \citet{asgari/etal:2019} in KV450, which were consistent with zero.
 Since the B-modes created by varying depth are smaller than these by a factor of 50, we conclude that this effect cannot create measurable B-modes in the KV450 survey.
-It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield a significant detection of B-modes.
+It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to varying depth will also yield a significant detection of B-modes.
 Additionally, the created pattern is very characteristic, which makes it easy to recognize in a B-mode analysis of an actual survey \citep[see][]{2018arXiv181002353A}.
@@
 \label{sec:discussion}
-With our semi-analytic model we describe the impact of varying depth in ground-based cosmic shear surveys. During our analysis we have made several simplifications, which we discuss below.
-\begin{enumerate}
-\item In the most general terms, we are analysing the effects of a position-dependent selection function on cosmic shear surveys.
+With our semi-analytic model we describe the impact of varying depth in ground-based cosmic shear surveys. During our analysis we made several simplifications, which we discuss below.
+
+In the most general terms, we analyze the effects of a position-dependent selection function on cosmic shear surveys.
 In our analysis, this selection function was governed by the KiDS $r$-band depth of a pointing.
@@
 
-\item We have assumed an uncorrelated distribution of the depth-function and neglected boundary effects as well as the sample variance of the depth-distribution between pointings.
+We assumed an uncorrelated distribution of the depth-function and neglected boundary effects as well as the sample variance of the depth-distribution between pointings.
 While the boundary effects arising from a finite survey footprint have a small impact on the shape of the function $E(\theta)$\footnote{This would be due to the fact that a pointing next to a boundary has fewer neighbours, therefore making it more likely that a galaxy pair is in the same pointing.}, the governing factor is the sample variance of the depth-distribution.
-We have assumed that the probability for any pointing to be in quantile $n$ is exactly the expectation value, namely $1/10$.
+We assumed that the probability for any pointing to be in quantile $n$ is exactly the expectation value, namely $1/10$.
 While this would be true for an infinitely large survey with an uncorrelated distribution of the depth-function, it does not necessarily hold for a real survey.
 However, our analysis in App.~\ref{sec:expand_eoftheta} suggests that these effects are not significant for the KV450 survey.
-In the models, we have also assumed an uncorrelated distribution of the depth-function.
+In the models, we also assumed an uncorrelated distribution of the depth-function.
 As can be seen in Fig \ref{fig:all_xis}, this approximation introduces a small error when compared to the simulations.
 
-\item In our MCMC runs we did not account for degeneracies with other cosmological parameters or observational effects.
-Especially intrinsic alignments and baryon feedback also modify the correlation functions primarily on small scales, so they are likely to be degenerate with the effect of varying depth \citep{Troxel:2015}.
+In our MCMC runs, we did not account for degeneracies with other cosmological parameters or observational effects.
+In particular, intrinsic alignments and baryon feedback also modify the correlation functions primarily on small scales, so they are likely to be degenerate with the effect of varying depth \citep{Troxel:2015}.
 In an MCMC run that includes these nuisance parameters, we suspect that the parameters for intrinsic alignments and baryon feedback change to mitigate this effect, so that the impact on cosmological parameters will be smaller than in our results.
@@
 This gives rise to the assumption that the results of an MCMC with the full parameter space, including observational effects, will differ from our results.
-\end{enumerate}
 
 Despite these repercussions, we are confident to say that the effects of varying depth are not significant for the KV450 survey.
-In particular this means that a varying depth cannot explain the tension between observations of the low-redshift Universe and results from analysis of the CMB.
+In particular, this means that a varying depth cannot explain the tension between observations of the low-redshift Universe and results from analysis of the CMB.
 
-For next-generation surveys like Euclid and LSST we have demonstrated that if variable depth is unaccounted for in the analysis, the resulting bias is likely to be significant.
+For next-generation surveys like Euclid and LSST, we have demonstrated that if variable depth is unaccounted for in the analysis, the resulting bias is likely to be significant.
 A detailed LSST and Euclid study that uses a realistic variation of depth should therefore be conducted.
@@
 
-{\bf Although the analytic model (Eq.~\ref{eq:xipm_analytic}) does not fully describe the effect, it can be used as a valid approximation to estimate the importance of varying depth for an arbitrary survey: As can be seen in Fig.~\ref{fig:nz_of_meanz}, in the KiDS-survey the characteristic changes both in redshift and number density for the third redshift bin are about $0.1$.
+Although the analytic model (Eq.~\ref{eq:xipm_analytic}) does not fully describe the effect, it can be used as a valid approximation to estimate the importance of varying depth for an arbitrary survey: As can be seen in Fig.~\ref{fig:nz_of_meanz}, in the KiDS-survey the characteristic changes both in redshift and number density for the third redshift bin are about $0.1$.
 Setting $\la n^in^j\ra=\la w^iw^j\ra=\la n^iw^j\ra = 0.01$ yields $\xi^{ij}_\pm/\xi_\pm^{ij,\rm{obs}}(0)\approx 0.97$, which roughly agrees with the actual results (see Fig.~\ref{fig:all_xis}).
 For a survey with only half the variation in depth, one gets $\xi^{ij}_\pm/\xi_\pm^{ij,\rm{obs}}(0)\approx 0.993$.
-This method allows us to estimate a threshold for an acceptable variation of depth, given a required precision for the shear correlation functions.}
+This method allows us to estimate a threshold for an acceptable variation of depth, given a required precision for the shear correlation functions.
 
@@
 The variations in depth will also affect the covariance of a survey, both because they modify the signal and because they introduce an additional term of sample variance in terms of the distribution of depth.
-This effect will be investigated in a forthcoming publication (Joachimi, Lin, et al.
-in prep.).
+This effect will be investigated in a forthcoming publication (Joachimi, Lin, et al., in prep.).
 
@@
 \begin{acknowledgements}
-{\bf We thank the anonymous referee for very constructive and helpful comments.}
+We thank the anonymous referee for very constructive and helpful comments.
 The results in this paper are based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 177.A-3016, 177.A-3017, 177.A-3018 and 179.A-2004, and on data products produced by the KiDS consortium.
@@
 \subsection{Calculation of the power spectrum}
-Here we will perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$.
+Here we perform the calculation for the observed power spectrum $P^{\text{obs}}(\b \ell)$.
 For this, we assume an infinitely large field in order to perform our integration over $\mathbb{R}^2$.
@@
 \end{align}
-It is important to keep in mind that the ensemble averages of the weight function are independent of the ensemble averages of the shear values, meaning $\la W(\b \theta)\gamma(\b \theta)\ra = \la W(\b \theta)\ra \la \gamma(\b \theta)\ra$.
+It is important to keep in mind, that the ensemble averages of the weight function are independent of the ensemble averages of the shear values, meaning $\la W(\b \theta)\gamma(\b \theta)\ra = \la W(\b \theta)\ra \la \gamma(\b \theta)\ra$.
 We can define $W(\b \theta)=1+w(\b\theta)$ with $\la w(\b \theta)\ra = 0$, which leads to the expession
@@
 which is a convolution of the power spectrum and the 2-dimensional sinc function \eqref{eq:sinc}.
-Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail.
+We note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail.
 In particular, $\langle \gamma(\b \theta)\gamma^*(\b \theta')\rangle$ does not only depend on the separation vector $\b \theta'-\b \theta$, but also on the position $\b \theta$.
@@
 }
-When computing the shear correlation between a pair of galaxies, it is of central importance whether those two galaxies lie in the same pointing or not.
-We want to model the probability that a pair of galaxies with separation $\b\theta$ lie in the same pointing by the function $E(\b\theta)$, which we will derive here:
+When computing the shear correlation between a pair of galaxies, it is of central importance whether or not those two galaxies lie in the same pointing.
+We want to model the probability that a pair of galaxies with separation $\b\theta$ lies in the same pointing by the function $E(\b\theta)$, which we will derive here:
 Given one square field of length $L$ (in our case $L=60\arcmin$) and a separation vector $\b\theta = (\theta_1,\theta_2)$, without loss of generality we can assume $\theta_1,\theta_2\geq 0$.
@@
 \label{sec:calc of xipm}
-Given a set of galaxies we calculate the shear correlation function $\xi_+^{ij}$ via \begin{equation}
+Given a set of galaxies, we calculate the shear correlation function $\xi_+^{ij}$ via \begin{equation}
 \xi^{ij}_+(\theta) = \frac{\sum_{a,b}w_a^iw_b^j\epsilon_a^i\epsilon_b^{j*}\Delta(|\b\theta_a^i-\b\theta_b^i|)}{\sum_{a,b}w_a^iw_b^j\Delta(|\b\theta_a^i-\b\theta_b^i|)}\, .
@@
  \end{equation}
-Taking the ratio of the two quantities, and setting $N_n^i = A\hat{n}_n^i$ we see that Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} are the same.
+Taking the ratio of the two quantities, and setting $N_n^i = A\hat{n}_n^i$, we see that Equations \eqref{eq:xip_from_observations} and \eqref{eq:correctionfunction1} are the same.
 \section{Finite field effects}
@@
 \end{figure}
-In this appendix we will outline how to calculate the correction of the correlation functions for a finite survey with a potentially correlated distribution of depth between pointings.
+In this appendix, we outline how to calculate the correction of the correlation functions for a finite survey with a potentially correlated distribution of depth between pointings.
 Essentially, this boils down to the calculation of $\mathcal{P}_{mn}^{ij}(\theta)$ from Eq.~\eqref{eq:def_xiobs}.
@@
 \end{equation}
- At first we define functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$.
+ At first, we define functions $E_{ab}(\b\theta)$ as the probabilty that a galaxy pair of separation $\b\theta$ is in pointings of distance $(a,b)$.
 This situation is depicted in Fig.~\ref{fig:expand_etheta}.
 Due to symmetry, for the azimuthal average of the functions, $E_{ab}(\theta) = E_{-ab}(\theta) = E_{ba}(\theta)$ holds for all combinations of $a$ and $b$.
-Note that $E_{00}(\theta)=E(\theta)$ and $\sum_{a,b}E_{ab}(\theta)\equiv 1$.
+We note that $E_{00}(\theta)=E(\theta)$ and $\sum_{a,b}E_{ab}(\theta)\equiv 1$.
 
@@
 \input{images/drawing.pdf_tex}
-\caption[Visualisation of the numerical computation for $E_{01}(\theta)$.]{Visualisation of the numerical computation for $E_{01}(\theta)$.
+\caption{Visualization of the numerical computation for $E_{01}(\theta)$.
 For a circle of radius $\theta$, the length of the red arc divided by $2\pi$ represents the fraction of galaxies within the respective pointing.

### 2019-12-16 Heydenreich_et_al.tex
removed comments

@@
 
-% \documentclass[referee]{aa}
 \pdfoutput=1
@@
 \usepackage[hidelinks]{hyperref}
-% \usepackage[section]{placeins}
 
@@
 
-%\newcommand{\todo}{\emph}
-
 \usepackage{bm}
@@
 \usepackage[section]{placeins}
-% \usepackage{subcaption}
-%\usepackage{hyperref}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage[options]{hyperref}
-% To add links in your PDF file, use the package "hyperref"
-% with options according to your LaTeX or PDFLaTeX drivers.
-%
 \usepackage{todonotes}
@@
 
-%   \subtitle{}
-
-   \author{Sven Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
+   \author{Sven Heydenreich\inst{1}
           \and Peter Schneider\inst{1} 
@@
 Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, The Netherlands
-% \and
-% Service d'Astrophysique, CEA Saclay, Orme des Merisiers, B\^at 709, 91191 Gif-sur-Yvette, France
-% \and 
-% Fenglin Veteran Hospital, 2 Zhongzheng Rd. Sec. 1, Fenglin Township, Hualien 97544, Taiwan
 \\ \email{sven@astro.uni-bonn.de, peter@astro.uni-bonn.de}
@@
 
-%It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from the CMB analysis by \citet{2018arXiv180706209P}.
-While their analysis determined a value of $S_8 = 0.830 \pm 0.013$, \citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from an analysis of the Subaru Hyper Suprime-Cam survey, \citet[][hereafter H18]{2018arXiv181206076H} obtained $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data, and the Dark Energy Survey \citep[DES,][]{2018PhRvD..98d3528T} arrived at $S_8=0.782\pm 0.027$.
-Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from their analysis of CFHTLens data.
-Reweighting the obtained redshifts of data from DES and combining this with KiDS data \citep[][Asgari et al.~in prep.]{Joudaki:2019}, yields even higher tension with the value determined for $S_8$ by the Planck Collaboration.
-This discrepancy has received a lot of attention.
-It could be interpreted as a statistical coincidence, a sign of new physics like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P}; or as the manifestation of a systematic effect, either in the cosmic shear surveys or in the Planck mission \citep{2016ApJ...818..132A}, that is not yet accounted for.
-
 For current cosmic shear surveys, the estimated systematic error is becoming comparable in magnitude to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary.
@@
 
-%The depth of a pointing primarily influences the number density as well as the average redshift of galaxies, meaning that a variation in depth is responsible for a correlation between those two quantities (see Fig.
-\ref{fig:nz_of_meanz}).
-%
-
 In Sect.
@@
 In the appendices, we present the full derivation of our model for finite field surveys.
-%App.~A is reserved for detailed calculations that cannot be done in the main paper, in App.~B we introduce way to apply our model to a given survey footprint.
-App.~C is reserved for figures and tables that cannot be displayed in the main body.
 We assume the standard weak gravitational lensing formalism, a summary of which can be found in \citet{2001PhR...340..291B}.
@@
 In our first model, we describe the impact of varying depth on the power spectrum, following the simplifications described above.
-% Following \citet{1993ApJ...404..441K}, we can simulate the shear $\gamma$ from the convergence by convolution with the kernel \begin{equation}
-%\mathcal{D}(\bm{\theta}) = \frac{\theta_2^2-\theta_1^2-2i\theta_1\theta_2}{\pi |\bm{\theta}|^4}\, .
-%\end{equation}
-%
-%Similarly, an observer that measures the shear $\gamma$ can reconstruct the convergence $\kappa$ by convolution with the kernel $\mathcal{D}^*$, where ${}^*$ denotes the complex conjugate.
-Assuming that the optical depth, and thus the source redshift populations, vary between pointing, an observer will measure a shear-signal that is modified by a depth-function $W(\bm{\theta}) = 1-w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds.
-The reconstruction of the observed convergence $\kappa^{\rm obs}$ will thus not yield the original convergence.
-In particular there is no reason why the convolution with a complex kernel should have a nonzero imaginary part.
-This allows us to separate our received signal into E- and B-modes following \begin{equation}
-% \kappa = \kappa^E+i\kappa^B\, ,
-%\end{equation}
-%where $B$-Modes cannot be generated by a lensing signal and are thus a tracer of remaining systematics.
-%2002A&A...389..729S SRC
-%
 In accordance with the definition of the shear power spectrum \begin{equation}
@@
 We note that there is still a correlation between $N$ and $W$ for the same galaxy.
-%For the calculation of the reference correlation functions $\xi_\pm^{ij}(\theta)$ we distribute the \textit{same} galaxies into our survey, only this time we will not order their weightings $W$ or their number densities $N$ by pointing.
-We can imagine this by cutting the footprint into infinitesimal elements $\d^2\b\theta$, and redistributing those at random.
-When we calculate the correlation function of this survey, we note that $\la n^i(\bth)\ra \la n^j(\bthp)\ra = 0$ holds for $\b\theta\neq \b 0$, as the two corresponding infinitesimal elements have uncorrelated weighting and number density.
-This is equivalent to setting $E(\theta)\equiv 0$.
  Performing the same calculations as above, this yields a relation between the correlation function of uniform depth, $\xi_\pm^{ij,\rm{uni}}$, and the one that is usually modeled, $\xi_\pm^{ij}$:
@@
 \end{figure}
-% Asserting an arbitrary cosmological model, we can transform the source redshift distributions $p^i_m(z)$ into comoving distance probability distributions $\mathcal{L}^i_m(\chi)$.
 
@@
 We therefore obtain \begin{equation}
-% \mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
-% \label{eq:pmnij_corr2}
-% \end{equation}
-% We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \begin{equation}
 \mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
@@
 It is noticeable that in the simulations, the value $\xi_\pm/\xi_\pm^{\rm{obs}}$ consistently stays below unity at large scales, which can be attributed to the fact that the depth of different pointings is not completely uncorrelated, as was assumed in the models.
-%Furthermore, we notice some strong features in the simulations at lower values of $\theta$, which arise due to the resolution limit of the simulations.
-%As the noise of the simulated correlation functions increases for decreasing $\theta$,\footnote{The logarithmic bins for the correlation functions were chosen in H17 such that the signal-to-noise ratio is roughly equal for each bin.
-However, in the simulations we ignore shape-noise, such that our only noise contribution is sample variance, which increases at lower $\theta$.} and we take the ratio of two functions that are subject to noise, these features can be attributed to sample variance.
-%In general, the semi-analytic model seems to over-estimate the effect compared to the simulations, which take the full distribution of depth into account.
-This slight discrepancy could be attributed to the fact that the simulations follow a finer magnitude-binning for the number densities of galaxies.
-Due to the fact that the discrepancies arise predominantly on small scales, the most likely reason for the discrepancy is that the simulations take the full variations in depth into account, which include scales smaller than one pointing (especially chip positions and dithering strategies).
-While it is impossible to include the entire sub-pointing variations in depth into our models, we tested a sub-division of one pointing into four smaller ones, all of which have a similar depth; this lowered the tension between models and simulation.
-Furthermore, we tested a coarser magnitude-binning in our models, which increased the tension.
-These tests suggest that both small-scale effects and a finer magnitude binning at least partly negate the varying depth between pointings.
-Note that the seemingly better agreement between mocks and the analytic method is purely coincidental.
 
@@
 \begin{figure*}
-% \begin{subfigure}{0.45\textwidth}
 $
@@
 \includegraphics[width=0.45\textwidth]{images/mcmc_kids.pdf}&
-% \end{subfigure}
-% \begin{subfigure}{0.45\textwidth}
 \includegraphics[width=0.45\textwidth]{images/mcmc_euclid.pdf}
-% \end{subfigure}
 \end{array}$
@@
 We note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.
-To estimate the B-modes created by this effect, we extract the COSEBIs
-%, once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then 
- from the correlation functions, $\xi_\pm^{\rm{obs}}$, that have been modified under the semi-analytic model, and from a reference set of correlation functions $\xi_\pm$.
+To estimate the B-modes created by this effect, we extract the COSEBIs from the correlation functions, $\xi_\pm^{\rm{obs}}$, that have been modified under the semi-analytic model, and from a reference set of correlation functions $\xi_\pm$.
 To be most sensitive to the effect of varying depth, we choose logarithmic COSEBIs with an angular range of $\theta_{\rm{min}}=0.\!'5$ to $\theta_{\rm{max}}=72'$.
@@
 In an MCMC run that includes these nuisance parameters, we suspect that the parameters for intrinsic alignments and baryon feedback change to mitigate this effect, so that the impact on cosmological parameters will be smaller than in our results.
-%Furthermore, when including the effects of dark energy we notice that our observation of $S_8$ being constant is no longer valid: For a `Euclid-like' survey we notice a bias of $\sim 0.8\sigma$.
-This gives rise to the assumption that the results of an MCMC with the full parameter space, including observational effects, will differ from our results.
 
@@
 
-%As an outlook it would be interesting to perform a full MCMC simulation, including both cosmological and nuisance parameters.
-One might also check the most popular extensions to the standard model of cosmology, and see whether varying depth could cause a bias towards one of these models.
-Furthermore, the method developed in Appendix \ref{sec:expand_eoftheta} could be applied to the actual footprint of the KV450 survey to see whether finite field effects or a correlated distribution of $r$-band depth are significant.
 Additionally, it is interesting to note that $E(\theta)$ is the azimuthal average of the function $E(\b\theta)$ derived in Sect.~\ref{sec:model_e}, which is not isotropic.
@@
 \begin{array}{cc}
-% \begin{subfigure}[c]{6cm}
 \def\svgwidth{100pt}
@@
 \input{images/e_1.pdf_tex}&
-% \end{subfigure}
-% \begin{subfigure}[c]{6cm}
 \def\svgwidth{100pt}
@@
 \input{images/e_2.pdf_tex}
-% \end{subfigure}
 \end{array}$
